### 2015-01-09 papers/B1555_EdgeOn/B1555_letter.tex
add Latex files and delete sth

1\documentclass[manuscript]{emulateapj}

\shorttitle{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
\shortauthors{TBD}

\begin{document}

\title{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
\author{TBD}

\begin{abstract}
With the latest infrared image of B1555+375, an edge-on disk is shown to over cross the strong lensed images. Indicating the flux ratio anomalie of B1555+375 is dominanted by its edge-on disk structure. We present a lens model with SIE bulge and exponential disk, base on the radio observation from \citet{Marlow}. And apply this model to SHARP infrared image.

\end{abstract}

\keywords{ gravitaional lensing}

\section{Introduction}
Flux ratio anomaly in gravitational lensed systems has been seen as a promising method to probe substructures within halos.
Base on the concordant cold dark matter cosmology, simulations show more substructures than up-to-date observation searches.
This ``missing satellite'' problem arose interesting discrepancy between theoretical and observational understanding on structure
formation. \\
One possible explanation to this discrepancy is the difficulties of searching low-mass satellites(typical mass range?). Recent research shows using gravitational lensing effects from substructures can lower the detectable mass limit (mass range). More satellite galaxy candidates would be discovered from flux ratio anomaly in strong lensed galaxy systems, which may give us new insights to structures within dark matter halo. \\
On the other hand, simulations haven't reach a concise conclusion on the cause of flux ratio anomaly. Substructures may not be the only reason for flux ratio anomalies in merging double or triple images. Dust extinction, micro lensing from stars, and structures belongs to lens galaxy can also contribute to flux ratio anomaly. These factors would affect the estimation of substructure mass and even give false signal when searching possible satellite candidates.\\
In the latest SHARP observation, we aimed on several strong lensed systems with flux ratio anomaly discovered. Clear edge-on disk is found in the infrared images of (systems). To probe the causes of flux ratio anomaly, we model one system, B1555+375, with a center bulge and an edge-on disk. (B1555 radio observation details in intro?) In this paper, we present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

\section{Data Collection \& Reduction}

\section{Lens Modeling}
There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models. We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}. Morlow et al. first published the flux ratio anomaly detection and lens model of B1555+375. However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band image (Fig. 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree. With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk. The position of lens galaxy is at $(-0.1620, -0.2401)$. Model best-fit parameters are stated as following. 
SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degree$. 
Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degree, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.

The comparison of radio observation and our modeling result is in Figure 2, Table 1 \& 2.\\

\begin{figure}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
Exponential disk is marled by the green ellipse in residue image. We believe strong dust extinction from the disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

\begin{figure}
\plotone{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2036,-0.1645)$, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

%%table1
\begin{table}
\begin{center}
\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-1}}
\begin{tabular}{lllccc}
\tableline\tableline
					&Radio	&		 & Model-predicted \\
Component &East &North &East 		&North\\ 
\tableline
A ........ &$0$    			&$0$		 			&$-0.0017$ &$+0.0022$   \\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0734$ &$+0.0456$   \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4120$ &$-0.0278$   \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1580$ &$-0.3608$   \\  
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.}
\end{center}
\end{table}

%%table2
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-2}}
\begin{tabular}{lllccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &					&$1.7$  \\ 
A/C 		&$2.0$ &					&$2.2$  \\
A/D			&$13.0$ &					&$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Infrared flux densities are...}
\end{center}
\end{table}

We then use an extended source to model SHARP infrared image. In Figure 1, B and D have no detection in K-band, which believed due to strong dust extinction from the edge-on disk. The region and orientation of exponential disk in lens model are consistent with this hypothesis. The flux ratios in infrared are much higher than in radio also supports as an evidence of dust extinction.

\section{Discussion}
We have seen a similar flux ratio anomaly pattern in our edge-on disk lens model of B1555+375. The model predicted point source images also well matched with radio observation. Our modeling result indicates structures of lens galaxy itself can dominant flux ratio anomalies on lensing images. 
Our follow up will be explore more similar SHARP systems with flux ratio anomaly and a recognizable edge-on disk. As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
We still have great expectation on the substructure searching approach from flux ratio anomaly by using strong lensing systems. At the meanwhile, we would like to draw some attention on other factors can cause flux ratio anomaly. These factors also give a clue of the structure and mass distribution of lens galaxy, which can be important to research required really accurate measurements, like time-delay.  For substructure searching, one should reconsider and rule out the possibility of edge-on disk before doing any further analysis.\\
Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.

\begin{thebibliography}{}
\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
\end{thebibliography}

\end{document}

### 2015-01-09 papers/B1555_EdgeOn/B1555_letter.tex
Fixed small typos

@@
-1\documentclass[manuscript]{emulateapj}
+\documentclass[manuscript]{emulateapj}
 
@@
 Model best-fit parameters are stated as following.
-SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degree$. 
-Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degree, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.
+SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degr$. 
+Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degr, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.
 

### 2015-01-13 papers/B1555_EdgeOn/B1555_letter.tex
figures and numbers updated, not much change in text

@@
 With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk.
-The position of lens galaxy is at $(-0.1620, -0.2401)$.
-Model best-fit parameters are stated as following.
-SIE: $\sigma =853 km/s, e=0.27, \theta = 105.5 \degr$. 
-Exponential disk: $M_{tot}=1.48 \times 10^{10} h^{-1} M_{\odot}, e=0.84, \theta=7.4 \degr, r_e = 0.20'' $, where $e$ is ellipticity and $\theta$ is the position angle measured east of north.
+The full best-fit parameters are shown in Table 1.
 
-The comparison of radio observation and our modeling result is in Figure 2, Table 1 \& 2.\\
+The comparison of radio observation and our modeling result is in Figure 2, Table 2 \& 3.\\
 
 \begin{figure}
+\plotone{B1555_Kp.eps}
+\plottwo{B1555_model.eps}{B1555_residue.eps}
 \caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
-Exponential disk is marled by the green ellipse in residue image.
-We believe strong dust extinction from the disk makes B and D no detection in infrared.
+Exponential disk is marked by the green ellipse in residue image.
+We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared.
 Thus leaving two negative holes in our residue.\label{fig1}}
@@
 \caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2036,-0.1645)$, marked by a black filled circle.
+The position of the source is at $(-0.2066,-0.1634)$, marked by a black filled circle.
 From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
@@
 \begin{center}
-\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-1}}
-\begin{tabular}{lllccc}
+\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
+\begin{tabular}{lcccccc}
+%%\tableline\tableline
+Model &		&		 &  \\
+\tableline\tableline
+SIE 	& $x$		& $y$ 		& $\sigma (km/s)$ 	& $e$	& $\theta$  \\  
+		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
+\tableline
+Expdisk	& $x$		& $y$		& $M_{tot} (h^{-1}M_{\odot})$	& $e$	& $\theta$	& $r_e$ \\
+		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.4 \degr$& $0.20 ''$  \\
+
+\tableline
+\end{tabular}
+%% Any table notes must follow the \end{tabular} command.
+\tablecomments{Positions are offsets measured from component A in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
+\end{center}
+\end{table}
+
+%%table2
+\begin{table}
+\begin{center}
+\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-2}}
+\begin{tabular}{lccccc}
 \tableline\tableline
@@
 \tableline
-A ........ &$0$    			&$0$		 			&$-0.0017$ &$+0.0022$   \\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0734$ &$+0.0456$   \\  
-C ........ &$-0.4117$  &$-0.0280$	&$-0.4120$ &$-0.0278$   \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1580$ &$-0.3608$   \\  
+A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
+B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
+C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
 \tableline
@@
 
-%%table2
+%%table3
 \begin{table}
 \begin{center}
-\caption{Flux Ratios of B1555+375 Components.\label{tbl-2}}
+\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
 \begin{tabular}{lllccc}
@@
 \tableline
-A/B			&$1.8$ &					&$1.7$  \\ 
-A/C 		&$2.0$ &					&$2.2$  \\
-A/D			&$13.0$ &					&$8.0$  \\
+A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
+A/C 		&$2.0$ &$1.0$ &$2.2$  \\
+A/D			&$13.0$ &$5.4$ &$8.0$  \\
 \tableline
@@
 %% Any table notes must follow the \end{tabular} command.
-\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Infrared flux densities are...}
+\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}.
+Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
 \end{center}
@@
 
-\begin{thebibliography}{}
-\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
-\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
-\end{thebibliography}
+\bibliographystyle{apj}
+\bibliography{reference.bib}
+
+%\begin{thebibliography}{}
+%\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
+%\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
+%\end{thebibliography}
 

### 2015-01-13 papers/B1555_EdgeOn/B1555_letter.tex
update point_source figure
large change in Intro, small change in Modeling. New references not updated yet

@@
 \section{Introduction}
-Flux ratio anomaly in gravitational lensed systems has been seen as a promising method to probe substructures within halos.
-Base on the concordant cold dark matter cosmology, simulations show more substructures than up-to-date observation searches.
-This ``missing satellite'' problem arose interesting discrepancy between theoretical and observational understanding on structure
-formation. \\
-One possible explanation to this discrepancy is the difficulties of searching low-mass satellites(typical mass range?).
-Recent research shows using gravitational lensing effects from substructures can lower the detectable mass limit (mass range).
-More satellite galaxy candidates would be discovered from flux ratio anomaly in strong lensed galaxy systems, which may give us new insights to structures within dark matter halo.
+To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly.
+However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way.
+This discrepency arises the famous ``missing satellite'' problem.
+Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group.
+Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way.
+Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies.
+These factors make gravitational effects be powerful and promising tools in the substructure searching.\\
+Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
+These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness due to perturbations in gravitational potential.
+Little perturbation from substructures (mass range?) is sufficent to bring flux ratio anomalies in strong lensed systems.
+In the observational view, radio observation is the best way to probe these flux ratio anomalous systems because it doesn't have severe extinction issue like in optical or infrared band.
+Also, most radio lensed images are point sources which are easier to model.
 \\
-On the other hand, simulations haven't reach a concise conclusion on the cause of flux ratio anomaly.
-Substructures may not be the only reason for flux ratio anomalies in merging double or triple images.
-Dust extinction, micro lensing from stars, and structures belongs to lens galaxy can also contribute to flux ratio anomaly.
-These factors would affect the estimation of substructure mass and even give false signal when searching possible satellite candidates.\\
-In the latest SHARP observation, we aimed on several strong lensed systems with flux ratio anomaly discovered.
-Clear edge-on disk is found in the infrared images of (systems).
-To probe the causes of flux ratio anomaly, we model one system, B1555+375, with a center bulge and an edge-on disk.
-(B1555 radio observation details in intro?) In this paper, we present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.
+On the other hand, results from numerical simulation haven't reach a concise conclusion on the cause of flux ratio anomaly.
+There are other possiblities can give rise to flux ratio anomaly.
+Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects.
+Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates.
+Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself.
+Thus, infrared image with high spatial resolution is essential in our study.\\
+The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lesing systems.
+We obtain high-resoltion images from Keck adaptive optics(AO) Hubble Space Telescope(HST) observations.
+In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses.
+We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly.
+We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.
 
@@
 \section{Lens Modeling}
-There are several public lens modeling codes allow researchers to model strong lensed systems with most common mass models.
-We use glafic \citep{Oguri} to explore B1555 with known position and flux data from the radio observation done by \citet{Marlow}.
+To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}.
 Morlow et al.
@@
 The full best-fit parameters are shown in Table 1.
+We also try on another model with two SIE mass profiles.
+This model will be used in the following up study with Simona...
 
@@
 %% Any table notes must follow the \end{tabular} command.
-\tablecomments{Positions are offsets measured from component A in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
+\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
 \end{center}

### 2015-01-14 papers/B1555_EdgeOn/B1555_letter.tex
new references and few type correction

@@
 However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way.
-This discrepency arises the famous ``missing satellite'' problem.
+This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999}.
 Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group.
@@
 \\
-On the other hand, results from numerical simulation haven't reach a concise conclusion on the cause of flux ratio anomaly.
+On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly.
 There are other possiblities can give rise to flux ratio anomaly.
@@
 Thus, infrared image with high spatial resolution is essential in our study.\\
-The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lesing systems.
-We obtain high-resoltion images from Keck adaptive optics(AO) Hubble Space Telescope(HST) observations.
+The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}.
+We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations.
 In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses.

### 2015-01-15 papers/B1555_EdgeOn/B1555_letter.tex
add best-fit parameters of 2-SIE model

@@
 1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree.
-With this information, we model B1555+375 with SIE for bulge and exponential disk model for edge-on disk.
+With this information, we model B1555+375 with two models.
+The first model consists of an SIE bulge and an exponential edge-on disk(SIE+Expdisk).
+The second model consists of two SIE mass profiles, for bulge and disk respectively.
 The full best-fit parameters are shown in Table 1.
-We also try on another model with two SIE mass profiles.
-This model will be used in the following up study with Simona...
-
-The comparison of radio observation and our modeling result is in Figure 2, Table 2 \& 3.\\
+Both of these models predict fairly matched results with the radio observation.
+The comparison of observation and SIE+Expdisk result is in Figure 2, Table 2 \& 3.\\
 
@@
 \caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2066,-0.1634)$, marked by a black filled circle.
+The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
 From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
@@
 %%\tableline\tableline
-Model &		&		 &  \\
+SIE&		&		 &  \\
++Expdisk\\
 \tableline\tableline
-SIE 	& $x$		& $y$ 		& $\sigma (km/s)$ 	& $e$	& $\theta$  \\  
+SIE& $x$		& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\
+	&					&					&  (km/s)			&			&						\\
 		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
 \tableline
-Expdisk	& $x$		& $y$		& $M_{tot} (h^{-1}M_{\odot})$	& $e$	& $\theta$	& $r_e$ \\
-		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.4 \degr$& $0.20 ''$  \\
+Expdisk	& $x$		& $y$		& $M_{tot} $					& $e$	& $\theta$	& $r_e$ \\
+				&				&				& $(h^{-1}M_{\odot})$	&			&						&				\\
+		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.40 \degr$& $0.20 ''$  \\  
+\tableline\tableline
+2-SIE\\
+\tableline
+Bulge& $x$				& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\  
+			&					&					&  (km/s)			&			&						\\
+						&$-0.1809$ 	&$-0.1702$& $81.67$ 					&$0.27$	& $97.71 \degr$   \\
+\tableline
+Disk\\
+						&$-0.1592$ 	&$-0.1833$& $69.91$ 					&$0.83$	& $7.40 \degr$   \\
+\tableline
 
-\tableline
 \end{tabular}

### 2015-01-17 papers/B1555_EdgeOn/B1555_letter.tex
update in references and Intro

@@
 Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
-These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness due to perturbations in gravitational potential.
-Little perturbation from substructures (mass range?) is sufficent to bring flux ratio anomalies in strong lensed systems.
-In the observational view, radio observation is the best way to probe these flux ratio anomalous systems because it doesn't have severe extinction issue like in optical or infrared band.
-Also, most radio lensed images are point sources which are easier to model.
-\\
-On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly.
+These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
+Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems.
+This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.
+In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band.
+However, the number of flux ratio anomalous systems (numbers?) in radio bands is not large enough to provide unbiased statistics.
+Another approach using narrow-line specstroscopy \citep{N14} may be able to find out more flux ratio anomalous strong lensing systems.
+All of these results show the power of lensing effects in substracture studies.\\
+On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}.
 There are other possiblities can give rise to flux ratio anomaly.

### 2015-01-17 papers/B1555_EdgeOn/B1555_letter.tex
add some references

@@
 However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way.
-This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999}.
-Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in Local Group.
-Most satellite galaxies are faint, which are extremely hard to directly detect in the system beyond Milky Way.
-Futhermore, some low-mass dark matter subhaloes are considered to be too small to contain dwarf galaxies.
+This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}.
+Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in local universe.
+Most satellite galaxies are too faint to be directly detected.
+Futhermore, low-mass dark matter subhaloes may contain too less gas to form stats \citep{P11}.
 These factors make gravitational effects be powerful and promising tools in the substructure searching.\\
@@
 In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band.
-However, the number of flux ratio anomalous systems (numbers?) in radio bands is not large enough to provide unbiased statistics.
-Another approach using narrow-line specstroscopy \citep{N14} may be able to find out more flux ratio anomalous strong lensing systems.
-All of these results show the power of lensing effects in substracture studies.\\
+However, only small number of flux ratio anomalous systems in radio are avaliable for analysis.
+Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis.
+All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
 	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}.

### 2015-01-20 papers/B1555_EdgeOn/B1555_letter.tex
A bit of rewriting of the intro to the B1555 paper

@@
 \section{Introduction}
-	To understand substructions and mass distribution within dark matter haloes, observations in Local Group bring the first view of mass profile on small scale by searching satellite galaxies directly.
-However, concordant cold dark matter cosmology predicts more substructures in numerical simulations than in observation results around our Milky Way.
-This discrepency arises the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}.
-Searching more satellite galaxies beyond Local Group is definite one of the keys to solve this discrepency, though, in approaches with huge differences from people used to do in local universe.
-Most satellite galaxies are too faint to be directly detected.
-Futhermore, low-mass dark matter subhaloes may contain too less gas to form stats \citep{P11}.
-These factors make gravitational effects be powerful and promising tools in the substructure searching.\\
+
+A common feature of simulations of structure formation is the presence
+of thousands of subhaloes that are associated with larger mass haloes.
+However, observations of the Local Group find many fewer satellite
+galaxies than are predicted by the simulations, even when taking into
+account completeness corrections arising from the limited sky coverage
+imposed by the Galactic Plane.  This is the famous ``missing
+satellite'' problem \citep{Klypin1999, Moore1999, S07}.  In order to understand
+this discrepancy, it is imperative to build up a large sample of satellites /
+subhalos in galaxies outside the Local Group.  This process is challenging
+due to the faintness of the satellite galaxies.  Furthermore, lower-mass
+satellites may not be able to retain the gas needed for ongoing star
+formation \citep[e.g.,][]{P11}, rendering them effectively dark.
+These
+factors make gravitational effects be powerful and promising tools in
+the substructure searching.
+
 	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
@@
 \section{Lens Modeling}
-To model B1555+375, we use the lens modeling code $glafic$ \citep{Oguri} with known position and flux data from the radio observation done by \citet{Marlow}.
-Morlow et al.
-first published the flux ratio anomaly detection and lens model of B1555+375.
-However, their SIE lens model cannot explain the flux ratio anomaly between image A and B (see Fig.6, Table 2 \& 3 in \citet{Marlow}).
-In K-band image (Fig.
-1, left), a recognizable edge-on disk is lie in the center with position angle $~10$ degree.
-With this information, we model B1555+375 with two models.
-The first model consists of an SIE bulge and an exponential edge-on disk(SIE+Expdisk).
-The second model consists of two SIE mass profiles, for bulge and disk respectively.
-The full best-fit parameters are shown in Table 1.
-Both of these models predict fairly matched results with the radio observation.
-The comparison of observation and SIE+Expdisk result is in Figure 2, Table 2 \& 3.\\
+To model B1555+375, we use the lens modeling code {\tt glafic}
+\citep{Oguri}.  The inputs to the model are the observed image positions
+and flux densities measured by the radio observations of \citet{Marlow}.
+These authors present a singular isothermal ellipsoid (SIE) model that
+provides an excellent fit to the image positions (?? IS THIS TRUE?) but
+does not reproduce the strong flux ratio anomaly between components A and B.
+(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
+image (Fig. 1, left), a recognizable edge-on disk is lie in the center
+with position angle $~10$ degree. With this information, we model
+B1555+375 with two models. The first model consists of an SIE bulge
+and an exponential edge-on disk(SIE+Expdisk). The second model
+consists of two SIE mass profiles, for bulge and disk
+respectively. The full best-fit parameters are shown in Table 1. Both
+of these models predict fairly matched results with the radio
+observation. The comparison of observation and SIE+Expdisk result is
+in Figure 2, Table 2 \& 3.
 

### 2015-01-21 papers/B1555_EdgeOn/B1555_letter.tex
rewrite on Intro and Discussion. Few references added.

@@
 Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis.
-All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
-	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}.
-There are other possiblities can give rise to flux ratio anomaly.
-Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects.
-Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates.
-Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself.
-Thus, infrared image with high spatial resolution is essential in our study.\\
+
+	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems.
+\citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring.
+Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study.
+On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems.
+The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems.
+
 	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}.
 We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations.
-In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses.
-We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly.
-We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.
+To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging.
+We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.
 
@@
 These authors present a singular isothermal ellipsoid (SIE) model that
-provides an excellent fit to the image positions (?? IS THIS TRUE?) but
+provides the first fit to the image positions but
 does not reproduce the strong flux ratio anomaly between components A and B.
@@
 in Figure 2, Table 2 \& 3.
+%These authors present a singular isothermal ellipsoid (SIE) model that
+%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)
 
@@
 \caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
+An edge-on disk can be seen in the center of SHARP K-band image.
 Exponential disk is marked by the green ellipse in residue image.
@@
 \caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
-\begin{tabular}{lllccc}
+\begin{tabular}{lccccc}
 \tableline\tableline
@@
 \section{Discussion}
-We have seen a similar flux ratio anomaly pattern in our edge-on disk lens model of B1555+375.
-The model predicted point source images also well matched with radio observation.
-Our modeling result indicates structures of lens galaxy itself can dominant flux ratio anomalies on lensing images.
-Our follow up will be explore more similar SHARP systems with flux ratio anomaly and a recognizable edge-on disk.
+We present new lens models of B1555+375 with a bulge and an edge-on disk.
+Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B.
+In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly.
+This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging.
+Our result is consistent with the conclusion from  \citet{Xu14}.
+Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.
+
+With our discover in B155+375, we show that the lens galaxy structure can dominate the flux ratio anomalous phenomenon in strong lensing system.
+This leads to a more general reminder.
+Not all of the flux anomalies indicate the existence of substructures.
+One must fully consider non-substructure effects before gathering any statistics or serious analysis.
+Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data and analysis.
+For the flux ratio anomalies caused by real dark matter substructures and dwarf galaxies, non-stucture effects would also influence the estimated mass and other derived properties.
+Thus, we would like to draw some attention on these non-substructure effects.
+Once we understand more about their role in flux anomalous phenomenon, we can be more confident on searching unseen dwarf galaxies and dark matter substructures by searching flux ratio anomalous systems.
+
+Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.
+The radio and narrow band observations are the best approaches to obtain accurate flux ratio data.
+However, optical and infrared imaging can provide more information on the structure of lens galaxy, which is also an important part in analyzing flux anomalous systems since we've shown that an edge-on disk can cause flux ratio anomaly.
+Our follow up will be explore more flux anomalous SHARP systems that we also notice a recognizable edge-on disk in the infrared imaging.
 As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
-We still have great expectation on the substructure searching approach from flux ratio anomaly by using strong lensing systems.
-At the meanwhile, we would like to draw some attention on other factors can cause flux ratio anomaly.
-These factors also give a clue of the structure and mass distribution of lens galaxy, which can be important to research required really accurate measurements, like time-delay.
-For substructure searching, one should reconsider and rule out the possibility of edge-on disk before doing any further analysis.\\
-Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.
 

### 2015-01-24 papers/B1555_EdgeOn/B1555_letter.tex
table format update. Model parameters not updated yet

@@
 \caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
-\begin{tabular}{lcccccc}
+\begin{tabular}{ccccccc}
 %%\tableline\tableline
-SIE&		&		 &  \\
-+Expdisk\\
+		&SIE+Expdisk& 2-SIE		   
+\\
 \tableline\tableline
-SIE& $x$		& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\
-	&					&					&  (km/s)			&			&						\\
-		&$-0.1883$ 	&$-0.1923$	&$93.74$ 			&$0.27$	& $105.5 \degr$   \\
-\tableline
-Expdisk	& $x$		& $y$		& $M_{tot} $					& $e$	& $\theta$	& $r_e$ \\
-				&				&				& $(h^{-1}M_{\odot})$	&			&						&				\\
-		&$-0.1615$  &$-0.2502$	&$1.19\times 10^{10} $ 			&$0.84$ &$7.40 \degr$& $0.20 ''$  \\  
-\tableline\tableline
-2-SIE\\
-\tableline
-Bulge& $x$				& $y$ 		& $\sigma $ 	& $e$	& $\theta$  \\  
-			&					&					&  (km/s)			&			&						\\
-						&$-0.1809$ 	&$-0.1702$& $81.67$ 					&$0.27$	& $97.71 \degr$   \\
-\tableline
-Disk\\
-						&$-0.1592$ 	&$-0.1833$& $69.91$ 					&$0.83$	& $7.40 \degr$   \\
+$x_1$  	& $-0.1883$	& $-0.1809$	  \\
+$y_1$	&$-0.1923$	&$-0.1702$	  \\
+$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
+$y_2$	&$-0.2502$	& $-0.1833$	  \\
+$\sigma_1$	&$93.74$ &	$81.67$	  \\
+$M_{tot} / \sigma_2$& $1.19\times 10^{10} $  &$69.91$ 	 \\  
+$e_1$	& $0.27$	& $0.27$ \\  
+$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
+$e_2$	&$0.84$	&$0.83$      \\
+$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
+$r_e$	& $0.20 ''$ &  -- \\
 \tableline
@@
 %% Any table notes must follow the \end{tabular} command.
-\tablecomments{Positions are offsets from component A measured in unit of arcsec. $e$ is ellipticity and $\theta$ is the position angle measured east of north.}
+\tablecomments{Subscripts 1 and 2 represent bulge and disk components in each model respectively.
+Positions are offsets from radio image component A measured in units of arcsec.
+The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
+$e$ is ellipticity and $\theta$ is the position angle measured east of north.}
 \end{center}

### 2015-01-24 papers/B1555_EdgeOn/B1555_letter.tex
new model parameters update

@@
 B1555+375 with two models. The first model consists of an SIE bulge
-and an exponential edge-on disk(SIE+Expdisk). The second model
-consists of two SIE mass profiles, for bulge and disk
+and an exponential edge-on disk (SIE+Expdisk). The second model
+consists of two SIE mass profiles (2-SIE), for bulge and disk
 respectively. The full best-fit parameters are shown in Table 1. Both
@@
 $y_2$	&$-0.2502$	& $-0.1833$	  \\
-$\sigma_1$	&$93.74$ &	$81.67$	  \\
-$M_{tot} / \sigma_2$& $1.19\times 10^{10} $  &$69.91$ 	 \\  
+$\sigma_1$	&$92.90$ &	$95.05$	  \\
+$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
 $e_1$	& $0.27$	& $0.27$ \\  

### 2015-02-11 papers/B1555_EdgeOn/B1555_letter.tex
rewrite on the beginning of Discussion
still work on it

@@
 consists of two SIE mass profiles (2-SIE), for bulge and disk
-respectively. The full best-fit parameters are shown in Table 1. Both
+respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
 of these models predict fairly matched results with the radio
@@
 \section{Discussion}
+The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
+The discrepency between numerical simulations and observations within local universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
+Lensing shows a promising potential on substructure detection beyond the Local Group.
+The main reason is that gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
+
+Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref).
+Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey.
+Radio data provides reliable positions and fluxes of source for constraint and modeling because it avoids the problem of severe extinction and micro lensing from stars.
+On the other hand, optical or near infrared imaging also gives useful information about the lensing system.
+In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling.
+The lack of knowledge about host galaxy, e.g.
+modeling with radio data alnog, may lead to an inapropreiate lens model.
+
+Searching substructures with flux ratio anomalies 
+we must be certain that perturbation are from substructure rather than other reason
+
+In the SHARP IR imaging, we notice that edge-on disk
+Previously studies assume that smooth potential from host galaxy is not possible to cause flux ratio anomaly.
 We present new lens models of B1555+375 with a bulge and an edge-on disk.

### 2015-02-12 papers/B1555_EdgeOn/B1555_letter.tex
new update to Discussion[complete]

@@
 In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling.
-The lack of knowledge about host galaxy, e.g.
-modeling with radio data alnog, may lead to an inapropreiate lens model.
+The lack of knowledge about lens galaxy, e.g.
+modeling with radio data alnog, may lead to an improper lens model.
 
-Searching substructures with flux ratio anomalies 
-we must be certain that perturbation are from substructure rather than other reason
+The idea of detecting substructures with flux ratio anomalies assumes that lens galaxy has completely smooth gravitational potential.
+Thus the perturbation is considered to be from faint satellite galaxy or ``dark'' subhalo.
+Numerical simulations have examined this approach with unkown systems.
+In \citet{Xu14}, only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos.
+The rest of them are only few percent likely or very unlikely to have their flux anomalies due to substructure, including B1555+375.
+Their results support that even using radio data, there are other possible reasons could cause flux anomalies.
+The answer to this concern may be explained by the high resolution IR imaging.
+In the SHARP K-band imaging of B1555+375, an edge-on disk lies across between the positions of radio merging double A \& B.
 
-In the SHARP IR imaging, we notice that edge-on disk
-Previously studies assume that smooth potential from host galaxy is not possible to cause flux ratio anomaly.
-We present new lens models of B1555+375 with a bulge and an edge-on disk.
+In sec.
+2, we present new lens models of B1555+375 with a bulge and an edge-on disk.
 Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B.
@@
 The radio and narrow band observations are the best approaches to obtain accurate flux ratio data.
-However, optical and infrared imaging can provide more information on the structure of lens galaxy, which is also an important part in analyzing flux anomalous systems since we've shown that an edge-on disk can cause flux ratio anomaly.
-Our follow up will be explore more flux anomalous SHARP systems that we also notice a recognizable edge-on disk in the infrared imaging.
-As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
+However, optical and infrared imaging can provide more information on the structure of lens galaxy.
+With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems.
+In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
+The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
 

### 2015-02-12 papers/B1555_EdgeOn/B1555_letter.tex
fix typo

@@
 
-\shorttitle{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
+\shorttitle{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
 \shortauthors{TBD}
@@
 
-\title{Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375}
+\title{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
 \author{TBD}
@@
 
-\section{Lens Modeling}
-To model B1555+375, we use the lens modeling code {\tt glafic}
+\section{Lens Modelling}
+To model B1555+375, we use the lens modelling code {\tt glafic}
 \citep{Oguri}.  The inputs to the model are the observed image positions
@@
 Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey.
-Radio data provides reliable positions and fluxes of source for constraint and modeling because it avoids the problem of severe extinction and micro lensing from stars.
+Radio data provides reliable positions and fluxes of source for constraint and modelling because it avoids the problem of severe extinction and micro lensing from stars.
 On the other hand, optical or near infrared imaging also gives useful information about the lensing system.
-In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling.
+In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
 The lack of knowledge about lens galaxy, e.g.
-modeling with radio data alnog, may lead to an improper lens model.
+modelling with radio data alnog, may lead to an improper lens model.
 
@@
 Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B.
-In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly.
+In our modelling, substructure is not neccessary to exist to cause the observed flux ratio anomaly.
 This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging.

### 2015-02-28 papers/B1555_EdgeOn/B1555_letter.tex
Added new text from Simona

@@
 \documentclass[manuscript]{emulateapj}
+
+\usepackage{color}
+\definecolor{simonacolor}{cmyk}{0, 0.9808, 0.4429, 0.1412}
+\newcommand{\simona}[1]{\textcolor{simonacolor}{#1}}
 
@@
 satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
-this discrepancy, it is imperative to build up a large sample of satellites /
-subhalos in galaxies outside the Local Group.  This process is challenging
+this discrepancy, it is imperative to build up a large sample of satellites/\simona{subhaloes} in galaxies outside the Local Group.  
+This process is challenging
 due to the faintness of the satellite galaxies.  Furthermore, lower-mass
@@
 formation \citep[e.g.,][]{P11}, rendering them effectively dark.
-These
-factors make gravitational effects be powerful and promising tools in
-the substructure searching.
+These factors make gravitational \simona{lensing a powerful and promising tool for the detection of substructure.}
 
-	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
+\simona{It was first suggested by Mao \& Schneider 1998 that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
+%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
 These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
-Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems.
-This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.
-In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band.
-However, only small number of flux ratio anomalous systems in radio are avaliable for analysis.
-Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis.
+\simona{Indeed,} little perturbation\simona{s} in \simona{the} gravitational potential \simona{are} sufficent to bring flux ratio anomalies in strong lensed systems. 
+\simona{Moreover, unlike in the optical or infrared,} in \simona{the} radio band, lens\simona{ed} images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
+This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
+\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}.
+While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by Koopmans 2005 and \citet{V09}.
+Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations (Vegetti et al.
+2014).}
 
-	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems.
+\simona{While} future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies.
+In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex host galaxy mass distribution than initially considered.
+To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP).
+The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12} (Vegetti et al.
+2012).
+\simona{In particular,} to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging.
+\simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
+%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable.
+Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}.
+%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems.
 \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring.
@@
 The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems.
-
-	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}.
+%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}.
 We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations.
-To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging.
+%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging.
 We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.
@@
 
-\begin{figure}
-\plotone{B1555_Kp.eps}
-\plottwo{B1555_model.eps}{B1555_residue.eps}
-\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
-An edge-on disk can be seen in the center of SHARP K-band image.
+%\begin{figure}
+%\plotone{B1555_Kp.eps}
+%\plottwo{B1555_model.eps}{B1555_residue.eps}
+%\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
+%An edge-on disk can be seen in the center of SHARP K-band image.
 Exponential disk is marked by the green ellipse in residue image.
@@
 Thus leaving two negative holes in our residue.\label{fig1}}
-\end{figure}
-
-\begin{figure}
-\plotone{point_source.eps}
-\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
+%\end{figure}
+%
+%\begin{figure}
+%\plotone{point_source.eps}
+%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
 The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
 From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
-\end{figure}
+%\end{figure}
 
@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-The discrepency between numerical simulations and observations within local universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
+The discrepency between numerical simulations and observations within \simona{the} \simona{L}ocal \simona{U}niverse gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
 Lensing shows a promising potential on substructure detection beyond the Local Group.
-The main reason is that gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
+The main reason is that \simona{the} gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
 

### 2015-02-28 papers/B1555_EdgeOn/B1555_letter.tex
add new ref mentioned in Simona's new text

@@
 satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
-this discrepancy, it is imperative to build up a large sample of satellites/\simona{subhaloes} in galaxies outside the Local Group.  
+this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.  
 This process is challenging
@@
 
-\simona{It was first suggested by Mao \& Schneider 1998 that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
+\simona{It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
 %Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
 These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
-\simona{Indeed,} little perturbation\simona{s} in \simona{the} gravitational potential \simona{are} sufficent to bring flux ratio anomalies in strong lensed systems. 
-\simona{Moreover, unlike in the optical or infrared,} in \simona{the} radio band, lens\simona{ed} images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
+\simona{Indeed,} little perturbations in the gravitational potential are sufficent to bring flux ratio anomalies in strong lensed systems. 
+\simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
 This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
 \simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}.
-While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by Koopmans 2005 and \citet{V09}.
-Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations (Vegetti et al.
-2014).}
+While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}.
+Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a} (which one?).}
 
-\simona{While} future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies.
+While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies.
 In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex host galaxy mass distribution than initially considered.
 To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP).
-The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12} (Vegetti et al.
-2012).
-\simona{In particular,} to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging.
+The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12,V12} .
+In particular, to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging.
 \simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-The discrepency between numerical simulations and observations within \simona{the} \simona{L}ocal \simona{U}niverse gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
+The discrepency between numerical simulations and observations within the Local Universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
 Lensing shows a promising potential on substructure detection beyond the Local Group.
-The main reason is that \simona{the} gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
+The main reason is that the gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
 

### 2015-03-02 papers/B1555_EdgeOn/B1555_letter.tex
fix type

@@
 While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}.
-Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a} (which one?).}
+Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.}
 

### 2015-03-02 papers/B1555_EdgeOn/B1555_letter.tex
Reorder/rewrite on Discussion[incomplete]

@@
 These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
-\simona{Indeed,} little perturbations in the gravitational potential are sufficent to bring flux ratio anomalies in strong lensed systems. 
+\simona{Indeed,} little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
 \simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
@@
 image (Fig. 1, left), a recognizable edge-on disk is lie in the center
-with position angle $~10$ degree. With this information, we model
+with position angle $~10$ degree. With this new information from A/O image, we model
 B1555+375 with two models. The first model consists of an SIE bulge
@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-The discrepency between numerical simulations and observations within the Local Universe gives two possible arguments: an alternative structure formation model or the selection bias of local universe samples.
-Lensing shows a promising potential on substructure detection beyond the Local Group.
-The main reason is that the gravitational perturbation from the substructure reflects the total mass, regardless it's luminous or not.
+The discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
+Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites.
+This makes gravitational lensing a powerful tool for the detection of substructures.
+The gravitational perturbation from substructure is sufficient to bring flux ratio anomaly in strong lensing systems.
+These perturbations reflect the total mass of substructures.
+Give directly measurement of mass function and avoid assumptions on how baryonic matter distributes with dark matter.
 
-Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref).
-Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey.
-Radio data provides reliable positions and fluxes of source for constraint and modelling because it avoids the problem of severe extinction and micro lensing from stars.
-On the other hand, optical or near infrared imaging also gives useful information about the lensing system.
-In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
-The lack of knowledge about lens galaxy, e.g.
-modelling with radio data alnog, may lead to an improper lens model.
-
-The idea of detecting substructures with flux ratio anomalies assumes that lens galaxy has completely smooth gravitational potential.
-Thus the perturbation is considered to be from faint satellite galaxy or ``dark'' subhalo.
-Numerical simulations have examined this approach with unkown systems.
-In \citet{Xu14}, only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos.
-The rest of them are only few percent likely or very unlikely to have their flux anomalies due to substructure, including B1555+375.
-Their results support that even using radio data, there are other possible reasons could cause flux anomalies.
-The answer to this concern may be explained by the high resolution IR imaging.
-In the SHARP K-band imaging of B1555+375, an edge-on disk lies across between the positions of radio merging double A \& B.
+The discussion on substructure searching in strong lensing systems are mostly done by multiple images of lensed quasar.
+Until now there are a dozen(?) flux anomalous lensed quasars and the number must increase in the future surveys.
+With the assumption of smooth gravitational potential from lens galaxy, flux ratio anomalies are brought by substructure perturbations.
+Numerical simulations have examined this idea with known lensed quasars.
+In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena.
+Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system.
+The rest of them are only few percent likely to have substructure origined flux anomalies, including B1555+375.
+They conclude B1555+375 with improper lens model.
+This result can be supported by SHARP K-band image, which an edge-on disk lies across between the positions of radio merging double A \& B.
+more complicated structure
 
@@
 
+Thus radio data provides reliable information for constraint and modelling because it avoids the problem of dust extinction and micro lensing from stars.
+On the other hand, optical or near infrared imaging also gives useful information about the lensing system.
+In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
+The lack of knowledge about lens galaxy, e.g.
+modelling with radio data alnog, may lead to an improper lens model.
 Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.

### 2015-03-02 papers/B1555_EdgeOn/B1555_letter.tex
Rewrite on Discussion[complete version]

@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-The discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
+Discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
 Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites.
 This makes gravitational lensing a powerful tool for the detection of substructures.
-The gravitational perturbation from substructure is sufficient to bring flux ratio anomaly in strong lensing systems.
-These perturbations reflect the total mass of substructures.
-Give directly measurement of mass function and avoid assumptions on how baryonic matter distributes with dark matter.
+With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass.
+Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.
 
-The discussion on substructure searching in strong lensing systems are mostly done by multiple images of lensed quasar.
-Until now there are a dozen(?) flux anomalous lensed quasars and the number must increase in the future surveys.
-With the assumption of smooth gravitational potential from lens galaxy, flux ratio anomalies are brought by substructure perturbations.
+Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar.
+Until now there are a dozen(?) flux anomalous lensed quasars, and the number must increase in the future surveys.
+In the ideal case(no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential.
 Numerical simulations have examined this idea with known lensed quasars.
@@
 Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system.
-The rest of them are only few percent likely to have substructure origined flux anomalies, including B1555+375.
+The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375.
 They conclude B1555+375 with improper lens model.
-This result can be supported by SHARP K-band image, which an edge-on disk lies across between the positions of radio merging double A \& B.
-more complicated structure
+This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B.
+A more complicated lens model (e.g.
+include an exponential disk) must be applied on B1555+375.
 
-In sec.
-2, we present new lens models of B1555+375 with a bulge and an edge-on disk.
+In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk.
 Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B.
-In our modelling, substructure is not neccessary to exist to cause the observed flux ratio anomaly.
-This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging.
-Our result is consistent with the conclusion from \citet{Xu14}.
-Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.
+In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly.
+This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure.
+Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars.
+A complex host galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar.
+Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis.
+Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis.
+For the case oringinated by real  substructures, mass distribution of host galaxy may also influence the estimated mass and other derived properties.
+We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar.
+Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from  lensed quasars may contain large systematic bias.
 
-With our discover in B155+375, we show that the lens galaxy structure can dominate the flux ratio anomalous phenomenon in strong lensing system.
-This leads to a more general reminder.
-Not all of the flux anomalies indicate the existence of substructures.
-One must fully consider non-substructure effects before gathering any statistics or serious analysis.
-Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data and analysis.
-For the flux ratio anomalies caused by real dark matter substructures and dwarf galaxies, non-stucture effects would also influence the estimated mass and other derived properties.
-Thus, we would like to draw some attention on these non-substructure effects.
-Once we understand more about their role in flux anomalous phenomenon, we can be more confident on searching unseen dwarf galaxies and dark matter substructures by searching flux ratio anomalous systems.
-
-Thus radio data provides reliable information for constraint and modelling because it avoids the problem of dust extinction and micro lensing from stars.
-On the other hand, optical or near infrared imaging also gives useful information about the lensing system.
+Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.
+Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of host galaxy.
 In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
-The lack of knowledge about lens galaxy, e.g.
-modelling with radio data alnog, may lead to an improper lens model.
-Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.
-The radio and narrow band observations are the best approaches to obtain accurate flux ratio data.
-However, optical and infrared imaging can provide more information on the structure of lens galaxy.
+The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly.
+Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes.
 With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems.

### 2015-03-03 papers/B1555_EdgeOn/B1555_letter.tex
Change in Table 3
little change in Discussion

@@
 While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies.
-In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex host galaxy mass distribution than initially considered.
+In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex lens galaxy mass distribution than initially considered.
 To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP).
@@
 \tableline\tableline
-				&Radio &Infrared  &Model-predicted\\
+				&5 GHz & 15 GHz & Ks  &Model-predicted\\
 \tableline
-A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
-A/C 		&$2.0$ &$1.0$ &$2.2$  \\
-A/D			&$13.0$ &$5.4$ &$8.0$  \\
+A/B			&$1.8$ & $1.8$ & $3.5$ &$1.7$  \\ 
+A/C 		&$2.0$ 	&$2.4$ &$1.0$ &$2.2$  \\
+A/D			&$13.0$ &$ 12.9$ & $5.4$ &$8.0$  \\
 \tableline
@@
 %% Any table notes must follow the \end{tabular} command.
-\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}.
+\tablecomments{Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.
 Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
@@
 Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar.
-Until now there are a dozen(?) flux anomalous lensed quasars, and the number must increase in the future surveys.
-In the ideal case(no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential.
+In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential.
 Numerical simulations have examined this idea with known lensed quasars.
@@
 This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B.
-A more complicated lens model (e.g.
+A more complex lens model (e.g.
 include an exponential disk) must be applied on B1555+375.
@@
 This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure.
+Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future.
 Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars.
-A complex host galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar.
+A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar.
 Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis.
 Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis.
-For the case oringinated by real  substructures, mass distribution of host galaxy may also influence the estimated mass and other derived properties.
+For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties.
 We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar.
-Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from  lensed quasars may contain large systematic bias.
+[here for a precise estimate on substurcture number, mass function, property missing satellite problem]Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from lensed quasars may contain large systematic bias.
 
-Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.
-Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of host galaxy.
+Our result also shows that multi-wavelength image is helpful on exploring flux anomalous quasars.
+Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy.
 In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
@@
 Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes.
-With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems.
+[Cant determine on substructure detection] With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.

### 2015-03-03 papers/B1555_EdgeOn/B1555_letter.tex
Minor change in Discussion

@@
 We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar.
-[here for a precise estimate on substurcture number, mass function, property missing satellite problem]Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from lensed quasars may contain large systematic bias.
+For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.
 
-Our result also shows that multi-wavelength image is helpful on exploring flux anomalous quasars.
-Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy.
+Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars.
+Although radio band provides reliable data on position and fluxe of lensed images, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy.
 In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
 The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly.
-Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes.
-[Cant determine on substructure detection] With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems.
+Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes and can have impacts on statics and derived properties among substructure detection.
+With the first system being analyzed and shown that an edge-on disk can explain its flux ratio anomaly, our follow up will be explore other SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.

### 2015-03-04 papers/B1555_EdgeOn/B1555_letter.tex
Start of text for Section 2

@@
 \section{Data Collection \& Reduction}
+
+\subsection{Hubble Space Telescope Archival Imaging}
+
+\subsection{Keck Adaptive Optics Imaging}
+
+The B1555+375 system was observed using the NIRC2 camera on the Keck 2
+Telescope on the night of 2012 May 16 UT.  The adaptive optics system
+was used, with the corrections derived from the laser guide star and a
+$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
+system.  The ``narrow camera'' mode was used, giving a field of view
+of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
+Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
+data were reduced with the standard SHARP pipeline, which is a
+python-based package that is a refinement of the process described in
+\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
+is shown in Fig.~??b and again in Fig.~??c with contours from the
+MERLIN radio observations of \citet{Marlow} overlaid.
 

### 2015-03-10 papers/B1555_EdgeOn/B1555_letter.tex
Take off IR flux ratio in Table

@@
 \tableline\tableline
-				&5 GHz & 15 GHz & Ks  &Model-predicted\\
+				&5 GHz & 15 GHz  &Model-predicted\\
 \tableline
-A/B			&$1.8$ & $1.8$ & $3.5$ &$1.7$  \\ 
-A/C 		&$2.0$ 	&$2.4$ &$1.0$ &$2.2$  \\
-A/D			&$13.0$ &$ 12.9$ & $5.4$ &$8.0$  \\
+A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
+A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
+A/D			&$13.0$ &$ 12.9$ & $8.0$  \\
 \tableline
@@
 %% Any table notes must follow the \end{tabular} command.
-\tablecomments{Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.
-Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
+\tablecomments{Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.}
 \end{center}
@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-Discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
+Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
 Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites.

### 2015-03-14 papers/B1555_EdgeOn/B1555_letter.tex
Additional text for Section 2

@@
 
-While future large-scale surveys, such as the LSST, \simona{are expected to deliver new large samples of gravitationally lensed quasar, in the near future the discovery of new systems using} narrow-line quasar emission \citep{N14} \simona{will provide new invaluable statistical perspective on current constraints based on flux ratio anomalies.
-In this paper, we explore the alternative idea that flux ratio anomalies are not related to the presence of substructure but originate in a more complex lens galaxy mass distribution than initially considered.
-To this end we use new infra-red data from the Strong lensing at High Angular Resolution Program(SHARP).
-The main goal of the SHARP} project \simona{is to re-observe} known quadruple and Einstein ring lens systems at a much higher angular resolution by making use of the Keck adaptive optics (AO) telescope and large interferometric arrays \citep{SHARP12,V12} .
-In particular, to better understand the cause of flux ratio anomalies in strong lens systems \simona{we focus on the lens modelling of the lens system B1555+375 (included in both the observational and theoretical analysis of  \citet{Dalal2002} and \citet{Xu14}, respectively) by making use of} the new information obtained from the latest SHARP infrared imaging.
-\simona{The paper is organized as follows: the latest SHARP data is introduced in section 2; in section 3 we present the lens model while the results of this analysis and their implication are discussed in section 4.}
+While future large-scale surveys, such as the LSST, \simona{are
+  expected to deliver new large samples of gravitationally lensed
+  quasar, in the near future the discovery of new systems using}
+narrow-line quasar emission \citep{N14} \simona{will provide new
+  invaluable statistical perspective on current constraints based on
+  flux ratio anomalies.  In this paper, we explore the alternative
+  idea that flux ratio anomalies are not related to the presence of
+  substructure but originate in a more complex lens galaxy mass
+  distribution than initially considered. To this end we use new
+  infra-red data from the Strong lensing at High Angular Resolution
+  Program(SHARP). The main goal of the SHARP} project \simona{is to
+  re-observe} known quadruple and Einstein ring lens systems at a much
+higher angular resolution by making use of the Keck adaptive optics
+(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
+. In particular, to better understand the cause of flux ratio
+anomalies in strong lens systems \simona{we focus on the lens
+  modelling of the lens system B1555+375 (included in both the
+  observational and theoretical analysis of \citet{Dalal2002} and
+  \citet{Xu14}, respectively) by making use of} the new information
+obtained from the latest SHARP infrared imaging. \simona{The paper is
+  organized as follows: the latest SHARP data is introduced in section
+  2; in section 3 we present the lens model while the results of this
+  analysis and their implication are discussed in section 4.}
+
 %However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable.
@@
 
-\subsection{Hubble Space Telescope Archival Imaging}
-
 \subsection{Keck Adaptive Optics Imaging}
@@
 is shown in Fig.~??b and again in Fig.~??c with contours from the
-MERLIN radio observations of \citet{Marlow} overlaid.
+MERLIN radio observations of \citet{Marlow} overlaid.  There are several
+notable features in the Keck AO data.  These
+include the nearly complete lack of emission associated with the
+B and D lensed images, as can be seen by comparing the radio contours
+to the $K^\prime$-band emission, and faint but clearly visible emission
+from what appears to be an edge-on lensing galaxy.
+
+\subsection{Hubble Space Telescope Archival Imaging}
+
+The B1555+375 system was also observed by the Hubble Space Telescope
+(HST) in three broad bands.  The optical data were obtained with the
+Wide-Field Planetary Camera 2 (WFPC2) in the $F555W$ and $F814W$ bands
+(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
+Spectrograph (NICMOS) was used to observe the system in the $F160W$
+band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
+obtained with the NIC2 camera.  We reduced all of the archival HST
+data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
+MATT], producing final drizzled images with pixel scales of
+50~mas.  The reduced images are shown in Figure~??.  The lens system
+is not detected at high significance in the optical bands, but is
+clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
+stands out in the NICMOS image.
+
+%===========================================================================
 
 \section{Lens Modelling}
+
 To model B1555+375, we use the lens modelling code {\tt glafic}

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
Added initial version of figures

@@
 
-\shorttitle{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
-\shortauthors{TBD}
+\shorttitle{Beware the Effect of Edge-on Disks}
+\shortauthors{Hsueh et al.}
 
@@
 
+\begin{figure*}
+\plotone{B1555_gallery.eps}
+\caption{High-resolution multiband imaging of the B1555+375 lens system.
+All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
+represents 1\arcsec.  From left to right the figures show data from
+HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
+in the F160W band, and Keck AO imaging in the $K^\prime$ band.
+%
+\label{fig:multiband}}
+\end{figure*}
+
 \subsection{Keck Adaptive Optics Imaging}
@@
 python-based package that is a refinement of the process described in
-\citet{Auger_EELS1}.  A ??x?? cutout of the final reduced image
-is shown in Fig.~??b and again in Fig.~??c with contours from the
-MERLIN radio observations of \citet{Marlow} overlaid.  There are several
-notable features in the Keck AO data.  These
-include the nearly complete lack of emission associated with the
+\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
+Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
+contours from the MERLIN radio observations of \citet{Marlow}
+overlaid.  There are several notable features in the Keck AO data.
+These include the nearly complete lack of emission associated with the
 B and D lensed images, as can be seen by comparing the radio contours
-to the $K^\prime$-band emission, and faint but clearly visible emission
-from what appears to be an edge-on lensing galaxy.
+to the $K^\prime$-band emission, and faint but clearly visible
+emission from what appears to be an edge-on lensing galaxy.
+
+\begin{figure}
+\plotone{1555_ao_merlin_overlay.eps}
+\caption{High-resolution multiband imaging of the B1555+375 lens system.
+All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
+represents 1\arcsec.  From left to right the figures show data from
+HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
+in the F160W band, and Keck AO imaging in the $K^\prime$ band.
+%
+\label{fig:merlin}}
+\end{figure}
 
@@
 (HST) in three broad bands.  The optical data were obtained with the
-Wide-Field Planetary Camera 2 (WFPC2) in the $F555W$ and $F814W$ bands
+Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
 (GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
change template to MNRAS

@@
-\documentclass[manuscript]{emulateapj}
+% mn2esample.tex
+%
+% v2.1 released 22nd May 2002 (G. Hutton)
+%
+% The mnsample.tex file has been amended to highlight
+% the proper use of LaTeX2e code with the class file
+% and using natbib cross-referencing. These changes
+% do not reflect the original paper by A. V. Raveendran.
+%
+% Previous versions of this sample document were
+% compatible with the LaTeX 2.09 style file mn.sty
+% v1.2 released 5th September 1994 (M. Reed)
+% v1.1 released 18th July 1994
+% v1.0 released 28th January 1994
 
-\usepackage{color}
-\definecolor{simonacolor}{cmyk}{0, 0.9808, 0.4429, 0.1412}
-\newcommand{\simona}[1]{\textcolor{simonacolor}{#1}}
+\documentclass[useAMS,usenatbib]{mn2e}
 
-\shorttitle{Beware the Effect of Edge-on Disks}
-\shortauthors{Hsueh et al.}
+% If your system does not have the AMS fonts version 2.0 installed, then
+% remove the useAMS option.
+%
+% useAMS allows you to obtain upright Greek characters.
+% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
+% this guide for further information.
+%
+% If you are using AMS 2.0 fonts, bold math letters/symbols are available
+% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
+% preferably \bmath).
+%
+% The usenatbib command allows the use of Patrick Daly's natbib.sty for
+% cross-referencing.
+%
+% If you wish to typeset the paper in Times font (if you do not have the
+% PostScript Type 1 Computer Modern fonts you will need to do this to get
+% smoother fonts in a PDF file) then uncomment the next line
+% \usepackage{Times}
 
+%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
+\author[Jen-Wei Hsueh and A. N. Other]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
+email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
+Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
+highlight the proper use of \LaTeXe\ code with the class file.
+These changes are for illustrative purposes and do not reflect the
+original paper by A. V. Raveendran.}\\
+$^{1}$University of California, Davis, Davis 95616, USA\\
+$^{2}$Building, Institute, Street Address, City, Code, Country}
 \begin{document}
 
-\title{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
-\author{TBD}
+\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}
+
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}
+
+\maketitle
+
+\label{firstpage}
 
@@
 And apply this model to SHARP infrared image.
-
 \end{abstract}
 
-\keywords{ gravitaional lensing}
+\begin{keywords}
+gravitaional lensing.
+\end{keywords}
 
@@
 formation \citep[e.g.,][]{P11}, rendering them effectively dark.
-These factors make gravitational \simona{lensing a powerful and promising tool for the detection of substructure.}
+These factors make gravitational lensing a powerful and promising tool for the detection of substructure.
 
-\simona{It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.}
+It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
 %Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
 These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
-\simona{Indeed,} little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
-\simona{Moreover, unlike in the optical or infrared,} in the radio band, lensed images are not sensitive to micro lensing from stars \simona{nor dust extinction}. 
+Indeed, little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
+Moreover, unlike in the optical or infrared, in the radio band, lensed images are not sensitive to micro lensing from stars nor dust extinction. 
 This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
-\simona{At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}.
-While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.} \simona{An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}.
-Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.}
+At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}.
+While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.
+An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}.
+Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.
 
-While future large-scale surveys, such as the LSST, \simona{are
+While future large-scale surveys, such as the LSST, are
   expected to deliver new large samples of gravitationally lensed
-  quasar, in the near future the discovery of new systems using}
-narrow-line quasar emission \citep{N14} \simona{will provide new
+  quasar, in the near future the discovery of new systems using
+narrow-line quasar emission \citep{N14} will provide new
   invaluable statistical perspective on current constraints based on
@@
   infra-red data from the Strong lensing at High Angular Resolution
-  Program(SHARP). The main goal of the SHARP} project \simona{is to
-  re-observe} known quadruple and Einstein ring lens systems at a much
+  Program(SHARP). The main goal of the SHARP project is to
+  re-observe known quadruple and Einstein ring lens systems at a much
 higher angular resolution by making use of the Keck adaptive optics
@@
 . In particular, to better understand the cause of flux ratio
-anomalies in strong lens systems \simona{we focus on the lens
+anomalies in strong lens systems we focus on the lens
   modelling of the lens system B1555+375 (included in both the
   observational and theoretical analysis of \citet{Dalal2002} and
-  \citet{Xu14}, respectively) by making use of} the new information
-obtained from the latest SHARP infrared imaging. \simona{The paper is
+  \citet{Xu14}, respectively) by making use of the new information
+obtained from the latest SHARP infrared imaging. The paper is
   organized as follows: the latest SHARP data is introduced in section
   2; in section 3 we present the lens model while the results of this
-  analysis and their implication are discussed in section 4.}
+  analysis and their implication are discussed in section 4.
 
@@
 \begin{figure*}
-\plotone{B1555_gallery.eps}
+\begin{minipage}{140mm}
+%\includegraphics[width=84mm]{B1555_gallery.eps}
 \caption{High-resolution multiband imaging of the B1555+375 lens system.
@@
 HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
-in the F160W band, and Keck AO imaging in the $K^\prime$ band.
+in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
 %
-\label{fig:multiband}}
+\end{minipage}
+
 \end{figure*}
+
+\begin{table}
+ \centering
+ %\begin{minipage}{140mm}
+  \caption{Multiband observation details of the B1555+375 lens system.}
+  \begin{tabular}{@{}llccc}
+
+\hline
+  Telescope     &      Camera     &  Band & Date &$t_{exp}$ (s) \\
+
+ \hline
+   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
+   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
+   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
+   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
+   \hline
+\end{tabular}
+%\end{minipage}
+\end{table}
 
@@
 \begin{figure}
-\plotone{1555_ao_merlin_overlay.eps}
-\caption{High-resolution multiband imaging of the B1555+375 lens system.
-All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
-represents 1\arcsec.  From left to right the figures show data from
-HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
-in the F160W band, and Keck AO imaging in the $K^\prime$ band.
+%\plotone{1555_ao_merlin_overlay.eps}
+\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
 %
@@
 
+The observation details of Keck AO and HST imaging are shown in Table 1.
+
 %===========================================================================
@@
 does not reproduce the strong flux ratio anomaly between components A and B.
-(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
-image (Fig. 1, left), a recognizable edge-on disk is lie in the center
-with position angle $~10$ degree. With this new information from A/O image, we model
+(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
+imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
+with position angle $~10$ degree.
+The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right).
+Its orientation is aligned with image B \& D.
+With this new information from AO image, we model
 B1555+375 with two models. The first model consists of an SIE bulge
@@
 consists of two SIE mass profiles (2-SIE), for bulge and disk
-respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 1. Both
+respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
 of these models predict fairly matched results with the radio
 observation. The comparison of observation and SIE+Expdisk result is
-in Figure 2, Table 2 \& 3.
-%These authors present a singular isothermal ellipsoid (SIE) model that
-%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)
+in Figure 3, Table 3 \& 4.
 
-%\begin{figure}
-%\plotone{B1555_Kp.eps}
-%\plottwo{B1555_model.eps}{B1555_residue.eps}
-%\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
-%An edge-on disk can be seen in the center of SHARP K-band image.
-Exponential disk is marked by the green ellipse in residue image.
-We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared.
-Thus leaving two negative holes in our residue.\label{fig1}}
-%\end{figure}
-%
-%\begin{figure}
-%\plotone{point_source.eps}
-%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
-From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
-%\end{figure}
-
-%%table1
 \begin{table}
-\begin{center}
-\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
-\begin{tabular}{ccccccc}
-%%\tableline\tableline
-		&SIE+Expdisk& 2-SIE		   
+% \centering
+% \begin{minipage}{140mm}
+  \caption{Best-fit parameters of B1555+375 lens model.}
+  \begin{tabular}{@{}ccc}
+\hline 
+ Parameter  & \multicolumn{2}{c}{Lens model} \\
+		&SIE+expdisk& 2-SIE		   
 \\
-\tableline\tableline
+\hline
 $x_1$  	& $-0.1883$	& $-0.1809$	  \\
@@
 $r_e$	& $0.20 ''$ &  -- \\
-\tableline
+\hline
+\end{tabular}
 
-\end{tabular}
-%% Any table notes must follow the \end{tabular} command.
-\tablecomments{Subscripts 1 and 2 represent bulge and disk components in each model respectively.
+%\end{minipage}
+\medskip
+Subscripts 1 and 2 represent bulge and disk components in each model respectively.
 Positions are offsets from radio image component A measured in units of arcsec.
 The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
-$e$ is ellipticity and $\theta$ is the position angle measured east of north.}
-\end{center}
+$e$ is ellipticity and $\theta$ is the position angle measured east of north.
+
 \end{table}
 
-%%table2
 \begin{table}
-\begin{center}
-\caption{Radio Observation and Model-predicted Image Positions.\label{tbl-2}}
-\begin{tabular}{lccccc}
-\tableline\tableline
-					&Radio	&		 & Model-predicted \\
-Component &East &North &East 		&North\\ 
-\tableline
+% \centering
+% \begin{minipage}{140mm}
+  \caption{Radio observation and model-predicted lensed image positions.}
+  \begin{tabular}{@{}ccccc}
+
+\hline
+
+Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{2}{c}{Model} \\
+					&\multicolumn{2}{c}{5 GHz}		&			\\
+					 &East &North &East 		&North\\ 
+\hline
 A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
@@
 D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
-\tableline
+\hline
 \end{tabular}
-%% Any table notes must follow the \end{tabular} command.
-\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.}
-\end{center}
+
+%\end{minipage}
+\medskip
+Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.
+
 \end{table}
 
-%%table3
 \begin{table}
-\begin{center}
-\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
-\begin{tabular}{lccccc}
-\tableline\tableline
-				&5 GHz & 15 GHz  &Model-predicted\\
-\tableline
+% \centering
+% \begin{minipage}{140mm}
+  \caption{Flux ratios of B1555+375 components.}
+  \begin{tabular}{@{}ccccc}
+
+\hline
+Flux ratio	& \multicolumn{2}{c}{MERLIN} & Model\\
+		&5 GHz & 15 GHz  &\\
+\hline
 A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
@@
 A/D			&$13.0$ &$ 12.9$ & $8.0$  \\
-\tableline
+
+\hline
 \end{tabular}
-%% Any table notes must follow the \end{tabular} command.
-\tablecomments{Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.}
-\end{center}
+
+%\end{minipage}
+\medskip
+Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.
+
 \end{table}
-
-We then use an extended source to model SHARP infrared image.
-In Figure 1, B and D have no detection in K-band, which believed due to strong dust extinction from the edge-on disk.
-The region and orientation of exponential disk in lens model are consistent with this hypothesis.
-The flux ratios in infrared are much higher than in radio also supports as an evidence of dust extinction.
 
@@
 
-\bibliographystyle{apj}
+\section*{Acknowledgments}
+
+\bibliographystyle{mn2e}
 \bibliography{reference.bib}
 
-%\begin{thebibliography}{}
-%\bibitem[Oguri(2010)]{Oguri} Oguri, M. 2010, \pasj, 62, 1017
-%\bibitem[Marlow et al.(1999)]{Marlow} Marlow, D. R., et al. 1999, \apj, 118, 654
-%\end{thebibliography}
+\label{lastpage}
 

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
Figures display now

@@
 
+%\documentclass[useAMS,usenatbib]{mn2e}
 \documentclass[useAMS,usenatbib]{mn2e}
-
+\usepackage{graphicx}
 % If your system does not have the AMS fonts version 2.0 installed, then
@@
 \title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
-\author[Jen-Wei Hsueh and A. N. Other]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
+\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
 email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
@@
 \begin{minipage}{140mm}
-%\includegraphics[width=84mm]{B1555_gallery.eps}
+\includegraphics[width=140mm]{B1555_gallery.eps}
 \caption{High-resolution multiband imaging of the B1555+375 lens system.
@@
 %\plotone{1555_ao_merlin_overlay.eps}
+\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
 \caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
@@
 in Figure 3, Table 3 \& 4.
+
+\begin{figure}
+%\plotone{point_source.eps}
+\includegraphics[width=84mm]{point_source.eps}
+\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
+The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
+From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
+\end{figure}
 

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
Fixed gitignore
newcommand for non-recognizable journals
Modified abstract

@@
-% mn2esample.tex
-%
-% v2.1 released 22nd May 2002 (G. Hutton)
-%
-% The mnsample.tex file has been amended to highlight
-% the proper use of LaTeX2e code with the class file
-% and using natbib cross-referencing. These changes
-% do not reflect the original paper by A. V. Raveendran.
-%
-% Previous versions of this sample document were
-% compatible with the LaTeX 2.09 style file mn.sty
-% v1.2 released 5th September 1994 (M. Reed)
-% v1.1 released 18th July 1994
-% v1.0 released 28th January 1994
+\documentclass[useAMS,usenatbib]{mn2e}
+%\documentclass[usenatbib]{mn2e}
+\usepackage{graphicx}
+\usepackage[nottoc]{tocbibind}
 
-%\documentclass[useAMS,usenatbib]{mn2e}
-\documentclass[useAMS,usenatbib]{mn2e}
-\usepackage{graphicx}
 % If your system does not have the AMS fonts version 2.0 installed, then
@@
 
+% Journal definitions
+\newcommand{\apj}[1]{ApJ}
+\newcommand{\mnras}[1]{MNRAS}
+\newcommand{\apjl}[1]{ApJL}
+\newcommand{\pasj}[1]{PASJ}
+\newcommand{\aj}[1]{AJ}
+\newcommand{\nat}[1]{Nature}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
-Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
-highlight the proper use of \LaTeXe\ code with the class file.
-These changes are for illustrative purposes and do not reflect the
-original paper by A. V. Raveendran.}\\
-$^{1}$University of California, Davis, Davis 95616, USA\\
+Other$^{2}$\\
+$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
+Davis, CA 95616, USA\\
 $^{2}$Building, Institute, Street Address, City, Code, Country}
@@
 
-\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}
+%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}
 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}
 
@@
 \begin{abstract}
-With the latest infrared image of B1555+375, an edge-on disk is shown to over cross the strong lensed images.
-Indicating the flux ratio anomalie of B1555+375 is dominanted by its edge-on disk structure.
-We present a lens model with SIE bulge and exponential disk, base on the radio observation from \citet{Marlow}.
-And apply this model to SHARP infrared image.
+
+Gravitational lens flux-ratio anomalies provide a powerful technique
+for detecting the presence of dark matter substructure in distant
+galaxies.  However, before using the statistics of systems with these
+anomalies, it is imperative to ascertain that a given system does not
+have properties that could plausibly cause the observed anomaly
+without the need for substructure.  In this letter, we present the
+case of the B1555+375 lens system, which has a strong radio-wavelength
+flux-ratio anomaly but where the lensing galaxy is also revealed in
+high-resolution imaging to have a clear edge-on disk component.  The
+disk crosses directly over the pair of images that exhibit the
+anomaly, and we show that simple models that include the disk can
+reproduce the anomaly without requiring substructure.  Several [??]
+other lens systems that we have observed with adaptive optics imaging
+as part of the Strong lensing at High Angular Resolution Programme (SHARP)
+show similar behaviour.  These results suggest that the assumption that
+all flux-ratio anomalies are due to substructure will likely overestimate
+the substructure fraction in massive galaxies.
+
 \end{abstract}
@@
 \begin{keywords}
-gravitaional lensing.
+gravitational lensing
 \end{keywords}

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
Minor format changes

@@
 imposed by the Galactic Plane.  This is the famous ``missing
-satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to understand
-this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.  
-This process is challenging
-due to the faintness of the satellite galaxies.  Furthermore, lower-mass
-satellites may not be able to retain the gas needed for ongoing star
-formation \citep[e.g.,][]{P11}, rendering them effectively dark.
-These factors make gravitational lensing a powerful and promising tool for the detection of substructure.
+satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
+understand this discrepancy, it is imperative to build up a large
+sample of satellites/subhaloes in galaxies outside the Local Group.
+This process is challenging due to the faintness of the satellite
+galaxies.  Furthermore, lower-mass satellites may not be able to
+retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
+rendering them effectively dark.  These factors make gravitational
+lensing a powerful and promising tool for the detection of
+substructure.
 
@@
 These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
-Indeed, little perturbations in the gravitational potential are sufficient to bring flux ratio anomalies in strong lensed systems. 
-Moreover, unlike in the optical or infrared, in the radio band, lensed images are not sensitive to micro lensing from stars nor dust extinction. 
-This makes flux ratio anomalies a promising tool to detect dark matter substructures \citep{Dalal2002, N13}.  
-At present, the amount of substructure derived from flux ratio anomalies is in disagreement with predictions from numerical simulations, with the former requiring a larger fraction of mass in substructure than expected \citet{Xu14}.
-While this could be the result of small sample statistics, it could also be the indication that flux ratio anomalies have a different origin than substructure.
-An alternative method for the detection of substructure in gravitational lens galaxies based on the surface brightness distribution of extended arcs and Einstein ring has been introduced by \citet{K05,V09}.
-Interestingly, the fraction of substructure measured with this \emph{gravitational imaging technique} is currently in agreement with theoretical expectations \citep{V14a}.
+Indeed, small perturbations in the gravitational potential are
+sufficient to bring flux ratio anomalies in strong lensed systems.
+Moreover, unlike in the optical or infrared, in the radio band, lensed
+images are not sensitive to micro lensing from stars nor dust
+extinction.  This makes flux ratio anomalies a promising tool to
+detect dark matter substructures \citep{Dalal2002, N13}.  At present,
+the amount of substructure derived from flux ratio anomalies is in
+disagreement with predictions from numerical simulations, with the
+former requiring a larger fraction of mass in substructure than
+expected \citet{Xu14}. While this could be the result of small sample
+statistics, it could also be the indication that flux ratio anomalies
+have a different origin than substructure. An alternative method for
+the detection of substructure in gravitational lens galaxies based on
+the surface brightness distribution of extended arcs and Einstein ring
+has been introduced by \citet{K05,V09}. Interestingly, the fraction of
+substructure measured with this \emph{gravitational imaging technique}
+is currently in agreement with theoretical expectations \citep{V14a}.
 
-While future large-scale surveys, such as the LSST, are
-  expected to deliver new large samples of gravitationally lensed
-  quasar, in the near future the discovery of new systems using
-narrow-line quasar emission \citep{N14} will provide new
-  invaluable statistical perspective on current constraints based on
-  flux ratio anomalies.  In this paper, we explore the alternative
-  idea that flux ratio anomalies are not related to the presence of
-  substructure but originate in a more complex lens galaxy mass
-  distribution than initially considered. To this end we use new
-  infra-red data from the Strong lensing at High Angular Resolution
-  Program(SHARP). The main goal of the SHARP project is to
-  re-observe known quadruple and Einstein ring lens systems at a much
-higher angular resolution by making use of the Keck adaptive optics
-(AO) telescope and large interferometric arrays \citep{SHARP12,V12}
-. In particular, to better understand the cause of flux ratio
-anomalies in strong lens systems we focus on the lens
+While future large-scale surveys, such as the LSST, are expected to
+deliver new large samples of gravitationally lensed quasars, in the
+near future the discovery of new systems using narrow-line quasar
+emission \citep{N14} will provide new invaluable statistical
+perspective on current constraints based on flux ratio anomalies.  In
+this paper, we explore the alternative idea that flux ratio anomalies
+are not related to the presence of substructure but originate in a
+more complex lens galaxy mass distribution than initially
+considered. To this end we use new infra-red data from the Strong
+lensing at High Angular Resolution Program(SHARP). The main goal of
+the SHARP project is to re-observe known quadruple and Einstein ring
+lens systems at a much higher angular resolution by making use of the
+Keck adaptive optics (AO) telescope and large interferometric arrays
+\citep{SHARP12,V12} . In particular, to better understand the cause of
+flux ratio anomalies in strong lens systems we focus on the lens
 modelling of the lens system B1555+375 (included in both the
@@
 \begin{figure*}
-\begin{minipage}{140mm}
-\includegraphics[width=140mm]{B1555_gallery.eps}
+%\begin{minipage}{140mm}
+%\includegraphics[width=140mm]{B1555_gallery.eps}
+\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
 \caption{High-resolution multiband imaging of the B1555+375 lens system.
@@
 %
-\end{minipage}
+%\end{minipage}
 
 \end{figure*}
-
-\begin{table}
- \centering
- %\begin{minipage}{140mm}
-  \caption{Multiband observation details of the B1555+375 lens system.}
-  \begin{tabular}{@{}llccc}
-
-\hline
-  Telescope     &      Camera     &  Band & Date &$t_{exp}$ (s) \\
-
- \hline
-   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
-   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
-   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
-   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
-   \hline
-\end{tabular}
-%\end{minipage}
-\end{table}
 
@@
 
-\begin{figure}
-%\plotone{1555_ao_merlin_overlay.eps}
-\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
-%
-\label{fig:merlin}}
-\end{figure}
-
 \subsection{Hubble Space Telescope Archival Imaging}
@@
 The observation details of Keck AO and HST imaging are shown in Table 1.
+
+\begin{table}
+ \centering
+ %\begin{minipage}{140mm}
+  \caption{Multiband observation details of the B1555+375 lens system.}
+  \begin{tabular}{@{}llccc}
+
+\hline
+  Telescope     &      Camera     &  Band & Date &$t_{exp}$ (s) \\
+
+ \hline
+   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
+   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
+   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
+   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
+   \hline
+\end{tabular}
+%\end{minipage}
+\end{table}
 
@@
 in Figure 3, Table 3 \& 4.
+
+\begin{figure}
+%\plotone{1555_ao_merlin_overlay.eps}
+\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
+\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
+%
+\label{fig:merlin}}
+\end{figure}
 

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
update to Table 1 and Table 4

@@
  \hline
-   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
-   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
-   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
+   HST				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
+   HST				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
+   HST				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
    Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
@@
 \medskip
-Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.
+Comparision between radio and model-predicted lensed image positions.
+Observation data quoted from Table 2 in \citet{Marlow}.
+Position offsets are in unit of arcsec.
+Both SIE+expdisk and 2-SIE lens models predict the same lens image positions.
 
@@
   \caption{Flux ratios of B1555+375 components.}
-  \begin{tabular}{@{}ccccc}
+  \begin{tabular}{@{}ccccccc}
 
 \hline
-Flux ratio	& \multicolumn{2}{c}{MERLIN} & Model\\
-		&5 GHz & 15 GHz  &\\
+	& \multicolumn{2}{c}{MERLIN} & \multicolumn{3}{c}{Model}\\
+		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
 \hline
-A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
-A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
-A/D			&$13.0$ &$ 12.9$ & $8.0$  \\
+A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
+A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
+A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\
 
@@
 \medskip
-Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.
+Comparision between radio data and model-predicted flux ratios. Radio observation data is quoted from Table 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.
 

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
update Table 4 for model-predicted image positions

@@
 
-\begin{table}
-% \centering
-% \begin{minipage}{140mm}
+\begin{table*}
+%\centering
+ \begin{minipage}{140mm}
   \caption{Radio observation and model-predicted lensed image positions.}
-  \begin{tabular}{@{}ccccc}
+  \begin{tabular}{@{}ccccccc}
 
@@
 
-Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{2}{c}{Model} \\
-					&\multicolumn{2}{c}{5 GHz}		&			\\
-					 &East &North &East 		&North\\ 
+Component	&\multicolumn{2}{c}{MERLIN}		 & \multicolumn{4}{c}{Model} \\
+					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
+					 &East &North &East 		&North &East 		&North\\ 
 \hline
-A ........ &$0$    		&$0$		&$-0.0000$ &$+0.0000$   \\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$   \\  
-C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$   \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$   \\  
+A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
+B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
+C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$  & $-0.1618$    &  $+0.3680$ \\  
 \hline
@@
 
-%\end{minipage}
+\end{minipage}
 \medskip
+
 Comparision between radio and model-predicted lensed image positions.
@@
 Position offsets are in unit of arcsec.
-Both SIE+expdisk and 2-SIE lens models predict the same lens image positions.
+Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.
 
-\end{table}
+\end{table*}
 

### 2015-03-18 papers/B1555_EdgeOn/B1555_letter.tex
reference update and flux ratio description

@@
 substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14a}.
+is currently in agreement with theoretical expectations \citep{V14b}.
 
@@
 of these models predict fairly matched results with the radio
-observation. The comparison of observation and SIE+Expdisk result is
+observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
 in Figure 3, Table 3 \& 4.

### 2015-03-19 papers/B1555_EdgeOn/B1555_letter.tex
minor change in table, add ref to bib file

@@
 \usepackage{graphicx}
-\usepackage[nottoc]{tocbibind}
+%\usepackage[nottoc]{tocbibind}
 
@@
 statistics, it could also be the indication that flux ratio anomalies
-have a different origin than substructure. An alternative method for
+have a different origin than substructure.
+
+An alternative method for
 the detection of substructure in gravitational lens galaxies based on
@@
 substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14b}.
+is currently in agreement with theoretical expectations \citep{V14a}.
 
@@
 \hline
-	& \multicolumn{2}{c}{MERLIN} & \multicolumn{3}{c}{Model}\\
+	& MERLIN & VLA & \multicolumn{3}{c}{Model}\\
 		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\

### 2015-03-20 papers/B1555_EdgeOn/B1555_letter.tex
add radio scatter discussion

@@
 \hline
-	& MERLIN & VLA & \multicolumn{3}{c}{Model}\\
+	& MERLIN & VLA & \multicolumn{3}{l}{Model}\\
 		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
 \hline
-A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
-A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
-A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\
+$f_A/f_B$			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
+$f_A/f_C$		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
+$f_A/f_D$		&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\
 
@@
 They conclude B1555+375 with improper lens model.
-This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B.
+This result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B.
 A more complex lens model (e.g.
@@
 In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk.
-Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B.
-In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly.
-This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure.
-Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future.
+Our models predict the radio image positions and flux ratio anomaly between components A and B, which the 1-SIE model in \citet{Marlow} fails.
+Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies.
+An edge-on disk with high ellipcity can well explain the observed flux ratios and substructure is not neccessary to presence.
 Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars.
 A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar.
-Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis.
+Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future.
+One must fully consider non-substructure effects before gathering any statistics or serious analysis.
 Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis.

### 2015-03-25 papers/B1555_EdgeOn/B1555_letter.tex
text change in Modelling and Discussion

@@
 imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
-with position angle $~10$ degree.
-The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right).
-Its orientation is aligned with image B \& D.
-With this new information from AO image, we model
-B1555+375 with two models. The first model consists of an SIE bulge
-and an exponential edge-on disk (SIE+Expdisk). The second model
+with position angle $\approx 10$ degree.
+The detection of edge-on disk also explain the missing images B \& D in near-infrared (Fig 1, right).
+Image B \& D very likely are extincted by the edge-on disk since the images have the same orientation with the disk.
+
+By adding a disk component, we apply our new discover from AO image to the
+B1555+375 modelling. The first model consists of an SIE bulge
+and an exponential edge-on disk (SIE+expdisk). And the second model
 consists of two SIE mass profiles (2-SIE), for bulge and disk
@@
 The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe.
-Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites.
-This makes gravitational lensing a powerful tool for the detection of substructures.
-With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass.
-Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.
+Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample arise from nowaday observation.
+Difficulties emerge in direct detection when searching beyond the Local Group.
+Until now, most of known satellites are at high mass end in the mass function.
+However, the gravitational perturbations from substructures can cause detectable change in surface brightness among lensed images.
+This makes gravitational lensing a powerful tool for searching substructures.
+Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhalo.
+Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function which avoid making assumptions on baryonic matter distribution assoociated with dark matter.
 
-Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar.
-In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential.
-Numerical simulations have examined this idea with known lensed quasars.
-In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena.
+In the most of discussions upon multiple image lensed quasars, flux ratio anomalies are brought only by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential (in ideal case, i.e.
+no dust extinction, micro lensing, scattering etc.).
+Numerical simulations have examined this idea with known flux anomalous lensed quasars.
+In \citet{Xu14}, they found that substructure cannot expalin for all of these radio flux anomalies.
 Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system.
-The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375.
-They conclude B1555+375 with improper lens model.
-This result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B.
+The rest of them are only few percent likely to have substructure originated flux anomaly, including our target B1555+375.
+They conclude the failure on B1555+375 with improper lens model.
+Their result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B.
 A more complex lens model (e.g.
-include an exponential disk) must be applied on B1555+375.
+include an exponential disk) must be considered for B1555+375.
 
-In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk.
-Our models predict the radio image positions and flux ratio anomaly between components A and B, which the 1-SIE model in \citet{Marlow} fails.
+In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk components.
+Our models predict the radio image positions and also flux ratio anomalies, which the 1-SIE model in \citet{Marlow} fails.
 Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies.
-An edge-on disk with high ellipcity can well explain the observed flux ratios and substructure is not neccessary to presence.
-Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars.
-A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar.
-Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future.
+An edge-on disk with high ellipcity in lens models well explains the observed flux ratios without the presense of substructrues.
+Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
+A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system.
+Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
 One must fully consider non-substructure effects before gathering any statistics or serious analysis.
@@
 Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars.
-Although radio band provides reliable data on position and fluxe of lensed images, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy.
-In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling.
-The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly.
-Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes and can have impacts on statics and derived properties among substructure detection.
-With the first system being analyzed and shown that an edge-on disk can explain its flux ratio anomaly, our follow up will be explore other SHARP systems.
+While radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
+In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling.
+The improvement is even more dramatic in B1555+375.
+With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies.
+Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection.
+With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.

### 2015-04-04 papers/B1555_EdgeOn/B1555_letter.tex
change text in Discussion

@@
 
-In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk components.
-Our models predict the radio image positions and also flux ratio anomalies, which the 1-SIE model in \citet{Marlow} fails.
-Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies.
-An edge-on disk with high ellipcity in lens models well explains the observed flux ratios without the presense of substructrues.
-Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
-A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system.
+In part 3, we present new lens models of B1555+375.
+The most significant difference comparing to previous modelling is a new edge-on disk component.
+With a bulge plus an edge-on disk, our models fairly match the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail.
+Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}.
+Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375.
+An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues.
+This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations.
+It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
+Our discover shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system.
 Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-One must fully consider non-substructure effects before gathering any statistics or serious analysis.
-Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis.
-For the case oringinated by real substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties.
-We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar.
-For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.
+To gather correct statistics, one must fully consider non-substructure effects.
+Otherwise, possible ``false'' substructures detected by flux anomalies can serverly biased the data analysis.
+Even with real substructures presence, lens galaxy structure can still dominate the flux anomalous phenomenon and have impact on estimated mass and also other derived properties.
+We would like to draw attention on this non-substructure effect brought by a large, high ellipcity edge-on disk.
+For precise measurement on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, careful estimation on non-substructure effects are important.
 
 Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars.
-While radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
+Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
 In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling.

### 2015-04-13 papers/B1555_EdgeOn/B1555_letter.tex
Change in paragraph order in Discussion

@@
 \section{Discussion}
-The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies.
-Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample arise from nowaday observation.
-Difficulties emerge in direct detection when searching beyond the Local Group.
-Until now, most of known satellites are at high mass end in the mass function.
-However, the gravitational perturbations from substructures can cause detectable change in surface brightness among lensed images.
-This makes gravitational lensing a powerful tool for searching substructures.
-Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhalo.
-Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function which avoid making assumptions on baryonic matter distribution assoociated with dark matter.
 
-In the most of discussions upon multiple image lensed quasars, flux ratio anomalies are brought only by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential (in ideal case, i.e.
-no dust extinction, micro lensing, scattering etc.).
-Numerical simulations have examined this idea with known flux anomalous lensed quasars.
-In \citet{Xu14}, they found that substructure cannot expalin for all of these radio flux anomalies.
-Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system.
-The rest of them are only few percent likely to have substructure originated flux anomaly, including our target B1555+375.
-They conclude the failure on B1555+375 with improper lens model.
-Their result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B.
-A more complex lens model (e.g.
-include an exponential disk) must be considered for B1555+375.
-
-In part 3, we present new lens models of B1555+375.
-The most significant difference comparing to previous modelling is a new edge-on disk component.
-With a bulge plus an edge-on disk, our models fairly match the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail.
+We present new lens models of B1555+375.
+With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component.
+With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail.
 Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}.
@@
 It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
-Our discover shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system.
-Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-To gather correct statistics, one must fully consider non-substructure effects.
-Otherwise, possible ``false'' substructures detected by flux anomalies can serverly biased the data analysis.
-Even with real substructures presence, lens galaxy structure can still dominate the flux anomalous phenomenon and have impact on estimated mass and also other derived properties.
-We would like to draw attention on this non-substructure effect brought by a large, high ellipcity edge-on disk.
-For precise measurement on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, careful estimation on non-substructure effects are important.
+Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in the strongly lensed system.
 
-Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars.
+The abundance of substructures within galaxy-size haloes has been an undetermined problem in structure formation studies.
+Discrepencies between numerical simulations and observations within the local universe gives two possible interpretations: an alternative structure formation model or a small sample set from nowaday observations.
+Difficulties emerge in direct detection when searching beyond the Local Group.
+Until now, most of known satellites are at high mass end in the mass function.
+However, the gravitational perturbation from substructures can cause detectable change in surface brightness among lensed images.
+This makes gravitational lensing a powerful tool for searching substructures.
+Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhaloes.
+Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function, avoid making assumptions on baryonic matter distribution assoociated with dark matter.
+
+Given the assumption that lens galaxy has smooth gravitational potential, only substructure perturbations can cause flux ratio anomalies (in ideal case, i.e.
+no dust extinction, micro lensing, scattering etc.).
+Numerical simulations demostrate this idea with known flux anomalous lensed quasars.
+In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies.
+By adding subhaloes on to those systems, only one out of six lens systems reproduce the flux anomalies.
+The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375.
+\citet{Xu14} conclude the failure on B1555+375 due to improper lens models.
+This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.
+
+From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
+include an exponential disk), rather than just assuming smooth potential.
+Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
+It is important to fully consider non-substructure effects before any statistical analysis .Otherwise, possible ``false'' substructures detected by flux anomalies can serverly bias the data analysis.
+Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena and impacts on estimated mass and also other derived properties.
+We would like to draw attention to this non-substructure effect caused by a large, high ellipcity edge-on disk.
+For precise measurements on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.
+
+Our results also show that multi-wavelength imagimg is helpful to explore flux anomalous lensed quasars.
 Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
@@
 The improvement is even more dramatic in B1555+375.
-With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies.
-Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection.
-With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
+With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly.
+Lack of knowledge of the lens galaxies can lead to improper lens modelling and bias to statistics among substructure detection.
+With the first system analyzing and showing that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
+An edge-on disk structure may also able to expalin the flux ratio anomalies of these systems.\\
 

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
Edits to modeling section of B1555 paper

@@
 HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
-in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
+in the F160W band, and Keck AO imaging in the $K^\prime$ band.
+\label{fig:multiband}}
 %
@@
 data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
-MATT], producing final drizzled images with pixel scales of
-50~mas.  The reduced images are shown in Figure~??.  The lens system
-is not detected at high significance in the optical bands, but is
-clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
-stands out in the NICMOS image.
+  MATT], producing final drizzled images with pixel scales of 50~mas.
+The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
+system is not detected at high significance in the optical bands, but
+is clearly seen in the NICMOS $F160W$ image.  The edge-on lensing
+galaxy stands out in the NICMOS image.
 
@@
 
-To model B1555+375, we use the lens modelling code {\tt glafic}
-\citep{Oguri}.  The inputs to the model are the observed image positions
-and flux densities measured by the radio observations of \citet{Marlow}.
-These authors present a singular isothermal ellipsoid (SIE) model that
-provides the first fit to the image positions but
-does not reproduce the strong flux ratio anomaly between components A and B.
-(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
-imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
-with position angle $\approx 10$ degree.
-The detection of edge-on disk also explain the missing images B \& D in near-infrared (Fig 1, right).
-Image B \& D very likely are extincted by the edge-on disk since the images have the same orientation with the disk.
+To model B1555+375, we use the lens modeling code {\tt glafic}
+\citep{Oguri}.  The inputs to the model are the observed image
+positions and flux densities measured by the radio observations of
+\citet{Marlow}.  These authors present a singular isothermal ellipsoid
+(SIE) model that provides the first fit to the image positions but
+does not reproduce the strong flux ratio anomaly between components A
+and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow}.  Although
+the flux ratio anomaly that is observed in the radio data may be
+caused by substructure in the lensing galaxy, our high-resolution near
+infrared imaging suggests another explanation.  In both the $K^\prime$
+band adaptive optics data and the HST imaging (two rightmost panels in
+Fig. 1), the lensing galaxy has a clear edge-on disk component with a
+position angle of $\approx 10$ degree.  We therefore model the system
+with a disk component in order to see if such a model can explain the
+flux ratio anomaly without the need for substructure.  The edge on
+disk may also explain the system morphology that is observed in the
+near infrared imaging.  In particular, neither image B nor image D is
+detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
+these lensed images lie on or close to the edge-on disk.  Thus, strong
+extinction in the disk could cause the lack of detection of these
+images.
 
-By adding a disk component, we apply our new discover from AO image to the
-B1555+375 modelling. The first model consists of an SIE bulge
-and an exponential edge-on disk (SIE+expdisk). And the second model
-consists of two SIE mass profiles (2-SIE), for bulge and disk
-respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
-of these models predict fairly matched results with the radio
-observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
-in Figure 3, Table 3 \& 4.
+We have created two separate models of the lensing potential.  In the
+first we treat the lens as a SIE bulge and an exponential edge-on disk
+(SIE+expdisk).  In the second model the disk is represented as a very
+elongated SIE component (2-SIE).  The lens system is red, with a
+strong jump in flux between the F814W (roughly I) and F160W (roughly
+H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
+$z_\ell = 1.0$ and a source redshift of $z_s =$?? [{\bf WHAT VALUE DID
+    WE USE??}].  The full best-fit parameters are shown in Table
+2. Both of these models predict fairly matched results with the radio
+observation, and the 2-SIE model has a better performance in flux
+ratios. The comparison of observation and our lens modelling is given
+in Figure 3 and Tables 3 \& 4.
 
@@
 \includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
+\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
+with contours from the MERLIN observation of \citet{Marlow} overlaid.
 %

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
update Table2 paras (SIE+expdisk only, zl=1.0)

@@
 H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
-$z_\ell = 1.0$ and a source redshift of $z_s =$?? [{\bf WHAT VALUE DID
-    WE USE??}].  The full best-fit parameters are shown in Table
+$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
 2. Both of these models predict fairly matched results with the radio
@@
 $y_2$	&$-0.2502$	& $-0.1833$	  \\
-$\sigma_1$	&$92.90$ &	$95.05$	  \\
-$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
+$\sigma_1$	&$141.3$ &	$95.05$	  \\
+$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$81.36$ 	 \\  
 $e_1$	& $0.27$	& $0.27$ \\  

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
Update mass term in Table 2 due to redshift change
Text change in Discussion

@@
 $y_2$	&$-0.2502$	& $-0.1833$	  \\
-$\sigma_1$	&$141.3$ &	$95.05$	  \\
-$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$81.36$ 	 \\  
+$\sigma_1$	&$141.3$ &	$144.6$	  \\
+$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$123.8$ 	 \\  
 $e_1$	& $0.27$	& $0.27$ \\  
@@
 It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
-Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in the strongly lensed system.
+Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in a strongly lensed system.
 
@@
 In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies.
-By adding subhaloes on to those systems, only one out of six lens systems reproduce the flux anomalies.
+By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies.
 The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375.
-\citet{Xu14} conclude the failure on B1555+375 due to improper lens models.
+\citet{Xu14} conclude the failure on B1555+375 is due to improper lens models.
 This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.
@@
 Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-It is important to fully consider non-substructure effects before any statistical analysis .Otherwise, possible ``false'' substructures detected by flux anomalies can serverly bias the data analysis.
-Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena and impacts on estimated mass and also other derived properties.
-We would like to draw attention to this non-substructure effect caused by a large, high ellipcity edge-on disk.
-For precise measurements on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.
+If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis.
+Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena.
+For precise measurements on substurcture population, mass function, and any derived properties from strongly lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.
+We would like to draw attention to this edge-on disk orginated flux anomalies due to its impacts on substructure searching.
 
-Our results also show that multi-wavelength imagimg is helpful to explore flux anomalous lensed quasars.
+Our results also demostrate that multi-wavelength imaging is helpful to explore flux anomalous lensed quasars.
 Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
@@
 With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly.
-Lack of knowledge of the lens galaxies can lead to improper lens modelling and bias to statistics among substructure detection.
-With the first system analyzing and showing that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
+Lack of knowledge of lens galaxies can lead to improper lens modelling and bias to statistics among substructure detections.
+With the first system analyzing and finding that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also able to expalin the flux ratio anomalies of these systems.\\
+An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\
 

### 2015-04-20 papers/B1555_EdgeOn/B1555_letter.tex
update 2-SIE paras to text
Small updates to text

@@
 have a different origin than substructure. 
-
+%
 An alternative method for
@@
 perspective on current constraints based on flux ratio anomalies.  In
-this paper, we explore the alternative idea that flux ratio anomalies
-are not related to the presence of substructure but originate in a
+this paper, we explore the idea that not all flux ratio anomalies are
+related to the presence of substructure, but that some originate in a
 more complex lens galaxy mass distribution than initially
 considered. To this end we use new infra-red data from the Strong
-lensing at High Angular Resolution Program(SHARP). The main goal of
-the SHARP project is to re-observe known quadruple and Einstein ring
-lens systems at a much higher angular resolution by making use of the
-Keck adaptive optics (AO) telescope and large interferometric arrays
-\citep{SHARP12,V12} . In particular, to better understand the cause of
-flux ratio anomalies in strong lens systems we focus on the lens
-modelling of the lens system B1555+375 (included in both the
-observational and theoretical analysis of \citet{Dalal2002} and
-\citet{Xu14}, respectively) by making use of the new information
-obtained from the latest SHARP infrared imaging. The paper is
-organized as follows: the latest SHARP data is introduced in section
-2; in section 3 we present the lens model while the results of this
-analysis and their implication are discussed in section 4.
+lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
+in prep). The main goal of the SHARP project is to re-observe known
+quadruple and Einstein ring lens systems at a much higher angular
+resolution by making use of observations with (1) adaptive optics (AO)
+on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
+interferometric arrays \citep{SHARP12,V12}. In particular, to better
+understand the causes of flux ratio anomalies in gravitational lenses
+we focus on the B1555+375 lens system\citep{Marlow}.  This system was
+discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
+has a pair of merging images that show a strong flux ratio anomaly at
+radio wavelengths.  Follow-up observations ruled out radio propagation
+effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
+system was included in both the observational and theoretical analysis
+of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
+mass distribution is of key importantce.  Our analysis makes use of
+the new information obtained from the latest SHARP infrared imaging.
+The paper is organized as follows: the latest SHARP data are
+introduced in section 2; in section 3 we present the lens model while
+the results of this analysis and their implications are discussed in
+section 4.
 
@@
 $\sigma_1$ &$141.3$     & $144.6$ \\
-$M_{tot} / \sigma_2$& $3.59\times 10^{10} $  &$123.8$ 	 \\  
 $e_1$	  & $0.27$	& $0.27$ \\
 $\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
+$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
+$\sigma_2$ & ...        &$123.8$ \\  
 $e_2$	  &$0.84$	&$0.83$  \\
 $\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
-$r_e$	& $0.20 ''$ &  -- \\
+$r_e$	  & $0.20 ''$ &  ... \\
 \hline
@@
 \medskip
-Comparision between radio data and model-predicted flux ratios. Radio observation data is quoted from Table 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.
+Comparision between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.
 
@@
 
-We present new lens models of B1555+375.
-With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component.
-With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail.
-Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}.
-Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375.
-An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues.
-This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations.
-It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures.
-Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in a strongly lensed system.
+In our models based on the new imaging from the SHARP $K^{\prime}$
+band observations, the most significant difference in comparison to
+previous modelling is a new edge-on disk component. With a bulge plus
+an edge-on disk, our models produce matches to both the radio image
+positions and flux ratio anomalies, while models with only one SIE
+component \citep{Marlow,Xu14} fail to reproduce the fluxes
+correctly. Our successful modelling indicates that the
+kiloparsec-scale structure of lens galaxy itself is sufficient to
+explain the flux ratio anomalies in B1555+375, without any need to
+invoke the presense of substructrue. This breaks the idea that in
+strongly lensed quasars, radio flux ratio anomalies are most likely
+originated from substructure perturbations. It is worth noticing not
+all of flux ratio anomalies in lensed quasars indicate the existence
+of substructures. Our discovery shows a complex lens galaxy mass
+distribution can dominate flux ratio anomalous phenomena in a strongly
+lensed system.
 

### 2015-04-21 papers/B1555_EdgeOn/B1555_letter.tex
update 2-SIE paras in text
Small addition to B1555 discussion

@@
 \hline
-$x_1$  	  & $-0.1883$	& $-0.1809$  \\
-$y_1$	  &$-0.1923$	&$-0.1702$  \\
-$x_2$	  &$-0.1615$ 	&$-0.1592$  \\
-$y_2$	  &$-0.2502$	& $-0.1833$  \\
-$\sigma_1$ &$141.3$     & $144.6$ \\
+$x_1$  	  & $-0.1883$	& $-0.1813$  \\
+$y_1$	  &$-0.1923$	&$-0.1695$  \\
+$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
+$y_2$	  &$-0.2502$	& $-0.1843$  \\
+$\sigma_1$ &$141.3$     & $144.9$ \\
 $e_1$	  & $0.27$	& $0.27$ \\
@@
 $M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
-$\sigma_2$ & ...        &$123.8$ \\  
+$\sigma_2$ & ...        &$123.5$ \\  
 $e_2$	  &$0.84$	&$0.83$  \\
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
+B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0481$  \\  
 C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1609$ &$-0.3678$  & $-0.1618$    &  $+0.3680$ \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1620$    &  $+0.3682$ \\  
 \hline
@@
 \section{Discussion}
+
+Gravitational lensing is [one of] the most powerful methods for
+studying substructure in galaxies outside of the Local Universe, and
+the flux ratio anomaly systems are a key aspect of these
+investigations.  However, before using the flux ratio anomaly in any
+given system to investigate structure formation and the properties of
+dark matter, it is critical to eliminate other possible explanations
+for the difference between the observed and expected fluxes.  It
+is for this reason that much of the effort in the flux-ratio technique
+has been focused on radio-loud lens systems.  At these wavelengths,
+dust extinction and microlensing effects should be minimal (although
+see Koopmans et al. ?? for a rare example of radio microlensing).
+Radio propagation effects can  affect radio fluxes, as is clearly
+shown in the B0128 system [REF??].  However, these propagation effects
+can be disentangled from substructure lensing because they have well
+known dependencies on wavelength. [COMMENTS ABOUT B1555 AND OTHER
+RADIO-LOUD SYSTEMS].
 

### 2015-04-21 papers/B1555_EdgeOn/B1555_letter.tex
Change in Discussion and also new ref

@@
 with a disk component in order to see if such a model can explain the
-flux ratio anomaly without the need for substructure.  The edge on
+flux ratio anomaly without the need for substructure.  The edge-on
 disk may also explain the system morphology that is observed in the
@@
 
-We have created two separate models of the lensing potential.  In the
+As a first trail of modelling, we create a single SIE model to 
+justify the perforamnce of a simple lensing potential. Like previous studies
+\citep{Marlow, Xu14}, flux anomaly in B1555+375 cannot be predcited
+with a single elliptical lensing potential. 
+We then create two separate models of the lensing potential.  In the
 first we treat the lens as a SIE bulge and an exponential edge-on disk
@@
 dust extinction and microlensing effects should be minimal (although
-see Koopmans et al. ?? for a rare example of radio microlensing).
+see \citet{K2000} for a rare example of radio microlensing).
 Radio propagation effects can  affect radio fluxes, as is clearly
-shown in the B0128 system [REF??].  However, these propagation effects
+shown in the B0128 system [REF??, In Dandan's paper?].  However, these propagation effects
 can be disentangled from substructure lensing because they have well
 known dependencies on wavelength. [COMMENTS ABOUT B1555 AND OTHER
-RADIO-LOUD SYSTEMS].
+RADIO-LOUD SYSTEMS, from K03 paper].
 
@@
 
-The abundance of substructures within galaxy-size haloes has been an undetermined problem in structure formation studies.
-Discrepencies between numerical simulations and observations within the local universe gives two possible interpretations: an alternative structure formation model or a small sample set from nowaday observations.
-Difficulties emerge in direct detection when searching beyond the Local Group.
-Until now, most of known satellites are at high mass end in the mass function.
-However, the gravitational perturbation from substructures can cause detectable change in surface brightness among lensed images.
-This makes gravitational lensing a powerful tool for searching substructures.
-Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhaloes.
-Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function, avoid making assumptions on baryonic matter distribution assoociated with dark matter.
+Recent studies on numerical simulation support our discover on B1555+375.
+In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalous phenomena in radio loud lensed systems.
+By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies.
+The rest of them are unlikely (only few percent likelihood) to have substructure originated flux anomalies, including our target B1555+375.
+\citet{Xu14} conclude the failure in predicting fluxes of those lens systems is due to improper lens models.
+Their results are consistent with the SHARP $K^{\prime}$ band observations, which in B1555+375, an edge-on disk lies cross the radio merging double.
+Here we would like to draw attention to the possible impacts on substructure searching from the enge-on disk orginated flux anomalies.
+In SHARP observations, we find B1555+375 is not the only system having edge-on disk detection in high resolution near-infrared imaging (see Fig 4).
+It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars.
+It may be worth considering an upper limit of flux anomalies fraciton from observation results to avoid over estimate the number of substructure detections.
+Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
+For further analysis on substurcture population, mass function etc., it is always important to rule out other non-substructure effects.
 
-Given the assumption that lens galaxy has smooth gravitational potential, only substructure perturbations can cause flux ratio anomalies (in ideal case, i.e.
-no dust extinction, micro lensing, scattering etc.).
-Numerical simulations demostrate this idea with known flux anomalous lensed quasars.
-In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies.
-By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies.
-The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375.
-\citet{Xu14} conclude the failure on B1555+375 is due to improper lens models.
-This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.
+In this paper we also demostrate the power of combining multiwavelength high resolution data.
+All the flux anomalous lensed quasars are radio loud systems and are first discovered in radio observations.
+Radio data provides reliable information on positions and fluxes of lensed images but often unable to detect lens galaxies.
+Since lens galaxies are mostly in low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens gaxies and obtain prior on underlying mass distribution.
+In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling.
+The improvement is even more dramatic in B1555+375.
+With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375.
+This new discovered edge-on disk provides a strong hint to our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375.
+Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models.
+Modelling with only four image positions from radio data can also cause a lot of degeneracy.
+With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems.
+In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
+An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\
 
-From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
+%From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
 include an exponential disk), rather than just assuming smooth potential.
@@
 We would like to draw attention to this edge-on disk orginated flux anomalies due to its impacts on substructure searching.
-
-Our results also demostrate that multi-wavelength imaging is helpful to explore flux anomalous lensed quasars.
-Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy.
-In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling.
-The improvement is even more dramatic in B1555+375.
-With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly.
-Lack of knowledge of lens galaxies can lead to improper lens modelling and bias to statistics among substructure detections.
-With the first system analyzing and finding that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems.
-In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\
 

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
Rewrite Discussion for new comments

@@
 \newcommand{\nat}[1]{Nature}
+\newcommand{\aap}{A\&A}
 
@@
 account completeness corrections arising from the limited sky coverage
-imposed by the Galactic Plane.  This is the famous ``missing
+imposed by the Galactic Plane. [NEED REF]  This is the famous ``missing
 satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
@@
 Indeed, small perturbations in the gravitational potential are
-sufficient to bring flux ratio anomalies in strong lensed systems.
+sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
 Moreover, unlike in the optical or infrared, in the radio band, lensed
@@
 the surface brightness distribution of extended arcs and Einstein ring
-has been introduced by \citet{K05,V09}. Interestingly, the fraction of
+has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
 substructure measured with this \emph{gravitational imaging technique}
@@
 in Figure 3 and Tables 3 \& 4.
+[WHY NO EXTERNAL SHEAR?---WE THINK WITH ONLY RADIO DATA ITS LACK OF CONSTRAINT]
+
+[WHERE DO WE PUT MODEL CHI-SQUARE??]
 
@@
 Radio propagation effects can  affect radio fluxes, as is clearly
-shown in the B0128 system [REF??, In Dandan's paper?].  However, these propagation effects
+shown in the B0128 system \citep{B04}.  However, these propagation effects
 can be disentangled from substructure lensing because they have well
-known dependencies on wavelength. [COMMENTS ABOUT B1555 AND OTHER
-RADIO-LOUD SYSTEMS, from K03 paper].
+known dependencies on wavelength. \citet{KD04} examine all eight radio loud flux anomalous lenses: MG 0414+0534, B0712+472,  B1359+154, B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265. 
+They find no strong wavelength dependence in the flux ratios of all these systems and rule out the possible affects from radio propagation.
 
@@
 an edge-on disk, our models produce matches to both the radio image
-positions and flux ratio anomalies, while models with only one SIE
+positions and the flux ratio, while models with only one SIE
 component \citep{Marlow,Xu14} fail to reproduce the fluxes
@@
 strongly lensed quasars, radio flux ratio anomalies are most likely
-originated from substructure perturbations. It is worth noticing not
-all of flux ratio anomalies in lensed quasars indicate the existence
-of substructures. Our discovery shows a complex lens galaxy mass
+originated from substructure perturbations. Our discovery shows a complex lens galaxy mass
 distribution can dominate flux ratio anomalous phenomena in a strongly
@@
 
-Recent studies on numerical simulation support our discover on B1555+375.
-In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalous phenomena in radio loud lensed systems.
-By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies.
-The rest of them are unlikely (only few percent likelihood) to have substructure originated flux anomalies, including our target B1555+375.
-\citet{Xu14} conclude the failure in predicting fluxes of those lens systems is due to improper lens models.
-Their results are consistent with the SHARP $K^{\prime}$ band observations, which in B1555+375, an edge-on disk lies cross the radio merging double.
-Here we would like to draw attention to the possible impacts on substructure searching from the enge-on disk orginated flux anomalies.
-In SHARP observations, we find B1555+375 is not the only system having edge-on disk detection in high resolution near-infrared imaging (see Fig 4).
+From theoretical perspective, \citet{Xu14}  find that substructures cannot expalin radio flux anomalies in all these lenses.
+By adding subhaloes from numerical simulations on to these systems, only one out of eight radio loud systems reproduces the flux anomalies.
+The rest of them are unlikely (only $1 \% - 4 \%$ probability) to have substructure originated flux anomalies, including our target B1555+375.
+Among those eight radio lenses, B1555+375 is one of the most anomalous systems, but it is also one of the most challenging systems to explain by substructures.
+\citet{Xu14} conclude the failure in predicting flux ratios is due to oversimplified/improper lens modelling.
+They also outline that the SIE component and the external shear are orthogonal indicates a possible missing ingredient in lens model.
+Their results are consistent with the SHARP $K^{\prime}$ band observations, which an edge-on disk lies cross the radio merging double in B1555+375.
+B1555+375 is not the only system having edge-on disk detection in SHARP near-infrared AO imaging (see Fig 4).
+We would like to draw attention to the possible impacts on substructure searching from this enge-on disk orginated flux anomalies.
 It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars.

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
add opt procedure

@@
 As a first trail of modelling, we create a single SIE model to 
-justify the perforamnce of a simple lensing potential. Like previous studies
-\citep{Marlow, Xu14}, flux anomaly in B1555+375 cannot be predcited
-with a single elliptical lensing potential. 
+justify the perforamnce of a simple lensing potential. Consistent with previous studies
+\citep{Marlow, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
 We then create two separate models of the lensing potential.  In the
@@
 H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
-$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
+$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.
+Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{marlow} as the start point of the bulge component and the source position.
+2) Let all parameters without priors vary to reach a temporary best-fit.
+3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors).
+4) Let all parameters vary to reach the final optimal model.
+The full best-fit parameters are shown in Table
 2. Both of these models predict fairly matched results with the radio

### 2015-04-22 python/sub.py

@@ -1,12 +1,15 @@
 from astropy.io import fits
 
-hdulist=fits.open('./glafic/B1555_try6.fits')
+#hdulist=fits.open('./glafic/out_image.fits')
+hdulist=fits.open('model_convolved.fits')
 model=hdulist[0].data
 
-hdulist2=fits.open('./B1555/B1555_nirc2_n_Kp_6x6.fits')
+#hdulist2=fits.open('./B1555/B1555_nirc2_n_Kp_6x6.fits')
+hdulist2=fits.open('B1555_cutout_120x120pix.fits')
+
 image=hdulist2[0].data
 
 res=image-model
 
 hdu=fits.PrimaryHDU(res)
-hdu.writeto('residue.fits')
+hdu.writeto('Simona_residue.fits')

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
Edits to discussion section

@@
 dark matter, it is critical to eliminate other possible explanations
-for the difference between the observed and expected fluxes.  It
-is for this reason that much of the effort in the flux-ratio technique
+for the difference between the observed and expected fluxes.  It is
+for this reason that much of the effort in the flux-ratio technique
 has been focused on radio-loud lens systems.  At these wavelengths,
-dust extinction and microlensing effects should be minimal (although
-see \citet{K2000} for a rare example of radio microlensing).
-Radio propagation effects can  affect radio fluxes, as is clearly
-shown in the B0128 system \citep{B04}.  However, these propagation effects
-can be disentangled from substructure lensing because they have well
-known dependencies on wavelength. \citet{KD04} examine all eight radio loud flux anomalous lenses: MG 0414+0534, B0712+472,  B1359+154, B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265. 
-They find no strong wavelength dependence in the flux ratios of all these systems and rule out the possible affects from radio propagation.
+dust extinction and microlensing effects should be minimal
+\citep[although see][for a rare example of radio microlensing]{K2000}.
+Radio propagation effects can affect radio fluxes, as is clearly shown
+in the B0128+437 system \citep{B04}.  However, these propagation
+effects can be disentangled from substructure lensing because they
+have well known dependencies on wavelength. \citet{KD04} examine all
+eight radio loud flux anomalous lenses besides B0128=437, namely: MG
+0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
+B1933+503, and B2045+265.  They find no strong wavelength dependence
+in the flux ratios of all these systems and therefore rule out radio
+propagation effects as significant contributors to the observed
+anomalies.
 
@@
 explain the flux ratio anomalies in B1555+375, without any need to
-invoke the presense of substructrue. This breaks the idea that in
-strongly lensed quasars, radio flux ratio anomalies are most likely
-originated from substructure perturbations. Our discovery shows a complex lens galaxy mass
-distribution can dominate flux ratio anomalous phenomena in a strongly
-lensed system.
+invoke the presense of substructure.
 
-From theoretical perspective, \citet{Xu14}  find that substructures cannot expalin radio flux anomalies in all these lenses.
-By adding subhaloes from numerical simulations on to these systems, only one out of eight radio loud systems reproduces the flux anomalies.
-The rest of them are unlikely (only $1 \% - 4 \%$ probability) to have substructure originated flux anomalies, including our target B1555+375.
-Among those eight radio lenses, B1555+375 is one of the most anomalous systems, but it is also one of the most challenging systems to explain by substructures.
-\citet{Xu14} conclude the failure in predicting flux ratios is due to oversimplified/improper lens modelling.
-They also outline that the SIE component and the external shear are orthogonal indicates a possible missing ingredient in lens model.
-Their results are consistent with the SHARP $K^{\prime}$ band observations, which an edge-on disk lies cross the radio merging double in B1555+375.
-B1555+375 is not the only system having edge-on disk detection in SHARP near-infrared AO imaging (see Fig 4).
-We would like to draw attention to the possible impacts on substructure searching from this enge-on disk orginated flux anomalies.
-It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars.
-It may be worth considering an upper limit of flux anomalies fraciton from observation results to avoid over estimate the number of substructure detections.
-Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-For further analysis on substurcture population, mass function etc., it is always important to rule out other non-substructure effects.
+% This breaks the idea that in strongly lensed quasars, radio flux ratio
+% anomalies are most likely originated from substructure
+% perturbations. Our discovery shows a complex lens galaxy mass
+% distribution can dominate flux ratio anomalous phenomena in a strongly
+% lensed system.
+
+From a theoretical perspective, \citet{Xu14} find that substructures
+cannot explain the observed radio flux anomalies in all the lenses
+that were considered. By adding subhaloes from numerical simulations
+on to these systems, only one out of eight radio loud systems
+reproduces the level of flux anomalies seen in the data.  The rest of
+them are unlikely (only $1 \% - 4 \%$ probability) to have flux
+anomalies produced by substructure, including our target B1555+375.
+In fact, among those eight radio lenses, B1555+375 is one of the most
+anomalous systems, but it is also one of the most challenging systems
+to explain by substructures. \citet{Xu14} conclude the failure in
+predicting flux ratios is due to oversimplified/improper lens
+modelling. They also point out that the SIE component and the external
+shear in their model are orthogonal, indicating a possible missing
+ingredient in lens model. Their results are consistent with the SHARP
+$K^{\prime}$ band observations, in which an edge-on disk crosses the
+radio merging double.
+
+Additional near-infrared AO imaging from SHARP shows that B1555+375 is
+not the only system having a significant disk component detection in
+the lensing galaxy (see Fig 4).  These systems will be investigated in
+future work, but the images alone strongly suggest that other lens
+systems have similar links between flux-ratio anomalies and disk
+components.  Although the number of radio loud flux anomalous lensed
+quasars remains small, a new technique using narrow-line emission
+regions will enlarge the sample and bring statistical perspective on
+substructures in the near future \citep{N14}. It is well known (e.g,
+Kochanek 199??) that lens models based only on the locations of lensed
+quasar/AGN images have large degeneracies.  Therefore, before
+concluding that the flux ratios in any given lens system are a result
+of substructure, it is critical to explore a range of smooth models
+that are informed by additional observations or to do a comprehensive
+analysis such as that conducted by \citet{Xu14}.  Otherwise, derived
+substructure fractions should be considered as upper limits.
+
+% We would like to draw attention to the possible impacts on
+% substructure searching from this enge-on disk orginated flux
+% anomalies. It is a sign that researchers should be careful about the
+% flux anomalies fraction in lensed quasars. It may be worth considering
+% an upper limit of flux anomalies fraciton from observation results to
+% avoid over estimate the number of substructure detections. For further
+% analysis on substurcture population, mass function etc., it is always
+% important to rule out other non-substructure effects.
+
+[PERHAPS REARRANGE THE FOLLOWING INTO A CONCLUSIONS SECTION??]
 
@@
 With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375.
-This new discovered edge-on disk provides a strong hint to our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375.
+This new discovered edge-on disk provides a strong prior for our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375.
 Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models.
@@
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.\\
+An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.
 

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
More small edits to the text

@@
 understand the causes of flux ratio anomalies in gravitational lenses
-we focus on the B1555+375 lens system\citep{Marlow}.  This system was
+we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
 discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
@@
 Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
-contours from the MERLIN radio observations of \citet{Marlow}
+contours from the MERLIN radio observations of \citet{Marlow99}
 overlaid.  There are several notable features in the Keck AO data.
@@
 positions and flux densities measured by the radio observations of
-\citet{Marlow}.  These authors present a singular isothermal ellipsoid
+\citet{Marlow99}.  These authors present a singular isothermal ellipsoid
 (SIE) model that provides the first fit to the image positions but
 does not reproduce the strong flux ratio anomaly between components A
-and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow}.  Although
+and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  Although
 the flux ratio anomaly that is observed in the radio data may be
@@
 justify the perforamnce of a simple lensing potential. Consistent with previous studies
-\citep{Marlow, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
+\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
 We then create two separate models of the lensing potential.  In the
@@
 $z_\ell = 1.0$ and a source redshift of $z_s =1.5$.
-Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{marlow} as the start point of the bulge component and the source position.
+Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position.
 2) Let all parameters without priors vary to reach a temporary best-fit.
@@
 in Figure 3 and Tables 3 \& 4.
-[WHY NO EXTERNAL SHEAR?---WE THINK WITH ONLY RADIO DATA ITS LACK OF CONSTRAINT]
+[WHY NO EXTERNAL SHEAR?---WITH ONLY THE RADIO POSITIONS AND FLUXES AS
+CONSTRAINTS, ADDING SHEAR WOULD MAKE THE PROBLEM EVEN MORE UNDERCONSTRAINED]
 
@@
 \caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
-with contours from the MERLIN observation of \citet{Marlow} overlaid.
+with contours from the MERLIN observation of \citet{Marlow99} overlaid.
 %
@@
 Comparision between radio and model-predicted lensed image positions.
-Observation data quoted from Table 2 in \citet{Marlow}.
+Observation data quoted from Table 2 in \citet{Marlow99}.
 Position offsets are in unit of arcsec.
@@
 \medskip
-Comparision between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.
+Comparision between radio data and model-predicted flux ratios.
+The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
+1-SIE model is quoted from Tabel 5 in \citet{Marlow99}.
 
@@
 positions and the flux ratio, while models with only one SIE
-component \citep{Marlow,Xu14} fail to reproduce the fluxes
+component \citep{Marlow99,Xu14} fail to reproduce the fluxes
 correctly. Our successful modelling indicates that the

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
update of Simona's change

@@
 %\usepackage[nottoc]{tocbibind}
+\setlength{\topmargin}{-1.2cm}
 
@@
 A common feature of simulations of structure formation is the presence
-of thousands of subhaloes that are associated with larger mass haloes.
+of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
 However, observations of the Local Group find many fewer satellite
@@
 account completeness corrections arising from the limited sky coverage
-imposed by the Galactic Plane. [NEED REF]  This is the famous ``missing
-satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
+imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies}. [NEED REF]  
+This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
 understand this discrepancy, it is imperative to build up a large
 sample of satellites/subhaloes in galaxies outside the Local Group.
-This process is challenging due to the faintness of the satellite
+{\bf However,} this process is challenging due to the faintness of the satellite
 galaxies.  Furthermore, lower-mass satellites may not be able to
@@
 It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
-%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other.
-These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness.
 Indeed, small perturbations in the gravitational potential are
@@
 the detection of substructure in gravitational lens galaxies based on
-the surface brightness distribution of extended arcs and Einstein ring
+the surface brightness distribution of extended arcs and Einstein rings
 has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
@@
 perspective on current constraints based on flux ratio anomalies.  In
-this paper, we explore the idea that not all flux ratio anomalies are
+this {\bf letter}, we explore the idea that not all flux ratio anomalies are
 related to the presence of substructure, but that some originate in a
@@
 of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
-mass distribution is of key importantce.  Our analysis makes use of
+mass distribution is of key importance.  Our analysis makes use of
 the new information obtained from the latest SHARP infrared imaging.
@@
 section 4.
-
-%However, only small number of flux ratio anomalous systems in \simona{the} radio are \simona{currently} avaliable.
-Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach \simona{is to} seek out more flux ratio anomalous systems \simona{using} narrow-line quasar emission \citep{N14}.
-%	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems.
-\citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring.
-Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study.
-On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems.
-The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems.
-%	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}.
-We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations.
-%To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging.
-We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.
 
@@
 As a first trail of modelling, we create a single SIE model to 
-justify the perforamnce of a simple lensing potential. Consistent with previous studies
+justify the performance of a simple lensing potential. Consistent with previous studies
 \citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
@@
 in Figure 3 and Tables 3 \& 4.
-[WHY NO EXTERNAL SHEAR?---WITH ONLY THE RADIO POSITIONS AND FLUXES AS
-CONSTRAINTS, ADDING SHEAR WOULD MAKE THE PROBLEM EVEN MORE UNDERCONSTRAINED]
-
-[WHERE DO WE PUT MODEL CHI-SQUARE??]
+{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
+to constrain such a model.
+However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e.
+shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}
 
@@
 
-Comparision between radio and model-predicted lensed image positions.
+Comparison between radio and model-predicted lensed image positions.
 Observation data quoted from Table 2 in \citet{Marlow99}.
@@
 
-Gravitational lensing is [one of] the most powerful methods for
+Gravitational lensing is, {\bf at present,} the most powerful tool for
 studying substructure in galaxies outside of the Local Universe, and
@@
 dark matter, it is critical to eliminate other possible explanations
-for the difference between the observed and expected fluxes.  It is
-for this reason that much of the effort in the flux-ratio technique
+for the difference between the observed and expected fluxes{\bf, such as propagation effects and assumptions on the mass distribution of the lens galaxy}.  
+It is for this reason that much of the effort in the flux-ratio technique
 has been focused on radio-loud lens systems.  At these wavelengths,
@@
 
-In our models based on the new imaging from the SHARP $K^{\prime}$
-band observations, the most significant difference in comparison to
-previous modelling is a new edge-on disk component. With a bulge plus
-an edge-on disk, our models produce matches to both the radio image
-positions and the flux ratio, while models with only one SIE
-component \citep{Marlow99,Xu14} fail to reproduce the fluxes
-correctly. Our successful modelling indicates that the
-kiloparsec-scale structure of lens galaxy itself is sufficient to
-explain the flux ratio anomalies in B1555+375, without any need to
-invoke the presense of substructure.
-
-% This breaks the idea that in strongly lensed quasars, radio flux ratio
-% anomalies are most likely originated from substructure
-% perturbations. Our discovery shows a complex lens galaxy mass
-% distribution can dominate flux ratio anomalous phenomena in a strongly
-% lensed system.
+{\bf In this letter, we focus on the effect of more complicated mass distributions for the lens galaxy on flux ratio anomalies.
+Traditionally, flux anomalous lensed quasars are radio loud systems that are firstly discovered in radio observations.
+While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies.
+Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux ratio anomaly.
+Since lens galaxies are mostly located at low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens galaxies and obtain useful prior information  
+on the underlying mass distribution.
+Indeed \citet{SHARP12} has shown that high resolution IR imaging can help to significantly improve the precision of the lens modelling.
+This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging, has allowed us to detect, for the fist time, the presence of an edge-on disk.
+This new discovered edge-on disk provides a strong prior for our lens modelling.
+With a bulge plus an edge-on disk, our models produce matches to both the radio image
+positions and their flux ratio, while models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly. Our successful modelling indicates that the
+kiloparsec-scale structure of the lens galaxy itself is sufficient to explain the flux ratio anomalies in B1555+375, without any need to invoke the presence of substructure.  }
 
@@
 not the only system having a significant disk component detection in
-the lensing galaxy (see Fig 4).  These systems will be investigated in
+the lensing galaxy.  These systems will be investigated in
 future work, but the images alone strongly suggest that other lens
@@
 
+\section{Conclusions}
+{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure.
+Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375 we have identified the existence of a previously undetected edge-on disk.
+By including this disk in the mass model of the lens galaxy we find a good fit for both the positions and flux ratios of the lensed images.
+Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies.
+We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias.
+Finally, our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects.
+In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.}
+
+%.
+Modelling with only four image positions from radio data can also cause a lot of degeneracy.
+With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems.
+In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
+An edge-on disk structure may also be able to explain the flux ratio anomalies of these systems.
+ %From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
+include an exponential disk), rather than just assuming smooth potential.
+Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
+If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis.
+% This breaks the idea that in strongly lensed quasars, radio flux ratio
+% anomalies are most likely originated from substructure
+% perturbations. Our discovery shows a complex lens galaxy mass
+% distribution can dominate flux ratio anomalous phenomena in a strongly
+% lensed system.
 % We would like to draw attention to the possible impacts on
@@
 
-[PERHAPS REARRANGE THE FOLLOWING INTO A CONCLUSIONS SECTION??]
-
-In this paper we also demostrate the power of combining multiwavelength high resolution data.
-All the flux anomalous lensed quasars are radio loud systems and are first discovered in radio observations.
-Radio data provides reliable information on positions and fluxes of lensed images but often unable to detect lens galaxies.
-Since lens galaxies are mostly in low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens gaxies and obtain prior on underlying mass distribution.
-In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling.
-The improvement is even more dramatic in B1555+375.
-With HST and SHARP AO high resolution imaging, we detect an edge-on disk which does not appear in any previous discussions on B1555+375.
-This new discovered edge-on disk provides a strong prior for our lens modelling and we show that it adequately explain sthe flux ratio anomaly in B1555+375.
-Our results demostrate that lack of knowledge of lens galaxies can lead to improper lens models.
-Modelling with only four image positions from radio data can also cause a lot of degeneracy.
-With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems.
-In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also be able to expalin the flux ratio anomalies of these systems.
-
-%From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
-include an exponential disk), rather than just assuming smooth potential.
-Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis.
-Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena.
-For precise measurements on substurcture population, mass function, and any derived properties from strongly lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.
-We would like to draw attention to this edge-on disk orginated flux anomalies due to its impacts on substructure searching.
-
 \section*{Acknowledgments}
-
+S.V. is grateful to Dandan Xu for useful discussion on the nature of flux ratio anomalies in high resolution numerical simulations.
 \bibliographystyle{mn2e}

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
fix typo

@@
 $z_\ell = 1.0$ and a source redshift of $z_s =1.5$.
-Our steps to explore the parameter space are: 1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position.
-2) Let all parameters without priors vary to reach a temporary best-fit.
-3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors).
-4) Let all parameters vary to reach the final optimal model.
+Our steps to explore the parameter space are: (1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position.
+(2) Let all parameters without priors vary to reach a temporary best-fit.
+(3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors).
+(4) Let all parameters vary to reach the final optimal model.
 The full best-fit parameters are shown in Table
@@
 have well known dependencies on wavelength. \citet{KD04} examine all
-eight radio loud flux anomalous lenses besides B0128=437, namely: MG
+eight radio loud flux anomalous lenses besides B0128+437, namely: MG
 0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
@@
 {\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure.
-Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375 we have identified the existence of a previously undetected edge-on disk.
-By including this disk in the mass model of the lens galaxy we find a good fit for both the positions and flux ratios of the lensed images.
+Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375, we have identified the existence of a previously undetected edge-on disk.
+By including this disk in the mass model of the lens galaxy, we find a good fit for both the positions and flux ratios of the lensed images.
 Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies.

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
add chi square
Add reference

@@
 account completeness corrections arising from the limited sky coverage
-imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies}. [NEED REF]  
+imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies} \citep{DES15,Kop15}.  
 This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
@@
 % \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 lens model.}
+  \caption{Best-fit parameters of B1555+375 lens models.}
   \begin{tabular}{@{}ccc}
@@
 $r_e$	  & $0.20 ''$ &  ... \\
+\hline
+$\chi ^2$ & $1.05$ & $0.04$ \\
 \hline
@@
 substructures in the near future \citep{N14}. It is well known (e.g,
-Kochanek 199??) that lens models based only on the locations of lensed
+\citep{Ka91}) that lens models based only on the locations of lensed
 quasar/AGN images have large degeneracies. Therefore, before

### 2015-04-23 papers/B1555_EdgeOn/B1555_letter.tex
Update of Simona's change

@@
 anomaly, and we show that simple models that include the disk can
-reproduce the anomaly without requiring substructure.  Several [??]
-other lens systems that we have observed with adaptive optics imaging
+reproduce the anomaly without requiring substructure.  
+Other lens systems that we have observed with adaptive optics imaging
 as part of the Strong lensing at High Angular Resolution Programme (SHARP)
-show similar behaviour.  These results suggest that the assumption that
+show a similar behaviour and will be the subject of a future paper.  
+These results suggest that the assumption that
 all flux-ratio anomalies are due to substructure will likely overestimate
@@
 former requiring a larger fraction of mass in substructure than
-expected \citet{Xu14}. While this could be the result of small sample
+expected \citep{Xu14}. While this could be the result of small sample
 statistics, it could also be the indication that flux ratio anomalies
@@
 0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
-B1933+503, and B2045+265.  They find no strong wavelength dependence
+B1933+503, and B2045+265.  They found no strong wavelength dependence
 in the flux ratios of all these systems and therefore rule out radio
@@
 anomalous systems, but it is also one of the most challenging systems
-to explain by substructures. \citet{Xu14} conclude the failure in
-predicting flux ratios is due to oversimplified/improper lens
+to explain by substructures. \citet{Xu14} have concluded that the failure in
+predicting flux ratios is most likely due to oversimplified/improper lens
 modelling. They also point out that the SIE component and the external
 shear in their model are orthogonal, indicating a possible missing
-ingredient in lens model. Their results are consistent with the SHARP
+ingredient in the lens model. Their results are consistent with the SHARP
 $K^{\prime}$ band observations, in which an edge-on disk crosses the
-radio merging double.
-
-Additional near-infrared AO imaging from SHARP shows that B1555+375 is
-not the only system having a significant disk component detection in
-the lensing galaxy.  These systems will be investigated in
-future work, but the images alone strongly suggest that other lens
-systems have similar links between flux-ratio anomalies and disk
-components.  Although the number of radio loud flux anomalous lensed
-quasars remains small, a new technique using narrow-line emission
-regions will enlarge the sample and bring statistical perspective on
-substructures in the near future \citep{N14}. It is well known (e.g,
+radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known (e.g,
 \citep{Ka91}) that lens models based only on the locations of lensed
@@
 
+Although the number of radio loud flux anomalous lensed
+quasars remains small, a new technique using narrow-line emission
+regions will enlarge the sample and bring statistical perspective on
+substructures in the near future \citep{N14}.
+
 \section{Conclusions}
@@
 We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias.
-Finally, our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects.
-In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.}
+Our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects.
+In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.
+Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only system having a significant disk component detection in
+the lensing galaxy.
+These systems will be investigated in future work, but the images alone strongly suggest that other lens systems have similar links between flux-ratio anomalies and disk components.
+}
 

### 2015-04-23 papers/B1555_EdgeOn/B1555_letter.tex
minor changes

@@
 account completeness corrections arising from the limited sky coverage
-imposed by the Galactic Plane {\bf and the latest discovery of new dwarf galaxies} \citep{DES15,Kop15}.  
+imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
 This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
@@
 sample of satellites/subhaloes in galaxies outside the Local Group.
-{\bf However,} this process is challenging due to the faintness of the satellite
+ However, this process is challenging due to the faintness of the satellite
 galaxies.  Furthermore, lower-mass satellites may not be able to
@@
 perspective on current constraints based on flux ratio anomalies.  In
-this {\bf letter}, we explore the idea that not all flux ratio anomalies are
+this letter, we explore the idea that not all flux ratio anomalies are
 related to the presence of substructure, but that some originate in a
@@
 
-Gravitational lensing is, {\bf at present,} the most powerful tool for
+Gravitational lensing is,  at present, the most powerful tool for
 studying substructure in galaxies outside of the Local Universe, and
@@
 dark matter, it is critical to eliminate other possible explanations
-for the difference between the observed and expected fluxes{\bf, such as propagation effects and assumptions on the mass distribution of the lens galaxy}.  
+for the difference between the observed and expected fluxes, such as propagation effects and assumptions on the mass distribution of the lens galaxy.  
 It is for this reason that much of the effort in the flux-ratio technique
@@
 $K^{\prime}$ band observations, in which an edge-on disk crosses the
-radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known (e.g,
-\citep{Ka91}) that lens models based only on the locations of lensed
+radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known 
+\citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
 quasar/AGN images have large degeneracies. Therefore, before
@@
 
-Although the number of radio loud flux anomalous lensed
-quasars remains small, a new technique using narrow-line emission
-regions will enlarge the sample and bring statistical perspective on
-substructures in the near future \citep{N14}.
+%Although the number of radio loud flux anomalous lensed
+%quasars remains small, a new technique using narrow-line emission
+%regions will enlarge the sample and bring statistical perspective on
+%substructures in the near future \citep{N14}.
 

### 2015-04-25 papers/B1555_EdgeOn/B1555_letter.tex
Small changes to text

@@
 
-\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
+\title[Beware the Effect of Edge-on Disks]{
+%Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375
+SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio
+Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
+Disks
+}
 \author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
-email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
+jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
 Other$^{2}$\\
@@
 flux-ratio anomaly but where the lensing galaxy is also revealed in
-high-resolution imaging to have a clear edge-on disk component.  The
+high-resolution infrared imaging to have a clear edge-on disk component.  The
 disk crosses directly over the pair of images that exhibit the
@@
 
-It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
-Indeed, small perturbations in the gravitational potential are
-sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
-Moreover, unlike in the optical or infrared, in the radio band, lensed
-images are not sensitive to micro lensing from stars nor dust
-extinction. This makes flux ratio anomalies a promising tool to
-detect dark matter substructures \citep{Dalal2002, N13}.  At present,
-the amount of substructure derived from flux ratio anomalies is in
-disagreement with predictions from numerical simulations, with the
-former requiring a larger fraction of mass in substructure than
+It was first suggested by \citet{Mao1998} that flux ratio anomalies
+observed in radio loud multiple images of lensed quasar could be
+interpreted as a telltale sign of the presence of substructure in lens
+galaxies.  Indeed, small perturbations in the gravitational potential
+are sufficient to cause flux ratio anomalies in strong lensed systems
+\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
+radio band, lensed images are not sensitive to micro lensing from
+stars nor dust extinction. This makes flux ratio anomalies a promising
+tool to detect dark matter substructures \citep{Dalal2002, N13}.  At
+present, the amount of substructure derived from flux ratio anomalies
+is in disagreement with predictions from numerical simulations, with
+the former requiring a larger fraction of mass in substructure than
 expected \citep{Xu14}. While this could be the result of small sample
@@
 considered. To this end we use new infra-red data from the Strong
-lensing at High Angular Resolution Program (SHARP; Fassnacht et al.,
-in prep). The main goal of the SHARP project is to re-observe known
-quadruple and Einstein ring lens systems at a much higher angular
+lensing at High Angular Resolution Program 
+\citep[SHARP;][Fassnacht et al., in prep]{CLASS1}.
+The main goal of the SHARP project is to re-observe known
+quadruple and Einstein ring lens systems at high angular
 resolution by making use of observations with (1) adaptive optics (AO)
@@
 the new information obtained from the latest SHARP infrared imaging.
-The paper is organized as follows: the latest SHARP data are
+The paper is organized as follows: the  SHARP data are
 introduced in section 2; in section 3 we present the lens model while
@@
 infrared imaging suggests another explanation.  In both the $K^\prime$
-band adaptive optics data and the HST imaging (two rightmost panels in
+band adaptive optics data and the HST infrared imaging (two rightmost panels in
 Fig. 1), the lensing galaxy has a clear edge-on disk component with a
@@
 
-As a first trail of modelling, we create a single SIE model to 
-justify the performance of a simple lensing potential. Consistent with previous studies
-\citep{Marlow99, Xu14}, our single elliptical potential model cannot predict flux anomaly in B1555+375. 
-We then create two separate models of the lensing potential.  In the
-first we treat the lens as a SIE bulge and an exponential edge-on disk
-(SIE+expdisk).  In the second model the disk is represented as a very
-elongated SIE component (2-SIE).  The lens system is red, with a
-strong jump in flux between the F814W (roughly I) and F160W (roughly
-H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
-$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.
-Our steps to explore the parameter space are: (1) Apply strong priors from SHARP AO image to the edge-on disk position angle and ellipticity, and use the best-fit model of \citet{Marlow99} as the start point of the bulge component and the source position.
-(2) Let all parameters without priors vary to reach a temporary best-fit.
-(3) Start with the best-fit in step 2 and let all parameters with priors vary to reach another best-fit (also ensure this best-fit is not far from the priors).
-(4) Let all parameters vary to reach the final optimal model.
-The full best-fit parameters are shown in Table
-2. Both of these models predict fairly matched results with the radio
-observation, and the 2-SIE model has a better performance in flux
-ratios. The comparison of observation and our lens modelling is given
-in Figure 3 and Tables 3 \& 4.
-{\bf We have not included an external shear component into our model because the constraints provided by the image positions and  fluxes would not be sufficient 
-to constrain such a model.
-However, we note that the image not affected by dust (image C) in the Keck AO data is consistent with negligible shear (i.e.
-shear strength $\Gamma_s=0.002$), when modelled with the pixelized technique by \citet{V09}.}
+As a first trial of modelling, we create a single SIE model to check
+the performance of a simple lensing potential. Consistent with
+previous studies \citep{Marlow99, Xu14}, our single elliptical
+potential model cannot predict the flux anomaly in B1555+375.  We then
+create two separate models of the lensing potential that both
+incorporate the disk.  In the first we treat the lens as a SIE bulge
+and an exponential edge-on disk (SIE+expdisk).  In the second model
+the disk is represented as a very elongated SIE component (2-SIE).
+The lens system is red, with a strong jump in flux between the F814W
+(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
+we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
+$z_s =1.5$. Our steps to explore the parameter space are: (1) Apply
+strong priors from SHARP AO image to the edge-on disk position angle
+and ellipticity, and use the best-fit model of \citet{Marlow99} as the
+starting point for the bulge component and the source position. (2)
+Let all parameters without priors vary to reach a temporary best
+fit. (3) Start with the best fit in step 2 and let all parameters with
+priors vary to reach another best fit (also ensure this best fit is
+not far from the priors). (4) Let all parameters vary to reach the
+final optimal model.  The full best-fit parameters are shown in Table
+2. Both of these models produce lensed images with positions and
+fluxes that are good matches to the radio observations.  While both of
+the two component models produce significantly improved matches to the
+fluxes than the single SIE model, the 2-SIE version has a somewhat
+better performance than the SIE+expdisk model in reproducing flux
+ratios. The comparison of the observations and our lens modelling is
+given in Figure 3 and Tables 3 \& 4.  We have not included an external
+shear component into our model because the constraints provided by the
+image positions and fluxes would not be sufficient to constrain such a
+model. However, we note that the image not affected by dust (image C)
+in the Keck AO data is consistent with negligible shear (i.e. shear
+strength $\Gamma_s=0.002$), when modelled with the pixelized technique
+of \citet{V09}.
 
@@
 dark matter, it is critical to eliminate other possible explanations
-for the difference between the observed and expected fluxes, such as propagation effects and assumptions on the mass distribution of the lens galaxy.  
-It is for this reason that much of the effort in the flux-ratio technique
-has been focused on radio-loud lens systems.  At these wavelengths,
-dust extinction and microlensing effects should be minimal
-\citep[although see][for a rare example of radio microlensing]{K2000}.
-Radio propagation effects can affect radio fluxes, as is clearly shown
-in the B0128+437 system \citep{B04}.  However, these propagation
-effects can be disentangled from substructure lensing because they
-have well known dependencies on wavelength. \citet{KD04} examine all
-eight radio loud flux anomalous lenses besides B0128+437, namely: MG
-0414+0534, B0712+472, B1359+154, B1422+231, B1555+375, B1608+656,
-B1933+503, and B2045+265.  They found no strong wavelength dependence
-in the flux ratios of all these systems and therefore rule out radio
-propagation effects as significant contributors to the observed
-anomalies.
+for the difference between the observed and expected fluxes, such as
+propagation effects and assumptions about the mass distribution of the
+lens galaxy.  It is for this reason that much of the effort in the
+flux-ratio technique has been focused on radio-loud lens systems.  At
+these wavelengths, dust extinction and microlensing effects should be
+minimal \citep[although see][for a rare example of radio
+  microlensing]{K2000}.  Radio propagation effects can affect radio
+fluxes, as is clearly shown in the B0128+437 system \citep{B04}.
+However, these propagation effects can be disentangled from
+substructure lensing because they have well known dependencies on
+wavelength. \citet{KD04} examine all eight radio loud flux anomalous
+lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
+B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
+no strong wavelength dependence in the flux ratios of all these
+systems and therefore rule out radio propagation effects as
+significant contributors to the observed anomalies.
 
-{\bf In this letter, we focus on the effect of more complicated mass distributions for the lens galaxy on flux ratio anomalies.
-Traditionally, flux anomalous lensed quasars are radio loud systems that are firstly discovered in radio observations.
-While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies.
-Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux ratio anomaly.
-Since lens galaxies are mostly located at low redshift, optical and near-infrared observations are ideal to measure the light distribution of lens galaxies and obtain useful prior information  
-on the underlying mass distribution.
-Indeed \citet{SHARP12} has shown that high resolution IR imaging can help to significantly improve the precision of the lens modelling.
-This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging, has allowed us to detect, for the fist time, the presence of an edge-on disk.
-This new discovered edge-on disk provides a strong prior for our lens modelling.
-With a bulge plus an edge-on disk, our models produce matches to both the radio image
-positions and their flux ratio, while models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly. Our successful modelling indicates that the
-kiloparsec-scale structure of the lens galaxy itself is sufficient to explain the flux ratio anomalies in B1555+375, without any need to invoke the presence of substructure.  }
+In this letter, we focus on the effect of more complicated mass
+distributions for the lens galaxy on flux ratio anomalies.
+Traditionally, flux anomalous lensed quasars are radio loud systems
+that are firstly discovered in radio observations. While radio data
+provide reliable information on the positions and the fluxes of the
+lensed images, they are often unable to detect the lens
+galaxies. Moreover, lens modelling based only on the positions of the
+four images can be highly degenerate and prior assumptions play a key
+role in the interpretation of the observed flux ratio anomaly.  Since
+lens galaxies are typically at redshifts of $z \leq 1$, optical and
+near-infrared observations are ideal for measuring the light distribution
+of lens galaxies and obtaining useful prior information on the underlying
+mass distributions. Indeed \citet{SHARP12} showned that high
+resolution IR imaging can help to significantly improve the precision
+of the lens modelling. This improvement is even more dramatic in the
+case of B1555+375, where HST and SHARP AO high resolution imaging has
+allowed us to detect, for the fist time, the presence of an edge-on
+disk. This new discovered edge-on disk provides a strong prior for our
+lens modelling.  With a bulge plus an edge-on disk, our models produce
+matches to both the radio image positions and their flux ratio, while
+models with only one SIE component \citep{Marlow99,Xu14} fail to
+reproduce the fluxes correctly. Our successful modelling indicates
+that the kiloparsec-scale structure of the lens galaxy itself is
+sufficient to explain the flux ratio anomalies in B1555+375, without
+any need to invoke the presence of substructure.
 
-From a theoretical perspective, \citet{Xu14} find that substructures
+From a theoretical perspective, \citet{Xu14} also find that substructures
 cannot explain the observed radio flux anomalies in all the lenses
-that were considered. By adding subhaloes from numerical simulations
-on to these systems, only one out of eight radio loud systems
-reproduces the level of flux anomalies seen in the data.  The rest of
+that were considered. After adding subhaloes from numerical simulations
+to these systems, only one out of the eight radio loud systems
+achieves the level of the flux anomalies seen in the observations.  The rest of
 them are unlikely (only $1 \% - 4 \%$ probability) to have flux
-anomalies produced by substructure, including our target B1555+375.
+anomalies produced only by substructure, including our target B1555+375.
 In fact, among those eight radio lenses, B1555+375 is one of the most
@@
 \section{Conclusions}
-{\bf In this letter we have taken advantage of the power of multi-wavelength high resolution data to investigate whether flux ratio anomalies could be explained by more complex smooth models for the lens galaxy mass distribution rather than substructure.
-Thanks to new imaging from the SHARP $K^{\prime}$ band observations of the gravitational lens system B1555+375, we have identified the existence of a previously undetected edge-on disk.
-By including this disk in the mass model of the lens galaxy, we find a good fit for both the positions and flux ratios of the lensed images.
-Our results clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of a few lensed images, can lead to improper lens models and a misinterpretation of the origin of flux ratio anomalies.
-We stress, therefore, that one should be very careful when interpreting the nature of flux ratio anomalies, as prior assumptions on the lens mass distribution are a significant source of bias.
-Our analysis shows that in order to derive precise quantification of the substructure population and any derived properties from strongly lensed flux anomalous systems, it is crucial to have a careful estimation of non-substructure effects.
-In fact, even in the presence of mass substructures, the observed flux ratio anomalies could be still dominated by the complex structure of the lens galaxy.
-Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only system having a significant disk component detection in
-the lensing galaxy.
-These systems will be investigated in future work, but the images alone strongly suggest that other lens systems have similar links between flux-ratio anomalies and disk components.
-}
+In this letter we have taken advantage of the power of
+multi-wavelength high resolution data to investigate whether flux
+ratio anomalies could be explained by more complex smooth models for
+the lens galaxy mass distribution rather than substructure. Thanks to
+new imaging from the SHARP $K^{\prime}$ band observations of the
+gravitational lens system B1555+375, we have identified the existence
+of a previously unknown edge-on disk. By including this disk in the
+mass model of the lens galaxy, we find a good fit for both the
+positions and flux ratios of the lensed images. Our results clearly
+demonstrate that the lack of knowledge on the lens galaxy mass
+distribution, combined with the limited information provided by the
+position of a few lensed images, can lead to improper lens models and
+a misinterpretation of the origin of flux ratio anomalies.  We stress,
+therefore, that one should be very careful when interpreting the
+nature of flux ratio anomalies, as prior assumptions on the lens mass
+distribution are a significant source of bias. Our analysis shows that
+in order to derive precise quantification of the substructure
+population and any derived properties from strongly lensed flux
+anomalous systems, it is crucial to have a careful estimation of
+non-substructure effects. In fact, even in the presence of mass
+substructures, the observed flux ratio anomalies could be still
+dominated by the complex structure of the lens galaxy. Finally,
+additional near-infrared AO imaging from SHARP shows that B1555+375 is
+not the only system having a significant disk component detection in
+the lensing galaxy.  These systems will be investigated in future
+work, but the images alone strongly suggest that other lens systems
+have similar links between flux-ratio anomalies and disk components.
 

### 2015-04-25 papers/B1555_EdgeOn/B1555_letter.tex
spell-check of current draft

@@
 A common feature of simulations of structure formation is the presence
-of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
+of thousands of subhalos that are associated with larger mass aloes \citep[e.g.][]{Springel08}.
 However, observations of the Local Group find many fewer satellite
@@
 understand this discrepancy, it is imperative to build up a large
-sample of satellites/subhaloes in galaxies outside the Local Group.
+sample of satellites/subhalos in galaxies outside the Local Group.
  However, this process is challenging due to the faintness of the satellite
@@
 lensing at High Angular Resolution Program 
-\citep[SHARP;][Fassnacht et al., in prep]{CLASS1}.
+\citep[SHARP;][Fassnacht et al., in prep]{SHARP12}.
 The main goal of the SHARP project is to re-observe known
@@
 
-\section{Lens Modelling}
+\section{Lens Modeling}
 
@@
 
-As a first trial of modelling, we create a single SIE model to check
+As a first trial of modeling, we create a single SIE model to check
 the performance of a simple lensing potential. Consistent with
@@
 better performance than the SIE+expdisk model in reproducing flux
-ratios. The comparison of the observations and our lens modelling is
+ratios. The comparison of the observations and our lens modeling is
 given in Figure 3 and Tables 3 \& 4.  We have not included an external
@@
 in the Keck AO data is consistent with negligible shear (i.e. shear
-strength $\Gamma_s=0.002$), when modelled with the pixelized technique
+strength $\Gamma_s=0.002$), when modeled with the pixelized technique
 of \citet{V09}.
@@
 \medskip
-Comparision between radio data and model-predicted flux ratios.
+Comparison between radio data and model-predicted flux ratios.
 The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
-1-SIE model is quoted from Tabel 5 in \citet{Marlow99}.
+1-SIE model is quoted from Table 5 in \citet{Marlow99}.
 
@@
 lensed images, they are often unable to detect the lens
-galaxies. Moreover, lens modelling based only on the positions of the
+galaxies. Moreover, lens modeling based only on the positions of the
 four images can be highly degenerate and prior assumptions play a key
@@
 of lens galaxies and obtaining useful prior information on the underlying
-mass distributions. Indeed \citet{SHARP12} showned that high
+mass distributions. Indeed \citet{SHARP12} showed that high
 resolution IR imaging can help to significantly improve the precision
-of the lens modelling. This improvement is even more dramatic in the
+of the lens modeling. This improvement is even more dramatic in the
 case of B1555+375, where HST and SHARP AO high resolution imaging has
@@
 disk. This new discovered edge-on disk provides a strong prior for our
-lens modelling.  With a bulge plus an edge-on disk, our models produce
+lens modeling.  With a bulge plus an edge-on disk, our models produce
 matches to both the radio image positions and their flux ratio, while
 models with only one SIE component \citep{Marlow99,Xu14} fail to
-reproduce the fluxes correctly. Our successful modelling indicates
+reproduce the fluxes correctly. Our successful modeling indicates
 that the kiloparsec-scale structure of the lens galaxy itself is
@@
 cannot explain the observed radio flux anomalies in all the lenses
-that were considered. After adding subhaloes from numerical simulations
+that were considered. After adding subhalos from numerical simulations
 to these systems, only one out of the eight radio loud systems
@@
 predicting flux ratios is most likely due to oversimplified/improper lens
-modelling. They also point out that the SIE component and the external
+modeling. They also point out that the SIE component and the external
 shear in their model are orthogonal, indicating a possible missing
@@
 %.
-Modelling with only four image positions from radio data can also cause a lot of degeneracy.
+Modeling with only four image positions from radio data can also cause a lot of degeneracy.
 With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems.
@@
 An edge-on disk structure may also be able to explain the flux ratio anomalies of these systems.
- %From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
+ %From the successful modeling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
 include an exponential disk), rather than just assuming smooth potential.

### 2015-04-27 papers/B1555_EdgeOn/B1555_letter.tex
quick change from Matt's comments
In bold form

@@
 \citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
-radio band, lensed images are not sensitive to micro lensing from
+radio band, lensed images are not sensitive to microlensing from
 stars nor dust extinction. This makes flux ratio anomalies a promising
-tool to detect dark matter substructures \citep{Dalal2002, N13}.  At
+tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002, N13}.  At
 present, the amount of substructure derived from flux ratio anomalies
@@
 expected \citep{Xu14}. While this could be the result of small sample
-statistics, it could also be the indication that flux ratio anomalies
+statistics, it could also be an indication that flux ratio anomalies
 have a different origin than substructure.
@@
 was used, with the corrections derived from the laser guide star and a
-$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
+$R$=14.4 tip-tilt \textbf{star} that was located 45$^{\prime\prime}$ from the lens
 system.  The ``narrow camera'' mode was used, giving a field of view

### 2015-04-27 papers/B1555_EdgeOn/B1555_letter.tex
change to text

@@
 A common feature of simulations of structure formation is the presence
-of thousands of subhalos that are associated with larger mass aloes \citep[e.g.][]{Springel08}.
+of thousands of subhalos that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
 However, observations of the Local Group find many fewer satellite
@@
 It was first suggested by \citet{Mao1998} that flux ratio anomalies
-observed in radio loud multiple images of lensed quasar could be
+observed in radio loud multiple images of lensed quasars could be
 interpreted as a telltale sign of the presence of substructure in lens
@@
 create two separate models of the lensing potential that both
-incorporate the disk.  In the first we treat the lens as a SIE bulge
+incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
 and an exponential edge-on disk (SIE+expdisk).  In the second model
@@
 we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
-$z_s =1.5$. Our steps to explore the parameter space are: (1) Apply
-strong priors from SHARP AO image to the edge-on disk position angle
+$z_s =1.5$.
+\textbf{This assumption on redshifts is due to that some lens model parameters contain distance information.
+Our choice of redshifts does not affects the predicted magnifications nor flux ratios.} Our steps to explore the parameter space are: (1) Apply
+strong priors from the SHARP AO image to the edge-on disk position angle
 and ellipticity, and use the best-fit model of \citet{Marlow99} as the
-starting point for the bulge component and the source position. (2)
+starting point for the bulge\textbf{/halo} component and the source position. (2)
 Let all parameters without priors vary to reach a temporary best
@@
 \caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
-with contours from the MERLIN observation of \citet{Marlow99} overlaid.
+with contours from the MERLIN observation of \citet{Marlow99} overlaid. \textbf{From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).}
 %
@@
 $y_1$	  &$-0.1923$	&$-0.1695$  \\
-$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
-$y_2$	  &$-0.2502$	& $-0.1843$  \\
+
 $\sigma_1$ &$141.3$     & $144.9$ \\
@@
 $\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
+\hline
+$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
+$y_2$	  &$-0.2502$	& $-0.1843$  \\
 $M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
@@
 \medskip
-Subscripts 1 and 2 represent bulge and disk components in each model respectively.
+Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
 Positions are offsets from radio image component A measured in units of arcsec.
@@
 1-SIE model is quoted from Table 5 in \citet{Marlow99}.
+[WE HAVE 1-SIE MODEL NOW.
+SHOULD I QUOTE FROM MARLOW OR OUR OWN?--JW]
 
@@
 allowed us to detect, for the fist time, the presence of an edge-on
-disk. This new discovered edge-on disk provides a strong prior for our
-lens modeling.  With a bulge plus an edge-on disk, our models produce
+disk. This newly discovered edge-on disk provides a strong prior for our
+lens modeling.  With \textbf{an additional disk component}, our models produce
 matches to both the radio image positions and their flux ratio, while

### 2015-04-28 papers/B1555_EdgeOn/B1555_letter.tex
change in Table 2
new result of 2SIE w/ prior
Minor edit to figure captions

@@
 \caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
-with contours from the MERLIN observation of \citet{Marlow99} overlaid. \textbf{From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).}
+with contours from the MERLIN observation of \citet{Marlow99} overlaid. 
 %
@@
 The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
-From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
+\label{fig2}}
 \end{figure}
@@
 \hline
-$\chi ^2$ & $1.05$ & $0.04$ \\
-\hline
+%$\chi ^2$ & $1.05$ & $0.04$ \\
+%\hline
 \end{tabular}
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0481$  \\  
+B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
 C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1620$    &  $+0.3682$ \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1619$    &  $+0.3680$ \\  
 \hline
@@
 \hline
-$f_A/f_B$			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
-$f_A/f_C$		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
-$f_A/f_D$		&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\
+$f_A/f_B$			&$1.75$ & $1.78$ &$1.04$& $1.66$ & $1.75$ \\ 
+$f_A/f_C$		&$2.05$ 	&$2.37$ &$3.20$ & $1.33$ & $2.27$\\
+$f_A/f_D$		&$13.08$ &$ 12.86$ &$9.82$& $5.83$ & $8.11$\\
 
@@
 \medskip
-Comparison between radio data and model-predicted flux ratios.
-The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
-1-SIE model is quoted from Table 5 in \citet{Marlow99}.
-[WE HAVE 1-SIE MODEL NOW.
-SHOULD I QUOTE FROM MARLOW OR OUR OWN?--JW]
+Comparison between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
 

### 2015-04-28 papers/B1555_EdgeOn/B1555_letter.tex
update of 2SIE parameters
update parameters of SIE+exp(temp)
new 2-SIE result fitting K03

@@
 \hline
-$x_1$  	  & $-0.1883$	& $-0.1813$  \\
-$y_1$	  &$-0.1923$	&$-0.1695$  \\
+$x_1$  	  & $-0.1833$	& $-0.1884$  \\
+$y_1$	  &$-0.1945$	&$-0.1607$  \\
 
-$\sigma_1$ &$141.3$     & $144.9$ \\
-$e_1$	  & $0.27$	& $0.27$ \\
-$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
+$\sigma_1$ &$140.3$     & $145.3$ \\
+$e_1$	  & $0.27$	& $0.24$ \\
+$\theta_1$ &$105.5 \degr$ & $99.5 \degr$ \\
 \hline
-$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
-$y_2$	  &$-0.2502$	& $-0.1843$  \\
+$x_2$	  &$-0.1615$ 	&$-0.1594$  \\
+$y_2$	  &$-0.2402$	& $-0.2225$  \\
 $M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
-$\sigma_2$ & ...        &$123.5$ \\  
-$e_2$	  &$0.84$	&$0.83$  \\
-$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
-$r_e$	  & $0.20 ''$ &  ... \\
+$\sigma_2$ & ...        &$122.7$ \\  
+$e_2$	  &$0.84$	&$0.82$  \\
+$\theta_2$ &$7.7\degr$ &$6.5\degr$  \\
+$r_e$	  & $0.19 ''$ &  ... \\
 \hline
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
+B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
 C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1619$    &  $+0.3680$ \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1620$ &$-0.3680$  & $-0.1619$    &  $+0.3680$ \\  
 \hline
@@
 \hline
-	& MERLIN & VLA & \multicolumn{3}{l}{Model}\\
-		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
+	& MERLIN  & \multicolumn{3}{c}{Model}\\
+		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
 \hline
-$f_A/f_B$			&$1.75$ & $1.78$ &$1.04$& $1.66$ & $1.75$ \\ 
-$f_A/f_C$		&$2.05$ 	&$2.37$ &$3.20$ & $1.33$ & $2.27$\\
-$f_A/f_D$		&$13.08$ &$ 12.86$ &$9.82$& $5.83$ & $8.11$\\
+$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.70$ & $1.61$ \\ 
+$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $1.42$ & $1.97$\\
+$f_A/f_D$		&$11.62 (3.24)$  &$9.82$& $5.84$ & $11.63$\\
 
@@
 \medskip
-Comparison between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
+Comparison between radio data and model-predicted flux ratios. The radio flux ratios and errors are from Table 1  in \citet{K03}.
 

### 2015-04-30 papers/B1555_EdgeOn/B1555_letter.tex
update expdisk model
update changes from John except Data part

@@
 \title[Beware the Effect of Edge-on Disks]{
-%Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375
-SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio
+%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
+SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
 Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
@@
 reproduce the anomaly without requiring substructure.  
-Other lens systems that we have observed with adaptive optics imaging
-as part of the Strong lensing at High Angular Resolution Programme (SHARP)
-show a similar behaviour and will be the subject of a future paper.  
+%Other lens systems that we have observed with adaptive optics imaging
+%as part of the Strong lensing at High Angular Resolution Programme (SHARP)
+%show a similar behaviour and will be the subject of a future paper.  
 These results suggest that the assumption that
@@
 A common feature of simulations of structure formation is the presence
-of thousands of subhalos that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
+of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
 However, observations of the Local Group find many fewer satellite
@@
 understand this discrepancy, it is imperative to build up a large
-sample of satellites/subhalos in galaxies outside the Local Group.
+sample of satellites/subhaloes in galaxies outside the Local Group.
  However, this process is challenging due to the faintness of the satellite
@@
 
-It was first suggested by \citet{Mao1998} that flux ratio anomalies
-observed in radio loud multiple images of lensed quasars could be
+It was first suggested by \citet{Mao1998} that flux-ratio anomalies
+observed in radio-loud multiple images of lensed quasars could be
 interpreted as a telltale sign of the presence of substructure in lens
 galaxies.  Indeed, small perturbations in the gravitational potential
-are sufficient to cause flux ratio anomalies in strong lensed systems
+are sufficient to cause flux-ratio anomalies in strong lensed systems
 \citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
 radio band, lensed images are not sensitive to microlensing from
-stars nor dust extinction. This makes flux ratio anomalies a promising
-tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002, N13}.  At
-present, the amount of substructure derived from flux ratio anomalies
+stars nor dust extinction. This makes flux-ratio anomalies a promising
+tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002}.  At
+present, the amount of substructure derived from flux-ratio anomalies
 is in disagreement with predictions from numerical simulations, with
@@
 expected \citep{Xu14}. While this could be the result of small sample
-statistics, it could also be an indication that flux ratio anomalies
+statistics, it could also be an indication that flux-ratio anomalies
 have a different origin than substructure.
@@
 substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14a}.
+is currently in agreement with theoretical expectations \citep{V14a,V12}.
 
-While future large-scale surveys, such as the LSST, are expected to
-deliver new large samples of gravitationally lensed quasars, in the
-near future the discovery of new systems using narrow-line quasar
-emission \citep{N14} will provide new invaluable statistical
-perspective on current constraints based on flux ratio anomalies.  In
-this letter, we explore the idea that not all flux ratio anomalies are
+%While future large-scale surveys, such as the LSST, are expected to
+%deliver new large samples of gravitationally lensed quasars, in the
+%near future the discovery of new systems using narrow-line quasar
+%emission \citep{N14} will provide new invaluable statistical
+%perspective on current constraints based on flux-ratio anomalies.  
+In this letter, we explore the idea that not all flux-ratio anomalies are
 related to the presence of substructure, but that some originate in a
@@
 interferometric arrays \citep{SHARP12,V12}. In particular, to better
-understand the causes of flux ratio anomalies in gravitational lenses
+understand the causes of flux-ratio anomalies in gravitational lenses
 we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
 discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
-has a pair of merging images that show a strong flux ratio anomaly at
+has a pair of merging images that show a strong flux-ratio anomaly at
 radio wavelengths.  Follow-up observations ruled out radio propagation
@@
 \caption{High-resolution multiband imaging of the B1555+375 lens system.
-All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
-represents 1\arcsec.  From left to right the figures show data from
-HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
+All of the panels are 3.7 arcsec on a side, and for each panel the scale bar 
+represents 1\arcsec.  From left to right the panels show data from
+\textit{HST}/WFPC2 in the F555W band, \textit{HST}/WFPC2 in the F814W band, \textit{HST}/NICMOS/NIC2
 in the F160W band, and Keck AO imaging in the $K^\prime$ band.
@@
 was used, with the corrections derived from the laser guide star and a
-$R$=14.4 tip-tilt \textbf{star} that was located 45$^{\prime\prime}$ from the lens
-system.  The ``narrow camera'' mode was used, giving a field of view
-of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
-Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
+$R$=14.4 tip-tilt \textbf{star} that was located 45 arcsec from the lens
+system.  The narrow camera mode was used, giving a field of view
+of roughly 10 arcsec on a side and a pixel scale of 10~mas.
+Six dithered 300~s exposures were obtained in the $K^{\prime}$ band filter.  The
 data were reduced with the standard SHARP pipeline, which is a
@@
 contours from the MERLIN radio observations of \citet{Marlow99}
-overlaid.  There are several notable features in the Keck AO data.
+overlaid.
+
+There are several notable features in the Keck AO data.
 These include the nearly complete lack of emission associated with the
@@
 
-The B1555+375 system was also observed by the Hubble Space Telescope
-(HST) in three broad bands.  The optical data were obtained with the
+The B1555+375 system was also observed with the \textit{Hubble Space Telescope
+(\textit{HST})} in three broad bands.  The optical data were obtained with the
 Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
@@
 band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
-obtained with the NIC2 camera.  We reduced all of the archival HST
+obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
 data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
@@
 system is not detected at high significance in the optical bands, but
-is clearly seen in the NICMOS $F160W$ image.  The edge-on lensing
-galaxy stands out in the NICMOS image.
+is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
+galaxy clearly stands out.}
 
-The observation details of Keck AO and HST imaging are shown in Table 1.
+The observation details of Keck AO and \textit{HST} imaging are shown in Table 1.
 
@@
  \hline
-   HST				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
-   HST				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
-   HST				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
+   \textit{HST}				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
+   \textit{HST}				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
+   \textit{HST}				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
    Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
@@
 
-\section{Lens Modeling}
+\section{Lens modelling}
 
-To model B1555+375, we use the lens modeling code {\tt glafic}
+To model B1555+375, we use the lens modelling code {\tt glafic}
 \citep{Oguri}.  The inputs to the model are the observed image
 positions and flux densities measured by the radio observations of
-\citet{Marlow99}.  These authors present a singular isothermal ellipsoid
-(SIE) model that provides the first fit to the image positions but
-does not reproduce the strong flux ratio anomaly between components A
-and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  Although
-the flux ratio anomaly that is observed in the radio data may be
+\citet{Marlow99}, \textbf{who also} presented a singular isothermal ellipsoid
+(SIE) model that provided the first fit[a good fit--John/ but It's not good compare to our model--JW] to the image positions but
+does not reproduce the strong flux-ratio anomaly between components A
+and B.  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
+Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
 caused by substructure in the lensing galaxy, our high-resolution near
 infrared imaging suggests another explanation.  In both the $K^\prime$
-band adaptive optics data and the HST infrared imaging (two rightmost panels in
+band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
 Fig. 1), the lensing galaxy has a clear edge-on disk component with a
@@
 with a disk component in order to see if such a model can explain the
-flux ratio anomaly without the need for substructure.  The edge-on
+flux-ratio anomaly without the need for substructure.  The edge-on
 disk may also explain the system morphology that is observed in the
@@
 these lensed images lie on or close to the edge-on disk.  Thus, strong
-extinction in the disk could cause the lack of detection of these
+extinction in the disk could cause the \textbf{non-}detection of these
 images.
 
-As a first trial of modeling, we create a single SIE model to check
+As a first trial of modelling, we create a single SIE model to check
 the performance of a simple lensing potential. Consistent with
 previous studies \citep{Marlow99, Xu14}, our single elliptical
-potential model cannot predict the flux anomaly in B1555+375.  We then
+potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.  We then
 create two separate models of the lensing potential that both
@@
 \textbf{This assumption on redshifts is due to that some lens model parameters contain distance information.
-Our choice of redshifts does not affects the predicted magnifications nor flux ratios.} Our steps to explore the parameter space are: (1) Apply
+Our choice of redshifts does not affects the predicted magnifications nor flux-ratios.}
+
+Our steps to explore the parameter space are: (1) Apply
 strong priors from the SHARP AO image to the edge-on disk position angle
@@
 better performance than the SIE+expdisk model in reproducing flux
-ratios. The comparison of the observations and our lens modeling is
+ratios. The comparison of the observations and our lens modelling is
 given in Figure 3 and Tables 3 \& 4.  We have not included an external
@@
 \caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle.
+The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle.
 \label{fig2}}
@@
 % \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 lens models.}
+  \caption{Best-fit parameters of B1555+375 lens models.
+Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
+Positions are offsets from radio image component A measured in units of arcsec.
+The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
+$e$ is ellipticity and $\theta$ is the position angle measured east of north.}
   \begin{tabular}{@{}ccc}
@@
 \hline
-$x_1$  	  & $-0.1833$	& $-0.1884$  \\
-$y_1$	  &$-0.1945$	&$-0.1607$  \\
+$x_1$  	  & $-0.1794$	& $-0.1884$  \\
+$y_1$	  &$-0.1881$	&$-0.1607$  \\
 
 $\sigma_1$ &$140.3$     & $145.3$ \\
-$e_1$	  & $0.27$	& $0.24$ \\
-$\theta_1$ &$105.5 \degr$ & $99.5 \degr$ \\
+$e_1$	  & $0.21$	& $0.24$ \\
+$\theta_1$ &$73.6 \degr$ & $99.5 \degr$ \\
 \hline
-$x_2$	  &$-0.1615$ 	&$-0.1594$  \\
-$y_2$	  &$-0.2402$	& $-0.2225$  \\
-$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
+$x_2$	  &$-0.1639$ 	&$-0.1594$  \\
+$y_2$	  &$-0.2542$	& $-0.2225$  \\
+$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
 $\sigma_2$ & ...        &$122.7$ \\  
 $e_2$	  &$0.84$	&$0.82$  \\
-$\theta_2$ &$7.7\degr$ &$6.5\degr$  \\
-$r_e$	  & $0.19 ''$ &  ... \\
+$\theta_2$ &$4.0\degr$ &$6.5\degr$  \\
+$r_e$	  & $0.21 ''$ &  ... \\
 \hline
@@
 %\end{minipage}
-\medskip
-Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
-Positions are offsets from radio image component A measured in units of arcsec.
-The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
-$e$ is ellipticity and $\theta$ is the position angle measured east of north.
 
@@
  \begin{minipage}{140mm}
-  \caption{Radio observation and model-predicted lensed image positions.}
+  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
   \begin{tabular}{@{}ccccccc}
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
-C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1620$ &$-0.3680$  & $-0.1619$    &  $+0.3680$ \\  
+B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
+C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $+0.0280$ \\  
+D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $+0.3680$ \\  
 \hline
@@
 
-Comparison between radio and model-predicted lensed image positions.
-Observation data quoted from Table 2 in \citet{Marlow99}.
-Position offsets are in unit of arcsec.
-Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.
-
 \end{table*}
@@
 % \begin{minipage}{140mm}
-  \caption{Flux ratios of B1555+375 components.}
+  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
   \begin{tabular}{@{}ccccccc}
@@
 \hline
-$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.70$ & $1.61$ \\ 
-$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $1.42$ & $1.97$\\
-$f_A/f_D$		&$11.62 (3.24)$  &$9.82$& $5.84$ & $11.63$\\
+$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.61$ \\ 
+$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $1.97$\\
+$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.63$\\
 
@@
 \medskip
-Comparison between radio data and model-predicted flux ratios. The radio flux ratios and errors are from Table 1  in \citet{K03}.
 
@@
 studying substructure in galaxies outside of the Local Universe, and
-the flux ratio anomaly systems are a key aspect of these
-investigations.  However, before using the flux ratio anomaly in any
+the flux-ratio anomaly systems are a key aspect of these
+investigations.  However, before using the flux-ratio anomaly in any
 given system to investigate structure formation and the properties of
@@
 minimal \citep[although see][for a rare example of radio
-  microlensing]{K2000}.  Radio propagation effects can affect radio
-fluxes, as is clearly shown in the B0128+437 system \citep{B04}.
+  microlensing]{K2000}.  \textbf{Also,  scatter broadening} can affect radio
+fluxes, as is clearly shown in the B0128+437 system \citep{B04}, and free-free absorption can change the flux-ratios as a function of frequency,
+for example, B0218+357 \citep{M07}.
 However, these propagation effects can be disentangled from
 substructure lensing because they have well known dependencies on
-wavelength. \citet{KD04} examine all eight radio loud flux anomalous
+wavelength. \citet{KD04} examine all eight radio-loud flux anomalous
 lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
 B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
-no strong wavelength dependence in the flux ratios of all these
+no strong wavelength dependence in the flux-ratios of all these
 systems and therefore rule out radio propagation effects as
@@
 In this letter, we focus on the effect of more complicated mass
-distributions for the lens galaxy on flux ratio anomalies.
-Traditionally, flux anomalous lensed quasars are radio loud systems
+distributions for the lens galaxy on flux-ratio anomalies.
+Traditionally, flux anomalous lensed quasars are radio-loud systems
 that are firstly discovered in radio observations. While radio data
@@
 lensed images, they are often unable to detect the lens
-galaxies. Moreover, lens modeling based only on the positions of the
+galaxies. Moreover, lens modelling based only on the positions of the
 four images can be highly degenerate and prior assumptions play a key
-role in the interpretation of the observed flux ratio anomaly.  Since
+role in the interpretation of the observed flux-ratio anomaly.  Since
 lens galaxies are typically at redshifts of $z \leq 1$, optical and
@@
 resolution IR imaging can help to significantly improve the precision
-of the lens modeling. This improvement is even more dramatic in the
-case of B1555+375, where HST and SHARP AO high resolution imaging has
+of the lens modelling. This improvement is even more dramatic in the
+case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
 allowed us to detect, for the fist time, the presence of an edge-on
 disk. This newly discovered edge-on disk provides a strong prior for our
-lens modeling.  With \textbf{an additional disk component}, our models produce
-matches to both the radio image positions and their flux ratio, while
+lens modelling.  With \textbf{an additional disk component}, our models produce
+matches to both the radio image positions and their flux-ratio, while
 models with only one SIE component \citep{Marlow99,Xu14} fail to
-reproduce the fluxes correctly. Our successful modeling indicates
+reproduce the fluxes correctly. Our successful modelling indicates
 that the kiloparsec-scale structure of the lens galaxy itself is
-sufficient to explain the flux ratio anomalies in B1555+375, without
+sufficient to explain the flux-ratio anomalies in B1555+375, without
 any need to invoke the presence of substructure.
@@
 cannot explain the observed radio flux anomalies in all the lenses
-that were considered. After adding subhalos from numerical simulations
-to these systems, only one out of the eight radio loud systems
+that were considered. After adding subhaloes from numerical simulations
+to these systems, only one out of the eight radio-loud systems
 achieves the level of the flux anomalies seen in the observations.  The rest of
-them are unlikely (only $1 \% - 4 \%$ probability) to have flux
+them are unlikely (only $1 - 4$ per cent probability) to have flux
 anomalies produced only by substructure, including our target B1555+375.
@@
 to explain by substructures. \citet{Xu14} have concluded that the failure in
-predicting flux ratios is most likely due to oversimplified/improper lens
-modeling. They also point out that the SIE component and the external
+predicting flux-ratios is most likely due to oversimplified/improper lens
+modelling. They also point out that the SIE component and the external
 shear in their model are orthogonal, indicating a possible missing
@@
 $K^{\prime}$ band observations, in which an edge-on disk crosses the
-radio merging double and which fully accounts for the observed flux ratio anomaly.  In general, it is well known 
+radio merging double and which fully accounts for the observed flux-ratio anomaly.  In general, it is well known 
 \citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
 quasar/AGN images have large degeneracies. Therefore, before
-concluding that the flux ratios in any given lens system are a result
+concluding that the flux-ratios in any given lens system are a result
 of substructure, it is critical to explore a range of smooth models
 that are informed by additional observations or to do a comprehensive
-analysis such as that conducted by \citet{Xu14}. Otherwise, derived
+analysis such as that conducted by \citet{Xu14}. Otherwise, the derived
 substructure fractions should be considered as upper limits.
 
-%Although the number of radio loud flux anomalous lensed
+%Although the number of radio-loud flux anomalous lensed
 %quasars remains small, a new technique using narrow-line emission
@@
 mass model of the lens galaxy, we find a good fit for both the
-positions and flux ratios of the lensed images. Our results clearly
+positions and flux-ratios of the lensed images.
+
+Our results clearly
 demonstrate that the lack of knowledge on the lens galaxy mass
@@
 position of a few lensed images, can lead to improper lens models and
-a misinterpretation of the origin of flux ratio anomalies.  We stress,
+a misinterpretation of the origin of flux-ratio anomalies. \textbf{While future large-scale surveys, such as the LSST, are expected to
+deliver new large samples of gravitationally lensed quasars, in the
+near future the discovery of new systems using narrow-line quasar
+emission \citep{N14} will provide new invaluable statistical
+perspective on current constraints based on flux-ratio anomalies.} We stress,
 therefore, that one should be very careful when interpreting the
-nature of flux ratio anomalies, as prior assumptions on the lens mass
+nature of flux-ratio anomalies, as prior assumptions on the lens mass
 distribution are a significant source of bias. Our analysis shows that
@@
 non-substructure effects. In fact, even in the presence of mass
-substructures, the observed flux ratio anomalies could be still
+substructures, the observed flux-ratio anomalies could be still
 dominated by the complex structure of the lens galaxy. Finally,
@@
 %.
-Modeling with only four image positions from radio data can also cause a lot of degeneracy.
-With the first system analyzing and finding an edge-on disk originated flux ratio anomaly, our follow up will be explore other similar SHARP systems.
+modelling with only four image positions from radio data can also cause a lot of degeneracy.
+With the first system analyzing and finding an edge-on disk originated flux-ratio anomaly, our follow up will be explore other similar SHARP systems.
 In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also be able to explain the flux ratio anomalies of these systems.
- %From the successful modeling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
+An edge-on disk structure may also be able to explain the flux-ratio anomalies of these systems.
+ %From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
 include an exponential disk), rather than just assuming smooth potential.
-Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
+Although the number of radio-loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
 If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis.
-% This breaks the idea that in strongly lensed quasars, radio flux ratio
+% This breaks the idea that in strongly lensed quasars, radio flux-ratio
 % anomalies are most likely originated from substructure
 % perturbations. Our discovery shows a complex lens galaxy mass
-% distribution can dominate flux ratio anomalous phenomena in a strongly
+% distribution can dominate flux-ratio anomalous phenomena in a strongly
 % lensed system.
@@
 \section*{Acknowledgments}
-S.V. is grateful to Dandan Xu for useful discussion on the nature of flux ratio anomalies in high resolution numerical simulations.
+S.V. is grateful to Dandan Xu for useful discussion on the nature of flux-ratio anomalies in high resolution numerical simulations.
 \bibliographystyle{mn2e}

### 2015-05-02 papers/B1555_EdgeOn/B1555_letter.tex
move some files

@@
 lensing at High Angular Resolution Program 
-\citep[SHARP;][Fassnacht et al., in prep]{SHARP12}.
+\citep[SHARP;][Fassnacht et al., in prep]{SHARP12, V12}.
 The main goal of the SHARP project is to re-observe known
@@
 on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
-interferometric arrays \citep{SHARP12,V12}. In particular, to better
-understand the causes of flux-ratio anomalies in gravitational lenses
-we focus on the B1555+375 lens system\citep{Marlow99}.  This system was
+interferometric arrays \citep{SHARP12,V12}. In particular, 
+we focus on the B1555+375 lens system\citep{Marlow99} to better
+understand the causes of flux-ratio anomalies in gravitational lenses.  This system was
 discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
@@
 of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
-mass distribution is of key importance.  Our analysis makes use of
-the new information obtained from the latest SHARP infrared imaging.
+mass distribution is of key importance.  
+%Our analysis makes use of
+%the new information obtained from the latest SHARP infrared imaging.
 The paper is organized as follows: the  SHARP data are
@@
 and an exponential edge-on disk (SIE+expdisk).  In the second model
-the disk is represented as a very elongated SIE component (2-SIE).
+the disk is represented as a very elongated SIE component (2-SIE). [WHY MODEL BULGE W/ SIE? COMMENT ON THE REASON FOR PICKING MODELS--LEON]
 The lens system is red, with a strong jump in flux between the F814W
@@
 not far from the priors). (4) Let all parameters vary to reach the
-final optimal model.  The full best-fit parameters are shown in Table
+final optimal model.  The \textbf{final} best-fit parameters are shown in Table
 2. Both of these models produce lensed images with positions and
@@
 The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
-$e$ is ellipticity and $\theta$ is the position angle measured east of north.}
+\textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
   \begin{tabular}{@{}ccc}
@@
 achieves the level of the flux anomalies seen in the observations.  The rest of
-them are unlikely (only $1 - 4$ per cent probability) to have flux
-anomalies produced only by substructure, including our target B1555+375.
+them are unlikely (only $1 - 4$ per cent probability) to have \textbf{observed distribution of flux
+anomalies} produced only by substructure, including our target B1555+375.
 In fact, among those eight radio lenses, B1555+375 is one of the most
@@
 position of a few lensed images, can lead to improper lens models and
-a misinterpretation of the origin of flux-ratio anomalies. \textbf{While future large-scale surveys, such as the LSST, are expected to
+a misinterpretation of the origin of flux-ratio anomalies. \textbf{While future large-scale surveys, such as the DES, KiDS-VIKING, Euclid, and LSST, are expected to
 deliver new large samples of gravitationally lensed quasars, in the
@@
 S.V. is grateful to Dandan Xu for useful discussion on the nature of flux-ratio anomalies in high resolution numerical simulations.
+L.V.E.K. is supported in part through an NWO-VICI career grant (project number 639.043.308).
 \bibliographystyle{mn2e}

### 2015-05-03 papers/B1555_EdgeOn/B1555_letter.tex
update of modelling approach and Dave's comment

@@
 \citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
-radio band, lensed images are not sensitive to microlensing from
-stars nor dust extinction. This makes flux-ratio anomalies a promising
+radio band, lensed images are neither sensitive to microlensing from
+stars, nor to dust extinction. This makes flux-ratio anomalies a promising
 tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002}.  At
@@
 An alternative method for
-the detection of substructure in gravitational lens galaxies based on
+the detection of substructure in gravitational lens galaxies, utilizing
 the surface brightness distribution of extended arcs and Einstein rings
@@
 $z_s =1.5$.
-\textbf{This assumption on redshifts is due to that some lens model parameters contain distance information.
-Our choice of redshifts does not affects the predicted magnifications nor flux-ratios.}
+\textbf{This assumption on redshifts is needed because some lens model parameters contain distance information.
+However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}
 
-Our steps to explore the parameter space are: (1) Apply
-strong priors from the SHARP AO image to the edge-on disk position angle
-and ellipticity, and use the best-fit model of \citet{Marlow99} as the
-starting point for the bulge\textbf{/halo} component and the source position. (2)
-Let all parameters without priors vary to reach a temporary best
-fit. (3) Start with the best fit in step 2 and let all parameters with
-priors vary to reach another best fit (also ensure this best fit is
-not far from the priors). (4) Let all parameters vary to reach the
-final optimal model.  The \textbf{final} best-fit parameters are shown in Table
+\textbf{For each model, we explore the parameter space in the following way: 
+(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \deg$ to the edge-on disk component.
+We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position.
+The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
+(2) Markov Chain Monte Carlo: In {\tt glafic}, we run MCMC to find the a proper set of parameters for further optimization.
+The smallest $\chi^2$ doesn't necessarily give a physical model.
+Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
+(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimize [CHECK THE ALGORITHM?] to reach the final best-fit for each model.}
+
+The \textbf{final} best-fit parameters are shown in Table
 2. Both of these models produce lensed images with positions and
@@
 the flux-ratio anomaly systems are a key aspect of these
-investigations.  However, before using the flux-ratio anomaly in any
+investigations.  However, before using the anomaly in any
 given system to investigate structure formation and the properties of
@@
 for the difference between the observed and expected fluxes, such as
-propagation effects and assumptions about the mass distribution of the
-lens galaxy.  It is for this reason that much of the effort in the
+propagation effects and assumptions about the lens galaxy's mass distribution.  
+It is for this reason that much of the effort in the
 flux-ratio technique has been focused on radio-loud lens systems.  At
@@
 substructure lensing because they have well known dependencies on
-wavelength. \citet{KD04} examine all eight radio-loud flux anomalous
+wavelength. In particular, \citet{KD04} examine all eight radio-loud flux anomalous
 lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
-B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They found
+B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They find
 no strong wavelength dependence in the flux-ratios of all these
@@
 lens modelling.  With \textbf{an additional disk component}, our models produce
-matches to both the radio image positions and their flux-ratio, while
+matches to both the radio image positions and their flux-ratio, wheras
 models with only one SIE component \citep{Marlow99,Xu14} fail to
@@
 position of a few lensed images, can lead to improper lens models and
-a misinterpretation of the origin of flux-ratio anomalies. \textbf{While future large-scale surveys, such as the DES, KiDS-VIKING, Euclid, and LSST, are expected to
+a misinterpretation of the origin of flux-ratio anomalies. \textbf{While upcoming large-scale surveys, such as the DES, KiDS-VIKING, Euclid, and LSST, are expected to
 deliver new large samples of gravitationally lensed quasars, in the

### 2015-05-03 papers/B1555_EdgeOn/B1555_letter.tex
Add about K+03 flux ratio measurements

@@
 \citep{Oguri}.  The inputs to the model are the observed image
-positions and flux densities measured by the radio observations of
-\citet{Marlow99}, \textbf{who also} presented a singular isothermal ellipsoid
-(SIE) model that provided the first fit[a good fit--John/ but It's not good compare to our model--JW] to the image positions but
+positions and flux densities measured by the radio observations.
+\textbf{We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
+(SIE) model that provided a good fit to the image positions but
 does not reproduce the strong flux-ratio anomaly between components A
-and B.  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
+and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
+\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities than in \citet{Marlow}.}
+
 Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
@@
 \textbf{For each model, we explore the parameter space in the following way: 
-(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \deg$ to the edge-on disk component.
+(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component.
 We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position.
@@
 Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
-(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimize [CHECK THE ALGORITHM?] to reach the final best-fit for each model.}
+(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}
 
@@
 B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
-C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $+0.0280$ \\  
-D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $+0.3680$ \\  
+C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $-0.0280$ \\  
+D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $-0.3680$ \\  
 \hline
@@
 
-In this letter, we focus on the effect of more complicated mass
-distributions for the lens galaxy on flux-ratio anomalies.
-Traditionally, flux anomalous lensed quasars are radio-loud systems
-that are firstly discovered in radio observations. While radio data
+In this letter, we \textbf{instead} focus on the effect that more complicated lens galaxy mass
+distributions \textbf{have} on flux-ratio anomalies.
+Traditionally, flux-anomalous lensed quasars \textbf{have been} radio-loud, initially discovered in radio observations. While radio data
 provide reliable information on the positions and the fluxes of the

### 2015-05-03 papers/B1555_EdgeOn/B1555_letter.tex
Update to Leon's comments

@@
 of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
-However, observations of the Local Group find many fewer satellite
+However, observations of the Local Group show many fewer satellite
 galaxies than are predicted by the simulations, even when taking into
@@
 stars, nor to dust extinction. This makes flux-ratio anomalies a promising
-tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002}.  At
-present, the amount of substructure derived from flux-ratio anomalies
-is in disagreement with predictions from numerical simulations, with
+tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13} [NEED MORE REF].  
+At present, the amount of substructure derived from flux-ratio anomalies
+seems to be disagreement with predictions from numerical simulations, with
 the former requiring a larger fraction of mass in substructure than
@@
 statistics, it could also be an indication that flux-ratio anomalies
-have a different origin than substructure.
+have a different origin than substructure.[COMMENT ON LINE OF SIGHT EFFECTS?--LEON]
 %
@@
 substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14a,V12}.
+is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.
 
@@
 discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
-has a pair of merging images that show a strong flux-ratio anomaly at
+has a pair of merging images that show a strong \textbf{persistent} flux-ratio anomaly at
 radio wavelengths.  Follow-up observations ruled out radio propagation
@@
 of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
-mass distribution is of key importance.  
+mass distribution is of key importance \textbf{to assess systematics in these statistics}.  
 %Our analysis makes use of
@@
  %\begin{minipage}{140mm}
-  \caption{Multiband observation details of the B1555+375 lens system.}
+  \caption{Observational details of the B1555+375 lens system.}
   \begin{tabular}{@{}llccc}
@@
 and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
-\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities than in \citet{Marlow}.}
+\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities.}
 
@@
 extinction in the disk could cause the \textbf{non-}detection of these
-images.
+images.[REF B0128 PAPER?--LEON]
 
@@
 the performance of a simple lensing potential. Consistent with
-previous studies \citep{Marlow99, Xu14}, our single elliptical
-potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.  We then
-create two separate models of the lensing potential that both
+previous studies \citep{Marlow99, Xu14}, a single elliptical
+potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
+[WHY MODEL BULGE W/ SIE? COMMENT ON THE REASON FOR PICKING MODELS--LEON]
+[I TRY TO EXPLAIN HERE AND MAY NEED TO BE MORE FOCUS--JW]
+\textbf{We notice that the lensed images are close to the center of B1555+375 since its edge-on disk spreads further out of the Einstein radius in the \textit{HST} imaging.
+Instead of constructing the lens galaxy with a primary NFW halo, a secondary bulge, plus an elongated disk, we consider only the bulge plus an disk component, reducing the number of free parameters in the model.
+Also with only four lensed images, mass profiles that are too complicated will not be informative in the lens modelling.}
+We then create two separate models of the lensing potential that both
 incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
 and an exponential edge-on disk (SIE+expdisk). In the second model
-the disk is represented as a very elongated SIE component (2-SIE). [WHY MODEL BULGE W/ SIE? COMMENT ON THE REASON FOR PICKING MODELS--LEON]
+the disk is represented as a very elongated SIE component (2-SIE). 
 The lens system is red, with a strong jump in flux between the F814W
@@
 shear in their model are orthogonal, indicating a possible missing
-ingredient in the lens model. Their results are consistent with the SHARP
-$K^{\prime}$ band observations, in which an edge-on disk crosses the
-radio merging double and which fully accounts for the observed flux-ratio anomaly.  In general, it is well known 
-\citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
+ingredient in the lens model.
+\textbf{Indeed, it's hard to find physical interpretation for an large [IS $\gamma = 0.14$ A LARGE SHEAR?] and orthogonal external shear.
+The SHARP $K^{\prime}$ band observations provide another explaination to their result. The edge-on disk crosses the
+radio merging double is consistent of this missing component and fully accounts for the observed flux-ratio anomaly.} 
+In general, it is well known  \citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
 quasar/AGN images have large degeneracies. Therefore, before

### 2015-05-05 papers/B1555_EdgeOn/B1555_letter.tex
change in modelling procedure description

@@
 \textbf{For each model, we explore the parameter space in the following way: 
-(1) Preparation of priors: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component.
+(1) Preparation of model starting point: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component.
 We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position.
 The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
-(2) Markov Chain Monte Carlo: In {\tt glafic}, we run MCMC to find the a proper set of parameters for further optimization.
-The smallest $\chi^2$ doesn't necessarily give a physical model.
+(2) First optimization: Bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec, and run optimization with amoeba algorithm in {\tt glafic} to reach a first optimal model.
+(3) Markov Chain Monte Carlo: Use the parameters from optimal result as the starting point. We then run MCMC in {\tt glafic} to obtain the best-fit parameters.} 
+%The smallest $\chi^2$ doesn't necessarily give a physical model.
 Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
-(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}
+%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}
 

### 2015-05-05 python/MCMC_full_2dplot.py

@@ -1,0 +1,35 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpat
+
+t=np.loadtxt('SIE2_free_mcmc.dat')
+
+
+chi2=t[:,0]
+sig1,sig2=t[:,1],t[:,6]
+x1,x2=t[:,2],t[:,7]
+y1,y2=t[:,3],t[:,8]
+e1,e2=t[:,4],t[:,9]
+pa1,pa2=t[:,5],t[:,10]
+
+#pick 2 parameters to plot
+para1=sig1
+para2=e1
+n_para='sigma1'
+tot='total counts = %d' %(len(chi2))
+
+plt.figure(1)
+n, bin, patches = plt.hist(para1,50,label=tot)
+plt.xlabel(n_para)
+plt.ylabel('counts')
+
+print len(chi2)
+
+#plt.figure(2)
+#plt.scatter(para1,chi2)
+#plt.xlabel(n_para)
+#plt.ylabel('chi^2')
+plt.legend()
+plt.show()
+
+

### 2015-07-19 papers/B1555_EdgeOn/B1555_letter.tex
update of current 2-SIE parameters
draft update & model dat files

@@
 stars, nor to dust extinction. This makes flux-ratio anomalies a promising
-tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13} [NEED MORE REF].  
+tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,K05,V09,N13}.  
 At present, the amount of substructure derived from flux-ratio anomalies
@@
 
-To model B1555+375, we use the lens modelling code {\tt glafic}
-\citep{Oguri}.  The inputs to the model are the observed image
+%To model B1555+375, we use the lens modelling code {\tt glafic} \citep{Oguri}.  
+\textbf{To model B1555+375, we use the lens modelling code {\tt gravlens} \citep{Kee01}.  
+The inputs to the model are the observed image
 positions and flux densities measured by the radio observations.
-\textbf{We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
+We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
 (SIE) model that provided a good fit to the image positions but
@@
 
-Although the flux-ratio anomaly that is observed in the radio data \textbf{implies there must be some perturbation to the mass model, which} may be
+Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
 caused by substructure in the lensing galaxy, our high-resolution near
 infrared imaging suggests another explanation.  In both the $K^\prime$
-band adaptive optics data and the \textit{HST} infrared imaging (\textbf{see} in
+band adaptive optics data and the \textit{HST} infrared imaging (see in
 Fig. 1), the lensing galaxy has a clear edge-on disk component with a
@@
 these lensed images lie on or close to the edge-on disk.  Thus, strong
-extinction in the disk could cause the \textbf{non-}detection of these
+extinction in the disk could cause the non-detection of these
 images.[REF B0128 PAPER?--LEON]
@@
 potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
-[WHY MODEL BULGE W/ SIE? COMMENT ON THE REASON FOR PICKING MODELS--LEON]
-[I TRY TO EXPLAIN HERE AND MAY NEED TO BE MORE FOCUS--JW]
-\textbf{We notice that the lensed images are close to the center of B1555+375 since its edge-on disk spreads further out of the Einstein radius in the \textit{HST} imaging.
-Instead of constructing the lens galaxy with a primary NFW halo, a secondary bulge, plus an elongated disk, we consider only the bulge plus an disk component, reducing the number of free parameters in the model.
-Also with only four lensed images, mass profiles that are too complicated will not be informative in the lens modelling.}
-We then create two separate models of the lensing potential that both
-incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
-and an exponential edge-on disk (SIE+expdisk). In the second model
-the disk is represented as a very elongated SIE component (2-SIE). 
+\textbf{Our next step is to examine the idea that if an edge-on disk can cause similar perturbations to the lens like substructures which resulting in flux ratio anomalies in merging images.
+In \citet{Kee98}, they explore strong lensing by spiral glaxies with SIE+ exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively.
+An exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk.
+We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of an edge-on disk passing through the merging double in the lens system.
+}
+%We then create two separate models of the lensing potential that both
+%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
+%and an exponential edge-on disk (SIE+expdisk). In the second model
+%the disk is represented as a very elongated SIE component (2-SIE). 
 The lens system is red, with a strong jump in flux between the F814W
@@
 
-\textbf{For each model, we explore the parameter space in the following way: 
-(1) Preparation of model starting point: Applying the information in the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the edge-on disk component.
-We then use the best-fit model of \citet{Marlow99} as the starting point for the bulge\textbf{/halo} component and also the source position.
-The rest of parameters in the disk component are set to be the same as the bulge/halo component as the starting point.
-(2) First optimization: Bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec, and run optimization with amoeba algorithm in {\tt glafic} to reach a first optimal model.
-(3) Markov Chain Monte Carlo: Use the parameters from optimal result as the starting point. We then run MCMC in {\tt glafic} to obtain the best-fit parameters.} 
+\textbf{To obtain the optimal lens model, we explore the parameter space in the following way: 
+(1) Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk.
+We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position.
+The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
+(2) Optimal model search: We let all model parameter varies but bind the centroid position of two conponents with a strong Gaussian prior ($\sigma = 0.05 $ arcsec).
+Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $chi^2$ in paramter space.
+(3) Markov Chain Monte Carlo: After obtaining the optimal lens model, we run MCMC to explore the parameter space for the model uncertainties.} 
 %The smallest $\chi^2$ doesn't necessarily give a physical model.
@@
 
-The \textbf{final} best-fit parameters are shown in Table
-2. Both of these models produce lensed images with positions and
-fluxes that are good matches to the radio observations.  While both of
-the two component models produce significantly improved matches to the
-fluxes than the single SIE model, the 2-SIE version has a somewhat
-better performance than the SIE+expdisk model in reproducing flux
-ratios. The comparison of the observations and our lens modelling is
-given in Figure 3 and Tables 3 \& 4.  We have not included an external
-shear component into our model because the constraints provided by the
+The best-fit parameters are shown in Table 2. 
+%Both of these models produce lensed images with positions and
+%fluxes that are good matches to the radio observations.  
+%While both of the two component models 
+\textbf{By adding an elongated exponential disk to a smooth potential model,  our lens model shows significant improvement on the flux ratios when comparing to the single SIE model, includeing the flux ratio anomaly between the merging images.}
+%the 2-SIE version has a somewhat
+%better performance than the SIE+expdisk model in reproducing flux
+%ratios. 
+The comparison of the observations and our lens modelling is
+given in Figure 3 and Tables 3 \& 4.  We have not included a third component such as an external
+shear component or NFW halo into our model because the number of constraints provided by the
 image positions and fluxes would not be sufficient to constrain such a
@@
 %\plotone{point_source.eps}
-\includegraphics[width=84mm]{point_source.eps}
-\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle.
+\includegraphics[width=84mm]{gravlens_exp_try5_plot.eps}
+\caption{Radio observation(blue plus sign) and model-predicted(red open circle) image positions of B1555+375.
+Criticle curves are shown with blue solid line and caustics are shown with red dash line.
+The position of the source is at $(-0.1953,-0.1494)$, marked by a red filled circle.
+The centroid positions of two lens components are marked by black filled triangles.
 \label{fig2}}
@@
 
+%\begin{figure}
+%\plotone{point_source.eps}
+%\includegraphics[width=84mm]{point_source.eps}
+%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
+The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle.
+\label{fig2}}
+%\end{figure}
+
 \begin{table}
-% \centering
+ \centering
 % \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 lens models.
-Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
+  \caption{Best-fit parameters of B1555+375 lens model.
 Positions are offsets from radio image component A measured in units of arcsec.
-The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
+The velocity dispersion $\sigma$ is in units of $km/s$.
 \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
@@
 \hline 
- Parameter  & \multicolumn{2}{c}{Lens model} \\
-		&SIE+expdisk& 2-SIE		   
+ Parameter  & SIE & Expdisk 		   
 \\
 \hline
-$x_1$  	  & $-0.1794$	& $-0.1884$  \\
-$y_1$	  &$-0.1881$	&$-0.1607$  \\
+$x$  	  & $-0.1818$	&$-0.1472$ 	  \\
+$y$	  &$-0.1988$	&$-0.2057$	 \\
 
-$\sigma_1$ &$140.3$     & $145.3$ \\
-$e_1$	  & $0.21$	& $0.24$ \\
-$\theta_1$ &$73.6 \degr$ & $99.5 \degr$ \\
-\hline
-$x_2$	  &$-0.1639$ 	&$-0.1594$  \\
-$y_2$	  &$-0.2542$	& $-0.2225$  \\
-$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
-$\sigma_2$ & ...        &$122.7$ \\  
-$e_2$	  &$0.84$	&$0.82$  \\
-$\theta_2$ &$4.0\degr$ &$6.5\degr$  \\
-$r_e$	  & $0.21 ''$ &  ... \\
+$b$ &$0.21 $  & ...   \\
+$\kappa_0$ & ... & $0.11$        \\  
+$e$	  & $0.31$	&$0.87$ \\
+$\theta$ &$2.96 \degr$ &$7.0\degr$ \\
+$r_s$	& ...  & $0.28$\\
 \hline
@@
 %\end{minipage}
-
 \end{table}
 
+%\begin{table}
+
+%  \caption{Best-fit parameters of B1555+375 lens models.
+Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
+Positions are offsets from radio image component A measured in units of arcsec.
+The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
+\textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
+%  \begin{tabular}{@{}ccc}
+%\hline 
+% Parameter  & \multicolumn{2}{c}{Lens model} \\
+%		&SIE+expdisk& 2-SIE		   
+%\\
+%\hline
+%$x_1$  	  & $-0.1794$	& $-0.1771$  \\
+%$y_1$	  &$-0.1881$	&$-0.2032$  \\
+
+%$\sigma_1$ &$140.3$     & $146.1$ \\
+%$e_1$	  & $0.21$	& $0.15$ \\
+%$\theta_1$ &$73.6 \degr$ & $155.3 \degr$ \\
+%\hline
+%$x_2$	  &$-0.1639$ 	&$-0.1562$  \\
+%$y_2$	  &$-0.2542$	& $-0.2195$  \\
+%$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
+%$\sigma_2$ & ...        &$122.6$ \\  
+%$e_2$	  &$0.84$	&$0.86$  \\
+%$\theta_2$ &$4.0\degr$ &$7.9\degr$  \\
+%$r_e$	  & $0.21 ''$ &  ... \\
+%\hline
+%$\chi ^2$ & $1.05$ & $0.04$ \\
+%\hline
+%\end{tabular}
+%\end{table}
+
 \begin{table*}
-%\centering
+\centering
  \begin{minipage}{140mm}
-  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
+  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).}
   \begin{tabular}{@{}ccccccc}
-
 \hline
 
-Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
-					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
-					 &East &North &East 		&North &East 		&North\\ 
+Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
+					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
+					 &East &North &East 		&North \\ 
 \hline
-A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0726 $  &  $+0.0480$  \\  
-C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4117 $  &   $-0.0280$ \\  
-D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1619$    &  $-0.3680$ \\  
+A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
+B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0727$ &$+0.0477$  \\  
+C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4117$ &$-0.0281$   \\  
+D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1630$ &$-0.3653$  \\  
 \hline
@@
 \medskip
-
 \end{table*}
 
+%\begin{table*}
+%\centering
+ %\begin{minipage}{140mm}
+ % \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
+ % \begin{tabular}{@{}ccccccc}
+
+%\hline
+
+%Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
+%					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
+%					 &East &North &East 		&North &East 		&North\\ 
+%\hline
+%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
+%B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0755 $  &  $+0.0414$  \\  
+%C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4122 $  &   $-0.0267$ \\  
+%D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1620$    &  $-0.3533$ \\  
+%\hline
+%\end{tabular}
+
+%\end{minipage}
+%medskip
+%\end{table*}
+
 \begin{table}
-% \centering
+ \centering
 % \begin{minipage}{140mm}
@@
 \hline
-	& MERLIN  & \multicolumn{3}{c}{Model}\\
-		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
+	& MERLIN  & \multicolumn{2}{c}{Model}\\
+		&5 GHz   & 1-SIE & SIE+expdisk \\
 \hline
-$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.61$ \\ 
-$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $1.97$\\
-$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.63$\\
+$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$  \\ 
+$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.17$ \\
+$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $8.69$ \\
 
@@
 \medskip
+\end{table}
 
-\end{table}
+%\begin{table}
+% \centering
+% \begin{minipage}{140mm}
+%  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
+% \begin{tabular}{@{}ccccccc}
+
+%\hline
+%	& MERLIN  & \multicolumn{3}{c}{Model}\\
+%		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
+%\hline
+%$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.62$ \\ 
+%$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $2.00$\\
+%$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.56$\\
+
+%\hline
+%\end{tabular}
+
+%\end{minipage}
+%\medskip
+%\end{table}
 

### 2015-07-19 models/B1555/glafic_code/emcee_expdisk.py

@@ -2,6 +2,11 @@ import os
 import numpy as np
 import emcee
 import scipy.stats
+import itertools as it
+
+img_obs=np.array([0.0,0.0,17.0,0.0726,0.0480,10.54,0.4117,-0.0280,8.619,0.1619,-0.3680,1.462])
+err_obs=np.array([1.0e-6,1.0e-6,1.70,0.01,0.01,0.97,0.01,0.01,0.83,0.06,0.06,0.13])
+
 
 def call_findimage(paras):
     
@@ -28,7 +33,7 @@ def call_findimage(paras):
             if i<2:
                     lens_para[2]=lens_para[2]+'%f '%paras[11+i]  #source
 
-	lens_para[1]=lens_para[1]+'%f '%paras[10] #r_e for sersic profile
+        lens_para[1]=lens_para[1]+'%f '%paras[10] #r_e for sersic profile
         
         # write lens models into input file
         inp.write('lens sie '+lens_para[0]+'0.0 0.0 \n')
@@ -47,23 +52,22 @@ def call_findimage(paras):
         ## run glafic
         
         #os.system('glafic')
-        os.system('glafic emcee_exp.input') #this line works for linux machine
-        #os.system('~/Documents/glafic/glafic emcee_exp.input')
+        #os.system('glafic emcee_exp.input') #this line works for linux machine
+        os.system('~/Documents/glafic/glafic emcee_exp.input')
         
         #sub.call('glafic emcee.input')
         
         # read findimg result
         r=np.loadtxt('emcee_exp_point.dat')
-        wash=open('emcee_exp_point.dat','w')
-        wash.write('0 0 0 0\n 0 0 0 0')
-        wash.close()  # wash out after load findimg result
 
-        print r
         rr=np.array(r[0])
+        mock=np.array([0])
+        mock=np.append(mock,rr)
         print rr
-        nimg=rr[0]
-
-	poss=np.array([rr[2],rr[3]]) #position of source
+        print mock
+        #        print r
+        
+        nimg=mock[1]
 
         if nimg==4:  # the n_img == 4
 	    
@@ -78,42 +82,64 @@ def call_findimage(paras):
         else:
             out=np.array([1]) # flag as not quad system
     
+        wash=open('emcee_exp_point.dat','w')
+        wash.write('0 0 0 0\n 0 0 0 0')
+        wash.close()  # wash out after load findimg result
 
 
         #print out
[…]

### 2015-07-19 models/B1555/gravlens_code/emcee_gravlens.py

@@ -1,0 +1,357 @@
+import os
+import numpy as np
+import emcee
+import scipy.stats
+import itertools as it
+import commands
+
+img_obs=np.array([0.0,0.0,17.0,0.0726,0.0480,10.54,0.4117,-0.0280,8.619,0.1619,-0.3680,1.462])
+err_obs=np.array([1.0e-6,1.0e-6,1.70,0.01,0.01,0.97,0.01,0.01,0.83,0.06,0.06,0.13])
+
+
+def call_findimage(paras):
+    
+    ## create input file
+        head=open('input_exp.head','r')
+        #tail=open('input_exp.tail','r')
+        inp=open('B1555_emcee.input','w')
+        
+        # read head of input template
+        for line in head.readlines():
+            #print line
+            inp.write(line)
+    
+        head.close()
+        inp.write('\n')
+        
+        # prepare for lens model parameters
+        lens_para=['','','']
+        
+        for i in range(5):
+            lens_para[0]=lens_para[0]+'%f '%paras[i]    #bulge
+            lens_para[1]=lens_para[1]+'%f '%paras[5+i]  #disk
+
+
+        lens_para[1]=lens_para[1]+'0.0 0.0 ''%f '%paras[10] #r_s for expdisk
+        
+        # write lens models into input file
+        inp.write('alpha '+lens_para[0]+'0.0 0.0 0.0 0.0 1.0 \n') #SIE
+        inp.write('expdisk '+lens_para[1]+'0.0 0.0 \n')       #expdisk
+
+        inp.write('\n 0 0 0 0 0 0 0 0 0 0 \n 0 0 0 0 0 0 0 0 0 0 \n')
+
+        # findimg [souce pos]
+
+        lens_para[2]=lens_para[2]+'%f '%paras[11]+'%f '%paras[12]
+
+        inp.write('\n findimg '+lens_para[2]+'\n')
+        
+
+        inp.close()
+        
+        ##
+        
+        ## run gravlens
+        
+        #os.system('glafic')
+        #os.system('glafic emcee_exp.input') #this line works for linux machine
+        #os.system('./lensmodel emcee_exp.input')
+
+        
+        # read findimg result [output on screen]
+        '''
+        r=np.loadtxt('emcee_exp_point.dat')
+
+        rr=np.array(r[0])
+        mock=np.array([0])
+        mock=np.append(mock,rr)
+        print rr
[…]

### 2015-07-19 python/emcee_corner.py

@@ -3,7 +3,7 @@ import triangle
 import matplotlib.pyplot as plt
 #import matplotlib.patches as mpat
 
-file_name=['chain_src.dat']
+file_name=['exp_chain.dat']
 
 k=0
 for i in file_name:
@@ -35,10 +35,10 @@ data=t
 
 #ndim, nsamples = 10, len(chi2)
 
-figure = triangle.corner(data, labels=[r"$\sigma 1$", r"$x1$", r"$y1$",
+figure = triangle.corner(data, labels=[r"$b1$", r"$x1$", r"$y1$",
                                        r"$e1$",r"$PA1$",
-                                        r"$x_{sh}$", r"$y_{sh}$",
-                                       r"$\gamma$",r"$PA_{sh}$"
+                                       r"$b2$", r"$x2$", r"$y2$",
+                                       r"$e2$",r"$PA2$",r"$rs$"
                                        ,r"x_s",r"y_s"],
 #                         extents=[(120.,170.),(0.1,0.25),(-0.35,-0.2),(0.,0.5),(60.,110.),
 #                                  (110.,160.),(0.1,0.25),(-0.3,-0.1),(0.75,0.95),(0.,20.)],

### 2015-07-19 python/gravlens_plot.py

@@ -6,7 +6,7 @@ import matplotlib.patches as mpat
 
 # gravlens file name
 
-name='mode1.crit'
+name='B1555_expdisk_try5.crit'
 
 # lensed images
 ## system == B1555
@@ -15,16 +15,16 @@ x0=[0.0, 0.0726,0.4117,0.1619]
 y0=[0.0, 0.0480, -0.0280,-0.3680]
 
 # model
-x=[0.4108 , 0.1617 ,-0.00,0.0728]
-y=[-0.0309,-0.3565,-0.0 ,0.0576]
+x=[0.4117 , 0.1629 ,-0.00,0.0727]
+y=[-0.0281,-0.3653,-0.00 ,0.0477]
 
 # model paras
 # source
-sx,sy=2.011120e-01, -1.430824e-01
+sx,sy= 1.952576e-01, -1.493771e-01
 
 # mass profile centeroid
-cx=[1.883924e-01,1.594156e-01] # x position
-cy=[-1.607033e-01, -2.224752e-01] # y position
+cx=[ 1.818271e-01, 1.471605e-01] # x position
+cy=[ -1.987580e-01, -2.056755e-01] # y position
 
 
 ##----call functions in the end----##
@@ -79,7 +79,7 @@ def caus():
 
 ## souce & component positions
 def model_plot():
-    plt.plot(sx,sy,'o',ms=5,mec='k',mfc='k',label='source')
+    plt.plot(sx,sy,'o',ms=5,mec='k',mfc='r',label='source')
     plt.plot(cx,cy,'^',label='lens',mfc='k')
 
 ##----
@@ -100,5 +100,8 @@ crit()
 caus()
 model_plot()
 img_pos()
+
+#plt.xlim(-0.1,0.5)
+#plt.ylim(-0.5,0.2)
 plt.legend(loc=4)
 plt.show()

### 2015-07-20 papers/B1555_EdgeOn/B1555_letter.tex
B1555 paper minor text change

@@
 
-\textbf{To obtain the optimal lens model, we explore the parameter space in the following way: 
+\textbf{To obtain the optimum lens model, we explore the parameter space with the following steps: 
 (1) Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk.
@@
 The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
-(2) Optimal model search: We let all model parameter varies but bind the centroid position of two conponents with a strong Gaussian prior ($\sigma = 0.05 $ arcsec).
-Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $chi^2$ in paramter space.
-(3) Markov Chain Monte Carlo: After obtaining the optimal lens model, we run MCMC to explore the parameter space for the model uncertainties.} 
+(2) Optimum model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec).
+Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
+(3) Markov Chain Monte Carlo: After obtaining the optimum lens model, we run MCMC to explore the parameter space for the uncertainties.} 
 %The smallest $\chi^2$ doesn't necessarily give a physical model.
@@
 
-The best-fit parameters are shown in Table 2. 
+The optimum model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
 %Both of these models produce lensed images with positions and
@@
 %While both of the two component models 
-\textbf{By adding an elongated exponential disk to a smooth potential model,  our lens model shows significant improvement on the flux ratios when comparing to the single SIE model, includeing the flux ratio anomaly between the merging images.}
 %the 2-SIE version has a somewhat
@@
 %ratios. 
-The comparison of the observations and our lens modelling is
-given in Figure 3 and Tables 3 \& 4.  We have not included a third component such as an external
+Tables 3 \& 4 show the comparison between radio data and model predicted image positions and flux ratios.  
+\textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}
+We have not included a third component such as an external
 shear component or NFW halo into our model because the number of constraints provided by the
@@
 % \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 lens model.
+  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model.
 Positions are offsets from radio image component A measured in units of arcsec.
@@
 $e$	  & $0.31$	&$0.87$ \\
-$\theta$ &$2.96 \degr$ &$7.0\degr$ \\
+$\theta$ &$2.96 \degr$ &$7.00\degr$ \\
 $r_s$	& ...  & $0.28$\\
@@
 % \begin{minipage}{140mm}
-  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
+  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
   \begin{tabular}{@{}ccccccc}
@@
 	& MERLIN  & \multicolumn{2}{c}{Model}\\
-		&5 GHz   & 1-SIE & SIE+expdisk \\
+		&5 GHz   & SIE-only & SIE+expdisk \\
 \hline

### 2015-07-20 models/B1555/gravlens_code/emcee_gravlens.py

@@ -263,10 +263,11 @@ nstep=10000  #number of MCMC steps
 mean=[2.052429e-01, 1.818271e-01, -1.987580e-01, 3.091056e-01, 2.957686e+00,
       1.100000e-01, 1.471605e-01, -2.056755e-01, 8.660612e-01, 6.996249e+00,2.770794e-01,
       1.952576e-01, -1.493771e-01]
-sig=[0.01,0.01,0.01,0.01,1,0.01,0.01,0.01,0.01,1,0.01,0.01,0.01]
+#sig=[0.01,0.01,0.01,0.01,1,0.01,0.01,0.01,0.01,1,0.01,0.01,0.01]
+sig=[0.05,0.05,0.05,0.02,10,0.05,0.05,0.05,0.02,10,0.05,0.05,0.05]
 #sig=np.zeros(13)
 
-w_factor=5.0 # range of random start point
+#w_factor=5.0 # range of random start point
 
 
 # random generate star points
@@ -289,7 +290,7 @@ find=open('exp_imgchain.dat','w')
 #pos, prob, state = sampler.run_mcmc(p0,burn)
 
 #print pos[0]
-
+'''
 ## collect valid start point
 
 flag=-5e11 # flag for failure chain
@@ -321,10 +322,12 @@ while k<(nwalker-1):
 p2=np.zeros(((nwalker,ndim)))
 for i in range(nwalker):
 	p2[i,:]=p1[(i*ndim):((i+1)*ndim)]
-
+'''
 ## (real) burn-in steps
 
-p3, prob, state = sampler.run_mcmc(p2,burn2)
+#p3, prob, state = sampler.run_mcmc(p2,burn2)
+p3, prob, state = sampler.run_mcmc(p0,burn2)
+
 
 # the end of burn-in step
 find.write('# \n')

### 2015-07-20 python/emcee_corner.py

@@ -35,9 +35,9 @@ data=t
 
 #ndim, nsamples = 10, len(chi2)
 
-figure = triangle.corner(data, labels=[r"$b1$", r"$x1$", r"$y1$",
+figure = triangle.corner(data, labels=[r"$b$", r"$x1$", r"$y1$",
                                        r"$e1$",r"$PA1$",
-                                       r"$b2$", r"$x2$", r"$y2$",
+                                       r"$kappa_0$", r"$x2$", r"$y2$",
                                        r"$e2$",r"$PA2$",r"$rs$"
                                        ,r"x_s",r"y_s"],
 #                         extents=[(120.,170.),(0.1,0.25),(-0.35,-0.2),(0.,0.5),(60.,110.),

### 2015-07-20 papers/B1555_EdgeOn/B1555_letter.tex
add para uncertainties to draft
more text change in Modelling part

@@
 potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
-\textbf{Our next step is to examine the idea that if an edge-on disk can cause similar perturbations to the lens like substructures which resulting in flux ratio anomalies in merging images.
-In \citet{Kee98}, they explore strong lensing by spiral glaxies with SIE+ exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively.
-An exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk.
-We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of an edge-on disk passing through the merging double in the lens system.
+\textbf{Our next step is to examine if an edge-on disk can cause similar perturbations in the stong lensing system like substructures which resulting in flux ratio anomalies within merging images.
+In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively.
+Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk.
+We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
 }
@@
 % \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model.
+  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties.
 Positions are offsets from radio image component A measured in units of arcsec.
@@
 \hline
-$x$  	  & $-0.1818$	&$-0.1472$ 	  \\
-$y$	  &$-0.1988$	&$-0.2057$	 \\
+$x$  	  & $-0.1818 (0.005)$	&$-0.1472 (0.003)$ 	  \\
+$y$	  &$-0.1988 (0.005)$	&$-0.2057 (0.010)$	 \\
 
-$b$ &$0.21 $  & ...   \\
-$\kappa_0$ & ... & $0.11$        \\  
-$e$	  & $0.31$	&$0.87$ \\
-$\theta$ &$2.96 \degr$ &$7.00\degr$ \\
-$r_s$	& ...  & $0.28$\\
+$b$ &$0.21 (0.01)$  & ...   \\
+$\kappa_0$ & ... & $0.11 (0.01)$        \\  
+$e$	  & $0.31(0.01)$	&$0.87 (0.01)$ \\
+$\theta$ &$2.96 \degr (0.64 \degr)$ &$7.00\degr (0.70 \degr)$ \\
+$r_s$	& ...  & $0.28 (0.005)$\\
 \hline

### 2015-08-04 papers/B1555_EdgeOn/B1555_letter.tex
minor change in B1555 paper draft

@@
 In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively.
-Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk.
+Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}.
 We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
-}
+Detail definition of mass profiles in {\tt gravlens}
+  can be found in \citet{Kee01}.}
 %We then create two separate models of the lensing potential that both

### 2015-08-16 models/B0712/glafic_code/emcee_SIE_sh.py
emcee code change
must update to other systems as well

@@ -37,7 +37,10 @@ def call_findimage(paras):
                     lens_para[2]=lens_para[2]+'%f '%paras[9+i]  #source
         
 	#print paras
-	#print lens_para
+	print lens_para
+
+        # write real chain
+        mcmc.write(lens_para[0]+lens_para[1]+lens_para[2]+'\n')
 
         # write lens models into input file
         inp.write('lens sie '+lens_para[0]+'0.0 0.0 \n')
@@ -50,6 +53,7 @@ def call_findimage(paras):
         
         tail.close()
         inp.close()
+
         
         ##
         
@@ -175,6 +179,7 @@ def lnprob(paras):
         else:
             chi2=np.inf
 
+        prob_chi2.write(chi2+'\n')
         return -0.5*np.absolute(chi2)
 
 
@@ -214,19 +219,21 @@ def writeimg(paras):
 
 #-------------main-----------------
 
-nwalker=200 #number of chains
+nwalker=30 #number of chains
 ndim=11   #number of parameters
 burn=10   #number of (burn in) collect step
-burn2=300 #number of (real) burn in step
-nstep=5000  #number of MCMC steps
+#burn2=2000 #number of (real) burn in step
+burn2=1
+nstep=10  #number of MCMC steps
 
 ## set up for start points
 
 # SIE+shear
-mean=[2.244092e+02,-8.169302e-01,-4.527316e-02,0.4,-6.346850e+01,
--5.842317e-01,  1.003198e-02,  2.491543e-01,  2.265247e+01
-,-8.356879e-01,  1.349689e-01]
-sig=[15,0.5,0.5,0.2,20,0.5,0.5,0.5,20,0.5,0.5]
+mean=[2.36496436e+02,  -1.10879100e+00,  -1.04252000e-01,
+      8.43468000e-01,   1.02018344e+02,  -1.11414000e-01,
+      -2.78323000e-01,   5.04820000e-01,   7.44723100e+00,
+      -6.85072000e-01,   2.71726000e-01]
+sig=[5,0.05,0.05,0.05,5,0.05,0.05,0.05,5,0.05,0.05]
 
 w_factor=1.0 # range of random start point
 
@@ -246,6 +253,10 @@ sampler=emcee.EnsembleSampler(nwalker,ndim,lnprob)
 find=open('imgchain.dat','w')
 
 
+# create real para chain & prob chain
[…]

### 2015-08-16 python/emcee_corner.py

@@ -3,7 +3,7 @@ import triangle
 import matplotlib.pyplot as plt
 #import matplotlib.patches as mpat
 
-file_name=['exp_chain.dat']
+file_name=['SIEsh_5_chain.dat']
 
 k=0
 for i in file_name:
@@ -37,8 +37,10 @@ data=t
 
 figure = triangle.corner(data, labels=[r"$b$", r"$x1$", r"$y1$",
                                        r"$e1$",r"$PA1$",
-                                       r"$kappa_0$", r"$x2$", r"$y2$",
-                                       r"$e2$",r"$PA2$",r"$rs$"
+#                                       r"$kappa_0$",
+                                       r"$x2$", r"$y2$",
+                                       r"$e2$",r"$PA2$"
+                                       #,r"$rs$"
                                        ,r"x_s",r"y_s"],
 #                         extents=[(120.,170.),(0.1,0.25),(-0.35,-0.2),(0.,0.5),(60.,110.),
 #                                  (110.,160.),(0.1,0.25),(-0.3,-0.1),(0.75,0.95),(0.,20.)],

### 2015-08-16 python/sigma.py

@@ -1,0 +1,31 @@
+import numpy as np
+
+file_name=['SIEsh_5_chain.dat']
+
+k=0
+for i in file_name:
+    temp=np.loadtxt(i)
+    if k==0:
+        t=temp
+    
+    else:
+        t=np.append(t,temp,axis=0)
+    
+    k=k+1
+
+
+data=t
+
+npara=t.shape[1]
+nch=t.shape[0]
+
+mid=nch/2 #median
+sigL=np.floor(0.16*nch)
+sigR=np.floor(0.84*nch)
+
+for i in range(npara):
+    array=t[:,i]
+    array=np.sort(array)
+#    print array[sigL],array[mid],array[sigR]
+    print array[mid]-array[sigL],array[sigR]-array[mid]
+

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
emcee code change
must update to other systems as well
update on Simona's comments

@@
 galaxies.  Furthermore, lower-mass satellites may not be able to
-retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
+retain the gas needed for ongoing star formation \citep[e.g.][]{P11},
 rendering them effectively dark.  These factors make gravitational
@@
 stars, nor to dust extinction. This makes flux-ratio anomalies a promising
-tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,K05,V09,N13}.  
-At present, the amount of substructure derived from flux-ratio anomalies
-seems to be disagreement with predictions from numerical simulations, with
-the former requiring a larger fraction of mass in substructure than
-expected \citep{Xu14}. While this could be the result of small sample
+tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
+%At present, the amount of substructure derived from flux-ratio anomalies
+%seems to be disagreement with predictions from numerical simulations, 
+%with the former requiring a larger fraction of mass in substructure than
+%expected \citep{Xu14}. 
+\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations, with the less level of flux anomalies showing in simulation results \citep{Xu14}.}
+While this could be the result of small sample
 statistics, it could also be an indication that flux-ratio anomalies
-have a different origin than substructure.[COMMENT ON LINE OF SIGHT EFFECTS?--LEON]
+have a different origin than substructure.[OTHER POSSIBLE ORIGONS--SIMONA]
 %
@@
 galaxy clearly stands out.}
+\textbf{The lens system is red, with a strong jump in flux between the F814W
+(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so 
+we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
+$z_s =1.5$.
+This assumption on redshifts is needed for the lens modelling because some lens model parameters contain distance information.
+However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}
 
@@
 infrared imaging suggests another explanation.  In both the $K^\prime$
-band adaptive optics data and the \textit{HST} infrared imaging (see in
+band adaptive optics data and the \textit{HST} infrared imaging (see 
 Fig. 1), the lensing galaxy has a clear edge-on disk component with a
@@
 potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
-\textbf{Our next step is to examine if an edge-on disk can cause similar perturbations in the stong lensing system like substructures which resulting in flux ratio anomalies within merging images.
-In \citet{Kee98}, they explore strong lensing by spiral glaxies with the SIE+exponential disk+NFW model, corresponding to the bulge, disk, and halo respectively.
+\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images.
 Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}.
 We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
-Detail definition of mass profiles in {\tt gravlens}
-  can be found in \citet{Kee01}.}
+The free parameters of the models are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$), and exponential disk: intrinsic central density ($kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
+Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
+  We have not included a third component such as an external
+shear component or NFW halo into our model because the number of constraints provided by the
+image positions and fluxes would not be sufficient to constrain such a
+model. However, we note that the image not affected by dust (image C)
+in the Keck AO data is consistent with negligible shear (i.e. shear
+strength $\Gamma_s=0.002$), when modeled with the pixelized technique
+of \citet{V09}.
 %We then create two separate models of the lensing potential that both
@@
 %the disk is represented as a very elongated SIE component (2-SIE).
-The lens system is red, with a strong jump in flux between the F814W
-(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so
-we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
-$z_s =1.5$.
-\textbf{This assumption on redshifts is needed because some lens model parameters contain distance information.
-However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}
 
-\textbf{To obtain the optimum lens model, we explore the parameter space with the following steps: 
-(1) Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk.
+To obtain \textbf{the minimum $\chi^2$} [OR BEST-FIT MODEL?--JEN] lens model, we explore the parameter space with the following steps: 
+\begin{itemize}
+\item Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk.
 We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position.
 The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
-(2) Optimum model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec).
+\item Best-fit model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec).
 Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
-(3) Markov Chain Monte Carlo: After obtaining the optimum lens model, we run MCMC to explore the parameter space for the uncertainties.} 
+\item Markov Chain Monte Carlo: After obtaining the best-fit lens model, we run MCMC to explore the parameter space for the uncertainties.
+\end{itemize}
 %The smallest $\chi^2$ doesn't necessarily give a physical model.
@@
 
-The optimum model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
+The best-fit model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
 %Both of these models produce lensed images with positions and
@@
 \textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}
-We have not included a third component such as an external
-shear component or NFW halo into our model because the number of constraints provided by the
-image positions and fluxes would not be sufficient to constrain such a
-model. However, we note that the image not affected by dust (image C)
-in the Keck AO data is consistent with negligible shear (i.e. shear
-strength $\Gamma_s=0.002$), when modeled with the pixelized technique
-of \citet{V09}.
 
@@
 \hline
-$x$  	  & $-0.1818 (0.005)$	&$-0.1472 (0.003)$ 	  \\
-$y$	  &$-0.1988 (0.005)$	&$-0.2057 (0.010)$	 \\
+$x$  	  & $-0.1818 \pm 0.005$	&$-0.1472 \pm 0.005$ 	  \\
+$y$	  &$-0.1988 \pm 0.005$	&$-0.2057 \pm 0.006$	 \\
 
-$b$ &$0.21 (0.01)$  & ...   \\
-$\kappa_0$ & ... & $0.11 (0.01)$        \\  
-$e$	  & $0.31(0.01)$	&$0.87 (0.01)$ \\
-$\theta$ &$2.96 \degr (0.64 \degr)$ &$7.00\degr (0.70 \degr)$ \\
-$r_s$	& ...  & $0.28 (0.005)$\\
+$b$ &$0.21 \pm 0.01$  & ...   \\
+$\kappa_0$ & ... & $0.11 \pm 0.01$        \\  
+$e$	  & $0.31\pm 0.01$	&$0.87 \pm 0.01$ \\
+$\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
+$R_s$	& ...  & $0.28 \pm 0.01$\\
 \hline
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
-B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0727$ &$+0.0477$  \\  
-C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4117$ &$-0.0281$   \\  
-D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1630$ &$-0.3653$  \\  
+B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
+C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
+D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
 \hline
@@
 \hline
-$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$  \\ 
-$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.17$ \\
-$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $8.69$ \\
+$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
+$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
+$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\
 
@@
 disk. This newly discovered edge-on disk provides a strong prior for our
-lens modelling.  With \textbf{an additional disk component}, our models produce
+lens modelling.  With an additional disk component, our model 
 matches to both the radio image positions and their flux-ratio, wheras
@@
 \section*{Acknowledgments}
-S.V. is grateful to Dandan Xu for useful discussion on the nature of flux-ratio anomalies in high resolution numerical simulations.
+S.V. is grateful to Dandan Xu for useful discussion.
 L.V.E.K. is supported in part through an NWO-VICI career grant (project number 639.043.308).

### 2015-08-17 models/B0712/glafic_code/emcee_SIE_sh.py

@@ -179,7 +179,7 @@ def lnprob(paras):
         else:
             chi2=np.inf
 
-        prob_chi2.write(chi2+'\n')
+        prob_chi2.write('%f'%chi2+'\n')
         return -0.5*np.absolute(chi2)
 
 
@@ -219,20 +219,18 @@ def writeimg(paras):
 
 #-------------main-----------------
 
-nwalker=30 #number of chains
+nwalker=200 #number of chains
 ndim=11   #number of parameters
-burn=10   #number of (burn in) collect step
-#burn2=2000 #number of (real) burn in step
-burn2=1
-nstep=10  #number of MCMC steps
+#burn=10   #number of (burn in) collect step
+burn2=100 #number of (real) burn in step
+nstep=10000  #number of MCMC steps
 
 ## set up for start points
 
 # SIE+shear
-mean=[2.36496436e+02,  -1.10879100e+00,  -1.04252000e-01,
-      8.43468000e-01,   1.02018344e+02,  -1.11414000e-01,
-      -2.78323000e-01,   5.04820000e-01,   7.44723100e+00,
-      -6.85072000e-01,   2.71726000e-01]
+mean=[2.324253e+02 ,-1.100387e+00, -9.439666e-02 , 8.593171e-01 , 1.015043e+02 ,
+      -1.068075e-01 ,-2.923237e-01,  5.218383e-01 , 9.857114e+00,
+      -6.550547e-01 , 2.884248e-01]
 sig=[5,0.05,0.05,0.05,5,0.05,0.05,0.05,5,0.05,0.05]
 
 w_factor=1.0 # range of random start point
@@ -273,19 +271,21 @@ p3, prob, state = sampler.run_mcmc(p0,burn2)
 
 # the end of burn-in step
 find.write('# \n')
+mcmc.write('# \n')
+prob_chi2.write('# \n')
 
 ## MCMC run
 sampler.reset()
 #pos, prob, state = sampler.run_mcmc(p2,nstep)
 
-'''
+
 f = open("chain.dat", "w")
 g = open('lnprob.dat', 'w')
 
 for result in sampler.sample(p3, iterations=nstep, storechain=False):
     position = result[0]
     lnpro = result[1]
-    
+    '''
     for k in range(nwalker):
 	st=''
 	st2='%f'%lnpro[k]
@@ -294,7 +294,7 @@ for result in sampler.sample(p3, iterations=nstep, storechain=False):
 
[…]

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
minor update to draft

@@
 %expected \citep{Xu14}. 
-\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations, with the less level of flux anomalies showing in simulation results \citep{Xu14}.}
+\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations.
+Utilizing the surface brightness distribution of extended arcs and Einstein rings
+has been introduced by \citet{K05} and \citet{V09}. The fraction of
+substructure measured with this \emph{gravitational imaging technique}
+is currently in agreement with theoretical expectations \citep{V14a,V12}, although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
 While this could be the result of small sample
 statistics, it could also be an indication that flux-ratio anomalies
-have a different origin than substructure.[OTHER POSSIBLE ORIGONS--SIMONA]
+have a different origin than substructure.
+\textbf{ISM and microlensing both can produce flux anomalies in lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}.
+These origins are ruled out among known radio loud flux anomlous systems support the detection of substructures.
+}[OTHER POSSIBLE ORIGONS--SIMONA]
 %
-An alternative method for
-the detection of substructure in gravitational lens galaxies, utilizing
-the surface brightness distribution of extended arcs and Einstein rings
-has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
-substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14a,V12}, \textbf{although the number of detections remains small}.
 

### 2015-08-17 papers/B1555_EdgeOn/B1555_letter.tex
change to save space and new mnras template

@@
-\documentclass[useAMS,usenatbib]{mn2e}
+%\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS,usenatbib]{mnras}
 %\documentclass[usenatbib]{mn2e}
@@
 % Journal definitions
-\newcommand{\apj}[1]{ApJ}
-\newcommand{\mnras}[1]{MNRAS}
-\newcommand{\apjl}[1]{ApJL}
-\newcommand{\pasj}[1]{PASJ}
-\newcommand{\aj}[1]{AJ}
-\newcommand{\nat}[1]{Nature}
-\newcommand{\aap}{A\&A}
+%\newcommand{\apj}[1]{ApJ}
+%\newcommand{\mnras}[1]{MNRAS}
+%\newcommand{\apjl}[1]{ApJL}
+%\newcommand{\pasj}[1]{PASJ}
+%\newcommand{\aj}[1]{AJ}
+%\newcommand{\nat}[1]{Nature}
+%\newcommand{\aap}{A\&A}
 
@@
 Utilizing the surface brightness distribution of extended arcs and Einstein rings
-has been introduced by \citet{K05} and \citet{V09}. The fraction of
+has been introduced by \citet{K05} and \citet{V09}, the fraction of
 substructure measured with this \emph{gravitational imaging technique}
@@
 have a different origin than substructure.
-\textbf{ISM and microlensing both can produce flux anomalies in lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}.
-These origins are ruled out among known radio loud flux anomlous systems support the detection of substructures.
+\textbf{ISM and microlensing both can produce flux anomalies in stong lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}.
+These alternative origins are ruled out among known radio loud flux anomlous systems support the detection of substructures.
 }[OTHER POSSIBLE ORIGONS--SIMONA]
@@
 
-\begin{table*}
+%\begin{table*}
+\begin{table}
 \centering
- \begin{minipage}{140mm}
-  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).}
-  \begin{tabular}{@{}ccccccc}
+ %\begin{minipage}{140mm}
+  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).
+Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).}
+  \begin{tabular}{@{}ccccc}
 \hline
@@
 A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
-B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
-C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
-D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
+B ........ &$-0.0726$ 	&$+0.0480 $	&$-0.0727$ &$+0.0477$  \\  
+C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0281$   \\  
+D ........ &$-0.1619$  &$-0.3680$	&$-0.1630$ &$-0.3653$  \\  
+%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
+%B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
+%C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
+%D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
 \hline
@@
 
-\end{minipage}
-\medskip
-\end{table*}
+%\end{minipage}
+%\medskip
+\end{table}
+%\end{table*}
 

### 2015-08-18 papers/B1555_EdgeOn/B1555_letter.tex
rewrite some sentences in B1555 draft

@@
 %expected \citep{Xu14}. 
-\textbf{At present, the amount of substructure derived from flux-ratio anomalies ease the disagremeent with direct-detections and numerical simulations.
-Utilizing the surface brightness distribution of extended arcs and Einstein rings
-has been introduced by \citet{K05} and \citet{V09}, the fraction of
-substructure measured with this \emph{gravitational imaging technique}
-is currently in agreement with theoretical expectations \citep{V14a,V12}, although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
+\textbf{At present, the amount of substructures derived from flux-ratio anomalies eases the disagremeent with direct detections and numerical simulations.
+\emph{Gravitational imaging technique}, by utilizing the surface brightness distribution of extended arcs and Einstein rings,
+has been introduced by \citet{K05} and \citet{V09} and gives the measurements of the fraction of
+substructure. The result
+is currently in agreement with theoretical expectations \citep{V14a,V12} although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
 While this could be the result of small sample
@@
 have a different origin than substructure.
-\textbf{ISM and microlensing both can produce flux anomalies in stong lens systems, but the effects from ISM show strong frequency dependence and observing in radio band can avoid microlensing from star-size objects \citep{KD04}.
-These alternative origins are ruled out among known radio loud flux anomlous systems support the detection of substructures.
+\textbf{ISM and microlensing both can produce flux anomalies in strong lens systems, but not like substurcture pertubations, the effects from ISM show strong frequency dependence and  microlensing from star-size objects is negligible in radio band.
+These alternative origins have been ruled out among known radio loud flux anomlous systems which implies detection of substructures \citep{KD04}.
 }[OTHER POSSIBLE ORIGONS--SIMONA]
@@
 We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
-The free parameters of the models are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$), and exponential disk: intrinsic central density ($kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
+The free parameters of the model are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
 Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
@@
 ingredient in the lens model.
-\textbf{Indeed, it's hard to find physical interpretation for an large [IS $\gamma = 0.14$ A LARGE SHEAR?] and orthogonal external shear.
+\textbf{Indeed, it's hard to find physical interpretation for an large and orthogonal external shear.
 The SHARP $K^{\prime}$ band observations provide another explaination to their result. The edge-on disk crosses the
 radio merging double is consistent of this missing component and fully accounts for the observed flux-ratio anomaly.} 
-In general, it is well known  \citep[e.g,][]{Ka91} that lens models based only on the locations of lensed
+In general, it is well known  \citep[e.g.][]{Ka91} that lens models based only on the locations of lensed
 quasar/AGN images have large degeneracies. Therefore, before

### 2015-08-21 papers/B1555_EdgeOn/B1555_letter.tex
update to title and table

@@
 %Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
-SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
-Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
-Disks
+%SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
+%Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
+%Disks
+SHAPR II: Dark Matter Substrcture? Beware the Effect of Edge-on Disks
 }
@@
 
-%\begin{table*}
-\begin{table}
+\begin{table*}
+%\begin{table}
 \centering
- %\begin{minipage}{140mm}
-  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).
-Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).}
-  \begin{tabular}{@{}ccccc}
+ \begin{minipage}{140mm}
+  \caption{Observation and lens model-predicted results summary.
+Radio lensed image positions \citep{Marlow99} (in arcsec) and flux ratios \citep{K03} are respect to image A.
+Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).
+}
+  \begin{tabular}{@{}cccccccc}
 \hline
 
-Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
-					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
-					 &East &North &East 		&North \\ 
+Component	&\multicolumn{3}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model-Predicted} \\
+					&\multicolumn{3}{c}{5 GHz}		&	\multicolumn{3}{c}{SIE+expdisk} & SIE-only 	\\
+					 &East &North & Flux Ratio &East 		&North & Flux Ratio &Flux Ratio \\ 
 \hline
-A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
-B ........ &$-0.0726$ 	&$+0.0480 $	&$-0.0727$ &$+0.0477$  \\  
-C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0281$   \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1630$ &$-0.3653$  \\  
+A ........ &$0$    		&$0$		&   $1$ &$0.0000$ &$0.0000$ &  $1$ & $1$\\  
+B ........ &$-0.0726$ 	&$+0.0480 $	& $0.620 \pm 0.039 $  &$-0.0727$ &$+0.0477$ & $0.620$ & $0.962 $ \\  
+C ........ &$-0.4117$  &$-0.0280$	& $0.507\pm 0.030$ &$-0.4117$ &$-0.0281$   & $ 0.461 $ & $0.313 $\\  
+D ........ &$-0.1619$  &$-0.3680$	& $0.086 \pm 0.024$  &$-0.1630$ &$-0.3653$  & $0.115$ & $0.103 $\\  
 %A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
@@
 
-%\end{minipage}
+\end{minipage}
 %\medskip
-\end{table}
-%\end{table*}
+%\end{table}
+\end{table*}
 
@@
 
-\begin{table}
- \centering
+%\begin{table}
+% \centering
 % \begin{minipage}{140mm}
-  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
-  \begin{tabular}{@{}ccccccc}
+%  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
+%  \begin{tabular}{@{}ccccccc}
 
-\hline
-	& MERLIN  & \multicolumn{2}{c}{Model}\\
-		&5 GHz   & SIE-only & SIE+expdisk \\
-\hline
-$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
-$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
-$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\
+%\hline
+%	& MERLIN  & \multicolumn{2}{c}{Model}\\
+%		&5 GHz   & SIE-only & SIE+expdisk \\
+%\hline
+%$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
+%$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
+%$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\
 
-\hline
-\end{tabular}
+%\hline
+%\end{tabular}
 
 %\end{minipage}
-\medskip
-\end{table}
+%\medskip
+%\end{table}
 

### 2015-08-28 papers/B1555_EdgeOn/B1555_letter.tex
syntext fixing
fix errors in paper text and reference

@@
 %Disks
-SHAPR II: Dark Matter Substrcture? Beware the Effect of Edge-on Disks
+SHAPR II: Dark Matter Substructure? Beware the Effect of Edge-on Disks
 }
@@
 We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
-The free parameters of the model are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
+The free parameters of the model are, SIE: Einstein radius ($b$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
 Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
@@
 Positions are offsets from radio image component A measured in units of arcsec.
-The velocity dispersion $\sigma$ is in units of $km/s$.
-\textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
+The Einstein radius b is in unit of arcsec.
+$e$ is ellipticity defined as the axis ratio $q=1-e$ and $\theta$ is the position angle measured east of north.}
   \begin{tabular}{@{}ccc}
@@
 $\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
-$R_s$	& ...  & $0.28 \pm 0.01$\\
+$R_d$	& ...  & $0.28 \pm 0.01$\\
 \hline

### 2015-08-28 python/gravlens_plot.py

@@ -101,7 +101,7 @@ caus()
 model_plot()
 img_pos()
 
-#plt.xlim(-0.1,0.5)
-#plt.ylim(-0.5,0.2)
+plt.xlim(-0.4,0.8)
+plt.ylim(-0.8,0.4)
 plt.legend(loc=4)
 plt.show()

### 2015-08-31 papers/B1555_EdgeOn/B1555_letter.tex
update of John's draft

--- 2015-08-18 papers/B1555_EdgeOn/B1555_letter.tex
@@
-%\documentclass[useAMS,usenatbib]{mn2e}
-\documentclass[useAMS,usenatbib]{mnras}
-%\documentclass[usenatbib]{mn2e}
+% mnras_template.tex
+%
+% LaTeX template for creating an MNRAS paper
+%
+% v3.0 released 14 May 2015
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
+
+% Change log
+%
+% v3.0 May 2015
+%    Renamed to match the new package name
+%    Version number matches mnras.cls
+%    A few minor tweaks to wording
+% v1.0 September 2013
+%    Beta testing only - never publicly released
+%    First version: a simple (ish) template for creating an MNRAS paper
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+%\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[a4paper,fleqn,usenatbib,useAMS]{mnras}
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+\usepackage{mathptmx}
+
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
+\usepackage[T1]{fontenc}
+\usepackage{ae,aecompl}
+
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+\usepackage{times}
+\usepackage{epstopdf}
 \usepackage{graphicx}
-%\usepackage[nottoc]{tocbibind}
+\usepackage{txfonts}
+\usepackage{natbib}
+\usepackage{array}
 \setlength{\topmargin}{-1.2cm}
 
-% If your system does not have the AMS fonts version 2.0 installed, then
-% remove the useAMS option.
-%
-% useAMS allows you to obtain upright Greek characters.
-% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
-% this guide for further information.
-%
-% If you are using AMS 2.0 fonts, bold math letters/symbols are available
-% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
-% preferably \bmath).
-%
-% The usenatbib command allows the use of Patrick Daly's natbib.sty for
-% cross-referencing.
-%
-% If you wish to typeset the paper in Times font (if you do not have the
-% PostScript Type 1 Computer Modern fonts you will need to do this to get
-% smoother fonts in a PDF file) then uncomment the next line
-% \usepackage{Times}
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
 
-%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Journal definitions
-%\newcommand{\apj}[1]{ApJ}
-%\newcommand{\mnras}[1]{MNRAS}
-%\newcommand{\apjl}[1]{ApJL}
-%\newcommand{\pasj}[1]{PASJ}
-%\newcommand{\aj}[1]{AJ}
-%\newcommand{\nat}[1]{Nature}
-%\newcommand{\aap}{A\&A}
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title[Beware the Effect of Edge-on Disks]{
-%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
-SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
-Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
-Disks
-}
-\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
-jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
-Other$^{2}$\\
-$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
-Davis, CA 95616, USA\\
-$^{2}$Building, Institute, Street Address, City, Code, Country}
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
+\title[Beware the effect of edge-on discs]{SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars}
+\author[Hsueh et al.]{Jen-Wei Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} A. N. Other,$^{2}$ A. N. Other,$^{2}$  A. N. Other,$^{2}$ A. N. Other,$^{2}$ A. N. Other,$^{2}$
+\newauthor and A. N. Other$^{2}$\\
+$^{1}$Department of Physics, University of California, Davis, 1 Shields Ave. Davis, CA 95616, USA\\
+$^{2}$Building, Institute, Street Address, City, Code, Country\\
+$^{3}$Building, Institute, Street Address, City, Code, Country\\
+$^{4}$Building, Institute, Street Address, City, Code, Country\\
+$^{5}$Building, Institute, Street Address, City, Code, Country\\
+$^{6}$Building, Institute, Street Address, City, Code, Country}
 \begin{document}
@@
 \begin{abstract}
-
-Gravitational lens flux-ratio anomalies provide a powerful technique
-for detecting the presence of dark matter substructure in distant
-galaxies.  However, before using the statistics of systems with these
-anomalies, it is imperative to ascertain that a given system does not
-have properties that could plausibly cause the observed anomaly
-without the need for substructure.  In this letter, we present the
-case of the B1555+375 lens system, which has a strong radio-wavelength
-flux-ratio anomaly but where the lensing galaxy is also revealed in
-high-resolution infrared imaging to have a clear edge-on disk component.  The
-disk crosses directly over the pair of images that exhibit the
-anomaly, and we show that simple models that include the disk can
-reproduce the anomaly without requiring substructure.  
-%Other lens systems that we have observed with adaptive optics imaging
-%as part of the Strong lensing at High Angular Resolution Programme (SHARP)
-%show a similar behaviour and will be the subject of a future paper.  
-These results suggest that the assumption that
-all flux-ratio anomalies are due to substructure will likely overestimate
-the substructure fraction in massive galaxies.
-
+Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies.
+However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo.
+Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W.
+M.
+Keck-II Telescope and the {\it Hubble Space Telescope} to have a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
+We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
+Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
 \end{abstract}
@@
 \begin{keywords}
-gravitational lensing
+gravitational lensing -- quasars: individual CLASS B1555+375 -- cosmology: observations 
 \end{keywords}
@@
 
-A common feature of simulations of structure formation is the presence
-of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
-However, observations of the Local Group show many fewer satellite
-galaxies than are predicted by the simulations, even when taking into
-account completeness corrections arising from the limited sky coverage
-imposed by the Galactic Plane and the latest discovery of new dwarf galaxies \citep{DES15,Kop15}.  
-This is the famous ``missing satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
-understand this discrepancy, it is imperative to build up a large
-sample of satellites/subhaloes in galaxies outside the Local Group.
- However, this process is challenging due to the faintness of the satellite
-galaxies.  Furthermore, lower-mass satellites may not be able to
-retain the gas needed for ongoing star formation \citep[e.g.][]{P11},
-rendering them effectively dark.  These factors make gravitational
-lensing a powerful and promising tool for the detection of
-substructure.
+A common feature of dark-matter only simulations of structure formation is the presence of thousands of sub-haloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
+However, observations of the Local Group show many fewer satellite galaxies than are predicted by the simulations, even when taking into account completeness corrections arising from the limited sky coverage imposed by the Galactic Plane and the latest discoveries of new dwarf galaxies \citep{DES15,Kop15}.
+This is the well-known {\it missing satellite problem} \citep{Klypin1999,Moore1999,S07}.
+In order to understand this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.
+However, this process is challenging due to the optical/infrared faintness of the satellite galaxies.
+Furthermore, lower-mass satellites may not be able to retain the gas needed for ongoing star formation \citep[e.g.][]{P11}, rendering them effectively dark.
 
-It was first suggested by \citet{Mao1998} that flux-ratio anomalies
-observed in radio-loud multiple images of lensed quasars could be
-interpreted as a telltale sign of the presence of substructure in lens
-galaxies.  Indeed, small perturbations in the gravitational potential
-are sufficient to cause flux-ratio anomalies in strong lensed systems
-\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
-radio band, lensed images are neither sensitive to microlensing from
-stars, nor to dust extinction. This makes flux-ratio anomalies a promising
-tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002,N13}.  
-%At present, the amount of substructure derived from flux-ratio anomalies
-%seems to be disagreement with predictions from numerical simulations, 
-%with the former requiring a larger fraction of mass in substructure than
-%expected \citep{Xu14}. 
-\textbf{At present, the amount of substructures derived from flux-ratio anomalies eases the disagremeent with direct detections and numerical simulations.
-\emph{Gravitational imaging technique}, by utilizing the surface brightness distribution of extended arcs and Einstein rings,
-has been introduced by \citet{K05} and \citet{V09} and gives the measurements of the fraction of
-substructure. The result
-is currently in agreement with theoretical expectations \citep{V14a,V12} although the simulation results show less level of flux anomalies than expected \citep{Xu14}.}
-While this could be the result of small sample
-statistics, it could also be an indication that flux-ratio anomalies
-have a different origin than substructure.
-\textbf{ISM and microlensing both can produce flux anomalies in strong lens systems, but not like substurcture pertubations, the effects from ISM show strong frequency dependence and  microlensing from star-size objects is negligible in radio band.
-These alternative origins have been ruled out among known radio loud flux anomlous systems which implies detection of substructures \citep{KD04}.
-}[OTHER POSSIBLE ORIGONS--SIMONA]
-%
+It was first suggested by \citet{Mao1998} that the flux-ratio anomalies observed in the multiple radio-loud images of lensed quasars could be interpreted as a sign of the presence of substructure in lens galaxies.
+Indeed, small perturbations in the gravitational potential are sufficient to cause flux-ratio anomalies in gravitationally lensed systems \citep{metcalf01,Dalal2002,Bradac02}, particularly for those systems with a close pair of merging images \citep{KD04}.
+At radio wavelengths, the lensed images are neither sensitive to micro-lensing from stars (\citealt{K03}; although see \citealt{koopmans00}), nor to dust extinction.
+Also, any variation in the properties of the radio images that are due to propagation effects (e.g.
+interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for (e.g.
+\citealt{biggs03,M07,winn04}).
+This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
+However, a recent comparison of the observational data (8 gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu14}.
 
-%While future large-scale surveys, such as the LSST, are expected to
-%deliver new large samples of gravitationally lensed quasars, in the
-%near future the discovery of new systems using narrow-line quasar
-%emission \citep{N14} will provide new invaluable statistical
-%perspective on current constraints based on flux-ratio anomalies.  
-In this letter, we explore the idea that not all flux-ratio anomalies are
-related to the presence of substructure, but that some originate in a
-more complex lens galaxy mass distribution than initially
-considered. To this end we use new infra-red data from the Strong
-lensing at High Angular Resolution Program 
-\citep[SHARP;][Fassnacht et al., in prep]{SHARP12, V12}.
-The main goal of the SHARP project is to re-observe known
-quadruple and Einstein ring lens systems at high angular
-resolution by making use of observations with (1) adaptive optics (AO)
-on the Keck telescopes, (2) the Hubble Space Telescope, and (3) large
-interferometric arrays \citep{SHARP12,V12}. In particular, 
-we focus on the B1555+375 lens system\citep{Marlow99} to better
-understand the causes of flux-ratio anomalies in gravitational lenses.  This system was
-discovered in the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2} and
-has a pair of merging images that show a strong \textbf{persistent} flux-ratio anomaly at
-radio wavelengths.  Follow-up observations ruled out radio propagation
-effects as the cause of the anomaly \citep{K03,KD04}.  The B1555+375
-system was included in both the observational and theoretical analysis
-of \citet{Dalal2002} and \citet{Xu14} and, thus, understanding its
-mass distribution is of key importance \textbf{to assess systematics in these statistics}.  
-%Our analysis makes use of
-%the new information obtained from the latest SHARP infrared imaging.
-The paper is organized as follows: the  SHARP data are
-introduced in section 2; in section 3 we present the lens model while
-the results of this analysis and their implications are discussed in
-section 4.
+The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}.
+This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
+The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear.
+While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.
 
-\section{Data Collection \& Reduction}
+In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered.
+To this end, we use new infrared imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][]{mckean07,lagattuta10,SHARP12, V12}.
+The main goal of the SHARP project is to re-observe known four-image and Einstein ring lens systems at high angular resolution by making use of observations with (1) adaptive optics (AO) on the W.
+M.
+Keck telescope, (2) the {\it Hubble Space Telescope (HST)}, and (3) large radio and mm interferometric arrays.
+
+Here we focus on CLASS B1555+375 \citep{Marlow99}, which was discovered as part of the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2}.
+B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}.
+As B1555+375 was included in both the observational and theoretical analysis of \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
+The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3.
+The results of this analysis and their implications are discussed in Section 4.
+Note that neither the lens galaxy or lensed source redshift are known for B1555+375, which we assume are at $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colour \citep{Marlow99}.
+This assumption has no effect on the derived magnifications or flux-ratios of our analysis.
+
+\section{Observations \& Data reduction}
+
+Our dataset consists of optical and infrared imaging taken with the W.
+M.
+Keck-II Telescope and the {\it HST}, and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.
+
+\subsection{Keck adaptive optics and {\it HST} imaging}
+
+B1555+375 was observed as part of SHARP using the NIRC2 camera on the W.
+M.
+Keck-II Telescope on 2012 May 16.
+The AO system was used, with the corrections derived from the laser guide star and a $R=14.4$-mag tip-tilt star that was located $\sim45$~arcsec from the lens.
+The narrow camera mode was used, giving a field-of-view of $\sim10$~arcsec on a side and a pixel scale of 10~mas.
+Six dithered 300~s exposures were obtained in the $K^{\prime}$-band filter.
+The data were reduced with the standard SHARP pipeline, which is a python-based package that is a refinement of the process described by \citet{Auger_EELS1}.
+A cutout of the final reduced image is shown in Fig.~\ref{fig:multiband} and also in Fig.~\ref{fig:merlin}, where the contours from 5-GHz Multi-Element Radio Link Interferometer Network (MERLIN) imaging by \citet{Marlow99} and 1.66-GHz VLBA imaging (see below) are overlaid.
+
+B1555+375 was also observed with the {\it HST} in three broad bands.
+The optical data were obtained with the Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands (GO-8804; PI: Falco), while the Near Infrared Multi-Object Spectrograph (NICMOS) was used to observe the system in the F160W band (GO-9744; PI: Kochanek).
+The NICMOS observations were obtained with the NIC2 camera.
+We reduced all of the archival \textit{HST} data with the standard {\sc multidrizzle} pipeline, producing final drizzled images with pixel-sizes of 50~mas.
+The reduced images are also shown in Fig.~\ref{fig:multiband}.
+The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image
+
+There are several notable features in the high-resolution AO and {\it HST} data.
+These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity of $\sim 0.8$.
+We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
+Therefore, the lack of emission that is seen from these images is likely due to dust extinction.
+
+\subsection{Very Long Baseline Array imaging}
+
+B1555+375 was observed with the 10 telescopes of the VLBA at a central observing frequency of 1.66 GHz on 2000 March 21 (BN0009; PI: Norbury).
+The data were recorded at 128 Mbits~s$^{-1}$ and then correlated to produce two spectral windows with 8 MHz bandwidth, 16 channels and both circular polarizations (RR and LL).
+The observations were phase referenced using J1544+398 every 3 min over the total observing time of 3 h.
+The data were reduced in the standard manner using the {\sc vlbaprocs} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS).
+Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6$~degr east of north.
+The final map has an rms of 78~$\mu$Jy~beam$^{-1}$ and is also shown in Fig.~\ref{fig:merlin}.
+
+We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in size.
+Image C is still compact on mas-scales, whereas image D is only marginally detected ($\sim6~\sigma$).
+We immediately see from the high resolution VLBA imaging that image B has a smaller angular size than image A, which is consistent with a perturbation in the mass model being responsible for the flux-ratio anomaly (recall that gravitational lensing conserves surface brightness), as opposed to free-free absorption or interstellar scattering.
 
 \begin{figure*}
-%\begin{minipage}{140mm}
-%\includegraphics[width=140mm]{B1555_gallery.eps}
 \includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
-\caption{High-resolution multiband imaging of the B1555+375 lens system.
-All of the panels are 3.7 arcsec on a side, and for each panel the scale bar 
-represents 1\arcsec.  From left to right the panels show data from
-\textit{HST}/WFPC2 in the F555W band, \textit{HST}/WFPC2 in the F814W band, \textit{HST}/NICMOS/NIC2
-in the F160W band, and Keck AO imaging in the $K^\prime$ band.
-\label{fig:multiband}}
-%
-%\end{minipage}
-
+\caption{High-resolution multi-band imaging of B1555+375 with {\it HST}/WFPC2 at F555W (left) and F814W (middle-left), with {\it HST}/NICMOS/NIC2 at F160W (middle-right) and with Keck adaptive optics at $K^\prime$-band (right).
+All of the panels are 3.7 arcsec on a side and the scale-bar represents 1 arcsec.}
+\label{fig:multiband}
 \end{figure*}
-
-\subsection{Keck Adaptive Optics Imaging}
-
-The B1555+375 system was observed using the NIRC2 camera on the Keck 2
-Telescope on the night of 2012 May 16 UT.  The adaptive optics system
-was used, with the corrections derived from the laser guide star and a
-$R$=14.4 tip-tilt \textbf{star} that was located 45 arcsec from the lens
-system.  The narrow camera mode was used, giving a field of view
-of roughly 10 arcsec on a side and a pixel scale of 10~mas.
-Six dithered 300~s exposures were obtained in the $K^{\prime}$ band filter.  The
-data were reduced with the standard SHARP pipeline, which is a
-python-based package that is a refinement of the process described in
-\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
-Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
-contours from the MERLIN radio observations of \citet{Marlow99}
-overlaid.
-
-There are several notable features in the Keck AO data.
-These include the nearly complete lack of emission associated with the
-B and D lensed images, as can be seen by comparing the radio contours
-to the $K^\prime$-band emission, and faint but clearly visible
-emission from what appears to be an edge-on lensing galaxy.
-
-\subsection{Hubble Space Telescope Archival Imaging}
-
-The B1555+375 system was also observed with the \textit{Hubble Space Telescope
-(\textit{HST})} in three broad bands.  The optical data were obtained with the
-Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
-(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
-Spectrograph (NICMOS) was used to observe the system in the $F160W$
-band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
-obtained with the NIC2 camera.  We reduced all of the archival \textit{HST}
-data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
-  MATT], producing final drizzled images with pixel scales of 50~mas.
-The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
-system is not detected at high significance in the optical bands, but
-is clearly seen in the NICMOS $F160W$ image \textbf{where the edge-on lensing
-galaxy clearly stands out.}
-\textbf{The lens system is red, with a strong jump in flux between the F814W
-(roughly I) and F160W (roughly H) bands (Fig.~\ref{fig:multiband}), so 
-we assign a lens redshift of $z_\ell = 1.0$ and a source redshift of
-$z_s =1.5$.
-This assumption on redshifts is needed for the lens modelling because some lens model parameters contain distance information.
-However, our choice of redshifts does not affect the predicted magnifications nor flux-ratios.}
-
-The observation details of Keck AO and \textit{HST} imaging are shown in Table 1.
 
@@
 \centering
- %\begin{minipage}{140mm}
-  \caption{Observational details of the B1555+375 lens system.}
-  \begin{tabular}{@{}llccc}
-
+\caption{Summary of the B1555+375 observations.}
+\begin{tabular}{llccc}
 \hline
 Telescope		& Camera			&  Band 		& Date				&$t_{exp}$ (s) \\
-
 \hline
-   \textit{HST}				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
-   \textit{HST}				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
-   \textit{HST}				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
-   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
+VLBA			&					& 1.66 GHz	& 	2000 Mar 21	& 10800\\
+\textit{HST}	& WFPC2    		& F555W		&	2000 Oct 09	& 5200\\
+\textit{HST}	& WFPC2    		& F814W		&	2000 Oct 09 	& 5200\\
+\textit{HST}	& NICMOS/NIC2	& F160W		&	2003 Nov 02	& 5376\\
+Keck-II			& NIRC2 AO		& $K^\prime$	& 	2012 May 16	& 1800\\
 \hline
 \end{tabular}
-%\end{minipage}
+\label{tab:obs}
 \end{table}
-
-%===========================================================================
 
@@
 
-%To model B1555+375, we use the lens modelling code {\tt glafic} \citep{Oguri}.  
-\textbf{To model B1555+375, we use the lens modelling code {\tt gravlens} \citep{Kee01}.  
-The inputs to the model are the observed image
-positions and flux densities measured by the radio observations.
-We use the image positions from \citet{Marlow99}, who also presented a singular isothermal ellipsoid
-(SIE) model that provided a good fit to the image positions but
-does not reproduce the strong flux-ratio anomaly between components A
-and B.}  %\citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow99}.  
-\textbf{The flux measurements are performed by \citet{K03} with a half year monitoring to obtain flux-ratio curves, providing throughout discussions in erros on flux densities.}
+The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu14}.
+However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens.
+To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly, without the need for additional substructure.
 
-Although the flux-ratio anomaly that is observed in the radio data implies there must be some perturbations to the mass model, which may be
-caused by substructure in the lensing galaxy, our high-resolution near
-infrared imaging suggests another explanation.  In both the $K^\prime$
-band adaptive optics data and the \textit{HST} infrared imaging (see 
-Fig. 1), the lensing galaxy has a clear edge-on disk component with a
-position angle of $\approx 10$ degree.  We therefore model the system
-with a disk component in order to see if such a model can explain the
-flux-ratio anomaly without the need for substructure.  The edge-on
-disk may also explain the system morphology that is observed in the
-near infrared imaging.  In particular, neither image B nor image D is
-detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
-these lensed images lie on or close to the edge-on disk.  Thus, strong
-extinction in the disk could cause the non-detection of these
-images.[REF B0128 PAPER?--LEON]
+We use the lens modelling code {\sc gravlens} \citep{Kee01} to model the compact radio components.
+The inputs to the model are the observed image positions measured from the MERLIN radio observations of \citet{Marlow99} as all of the images are significantly detected in these data.
+The flux-ratio measurements are taken from \citet{K03}, who used half a year of MERLIN monitoring to obtain flux-ratio curves.
+In total, there are 11 constraints to the mass model provided by the observational data.
+As a first trial of modelling, we re-create the singular isothermal ellipsoid (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
+Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =~??$).
 
-As a first trial of modelling, we create a single SIE model to check
-the performance of a simple lensing potential. Consistent with
-previous studies \citep{Marlow99, Xu14}, a single elliptical
-potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
-\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images.
-Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}.
-We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling.
-The free parameters of the model are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$).
-Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
-  We have not included a third component such as an external
-shear component or NFW halo into our model because the number of constraints provided by the
-image positions and fluxes would not be sufficient to constrain such a
-model. However, we note that the image not affected by dust (image C)
-in the Keck AO data is consistent with negligible shear (i.e. shear
-strength $\Gamma_s=0.002$), when modeled with the pixelized technique
-of \citet{V09}.
-%We then create two separate models of the lensing potential that both
-%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
-%and an exponential edge-on disk (SIE+expdisk). In the second model
-%the disk is represented as a very elongated SIE component (2-SIE).
+The next step is to examine if an edge-on disc can cause a physically plausible perturbation in the strong lensing mass model that results in the observed flux ratio anomaly of  merging images A and B.
+An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}.
+We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
+The free parameters of the model are the SIE velocity dispersion ($\sigma$), centroid position, ellipticity ($e$), and position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$), centroid position, ellipticity ($e$), position angle ($\theta$), and scale length ($R_s$).
+A Detailed definition of these mass profiles is described by \citet{Kee01}.
+The source position and flux add three additional model parameters.
+We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
+Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays will test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
 
-To obtain \textbf{the minimum $\chi^2$} [OR BEST-FIT MODEL?--JEN] lens model, we explore the parameter space with the following steps: 
-\begin{itemize}
-\item Preparation of model starting point: Applying the priori infromation from the SHARP AO image, we set ellipticity $e=0.8$ and position angle $\theta=10 \degr$ to the exponential disk.
-We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile and also the source position.
-The rest of parameters of exponential disk are set to be the same as the SIE component as the starting point.
-\item Best-fit model search: We let all model parameter varies but bind the centroid position of two conponents with a Gaussian prior ($\sigma = 0.05 $ arcsec).
-Run optimization with amoeba algorithm in {\tt gravlens} interatively to reach the global minimum of $\chi^2$ in paramter space.
-\item Markov Chain Monte Carlo: After obtaining the best-fit lens model, we run MCMC to explore the parameter space for the uncertainties.
-\end{itemize}
-%The smallest $\chi^2$ doesn't necessarily give a physical model.
-Here are the examples we would like to discard: the ellipticity and the position angle of the disk component are far from what we see in the SHARP AO image, the center positions of two components are too far apart physically, or the positions of the lenses and the source are clearly located outside the Einstein radius in the image.
-%(3) Optimize for physical lens models: We bind the positions of the two components with a strong Gaussian prior having the same central position and $\sigma = 0.05 $ arcsec and then run optimization with amoeba algorithm to reach the final best-fit for each model.}
+To obtain the best-fit lens model, we explore the parameter space with the following steps.
+First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10$ degr for the exponential disc.
+We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile.
+The rest of the parameters that describe the exponential disc are set to be the same as the SIE component as the starting point.
+All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
+The total number of free parameters is ??.
+After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.
 
-The best-fit model parameters are listed in Table 2 and the lens model is illustrated in Fig. 3. 
-%Both of these models produce lensed images with positions and
-%fluxes that are good matches to the radio observations.  
-%While both of the two component models 
-%the 2-SIE version has a somewhat
-%better performance than the SIE+expdisk model in reproducing flux
-%ratios. 
-Tables 3 \& 4 show the comparison between radio data and model predicted image positions and flux ratios.  
-\textbf{By adding an elongated exponential disk to a smooth potential model, the SIE+expdisk lens model shows significant improvement on the flux ratios when comparing to the SIE-only model, especially the flux ratio anomaly between the merging images.}
+The best-fit model parameters are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}.
+Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios.
+We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = ~??$.
+The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
+The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to there being an additional ellipticity in the model (e.g.
+from an external shear) that is being partly compensated for by the disc component.
+Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able confirm this.
 
 \begin{figure}
-%\plotone{1555_ao_merlin_overlay.eps}
 \includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
-with contours from the MERLIN observation of \citet{Marlow99} overlaid. 
-%
-\label{fig:merlin}}
+\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations of \citet{Marlow99} and the VLBA observations presented here overlaid.}
+\label{fig:merlin}
 \end{figure}
@@
 \begin{figure}
-%\plotone{point_source.eps}
-\includegraphics[width=84mm]{gravlens_exp_try5_plot.eps}
-\caption{Radio observation(blue plus sign) and model-predicted(red open circle) image positions of B1555+375.
-Criticle curves are shown with blue solid line and caustics are shown with red dash line.
-The position of the source is at $(-0.1953,-0.1494)$, marked by a red filled circle.
-The centroid positions of two lens components are marked by black filled triangles.
-\label{fig2}}
+\includegraphics[width=84mm]{gravlens_exp_try5_plot.pdf}
+\caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.
+The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dash line.
+The position of the source is at ($-0.1953$, $-0.1494$), which is marked by the red filled circle.
+The centroid positions of the two mass components of the lens (an SIE and an exponential disc) are marked by the black filled triangles.}
+\label{fig:model}
 \end{figure}
 
-%\begin{figure}
-%\plotone{point_source.eps}
-%\includegraphics[width=84mm]{point_source.eps}
-%\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375.
-The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model [NOT UPDETED YET], marked by a black filled circle.
-\label{fig2}}
-%\end{figure}
+\begin{table*}
+\centering
+\caption{A summary of the observational constraints and the predicted lens-model parameters.
+The lensed image positions in the radio \citep{Marlow99} (in arcsec) and average flux-ratios \citep{K03} are respect to image A.
+Uncertainties in the position measurements for images A, B and C are $0.001$~arcsec and for image D are $0.006$~arcsec.}
+\begin{tabular}{cccccccc}
+\hline
+Image	&\multicolumn{3}{c}{Observed MERLIN} 	 	& \multicolumn{4}{c}{Model-Predicted}\\
+		&\multicolumn{3}{c}{5 GHz}		& & & {SIE+ExpDisc} & SIE-only\\
+		&East &North & Flux ratio &East 	&North & Flux ratio &Flux ratio\\ 
+\hline
+A  &$0$    		&$0$			&  $1$ 				&$+0.000$  &$+0.000$	& $1$ 		& $1$\\  
+B  &$-0.073$	&$+0.048$	& $0.620 \pm 0.039$ 	&$-0.073$ &$+0.048$		& $0.620$ 	& $0.962$ \\  
+C  &$-0.412$ 	&$-0.028$	& $0.507\pm 0.030$	&$-0.412$ &$-0.028$		& $0.461$ 	& $0.313$\\  
+D  &$-0.162$	&$-0.368$	& $0.086 \pm 0.024$ 	&$-0.163$ &$-0.365$		& $0.115$ 	& $0.103$\\  
+\hline
+\end{tabular}
+\label{tab:results}
+\end{table*}
 
@@
 \centering
-% \begin{minipage}{140mm}
-  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties.
-Positions are offsets from radio image component A measured in units of arcsec.
-The velocity dispersion $\sigma$ is in units of $km/s$.
-\textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
-  \begin{tabular}{@{}ccc}
+\caption{Best-fit model parameters of B1555+375 for an SIE + exponential disc lens model and the uncertainties.
+The positions are measured in arcsec, relative to the radio position of image A.
+The ellipticity is defined as the axis ratio $q=1-e$ and the position angles are measured in degrees east of north.
+The Einstein radius $b$ and disc-scale radius are measured in arcsec.}
+\begin{tabular}{ccc}
 \hline 
- Parameter  & SIE & Expdisk 		   
-\\
+Parameter  & SIE & ExpDisc \\
 \hline
-$x$  	  & $-0.1818 \pm 0.005$	&$-0.1472 \pm 0.005$ 	  \\
-$y$	  &$-0.1988 \pm 0.005$	&$-0.2057 \pm 0.006$	 \\
-
-$b$ &$0.21 \pm 0.01$  & ...   \\
-$\kappa_0$ & ... & $0.11 \pm 0.01$        \\  
-$e$	  & $0.31\pm 0.01$	&$0.87 \pm 0.01$ \\
-$\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
-$R_s$	& ...  & $0.28 \pm 0.01$\\
+$\Delta$RA	& $-0.182 \pm 0.005$		& $-0.147 \pm 0.005$\\
+$\Delta$Dec	& $-0.199 \pm 0.005$		& $-0.206 \pm 0.006$ \\
+$b$ 			& $0.21 \pm 0.01$  		& $0.11 \pm 0.01$ \\
+$e$	  		& $0.31 \pm 0.01$			& $0.87 \pm 0.01$ \\
+$\theta$ 		& $3.0 \pm 0.6$			& $7.0 \pm 0.7$	 \\
+$R_s$			& ...  						& $0.28 \pm 0.01$	 \\
 \hline
-%$\chi ^2$ & $1.05$ & $0.04$ \\
-%\hline
+\label{tab:model}
 \end{tabular}
-
-%\end{minipage}
 \end{table}
 
-%\begin{table}
+\section{Discussion \& Conclusions}
 
-%  \caption{Best-fit parameters of B1555+375 lens models.
-Subscripts 1 and 2 represent bulge\textbf{/halo} and disk components in each model respectively.
-Positions are offsets from radio image component A measured in units of arcsec.
-The velocity dispersion $\sigma$ is in units of $km/s$ and disk mass $M_{tot}$ is in units of $h^{-1} M_{\odot}$.
-\textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
-%  \begin{tabular}{@{}ccc}
-%\hline 
-% Parameter  & \multicolumn{2}{c}{Lens model} \\
-%		&SIE+expdisk& 2-SIE		   
-%\\
-%\hline
-%$x_1$  	  & $-0.1794$	& $-0.1771$  \\
-%$y_1$	  &$-0.1881$	&$-0.2032$  \\
+Although flux-ratio anomalies provide a powerful tool to investigate low-mass substructure in lensing haloes out to cosmological redshifts, it is clear that some care is needed in interpreting the results.
+It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less effected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux-ratios.
+This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations from a smooth mass distribution \citep{Xu14}.
+In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}.
+Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass substructures as as been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux-ratio, or even astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
 
-%$\sigma_1$ &$140.3$     & $146.1$ \\
-%$e_1$	  & $0.21$	& $0.15$ \\
-%$\theta_1$ &$73.6 \degr$ & $155.3 \degr$ \\
-%\hline
-%$x_2$	  &$-0.1639$ 	&$-0.1562$  \\
-%$y_2$	  &$-0.2542$	& $-0.2195$  \\
-%$M_{tot,2}$  & $3.58\times 10^{10} $  & ...	 \\  
-%$\sigma_2$ & ...        &$122.6$ \\  
-%$e_2$	  &$0.84$	&$0.86$  \\
-%$\theta_2$ &$4.0\degr$ &$7.9\degr$  \\
-%$r_e$	  & $0.21 ''$ &  ... \\
-%\hline
-%$\chi ^2$ & $1.05$ & $0.04$ \\
-%\hline
-%\end{tabular}
-%\end{table}
+Here, we find evidence for an edge-on disc in the flux-ratio anomalous gravitational lens B1555+375 that can also account for the required perturbation in the mass model.
+Such high-order deviations from a smooth mass distribution have already been suggested \citep{evans03,congdon05}, but this is the first time that a disc has been observed and modelled to account for a flux-ratio anomaly.
+However, it is important to realise that by including observationally motivated perturbations like luminous dwarf companions or edge-on discs in the mass models, we are still limited in our interpretation since we must assume that the anomalies are due exclusively to these additional components.
+For B1555+375, it may be possible to independently constrain the mass of the disc through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which would test whether the disc makes a sufficient contribution to the mass model (e.g.
+as in the case of B1933+503; \citealt{suyu12}).
+Also, as we have shown here, B1555+375 shows evidence for an extended $\sim100$~mas gravitational arc at radio-wavelengths that is coincident with the edge-on disc.
+Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the extended disc is sufficient to cause the anomaly.
+Nevertheless, before concluding that the flux-ratios in any given lens system are a result of substructure, it is critical to explore a range of smooth models that are informed by additional observations or to do a comprehensive analysis such as that conducted by \citet{Xu14}.
+Otherwise, the derived substructure fractions should be considered as upper limits.
 
-%\begin{table*}
-\begin{table}
-\centering
- %\begin{minipage}{140mm}
-  \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec).
-Uncertainties in position measurements are $0.001^ {\prime \prime}$ expect image D with larger uncertainty ($0.006^ {\prime \prime}$).}
-  \begin{tabular}{@{}ccccc}
-\hline
+%Gravitational lensing is, at present, the most powerful tool for
+%studying substructure in galaxies outside of the Local Universe, and
+%the flux-ratio anomaly systems are a key aspect of these
+%investigations.  However, before using the anomaly in any
+%given system to investigate structure formation and the properties of
+%dark matter, it is critical to eliminate other possible explanations
+%for the difference between the observed and expected fluxes, such as
+%propagation effects and assumptions about the lens galaxy's mass distribution.  
+%It is for this reason that much of the effort in the
+%flux-ratio technique has been focused on radio-loud lens systems.  At
+%these wavelengths, dust extinction and microlensing effects should be
+%minimal \citep[although see][for a rare example of radio
+%  microlensing]{koopmans00}.  \textbf{Also,  scatter broadening} can affect radio
+%fluxes, as is clearly shown in the B0128+437 system \citep{B04}, and free-free absorption can change the flux-ratios as a function of frequency,
+%for example, B0218+357 \citep{M07}.
+%However, these propagation effects can be disentangled from
+%substructure lensing because they have well known dependencies on
+%wavelength. In particular, \citet{KD04} examine all eight radio-loud flux anomalous
+%lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
+%B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They find
+%no strong wavelength dependence in the flux-ratios of all these
+%systems and therefore rule out radio propagation effects as
+%significant contributors to the observed anomalies.
 
-Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{2}{c}{Model} \\
-					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} 	\\
-					 &East &North &East 		&North \\ 
-\hline
-A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
-B ........ &$-0.0726$ 	&$+0.0480 $	&$-0.0727$ &$+0.0477$  \\  
-C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0281$   \\  
-D ........ &$-0.1619$  &$-0.3680$	&$-0.1630$ &$-0.3653$  \\  
-%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   \\  
-%B ........ &$-0.0726\pm 0.001$ 	&$+0.0480 \pm 0.001$	&$-0.0727$ &$+0.0477$  \\  
-%C ........ &$-0.4117\pm 0.001$  &$-0.0280 \pm 0.001$	&$-0.4117$ &$-0.0281$   \\  
-%D ........ &$-0.1619\pm 0.006$  &$-0.3680\pm 0.006$	&$-0.1630$ &$-0.3653$  \\  
-\hline
-\end{tabular}
+%In this letter, we instead focus on the effect that more complicated lens galaxy mass distributions \textbf{have} on flux-ratio anomalies.
+Traditionally, flux-anomalous lensed quasars have been radio-loud, initially discovered in radio observations.
+While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies.
+Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux-ratio anomaly.
+Since lens galaxies are typically at redshifts of $z \leq 1$, optical and near-infrared observations are ideal for measuring the light distribution of lens galaxies and obtaining useful prior information on the underlying mass distributions.
+Indeed \citet{SHARP12} showed that high resolution IR imaging can help to significantly improve the precision of the lens modelling.
+This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging has allowed us to detect, for the fist time, the presence of an edge-on disk.
+This newly discovered edge-on disk provides a strong prior for our lens modelling.
+With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly.
+Our successful modelling indicates that the kpc-scale structure of the lens galaxy itself is sufficient to explain the flux-ratio anomalies in B1555+375, without any need to invoke the presence of substructure.
 
-%\end{minipage}
-%\medskip
-\end{table}
-%\end{table*}
+%From a theoretical perspective, \citet{Xu14} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered.
+After adding sub-haloes from numerical simulations to these systems, only one out of the eight radio-loud gravitational lenses achieves the level of the flux-ratio anomalies seen in the observations.
+The rest are unlikely (only $1 - 4$ per cent probability) to have an observed distribution of flux-ratio anomalies produced only by substructure, including our target B1555+375.
+In fact, among those eight radio lenses, B1555+375 is one of the most anomalous gravitational lenses, but it is also one of the most challenging systems to explain by substructures.
+\citet{Xu14} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter.
+They also point out that the SIE component and the external shear in their model are orthogonal, indicating a possible missing ingredient in the lens model.
+Indeed, it's hard to find physical interpretation for an large and orthogonal external shear, without the inclusions of an observationally motivated edge-on disc component.
 
-%\begin{table*}
-%\centering
- %\begin{minipage}{140mm}
- % \caption{Radio observation \citep{Marlow99} and model-predicted lensed image positions (in arcsec). Both SIE+expdisk and 2-SIE lens model-predicted positions well match to the radio observation.}
- % \begin{tabular}{@{}ccccccc}
+Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compcat lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
+While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
+We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution are a significant source of bias.
 
-%\hline
-
-%Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
-%					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
-%					 &East &North &East 		&North &East 		&North\\ 
-%\hline
-%A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
-%B ........ &$-0.0726(0.001)$ 	&$+0.0480(0.001)$	&$-0.0723$ &$+0.0480$ & $-0.0755 $  &  $+0.0414$  \\  
-%C ........ &$-0.4117(0.001)$  &$-0.0280(0.001)$	&$-0.4114$ &$-0.0282$  & $-0.4122 $  &   $-0.0267$ \\  
-%D ........ &$-0.1619(0.006)$  &$-0.3680(0.006)$	&$-0.1631$ &$-0.3628$  & $-0.1620$    &  $-0.3533$ \\  
-%\hline
-%\end{tabular}
-
-%\end{minipage}
-%medskip
-%\end{table*}
-
-\begin{table}
- \centering
-% \begin{minipage}{140mm}
-  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios from SIE-only and SIE+expdisk model.}
-  \begin{tabular}{@{}ccccccc}
-
-\hline
-	& MERLIN  & \multicolumn{2}{c}{Model}\\
-		&5 GHz   & SIE-only & SIE+expdisk \\
-\hline
-$f_A/f_B$			&$1.61 \pm 0.10$ &$1.04$& $1.62$  \\ 
-$f_A/f_C$		&$1.97 \pm 0.12$ 	 &$3.20$ & $2.17$ \\
-$f_A/f_D$		&$11.62 \pm 3.24 $  &$9.67$& $8.69$ \\
-
-\hline
-\end{tabular}
-
-%\end{minipage}
-\medskip
-\end{table}
-
-%\begin{table}
-% \centering
-% \begin{minipage}{140mm}
-%  \caption{Comparison between radio data \citep{K03} and model-predicted flux-ratios.}
-% \begin{tabular}{@{}ccccccc}
-
-%\hline
-%	& MERLIN  & \multicolumn{3}{c}{Model}\\
-%		&5 GHz   & 1-SIE & SIE+expdisk & 2-SIE\\
-%\hline
-%$f_A/f_B$			&$1.61 (0.10)$ &$1.04$& $1.62$ & $1.62$ \\ 
-%$f_A/f_C$		&$1.97 (0.12)$ 	 &$3.20$ & $2.89$ & $2.00$\\
-%$f_A/f_D$		&$11.62 (3.24)$  &$9.67$& $9.30$ & $11.56$\\
-
-%\hline
-%\end{tabular}
-
-%\end{minipage}
-%\medskip
-%\end{table}
-
-\section{Discussion}
-
-Gravitational lensing is, at present, the most powerful tool for
-studying substructure in galaxies outside of the Local Universe, and
-the flux-ratio anomaly systems are a key aspect of these
-investigations.  However, before using the anomaly in any
-given system to investigate structure formation and the properties of
-dark matter, it is critical to eliminate other possible explanations
-for the difference between the observed and expected fluxes, such as
-propagation effects and assumptions about the lens galaxy's mass distribution.  
-It is for this reason that much of the effort in the
-flux-ratio technique has been focused on radio-loud lens systems.  At
-these wavelengths, dust extinction and microlensing effects should be
-minimal \citep[although see][for a rare example of radio
-  microlensing]{K2000}.  \textbf{Also,  scatter broadening} can affect radio
-fluxes, as is clearly shown in the B0128+437 system \citep{B04}, and free-free absorption can change the flux-ratios as a function of frequency,
-for example, B0218+357 \citep{M07}.
-However, these propagation effects can be disentangled from
-substructure lensing because they have well known dependencies on
-wavelength. In particular, \citet{KD04} examine all eight radio-loud flux anomalous
-lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
-B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They find
-no strong wavelength dependence in the flux-ratios of all these
-systems and therefore rule out radio propagation effects as
-significant contributors to the observed anomalies.
-
-In this letter, we \textbf{instead} focus on the effect that more complicated lens galaxy mass
-distributions \textbf{have} on flux-ratio anomalies.
-Traditionally, flux-anomalous lensed quasars \textbf{have been} radio-loud, initially discovered in radio observations. While radio data
-provide reliable information on the positions and the fluxes of the
-lensed images, they are often unable to detect the lens
-galaxies. Moreover, lens modelling based only on the positions of the
-four images can be highly degenerate and prior assumptions play a key
-role in the interpretation of the observed flux-ratio anomaly.  Since
-lens galaxies are typically at redshifts of $z \leq 1$, optical and
-near-infrared observations are ideal for measuring the light distribution
-of lens galaxies and obtaining useful prior information on the underlying
-mass distributions. Indeed \citet{SHARP12} showed that high
-resolution IR imaging can help to significantly improve the precision
-of the lens modelling. This improvement is even more dramatic in the
-case of B1555+375, where \textit{HST} and SHARP AO high resolution imaging has
-allowed us to detect, for the fist time, the presence of an edge-on
-disk. This newly discovered edge-on disk provides a strong prior for our
-lens modelling.  With an additional disk component, our model 
-matches to both the radio image positions and their flux-ratio, wheras
-models with only one SIE component \citep{Marlow99,Xu14} fail to
-reproduce the fluxes correctly. Our successful modelling indicates
-that the kiloparsec-scale structure of the lens galaxy itself is
-sufficient to explain the flux-ratio anomalies in B1555+375, without
-any need to invoke the presence of substructure.
-
-From a theoretical perspective, \citet{Xu14} also find that substructures
-cannot explain the observed radio flux anomalies in all the lenses
-that were considered. After adding subhaloes from numerical simulations
-to these systems, only one out of the eight radio-loud systems
-achieves the level of the flux anomalies seen in the observations.  The rest of
-them are unlikely (only $1 - 4$ per cent probability) to have \textbf{observed distribution of flux
-anomalies} produced only by substructure, including our target B1555+375.
-In fact, among those eight radio lenses, B1555+375 is one of the most
-anomalous systems, but it is also one of the most challenging systems
-to explain by substructures. \citet{Xu14} have concluded that the failure in
-predicting flux-ratios is most likely due to oversimplified/improper lens
-modelling. They also point out that the SIE component and the external
-shear in their model are orthogonal, indicating a possible missing
-ingredient in the lens model.
-\textbf{Indeed, it's hard to find physical interpretation for an large and orthogonal external shear.
-The SHARP $K^{\prime}$ band observations provide another explaination to their result. The edge-on disk crosses the
-radio merging double is consistent of this missing component and fully accounts for the observed flux-ratio anomaly.} 
-In general, it is well known  \citep[e.g.][]{Ka91} that lens models based only on the locations of lensed
-quasar/AGN images have large degeneracies. Therefore, before
-concluding that the flux-ratios in any given lens system are a result
-of substructure, it is critical to explore a range of smooth models
-that are informed by additional observations or to do a comprehensive
-analysis such as that conducted by \citet{Xu14}. Otherwise, the derived
-substructure fractions should be considered as upper limits.
-
-%Although the number of radio-loud flux anomalous lensed
-%quasars remains small, a new technique using narrow-line emission
-%regions will enlarge the sample and bring statistical perspective on
-%substructures in the near future \citep{N14}.
-
-\section{Conclusions}
-In this letter we have taken advantage of the power of
-multi-wavelength high resolution data to investigate whether flux
-ratio anomalies could be explained by more complex smooth models for
-the lens galaxy mass distribution rather than substructure. Thanks to
-new imaging from the SHARP $K^{\prime}$ band observations of the
-gravitational lens system B1555+375, we have identified the existence
-of a previously unknown edge-on disk. By including this disk in the
-mass model of the lens galaxy, we find a good fit for both the
-positions and flux-ratios of the lensed images.
-
-Our results clearly
-demonstrate that the lack of knowledge on the lens galaxy mass
-distribution, combined with the limited information provided by the
-position of a few lensed images, can lead to improper lens models and
-a misinterpretation of the origin of flux-ratio anomalies. \textbf{While upcoming large-scale surveys, such as the DES, KiDS-VIKING, Euclid, and LSST, are expected to
-deliver new large samples of gravitationally lensed quasars, in the
-near future the discovery of new systems using narrow-line quasar
-emission \citep{N14} will provide new invaluable statistical
-perspective on current constraints based on flux-ratio anomalies.} We stress,
-therefore, that one should be very careful when interpreting the
-nature of flux-ratio anomalies, as prior assumptions on the lens mass
-distribution are a significant source of bias. Our analysis shows that
-in order to derive precise quantification of the substructure
-population and any derived properties from strongly lensed flux
-anomalous systems, it is crucial to have a careful estimation of
-non-substructure effects. In fact, even in the presence of mass
-substructures, the observed flux-ratio anomalies could be still
-dominated by the complex structure of the lens galaxy. Finally,
-additional near-infrared AO imaging from SHARP shows that B1555+375 is
-not the only system having a significant disk component detection in
-the lensing galaxy.  These systems will be investigated in future
-work, but the images alone strongly suggest that other lens systems
-have similar links between flux-ratio anomalies and disk components.
-
-%.
-modelling with only four image positions from radio data can also cause a lot of degeneracy.
-With the first system analyzing and finding an edge-on disk originated flux-ratio anomaly, our follow up will be explore other similar SHARP systems.
-In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging.
-An edge-on disk structure may also be able to explain the flux-ratio anomalies of these systems.
- %From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g.
-include an exponential disk), rather than just assuming smooth potential.
-Although the number of radio-loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}.
-If the non-substructure effect from edge-on disks does not included, expected ``false'' substructure detections can serverly bias the data analysis.
-% This breaks the idea that in strongly lensed quasars, radio flux-ratio
-% anomalies are most likely originated from substructure
-% perturbations. Our discovery shows a complex lens galaxy mass
-% distribution can dominate flux-ratio anomalous phenomena in a strongly
-% lensed system.
-% We would like to draw attention to the possible impacts on
-% substructure searching from this enge-on disk orginated flux
-% anomalies. It is a sign that researchers should be careful about the
-% flux anomalies fraction in lensed quasars. It may be worth considering
-% an upper limit of flux anomalies fraciton from observation results to
-% avoid over estimate the number of substructure detections. For further
-% analysis on substurcture population, mass function etc., it is always
-% important to rule out other non-substructure effects.
+Our analysis shows that in order to derive a precise quantification of the substructure population and any derived properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
+In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still dominated by the complex structure of the lens galaxy.
+Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.
+These gravitational lenses will be investigated in a future work, but the images alone strongly suggest that other systems may have similar links between flux-ratio anomalies and disc components.
 
 \section*{Acknowledgments}
-S.V. is grateful to Dandan Xu for useful discussion.
-L.V.E.K. is supported in part through an NWO-VICI career grant (project number 639.043.308).
-\bibliographystyle{mn2e}
+We are grateful to Dandan Xu for useful discussions.
+LVEK is supported in part through an NWO-VICI career grant (project number 639.043.308).
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute.
+STScI is operated by the Association of Universities for Research in Astronomy, Inc.
+under NASA contract NAS 5-26555.
+Some of the data presented herein were obtained at the W.
+M.
+Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration.
+The Observatory was made possible by the generous financial support of the W.
+M.
+Keck Foundation.
+The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
+We are most fortunate to have the opportunity to conduct observations from this mountain.
+
+\bibliographystyle{mnras}
 \bibliography{reference.bib}
 
+\bsp
 \label{lastpage}

### 2015-08-31 papers/B1555_EdgeOn/B1555_letter.tex
Small update to fix typo in paper text
update reference.bib from John

@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE velocity dispersion ($\sigma$), centroid position, ellipticity ($e$), and position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$), centroid position, ellipticity ($e$), position angle ($\theta$), and scale length ($R_s$).
+The free parameters of the model are the SIE Einstian radius ($b$), centroid position, ellipticity ($e$), and position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
 A Detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
-The total number of free parameters is ??.
+The total number of free parameters is 11.
 After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.
@@
 \begin{figure}
-\includegraphics[width=84mm]{gravlens_exp_try5_plot.pdf}
+\includegraphics[width=84mm]{gravlens_exp_try5_plot.eps}
 \caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.

### 2015-08-31 papers/B1555_EdgeOn/B1555_letter.tex
update of Modelling part

@@
 As a first trial of modelling, we re-create the singular isothermal ellipsoid (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
-Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =~??$).
+Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).
 
@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE Einstian radius ($b$), centroid position, ellipticity ($e$), and position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
+The free parameters of the model are the SIE Einstien radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
 A Detailed definition of these mass profiles is described by \citet{Kee01}.
-The source position and flux add three additional model parameters.
+The source position add two additional model parameters.
 We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
@@
 All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
-The total number of free parameters is 11.
+The total number of free parameters is 13.
 After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.
@@
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios.
-We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = ~??$.
+We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = 2.7$.
 The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
@@
 A  &$0$    		&$0$			&  $1$ 				&$+0.000$  &$+0.000$	& $1$ 		& $1$\\  
-B  &$-0.073$	&$+0.048$	& $0.620 \pm 0.039$ 	&$-0.073$ &$+0.048$		& $0.620$ 	& $0.962$ \\  
-C  &$-0.412$ 	&$-0.028$	& $0.507\pm 0.030$	&$-0.412$ &$-0.028$		& $0.461$ 	& $0.313$\\  
-D  &$-0.162$	&$-0.368$	& $0.086 \pm 0.024$ 	&$-0.163$ &$-0.365$		& $0.115$ 	& $0.103$\\  
+B  &$-0.073$	&$+0.048$	& $0.620 \pm 0.039$ 	&$-0.073$ &$+0.048$		& $0.620$ 	& $0.971$ \\  
+C  &$-0.412$ 	&$-0.028$	& $0.507\pm 0.030$	&$-0.412$ &$-0.028$		& $0.461$ 	& $0.312$\\  
+D  &$-0.162$	&$-0.368$	& $0.086 \pm 0.024$ 	&$-0.163$ &$-0.365$		& $0.115$ 	& $0.106$\\  
 \hline
@@
 \hline 
-Parameter  & SIE & ExpDisc \\
+Parameter    & Comp. 1  & Comp. 2  \\
+   & (SIE) & (ExpDisc)\\
 \hline

### 2015-09-04 papers/B1555_EdgeOn/B1555_letter.tex
small updates to paper text

@@
 
+\begin{figure*}
+\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
+\caption{High-resolution multi-band imaging of B1555+375 with {\it HST}/WFPC2 at F555W (left) and F814W (middle-left), with {\it HST}/NICMOS/NIC2 at F160W (middle-right) and with Keck adaptive optics at $K^\prime$-band (right).
+All of the panels are 3.7 arcsec on a side and the scale-bar represents 1 arcsec.}
+\label{fig:multiband}
+\end{figure*}
+
 It was first suggested by \citet{Mao1998} that the flux-ratio anomalies observed in the multiple radio-loud images of lensed quasars could be interpreted as a sign of the presence of substructure in lens galaxies.
@@
 To this end, we use new infrared imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][]{mckean07,lagattuta10,SHARP12, V12}.
-The main goal of the SHARP project is to re-observe known four-image and Einstein ring lens systems at high angular resolution by making use of observations with (1) adaptive optics (AO) on the W.
+The main goal of SHARP is to re-observe known four-image and Einstein ring lens systems at high angular resolution by making use of observations with (1) adaptive optics (AO) on the W.
 M.
@@
 B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}.
-As B1555+375 was included in both the observational and theoretical analysis of \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
+As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
 The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3.
 The results of this analysis and their implications are discussed in Section 4.
-Note that neither the lens galaxy or lensed source redshift are known for B1555+375, which we assume are at $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colour \citep{Marlow99}.
+Note that the redshifts of both the lens galaxy and the lensed source are unknown for B1555+375, so we assume redshifts of $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colours \citep{Marlow99}.
 This assumption has no effect on the derived magnifications or flux-ratios of our analysis.
@@
 The data were reduced in the standard manner using the {\sc vlbaprocs} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS).
-Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6$~degr east of north.
-The final map has an rms of 78~$\mu$Jy~beam$^{-1}$ and is also shown in Fig.~\ref{fig:merlin}.
+Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6^\circ$ east of north.
+The final map (also shown in Fig.~\ref{fig:merlin}) has an rms of 78~$\mu$Jy~beam$^{-1}$.
 
@@
 We immediately see from the high resolution VLBA imaging that image B has a smaller angular size than image A, which is consistent with a perturbation in the mass model being responsible for the flux-ratio anomaly (recall that gravitational lensing conserves surface brightness), as opposed to free-free absorption or interstellar scattering.
-
-\begin{figure*}
-\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
-\caption{High-resolution multi-band imaging of B1555+375 with {\it HST}/WFPC2 at F555W (left) and F814W (middle-left), with {\it HST}/NICMOS/NIC2 at F160W (middle-right) and with Keck adaptive optics at $K^\prime$-band (right).
-All of the panels are 3.7 arcsec on a side and the scale-bar represents 1 arcsec.}
-\label{fig:multiband}
-\end{figure*}
 
@@
 A Detailed definition of these mass profiles is described by \citet{Kee01}.
-The source position add two additional model parameters.
+The source position adds two additional model parameters.
 We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
@@
 To obtain the best-fit lens model, we explore the parameter space with the following steps.
-First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10$ degr for the exponential disc.
+First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$  for the exponential disc.
 We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile.
@@
 from an external shear) that is being partly compensated for by the disc component.
-Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able confirm this.
+Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able to confirm this.
 
@@
 \caption{A summary of the observational constraints and the predicted lens-model parameters.
-The lensed image positions in the radio \citep{Marlow99} (in arcsec) and average flux-ratios \citep{K03} are respect to image A.
+The lensed image positions in the radio \citep{Marlow99} (in arcsec) and average flux ratios \citep{K03} are respect to image A.
 Uncertainties in the position measurements for images A, B and C are $0.001$~arcsec and for image D are $0.006$~arcsec.}
@@
 \centering
-\caption{Best-fit model parameters of B1555+375 for an SIE + exponential disc lens model and the uncertainties.
+\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99}).
 The positions are measured in arcsec, relative to the radio position of image A.
@@
 \hline 
-Parameter    & Comp. 1  & Comp. 2  \\
-   & (SIE) & (ExpDisc)\\
+Parameter    & SIE Component & ExpDisc Component  \\
+%   & (SIE) & (ExpDisc)\\
 \hline
@@
 Although flux-ratio anomalies provide a powerful tool to investigate low-mass substructure in lensing haloes out to cosmological redshifts, it is clear that some care is needed in interpreting the results.
-It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less effected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux-ratios.
+It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios.
 This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations from a smooth mass distribution \citep{Xu14}.
 In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}.
-Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass substructures as as been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux-ratio, or even astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
+Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass substructures as as been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
 
@@
 as in the case of B1933+503; \citealt{suyu12}).
-Also, as we have shown here, B1555+375 shows evidence for an extended $\sim100$~mas gravitational arc at radio-wavelengths that is coincident with the edge-on disc.
+Also, as we have shown here, B1555+375 shows evidence for an extended $\sim100$~mas gravitational arc at radio-wavelengths that crosses the edge-on disc.
 Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the extended disc is sufficient to cause the anomaly.
@@
 LVEK is supported in part through an NWO-VICI career grant (project number 639.043.308).
-The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+[{\bf ADD CDF NSF}]  The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
 Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute.

### 2015-09-06 papers/B1555_EdgeOn/B1555_letter.tex
Added two-contour figure and small tweak to text

@@
 The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear.
-While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.
+While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu14}.
+
+%While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure.
 
@@
 \begin{figure}
-\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations of \citet{Marlow99} and the VLBA observations presented here overlaid.}
+%\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
+\includegraphics[width=84mm]{fig2_twocontour_g.eps}
+\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here overlaid.}
 \label{fig:merlin}

### 2015-09-07 papers/B1555_EdgeOn/B1555_letter.tex
update comments from Leon and Dandan also bib file

@@
 Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies.
-However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo.
+However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo or other propagation effects.
 Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W.
@@
 This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
-However, a recent comparison of the observational data (8 gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu14}.
+However, a recent comparison of the observational data (eight gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
 
 The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}.
-This method gives a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
-The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is not currently clear.
-While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu14}.
+This method has given a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
+The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is currently not clear.
+While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu15}.
 
@@
 B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}.
-As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu14}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
+As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu15}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
 The SHARP imaging data are introduced in Section 2 and we present a revised lens model using these data in Section 3.
@@
 M.
-Keck-II Telescope and the {\it HST}, and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.
+Keck-II Telescope and the Hubble Space Telescope ({\it HST}), and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.
 
@@
 There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity of $\sim 0.8$.
+These include the nearly complete lack of emission associated with lensed images B and D (see Fig.~\ref{fig:merlin} ), as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity ($e$, define as the axis ratio $q=1-e$) of $\sim 0.8$.
 We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
-Therefore, the lack of emission that is seen from these images is likely due to dust extinction.
+Therefore, the lack of emission that is seen from these images is likely due to dust extinction and additional demagnification due to lensing.
 
@@
 
-The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu14}.
+The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu12,Xu15}.
 However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens.
@@
 In total, there are 11 constraints to the mass model provided by the observational data.
-As a first trial of modelling, we re-create the singular isothermal ellipsoid (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
-Consistent with previous studies \citep{Marlow99,Xu14}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).
+As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
+Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).
 
@@
 We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
-Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays will test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
+Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
 
@@
 
-The best-fit model parameters are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}.
+The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}.
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios.
@@
 The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
+The differences in fluxes may due to the source could be slightly extended sphere while our model uses point-source.
 The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
@@
 It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios.
-This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations from a smooth mass distribution \citep{Xu14}.
+This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations in forms of clumpiness from a smooth mass distribution \citep{Dalal2002,KD04,Xu15}.
 In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}.
-Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass substructures as as been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
+Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass "dark" substructures as has been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
 
@@
 Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the extended disc is sufficient to cause the anomaly.
-Nevertheless, before concluding that the flux-ratios in any given lens system are a result of substructure, it is critical to explore a range of smooth models that are informed by additional observations or to do a comprehensive analysis such as that conducted by \citet{Xu14}.
+Nevertheless, before concluding that the flux-ratios in any given lens system are a result of substructure, it is critical to explore a range of smooth models that are informed by additional observations or to do a comprehensive analysis such as that conducted by \citet{Xu15}.
 Otherwise, the derived substructure fractions should be considered as upper limits.
@@
 This newly discovered edge-on disk provides a strong prior for our lens modelling.
-With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu14} fail to reproduce the fluxes correctly.
+With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu15} fail to reproduce the fluxes correctly.
 Our successful modelling indicates that the kpc-scale structure of the lens galaxy itself is sufficient to explain the flux-ratio anomalies in B1555+375, without any need to invoke the presence of substructure.
 
-%From a theoretical perspective, \citet{Xu14} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered.
+%From a theoretical perspective, \citet{Xu15} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered.
 After adding sub-haloes from numerical simulations to these systems, only one out of the eight radio-loud gravitational lenses achieves the level of the flux-ratio anomalies seen in the observations.
@@
 In fact, among those eight radio lenses, B1555+375 is one of the most anomalous gravitational lenses, but it is also one of the most challenging systems to explain by substructures.
-\citet{Xu14} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter.
+\citet{Xu15} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter.
 They also point out that the SIE component and the external shear in their model are orthogonal, indicating a possible missing ingredient in the lens model.
@@
 
-Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compcat lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
+Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
 While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
@@
 Our analysis shows that in order to derive a precise quantification of the substructure population and any derived properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
-In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still dominated by the complex structure of the lens galaxy.
+In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still affected by the complex structure of the lens galaxy.
 Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.

### 2015-09-07 python/gravlens_plot.py

@@ -9,6 +9,7 @@ import matplotlib.patches as mpat
 name='B1555_expdisk_try5.crit'
 
 # lensed images
+'''
 ## system == B1555
 # observe data
 x0=[0.0, 0.0726,0.4117,0.1619]
@@ -25,6 +26,25 @@ sx,sy= 1.952576e-01, -1.493771e-01
 # mass profile centeroid
 cx=[ 1.818271e-01, 1.471605e-01] # x position
 cy=[ -1.987580e-01, -2.056755e-01] # y position
+'''
+
+## system == B0712
+# observe data
+x0=[0.0, -0.075,-1.185,-1.71]
+y0=[0.0, -0.16, -0.67,0.46]
+
+# model
+x=[0.0, -0.075,-1.185,-1.7103]
+y=[0.0, -0.16, -0.67,0.46]
+
+# model paras
+# source
+sx,sy= -8.809485e-01,  2.514535e-01
+
+# mass profile centeroid
+cx=[ -8.335581e-01, -1.354868e+00] # x position
+cy=[ 3.426335e-01, 1.572431e-01] # y position
+
 
 
 ##----call functions in the end----##
@@ -96,12 +116,12 @@ def img_pos():
 
 ##---- call functions from here ----##
 
-crit()
-caus()
+#crit()
+#caus()
 model_plot()
 img_pos()
 
-plt.xlim(-0.4,0.8)
-plt.ylim(-0.8,0.4)
+plt.xlim(-1.8,0.2)
+#plt.ylim(-0.8,0.4)
 plt.legend(loc=4)
 plt.show()

### 2015-09-07 papers/B1555_EdgeOn/B1555_letter.tex
update for Matt's comment
changes in modelling about starting point setting

@@
 To obtain the best-fit lens model, we explore the parameter space with the following steps.
-First, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$  for the exponential disc.
-We then use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile.
-The rest of the parameters that describe the exponential disc are set to be the same as the SIE component as the starting point.
+First, to pick up a set of starting parameters, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles.
+However, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$ for the exponential disc.
 All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).

### 2015-09-07 python/gravlens_plot.py

@@ -6,7 +6,7 @@ import matplotlib.patches as mpat
 
 # gravlens file name
 
-name='B1555_expdisk_try5.crit'
+name='exp_try3_crit.dat'
 
 # lensed images
 '''
@@ -35,7 +35,7 @@ y0=[0.0, -0.16, -0.67,0.46]
 
 # model
 x=[0.0, -0.075,-1.185,-1.7103]
-y=[0.0, -0.16, -0.67,0.46]
+y=[0.0, -0.16, -0.67,0.4600]
 
 # model paras
 # source
@@ -109,19 +109,22 @@ def img_pos():
     plt.plot(x0,y0,'b+',ms=10,label='observe')
     plt.plot(x,y,'o',ms=10,mec='r',mfc='none',label='model')
     
+    #plt.xlabel('$\Delta$ $ \alpha $ (arcsec)')
+    #plt.ylabel('$\Delta \delta$ (arcsec)')
     plt.xlabel('arcsec')
     plt.ylabel('arcsec')
 
 
 
+
 ##---- call functions from here ----##
 
-#crit()
-#caus()
+crit()
+caus()
 model_plot()
 img_pos()
 
-plt.xlim(-1.8,0.2)
+#plt.xlim(-1.8,0.2)
 #plt.ylim(-0.8,0.4)
-plt.legend(loc=4)
+plt.legend(loc=1)
 plt.show()

### 2015-09-08 papers/B1555_EdgeOn/B1555_letter.tex
shrink the size of figures 84mm->72mm
take out chi^2 in text

@@
 As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
-Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}; reduced $\chi^2 =97.3$).
+Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}).
+%; reduced $\chi^2 =97.3$
 
@@
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios.
-We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model, with a reduced $\chi^2 = 2.7$.
+We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model.
+% with a reduced $\chi^2 = 2.7$
 The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
@@
 %\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\includegraphics[width=84mm]{fig2_twocontour_g.eps}
+\includegraphics[width=72mm]{fig2_twocontour_g.eps}
 \caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here overlaid.}
@@
 \begin{figure}
-\includegraphics[width=84mm]{gravlens_exp_try5_plot.eps}
+\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
 \caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.

### 2015-09-08 papers/B1555_EdgeOn/B1555_letter.tex
update to author list

@@
 \title[Beware the effect of edge-on discs]{SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars}
-\author[Hsueh et al.]{Jen-Wei Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} A. N. Other,$^{2}$ A. N. Other,$^{2}$  A. N. Other,$^{2}$ A. N. Other,$^{2}$ A. N. Other,$^{2}$
-\newauthor and A. N. Other$^{2}$\\
+\author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
+\newauthor  L. V. E. Koopmans,$^{4}$ and D. J. Lagattuta$^{6}$\\
 $^{1}$Department of Physics, University of California, Davis, 1 Shields Ave. Davis, CA 95616, USA\\
-$^{2}$Building, Institute, Street Address, City, Code, Country\\
-$^{3}$Building, Institute, Street Address, City, Code, Country\\
-$^{4}$Building, Institute, Street Address, City, Code, Country\\
-$^{5}$Building, Institute, Street Address, City, Code, Country\\
-$^{6}$Building, Institute, Street Address, City, Code, Country}
+$^{2}$Max Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, D-85740 Garching, Germany\\
+$^{3}$Netherlands Institute for Radio Astronomy (ASTRON), P.O. Box 2, 7990 AA Dwingeloo, The Netherlands\\
+$^{4}$Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands\\
+$^{5}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{6}$University of Lyon, 92 Rue Pasteur, 69007 Lyon, France}
 \begin{document}

### 2015-09-11 papers/B1555_EdgeOn/B1555_letter.tex
update of typo

@@
 % Keep the title short and informative.
-\title[Beware the effect of edge-on discs]{SHARP - II. Beware the effect of edge-on discs when interpreting the anomalous flux-ratios of gravitationally lensed quasars}
+\title[Beware the effect of edge-on discs]{SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios}
 \author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
@@
 The observations were phase referenced using J1544+398 every 3 min over the total observing time of 3 h.
-The data were reduced in the standard manner using the {\sc vlbaprocs} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS).
+The data were reduced in the standard manner using the {\sc vlbautlis} analysis pipeline that is part of the Astronomical Image Processing Software (AIPS).
 Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6^\circ$ east of north.

### 2015-09-14 papers/B1555_EdgeOn/B1555_letter.tex
nearly final updates to B1555 letter text

@@
 Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies.
-However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo or other propagation effects.
+However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo or propagation effects.
 Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W.
@@
 We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
-Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
+Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
 \end{abstract}
@@
 A common feature of dark-matter only simulations of structure formation is the presence of thousands of sub-haloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
-However, observations of the Local Group show many fewer satellite galaxies than are predicted by the simulations, even when taking into account completeness corrections arising from the limited sky coverage imposed by the Galactic Plane and the latest discoveries of new dwarf galaxies \citep{DES15,Kop15}.
+However, observations of the Local Group show many fewer satellite galaxies than are predicted by the simulations, even when taking into account the latest discoveries of new dwarf galaxies \citep{DES15,Kop15} and completeness corrections arising from the limited sky coverage imposed by the Galactic Plane.
 This is the well-known {\it missing satellite problem} \citep{Klypin1999,Moore1999,S07}.
@@
 This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
-However, a recent comparison of the observational data (eight gravitational lens systems with four or more images) with the expectations from a set of cold dark matter simulations, which are also representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
+However, a recent comparison between the observational data (eight gravitational lens systems with four or more images) and the predictions from a set of cold dark matter simulations that are representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
 
@@
 
-In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered.
+In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of clumpy substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered.
 To this end, we use new infrared imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][]{mckean07,lagattuta10,SHARP12, V12}.
-The main goal of SHARP is to re-observe known four-image and Einstein ring lens systems at high angular resolution by making use of observations with (1) adaptive optics (AO) on the W.
+The main goal of SHARP is to investigate galaxy structure and other astrophysical topics through the re-observation of known gravitational lens systems at high angular resolution, making use of observations with (1) adaptive optics (AO) on the W.
 M.
@@
 Here we focus on CLASS B1555+375 \citep{Marlow99}, which was discovered as part of the Cosmic Lens All-Sky Survey \citep{CLASS1,CLASS2}.
-B1555+375 has four lensed images with a maximum separation of 426~mas in a fold-configuration, where the two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths; previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}.
+B1555+375 has four lensed images with a maximum separation of 426~mas in a fold configuration.
+The two merging lensed images show a strong and persistent flux-ratio anomaly at radio wavelengths, and previous radio monitoring observations ruled out microlensing effects as the cause of the anomaly \citep{K03}.
 As B1555+375 was included in the observational and theoretical analyses of both \citet{Dalal2002} and \citet{Xu15}, understanding its mass distribution is of key importance to assess any systematics with the inferred level of substructure in the lensing halo with the flux-ratio anomaly method.
@@
 M.
-Keck-II Telescope and the Hubble Space Telescope ({\it HST}), and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.
+Keck-II Telescope and HST, and high-resolution radio imaging taken with the Very Long Baseline Array (VLBA), which are discussed below and are summarized in Table~\ref{tab:obs}.
 
@@
 M.
-Keck-II Telescope on 2012 May 16.
+Keck-II Telescope on 2012 May 16 (PI: Fassnacht).
 The AO system was used, with the corrections derived from the laser guide star and a $R=14.4$-mag tip-tilt star that was located $\sim45$~arcsec from the lens.
-The narrow camera mode was used, giving a field-of-view of $\sim10$~arcsec on a side and a pixel scale of 10~mas.
+The narrow camera mode was used, giving a field of view of $\sim10$~arcsec on a side and a pixel scale of 10~mas.
 Six dithered 300~s exposures were obtained in the $K^{\prime}$-band filter.
@@
 There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D (see Fig.~\ref{fig:merlin} ), as can be seen by comparing the radio contours to the $K^\prime$-band emission, and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity ($e$, define as the axis ratio $q=1-e$) of $\sim 0.8$.
-We note that this position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
+These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q as $$q=1-e$.
+We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
 Therefore, the lack of emission that is seen from these images is likely due to dust extinction and additional demagnification due to lensing.
@@
 
-The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line-of-sight to the lensed images \citep{Dalal2002,Xu12,Xu15}.
+The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line of sight to the lensed images \citep{Dalal2002,Xu12,Xu15}.
 However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens.
-To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly, without the need for additional substructure.
+To test this possibility, we model the system with a disc component in order to see if a plausible mass model can explain the flux-ratio anomaly without the need for additional substructure.
 
@@
 
-The next step is to examine if an edge-on disc can cause a physically plausible perturbation in the strong lensing mass model that results in the observed flux ratio anomaly of  merging images A and B.
+The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B.
 An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}.
@@
 The free parameters of the model are the SIE Einstien radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
-A Detailed definition of these mass profiles is described by \citet{Kee01}.
+A detailed definition of these mass profiles is described by \citet{Kee01}.
 The source position adds two additional model parameters.
@@
 To obtain the best-fit lens model, we explore the parameter space with the following steps.
-First, to pick up a set of starting parameters, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles.
-However, we apply the a priori information from the Keck AO image by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$ for the exponential disc.
+First, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles.
+We add information from the Keck AO image for the disc by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$.
 All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
@@
 The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}.
-Table \ref{tab:results} also shows the comparison between the observed radio data and the model predicted image positions and flux ratios.
+Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
 We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model.
@@
 The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
-The differences in fluxes may due to the source could be slightly extended sphere while our model uses point-source.
-The mass model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
-We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to there being an additional ellipticity in the model (e.g.
+The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
+The model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
@@
 \centering
-\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99}).
+\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99}) and so is not shown here.
 The positions are measured in arcsec, relative to the radio position of image A.
@@
 It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios.
-This has led to an often studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements that are most likely due to perturbations in forms of clumpiness from a smooth mass distribution \citep{Dalal2002,KD04,Xu15}.
+This has led to an oft-studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements \citep{Dalal2002,KD04,Xu15}.
 In general, lens models that are based only on the locations of lensed radio-loud images have large degeneracies due to the limited number of constraints that are provided by 50 to 200~mas imaging of the unresolved sources \citep[e.g.][]{Ka91}.
-Furthermore, the nature of the perturbation may not be due exclusively to a population of low-mass "dark" substructures as has been already shown to be the case for MG J0414+0534 and MG J2016+112, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
+Furthermore, observed flux-ratio anomalies may not be due exclusively to a population of low-mass "dark" substructures, as already seen in the MG J0414+0534 and MG J2016+112 systems, where there is evidence for luminous companion dwarf galaxies that can account for the observed flux ratios, and even observed astrometric anomalies (\citealt{ros00,chen07,more09}; see also \citealt{mckean07,jackson10}).
 
@@
 
-%Gravitational lensing is, at present, the most powerful tool for
-%studying substructure in galaxies outside of the Local Universe, and
-%the flux-ratio anomaly systems are a key aspect of these
-%investigations.  However, before using the anomaly in any
-%given system to investigate structure formation and the properties of
-%dark matter, it is critical to eliminate other possible explanations
-%for the difference between the observed and expected fluxes, such as
-%propagation effects and assumptions about the lens galaxy's mass distribution.  
-%It is for this reason that much of the effort in the
-%flux-ratio technique has been focused on radio-loud lens systems.  At
-%these wavelengths, dust extinction and microlensing effects should be
-%minimal \citep[although see][for a rare example of radio
-%  microlensing]{koopmans00}.  \textbf{Also,  scatter broadening} can affect radio
-%fluxes, as is clearly shown in the B0128+437 system \citep{B04}, and free-free absorption can change the flux-ratios as a function of frequency,
-%for example, B0218+357 \citep{M07}.
-%However, these propagation effects can be disentangled from
-%substructure lensing because they have well known dependencies on
-%wavelength. In particular, \citet{KD04} examine all eight radio-loud flux anomalous
-%lenses besides B0128+437, namely: MG 0414+0534, B0712+472, B1359+154,
-%B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265.  They find
-%no strong wavelength dependence in the flux-ratios of all these
-%systems and therefore rule out radio propagation effects as
-%significant contributors to the observed anomalies.
-
-%In this letter, we instead focus on the effect that more complicated lens galaxy mass distributions \textbf{have} on flux-ratio anomalies.
-Traditionally, flux-anomalous lensed quasars have been radio-loud, initially discovered in radio observations.
-While radio data provide reliable information on the positions and the fluxes of the lensed images, they are often unable to detect the lens galaxies.
-Moreover, lens modelling based only on the positions of the four images can be highly degenerate and prior assumptions play a key role in the interpretation of the observed flux-ratio anomaly.
-Since lens galaxies are typically at redshifts of $z \leq 1$, optical and near-infrared observations are ideal for measuring the light distribution of lens galaxies and obtaining useful prior information on the underlying mass distributions.
-Indeed \citet{SHARP12} showed that high resolution IR imaging can help to significantly improve the precision of the lens modelling.
-This improvement is even more dramatic in the case of B1555+375, where HST and SHARP AO high resolution imaging has allowed us to detect, for the fist time, the presence of an edge-on disk.
-This newly discovered edge-on disk provides a strong prior for our lens modelling.
-With an additional disk component, our model matches to both the radio image positions and their flux-ratio, wheras models with only one SIE component \citep{Marlow99,Xu15} fail to reproduce the fluxes correctly.
-Our successful modelling indicates that the kpc-scale structure of the lens galaxy itself is sufficient to explain the flux-ratio anomalies in B1555+375, without any need to invoke the presence of substructure.
-
-%From a theoretical perspective, \citet{Xu15} also find that substructures cannot explain the observed radio flux anomalies in all the gravitational lenses that were considered.
-After adding sub-haloes from numerical simulations to these systems, only one out of the eight radio-loud gravitational lenses achieves the level of the flux-ratio anomalies seen in the observations.
-The rest are unlikely (only $1 - 4$ per cent probability) to have an observed distribution of flux-ratio anomalies produced only by substructure, including our target B1555+375.
-In fact, among those eight radio lenses, B1555+375 is one of the most anomalous gravitational lenses, but it is also one of the most challenging systems to explain by substructures.
-\citet{Xu15} have concluded that the failure in predicting flux-ratios is most likely due to an oversimplified/improper lens modelling, which is consistent with the results of this letter.
-They also point out that the SIE component and the external shear in their model are orthogonal, indicating a possible missing ingredient in the lens model.
-Indeed, it's hard to find physical interpretation for an large and orthogonal external shear, without the inclusions of an observationally motivated edge-on disc component.
-
 Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
 While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
-We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution are a significant source of bias.
+We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution may a significant source of bias.
 
-Our analysis shows that in order to derive a precise quantification of the substructure population and any derived properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
-In fact, even in the presence of mass substructures, the observed flux-ratio anomalies could be still affected by the complex structure of the lens galaxy.
+Our analysis shows that in order to derive a precise quantification of the substructure population and other properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
+In fact, even in the presence of substructures, the observed flux-ratio anomalies could be still affected by the complex structure of the lens galaxy.
 Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.

### 2015-09-14 papers/B1555_EdgeOn/B1555_letter.tex
update for B1555 draft wording
non-smooth, clumpy

@@
 \title[Beware the effect of edge-on discs]{SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios}
-\author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
+\author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. P. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
 \newauthor  L. V. E. Koopmans,$^{4}$ and D. J. Lagattuta$^{6}$\\
@@
 Gravitational lens flux-ratio anomalies provide a powerful technique for measuring dark matter substructure in distant galaxies.
-However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other non-smooth component of the lensing galaxy halo or propagation effects.
+However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other component of the lensing galaxy halo or to propagation effects.
 Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W.
@@
 We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
-Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full non-smooth component of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
+Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
 \end{abstract}
@@
 This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
-However, a recent comparison between the observational data (eight gravitational lens systems with four or more images) and the predictions from a set of cold dark matter simulations that are representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
+However, a recent comparison between the observational data (eight gravitational lens systems with four or more images) and the predictions from a set of cold dark matter simulations that are representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the full observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
 
@@
 The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is currently not clear.
-While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than substructure \citep[see][for a discussion]{Xu15}.
+While this could be the result of small sample statistics, it could also be an indication that the flux-ratio anomalies have a different origin than clumpy substructure \citep[see][for a discussion]{Xu15}.
 
@@
 There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q as $$q=1-e$.
+These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q$ as $q=1-e$.
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.

### 2015-09-14 papers/B1555_EdgeOn/B1555_letter.tex
Added cover letter template, and NSF ack to paper

@@
 We are grateful to Dandan Xu for useful discussions.
+CDF and DJL acknowledge support from NSF-AST-0909119.
 LVEK is supported in part through an NWO-VICI career grant (project number 639.043.308).
-[{\bf ADD CDF NSF}]  The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
 Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute.

### 2015-09-15 papers/B1555_EdgeOn/B1555_letter.tex
Final edits and spell-checking

@@
 This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
-However, a recent comparison between the observational data (eight gravitational lens systems with four or more images) and the predictions from a set of cold dark matter simulations that are representative of the mass and redshift of the lens galaxies, suggest that there is only a 1--4 per cent probability that the full observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
+However, a recent comparison of the observational data (eight gravitational lens systems with four or more images) with the predictions from a set of cold dark matter simulations that are representative of the mass and redshift of the lens galaxies suggests that there is only a 1--4 per cent probability that the full observed flux-ratio distribution is produced only by substructure \citep{Xu15}.
 
@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE Einstien radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
+The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 First, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles.
-We add information from the Keck AO image for the disc by setting the ellipticity to $e=0.8$ and the position angle to $\theta=10^\circ$.
-All of the model parameters are then allowed to vary, but we fix the centroid position of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
+We add information from the Keck AO image for the disc, starting with an ellipticity of $e=0.8$ and a position angle of $\theta=10^\circ$.
+All of the model parameters are then allowed to vary, but we fix the centroid positions of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
 The total number of free parameters is 13.
@@
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
-We find that by adding an elongated exponential disc to a smooth potential model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model.
+We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model.
 % with a reduced $\chi^2 = 2.7$
@@
 %\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\includegraphics[width=72mm]{fig2_twocontour_g.eps}
-\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here overlaid.}
+\includegraphics[width=72mm]{fig2_twocontour_b.eps}
+\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.}
 \label{fig:merlin}
@@
 \caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.
-The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dash line.
+The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dashed line.
 The position of the source is at ($-0.1953$, $-0.1494$), which is marked by the red filled circle.
@@
 \centering
-\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99}) and so is not shown here.
+\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here).
 The positions are measured in arcsec, relative to the radio position of image A.
-The ellipticity is defined as the axis ratio $q=1-e$ and the position angles are measured in degrees east of north.
-The Einstein radius $b$ and disc-scale radius are measured in arcsec.}
+The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north.
+The Einstein radius $b$ and disc scale radius are measured in arcsec.}
 \begin{tabular}{ccc}
@@
 Although flux-ratio anomalies provide a powerful tool to investigate low-mass substructure in lensing haloes out to cosmological redshifts, it is clear that some care is needed in interpreting the results.
-It is now well established that observations of radio-loud gravitational lenses provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios.
+It is now well established that observations of radio-loud gravitational lenses may provide the most robust observational constraints because they are less affected by dust extinction and microlensing, and monitoring can determine the best estimate of the intrinsic flux ratios.
 This has led to an oft-studied sample of eight radio-loud gravitational lenses with well-defined flux-ratio measurements \citep{Dalal2002,KD04,Xu15}.
@@
 
-Our results for B1555+375 clearly demonstrate that the lack of knowledge on the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
+Our results for B1555+375 clearly demonstrate that a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
 While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.

### 2015-09-15 python/gravlens_plot.py
try to fix pdf

@@ -126,6 +126,8 @@ def img_pos():
 
 ##---- call functions from here ----##
 
+plt.figure(figsize=(5.7,5.7))
+
 crit()
 caus()
 model_plot()
@@ -134,4 +136,5 @@ img_pos()
 plt.xlim(0.4,-0.8)
 plt.ylim(-0.8,0.4)
 plt.legend(loc=1)
+
 plt.show()

### 2015-10-20 papers/B1555_EdgeOn/B1555_letter.tex
update for key words
try to fix pdf
update disc lens ratio in draft

@@
 \usepackage{ae,aecompl}
+\usepackage{aecompl}
 
@@
 \begin{keywords}
-gravitational lensing -- quasars: individual CLASS B1555+375 -- cosmology: observations 
+gravitational lensing -- quasars: individual CLASS B1555+375 -- galaxies: structure 
 \end{keywords}
@@
 \begin{figure}
-\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
+%\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
+\includegraphics[width=72mm]{gravlens_exp_try5_plot-2.eps}
+%\includegraphics[width=72mm]{fig2_twocontour_b.eps}
 \caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.
@@
 Our results for B1555+375 clearly demonstrate that a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
+We've seen 5 out of 25 SHARP lenses revealing a disc in AO imaging, which these lenses are source selected thus less possible to be biased (Fassnacht et al., in prep.).
 While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.

### 2015-11-04 papers/B1555_EdgeOn/B1555_letter.tex
text editing to modelling and discussion

@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the exponential disc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
-We note that there is a significant 0.036~arcsec offset between the SIE and exponential disc components, which is likely due to an additional ellipticity in the model (e.g.
+In IR imaging there is no sign of bulge, we then interpret the mass in ExpDisc component as the baryonic mass from lens galaxy.The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
-Again, more complex mass models that use the full extent of the gravitational arc and the compact lensed images from future high resolution radio imaging will be able to confirm this.
+Again, more complex mass models need the full extent of the gravitational arc for constraints.
+While the gravitational arc in IR band suffers severe dust extinction, the compact lensed images from future high resolution radio imaging will be able to confirm this.
 
@@
 
-Our results for B1555+375 clearly demonstrate that a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
-We've seen 5 out of 25 SHARP lenses revealing a disc in AO imaging, which these lenses are source selected thus less possible to be biased (Fassnacht et al., in prep.).
+Our analysis for B1555+375 shows that in order to derive a precise quantification of the substructure population and other properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
+%We find that in B1555+375, a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
 While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
 We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution may a significant source of bias.
-
-Our analysis shows that in order to derive a precise quantification of the substructure population and other properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
-In fact, even in the presence of substructures, the observed flux-ratio anomalies could be still affected by the complex structure of the lens galaxy.
 Finally, additional near-infrared AO imaging from SHARP shows that B1555+375 is not the only gravitational lens having a significant disc component detection in the lensing galaxy.
+5 out of 25 SHARP lenses are found discs in AO imaging (Fassnacht et al., in prep.).
 These gravitational lenses will be investigated in a future work, but the images alone strongly suggest that other systems may have similar links between flux-ratio anomalies and disc components.

### 2015-11-04 python/gravlens_plot.py

@@ -6,7 +6,7 @@ import matplotlib.patches as mpat
 
 # input files
 
-name='/Users/jwhsueh/Documents/SHARP_jw/DK02/mock.crit'
+#name='/Users/jwhsueh/Documents/SHARP_jw/DK02/mock.crit'
 
 name_findimg='/Users/jwhsueh/Documents/SHARP_jw/DK02/gravlens_mock_findimg.dat'
 
@@ -39,7 +39,7 @@ sx,sy= -1.952576e-01, -1.493771e-01
 # mass profile centeroid
 cx=[ -1.818271e-01, -1.471605e-01] # x position
 cy=[ -1.987580e-01, -2.056755e-01] # y position
-
+'''
 
 
 ## system == B0712
@@ -48,8 +48,8 @@ x0=[0.0, -0.075,-1.185,-1.71]
 y0=[0.0, -0.16, -0.67,0.46]
 
 # model
-x=[0.0, -0.075,-1.185,-1.7103]
-y=[0.0, -0.16, -0.67,0.4600]
+x=[-9.694099e-01, 4.912447e-02,-3.756152e-02,-1.223079e+00]
+y=[-7.651540e-01,  1.666924e-01, -2.644472e-01, 5.127648e-01]
 
 # model paras
 # source
@@ -58,7 +58,7 @@ sx,sy= -8.809485e-01,  2.514535e-01
 # mass profile centeroid
 cx=[ -8.7e-01, -1.08] # x position
 cy=[ 0.15, 0.08] # y position
-'''
+
 
 ##----read model details from files [glafic]----##
 
@@ -177,15 +177,15 @@ def img_pos():
 ##---- call functions from here ----##
 
 #sx,sy,cx,cy=read_lens()
-x,y=read_findimg()
+#x,y=read_findimg()
 
 plt.figure(figsize=(5.7,5.7))
 
-crit()
-caus()
+#crit()
+#caus()
 #model_plot()
-x0,y0=x,y
-print x,y
+#x0,y0=x,y
+#print x,y
 img_pos()
 
 #plt.xlim(0.4,-0.8)

### 2015-11-04 python/resample.py

@@ -1,0 +1,27 @@
+## Now it's only for change the scale size
+
+import pyfits
+import numpy as np
+
+ratio=5 # rescale ratio between pixel sizes
+
+ori=pyfits.open('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/B1555_nirc2_4x4.fits')
+img=ori[0].data
+
+size=img.shape[0]
+
+new=np.zeros((size/ratio,size/ratio))
+ace=np.zeros((ratio,ratio))
+
+for i in range(size/ratio):
+    for j in range(size/ratio):
+        ace=img[ratio*i:(ratio*i+ratio),ratio*j:(ratio*j+ratio)]
+        index=np.sum(ace)/ratio**2
+
+        new[i,j]=index
+
+
+#print new.shape
+
+hdu=pyfits.PrimaryHDU(new)
+hdu.writeto('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/test.fits')

### 2015-11-07 papers/B1555_EdgeOn/B1555_letter.tex
A few edit to text

@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-In IR imaging there is no sign of bulge, we then interpret the mass in ExpDisc component as the baryonic mass from lens galaxy.The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+{\bf In the IR imaging there is no sign of bulge; a formalwe then interpret the mass in ExpDisc component as the baryonic mass from lens galaxy.} The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
 We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.

### 2015-11-07 python/resample.py

@@ -2,26 +2,56 @@
 
 import pyfits
 import numpy as np
+from astropy.convolution import convolve
 
 ratio=5 # rescale ratio between pixel sizes
+root='/Users/jwhsueh/Documents/SHARP_jw/models/' # root path for fits files
+system='B0712' # name of system
+file='B0712_nirc2_n_Kp_6x6.fits'
+kfile='nirc2nic_GaussKernel.fits' # kernel is for original image
 
-ori=pyfits.open('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/B1555_nirc2_4x4.fits')
-img=ori[0].data
+ori=pyfits.open(root+system+'/'+file)
+orimg=ori[0].data
 
-size=img.shape[0]
 
-new=np.zeros((size/ratio,size/ratio))
-ace=np.zeros((ratio,ratio))
+def resamp(img):
+    #ori=pyfits.open('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/B1555_nirc2_4x4.fits')
+    #ori=pyfits.open(root+system+'/'+file)
+    #img=ori[0].data
 
-for i in range(size/ratio):
-    for j in range(size/ratio):
-        ace=img[ratio*i:(ratio*i+ratio),ratio*j:(ratio*j+ratio)]
-        index=np.sum(ace)/ratio**2
+    size=img.shape[0]
 
-        new[i,j]=index
+    new=np.zeros((size/ratio,size/ratio))
+    ace=np.zeros((ratio,ratio))
+
+    for i in range(size/ratio):
+        for j in range(size/ratio):
+            ace=img[ratio*i:(ratio*i+ratio),ratio*j:(ratio*j+ratio)]
+            index=np.sum(ace)/ratio**2
+
+            new[i,j]=index
+
+    return new
 
 
 #print new.shape
 
+    #hdu=pyfits.PrimaryHDU(new)
+    #hdu.writeto('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/test.fits')
+
+def conv(img):
+    kernel_file=pyfits.open(root+kfile)
+    kernel=kernel_file[0].data
+
+    new=convolve(img,kernel)
+
+    return new
+
+
+new=conv(orimg)
+new=resamp(new)
+
 hdu=pyfits.PrimaryHDU(new)
-hdu.writeto('/Users/jwhsueh/Documents/SHARP_jw/models/B1555/test.fits')
+hdu.writeto(root+system+'/test.fits')
+
+

### 2015-11-11 papers/B1555_EdgeOn/Resubmission/referee_response.txt
Started referee response

We thank the referee for his/her comments about the paper.  We have
responded to the comments below, and modified the text accordingly.
Overall, we have toned down our somewhat sweeping claims.

> Comments to the Author: This paper presents an interesting new
> observational result for the strong gravitational lens B1555+375,
> along with an abundance of poorly supported conjecture.  The
> observations of B1555+375 should be published, but the authors should
> either remove their speculations, or (more usefully) provide evidence
> in support of them.
> 
> CLASS B1555+375 is one of the "poster child" gravitational lens
> systems.  It is famous for its prototypical flux ratio anomaly, which
> has been cited as evidence for dark matter substructure in this
> system.  The new result presented in this paper is near-infrared
> imaging with Keck and HST which reveals a linear structure in the lens
> galaxy emission consistent with an edge-on thin disk.  Most
> intriguingly, this structure passes near the anomalous images, and
> could explain the observed flux anomaly without the need to invoke
> dark matter substructure.  This would be an important result, and
> hence should be published.
> 
> However, the discussion in the paper lacks important quantitative
> details.  For example, the paper does not describe the total
> luminosity of the disky component, compared to the spheroidal
> component of the lens galaxy.  This is important because the lens
> model discussed in the paper requires the disk component to comprise ~
> 10% of the mass within the Einstein radius, and it is unclear if that
> large mass fraction is consistent with the photometry shown in Figure
> 1.
>

RESPONSE: The referee is correct to point out that we did not quantify
the bulge/disk ratio in the lensing galaxy.  We have performed a
bulge+disk fit to the lens-galaxy surface brightness distribution.
Our fit returns a bulge component that is consistent with zero
emission.  [DO WE WANT TO MAKE M/L RATIO CALCULATIONS??].  We have
added text to the paper describing this result.  We note that the two
components in our lens model can be thought of as the edge-on disk and
the dark-matter halo of the lensing galaxy.

> More importantly, the large disk component in the lens model produces
> a significant distortion to the usually ellipsoidal critical curves
> found in strong lenses, as shown in Fig 3.  It has long been known
> that such departures from ellipsoidal density distributions are
> tightly constrained by extended emission from the source galaxies,
> e.g. arcs and Einstein rings that span a large range of azimuthal
> angle.  The imaging shown in Fig 2 exhibits faint extended arclets
> from the source galaxy that could constrain disky components in the
> lens mass distribution, but the lens modeling in the paper neglects to
> fit the extended emission, and instead only models the positions and
> fluxes of the pointlike radio quasar.  The signal-to-noise of the
> extended emission may be too low to provide meaningful constraints,
> but given that the authors have this data in hand, and given that the
> authors have considerable experience modeling this type of extended
> emission in lens systems, they should attempt to fit the observed
> arclets to see if a 10% mass fraction in an off-center thin disk is
> consistent with the observed arclets.

RESPONSE: The referee is correct in pointing out that the modelling of
the extended images would provide tighter constraints on the proposed
model. Unfortunately, in the case of B1555 IR imaging the disk is
responsible for a significant level of dust extinction that leave
images D and B unobservable, and even the arc near image A strongly
affected. We have, however, tried modelling this dataset by only
focusing on image C which is not affected by dust, and the results are
consistent with those found by modelling the point images positions
and fluxes. For the VLBI extended images the poor quality of the data
prevented us from modelling this dataset in a reliable manner.  
[ADD TEXT TO PAPER??]

> 
> The final section of the paper speculates that massive disc components
> may be prevalent in strong lenses, and that such discs may bias
> inferences on the abundance of dark matter substructure using strong
> lensing.  The authors fail to provide evidence supporting these
> speculations, even though they have the data to do so.  As noted
> above, strong lenses with extended source emission (arcs and rings)
> tightly constrain the presence of thin components in lens galaxies.
> In some cases with Einstein rings, disc components are excluded from
> contributing more than percent-level fractions of the mass density.
> It would therefore be highly surprising for a substantial fraction of
> strong lenses to contain hidden, massive edge-on discs that could
> distort the lensing so significantly, as the paper intimates.
> 
> Rather than wildly speculating, the authors could easily check the
> plausibility of this claim.  A number of the authors were members of
> the SLACS collaboration, whose dataset contains many lenses with
> extended emission from the source galaxies.  These systems are the
> obvious way to quantify the fraction of lens systems containing
> massive edge-on discs, since the arcs in many SLACS lenses span a wide
> range of azimuthal angle.  Once they have quantified the abundance of
> massive edge-on discs, the authors should then perform Monte Carlo
> calculations of quasar lenses to calculate the statistics of flux
> ratio anomalies produced by these discs.  Only then can they state
> whether hidden edge-on massive discs can bias observational
> measurements of dark matter substructure with gravitational lens flux
> ratios.

RESPONSE: In the SHARP sample, we find that 5 out of the 25 systems
that we imaged have clear disk components, indicating that this is not
a completely unexpected phenomenon.  While we agree with the referee
that it is important to quantify how common disks are in lensing
galaxies, we do not feel that the SLACS sample provides the
appropriate comparison.  This is because a significant portion of the
SHARP systems come from source-selected samples, such as CLASS, that
are agnostic about the nature of the lensing galaxy.  In contrast,
SLACS lenses were selected to be systems where the lensing galaxy was
known a priori to be a massive elliptical galaxy.  We would therefore
expect a lower incidence of disky systems in SLACS than in the SHARP
sample.  We agree completely with the referee that doing a
quantification of the statistics of massive disks and their effects on
flux-ratio anomalies is an extremely important task and, in fact, this
is one of the future projects that we are planning.  However, we feel
that such an extensive analysis is beyond the scope of this letter.
As such, we have modified the text to focus more on this individual
lens system and put more caveats on the possible generalization of the
results.

### 2015-11-12 papers/B1555_EdgeOn/B1555_letter.tex
Incorporate Matt's text into conclusions of paper

--- 2015-11-04 papers/B1555_EdgeOn/B1555_letter.tex
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-In IR imaging there is no sign of bulge, we then interpret the mass in ExpDisc component as the baryonic mass from lens galaxy.The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+{\bf In the IR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+We therefore interpret the mass in the ExpDisc component as the baryonic mass of lens galaxy.} The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
 We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
@@
 Again, more complex mass models need the full extent of the gravitational arc for constraints.
-While the gravitational arc in IR band suffers severe dust extinction, the compact lensed images from future high resolution radio imaging will be able to confirm this.
+{\bf The extinction in the AO imaging is so severe that components B and D are not visible, and the arc that connects A and B appears to be truncated.
+The low signal-to-noise ratio and the strong extinction prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.
+Future high resolution radio imaging is needed in order to place stronger constraints on the mass model.}
 
@@
 
-Here, we find evidence for an edge-on disc in the flux-ratio anomalous gravitational lens B1555+375 that can also account for the required perturbation in the mass model.
+{\bf Here, we find evidence for an edge-on disc in the flux-ratio
+anomalous gravitational lens B1555+375 that can also account for
+the required perturbation in the mass model.
+Such high-order deviations from a smooth mass distribution have already been suggested previously (Evans \& Witt 2003; Congdon \& Keeton 2005), but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly.
+However, it is important to realise that by including observationally-motivated perturbations to a `smooth' mass distribution, like luminous dwarf companions or edge-on discs, in the mass models,
+we are still limited in our interpretation since we must assume that
+the anomalies are due exclusively to these additional components.
+For B1555+375, it may be possible to independently constrain the
+mass of the disc through kinematic measurements (most likely from
+mm-wavelength resolved emission line observations), which would
+test whether the disc makes a sufficient contribution to the mass
+model (e.g. as in the case of B1933+503; Suyu et al. 2012). Also, as
+we have shown here, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the
+edge-on disc.
+Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}
+
+{\bf Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with
+the limited information provided by the position of compact lensed
+images, can lead to a misinterpretation of the origin of flux-ratio anomalies.
+Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account (e.g., Xu et al.~2015).
+This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can be measured using narrow lines (e.g., Nierenberg et al.~2014).
+Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
+Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; Evans \& Witt 2003), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+
+%Here, we find evidence for an edge-on disc in the flux-ratio anomalous gravitational lens B1555+375 that can also account for the required perturbation in the mass model.
 Such high-order deviations from a smooth mass distribution have already been suggested \citep{evans03,congdon05}, but this is the first time that a disc has been observed and modelled to account for a flux-ratio anomaly.
@@
 
-Our analysis for B1555+375 shows that in order to derive a precise quantification of the substructure population and other properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
+%Our analysis for B1555+375 shows that in order to derive a precise quantification of the substructure population and other properties from strongly lensed flux-ratio anomalies, it is crucial to have a careful estimation of non-substructure effects, such as galaxy discs and nearby massive satellites.
 %We find that in B1555+375, a lack of knowledge about the lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to improper lens models and a misinterpretation of the origin of flux-ratio anomalies.
-While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
+%While upcoming large-scale surveys with the Dark Energy Survey, Kilo-Degree Sky-VIKING, Square Kilometre Array, {\it Euclid}, and Large Synoptic Survey Telescope, are expected to deliver new large samples of gravitationally lensed quasars, in the near future the discovery of new systems using narrow-line quasar emission \citep{N14} will provide a new and invaluable statistical perspective on the current constraints based on flux-ratio anomalies.
 We stress, therefore, that one should be very careful when interpreting the nature of flux-ratio anomalies, as prior simple assumptions on the lens mass distribution may a significant source of bias.

### 2015-11-12 papers/B1555_EdgeOn/B1555_letter.tex
update reference link in text

@@
 $\Delta$Dec	& $-0.199 \pm 0.005$		& $-0.206 \pm 0.006$ \\
-$b$ 			& $0.21 \pm 0.01$  		& $0.11 \pm 0.01$  \\
+$b$ 			& $0.21 \pm 0.01$  		& ...  \\
+$\kappa_0$ & ... &$0.11 \pm 0.01$\\
 $e$	  		& $0.31 \pm 0.01$			& $0.87 \pm 0.01$ \\
@@
 the required perturbation in the mass model.
-Such high-order deviations from a smooth mass distribution have already been suggested previously (Evans \& Witt 2003; Congdon \& Keeton 2005), but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly.
+Such high-order deviations from a smooth mass distribution have already been suggested previously \citep{evans03, congdon05}, but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly.
 However, it is important to realise that by including observationally-motivated perturbations to a `smooth' mass distribution, like luminous dwarf companions or edge-on discs, in the mass models,
@@
 test whether the disc makes a sufficient contribution to the mass
-model (e.g. as in the case of B1933+503; Suyu et al. 2012). Also, as
+model (e.g. as in the case of B1933+503; \citet{suyu12}). Also, as
 we have shown here, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the
@@
 
-{\bf Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with
-the limited information provided by the position of compact lensed
-images, can lead to a misinterpretation of the origin of flux-ratio anomalies.
-Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account (e.g., Xu et al.~2015).
-This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can be measured using narrow lines (e.g., Nierenberg et al.~2014).
+\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies.
+Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
+ (e.g., \citet{Xu15}).
+This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
+  be measured using narrow lines (e.g., \citet{N14}).
 Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; Evans \& Witt 2003), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
 

### 2015-11-16 papers/B1555_EdgeOn/Resubmission/referee_response.txt
Small update to referee response

@@
 Our fit returns a bulge component that is consistent with zero
-emission.  [DO WE WANT TO MAKE M/L RATIO CALCULATIONS??].  We have
-added text to the paper describing this result.  We note that the two
-components in our lens model can be thought of as the edge-on disk and
-the dark-matter halo of the lensing galaxy.
+emission.  We have added text to the paper describing this result.  We
+note that the two components in our lens model can be thought of as
+the edge-on disk and the dark-matter halo of the lensing galaxy.
 
@@
 the extended images would provide tighter constraints on the proposed
-model. Unfortunately, in the case of B1555 IR imaging the disk is
-responsible for a significant level of dust extinction that leave
-images D and B unobservable, and even the arc near image A strongly
-affected. We have, however, tried modelling this dataset by only
-focusing on image C which is not affected by dust, and the results are
-consistent with those found by modelling the point images positions
-and fluxes. For the VLBI extended images the poor quality of the data
-prevented us from modelling this dataset in a reliable manner.  
-[ADD TEXT TO PAPER??]
+model. As a matter of fact, we had hoped to do exactly the analysis
+that the referee has suggested.  Unfortunately, in the case of B1555
+IR imaging the SNR of the lensed extended emission is low.  More
+importantly, the disk is responsible for a significant level of dust
+extinction that leave images D and B unobservable, and even the arc
+near image A strongly affected. We have, however, tried modelling this
+dataset by only focusing on image C which is not affected by dust, and
+the results are consistent with those found by modelling the point
+images positions and fluxes. For the VLBI extended images the poor
+quality of the data prevented us from modelling this dataset in a
+reliable manner.  We have added text to the manuscript explaining
+this.
 

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
Small updates to paper text and referee response

@@
 We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
-Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model will likely overestimate the substructure mass fraction in massive lensing galaxies.
+Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model {\bf may} overestimate the substructure mass fraction in massive lensing galaxies.
 \end{abstract}
@@
 Note that the redshifts of both the lens galaxy and the lensed source are unknown for B1555+375, so we assume redshifts of $z_l = 1$ and $z_s = 1.5$, respectively, due to their red colours \citep{Marlow99}.
-This assumption has no effect on the derived magnifications or flux-ratios of our analysis.
+This assumption has no effect on the derived magnifications or flux ratios of our analysis.
 
@@
 As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
-Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux-ratios in B1555+375 (see Table~\ref{tab:results}).
+Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux ratios in B1555+375 (see Table~\ref{tab:results}).
 %; reduced $\chi^2 =97.3$
@@
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
-We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux-ratios when compared to the results for the SIE-only model.
+We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model.
 % with a reduced $\chi^2 = 2.7$
-The positions are all in agreement, and the flux-ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
+The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-{\bf In the IR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the mass in the ExpDisc component as the baryonic mass of lens galaxy.} The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
-We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
+{\bf In the NIR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+We therefore interpret the mass in the ExpDisc component as the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
@@
 {\bf Here, we find evidence for an edge-on disc in the flux-ratio
-anomalous gravitational lens B1555+375 that can also account for
+anomaly gravitational lens B1555+375 that can also account for
 the required perturbation in the mass model.

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
Another small update to paper text

@@
 However, before using these flux-ratio anomalies to test galaxy formation models, it is imperative to ascertain that the given anomalies are indeed due to the presence of dark matter substructure and not due to some other component of the lensing galaxy halo or to propagation effects.
-Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly, but where the lensing galaxy is also revealed in high resolution infrared imaging with the W.
-M.
-Keck-II Telescope and the {\it Hubble Space Telescope} to have a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
+Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly.
+{\bf Our high-resolution near-infrared Keck~II adaptive optics imaging and archival {\it Hubble Space Telescope} data reveal the lensing galaxy in this system} to have  a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
 We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
fix typo in the text

@@
 The reduced images are also shown in Fig.~\ref{fig:multiband}.
-The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image
+The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image.
 
@@
 Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyway; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
 

### 2015-11-17 papers/B1555_EdgeOn/Resubmission/referee_response.txt
Small updates to paper text and referee response
More small changes.

@@
 the results are consistent with those found by modelling the point
-images positions and fluxes. For the VLBI extended images the poor
-quality of the data prevented us from modelling this dataset in a
-reliable manner.  We have added text to the manuscript explaining
+images positions and fluxes.  Similarly we hoped to use the VLBI
+images for the extended source modeling, but as mentioned in the text
+the poor quality of the data prevented us from modelling this dataset
+in a reliable manner.  We have added text to the manuscript explaining
 this.
@@
 SHARP systems come from source-selected samples, such as CLASS, that
-are agnostic about the nature of the lensing galaxy.  In contrast,
-SLACS lenses were selected to be systems where the lensing galaxy was
-known a priori to be a massive elliptical galaxy.  We would therefore
-expect a lower incidence of disky systems in SLACS than in the SHARP
-sample.  We agree completely with the referee that doing a
-quantification of the statistics of massive disks and their effects on
-flux-ratio anomalies is an extremely important task and, in fact, this
-is one of the future projects that we are planning.  However, we feel
-that such an extensive analysis is beyond the scope of this letter.
-As such, we have modified the text to focus more on this individual
-lens system and put more caveats on the possible generalization of the
-results.
+are agnostic about the nature of the lensing galaxy.  In fact, CLASS
+contains at least one other system, B1600+434 (albeit a double), where
+the lensing galaxy appears to be an edge-on disk with a very low
+bulge/disk ratio.  In contrast, SLACS lenses were selected to be
+systems where the lensing galaxy was known a priori to be a massive
+elliptical galaxy.  We would therefore expect a lower incidence of
+disky systems in SLACS than in the SHARP sample.  We agree completely
+with the referee that doing a quantification of the statistics of
+massive disks and their effects on flux-ratio anomalies is an
+extremely important task and, in fact, this is one of the future
+projects that we are planning.  However, we feel that such an
+extensive analysis is beyond the scope of this letter.  As such, we
+have modified the text to focus more on this individual lens system
+and put more caveats on the possible generalization of the results.

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
More small changes.

--- 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
@@
 {\bf Here, we find evidence for an edge-on disc in the flux-ratio
-anomaly gravitational lens B1555+375 that can also account for
-the required perturbation in the mass model.
-Such high-order deviations from a smooth mass distribution have already been suggested previously \citep{evans03, congdon05}, but this is the first time that an observed disc has been explicitly modelled to account for a flux-ratio anomaly.
-However, it is important to realise that by including observationally-motivated perturbations to a `smooth' mass distribution, like luminous dwarf companions or edge-on discs, in the mass models,
-we are still limited in our interpretation since we must assume that
-the anomalies are due exclusively to these additional components.
-For B1555+375, it may be possible to independently constrain the
-mass of the disc through kinematic measurements (most likely from
-mm-wavelength resolved emission line observations), which would
-test whether the disc makes a sufficient contribution to the mass
-model (e.g. as in the case of B1933+503; \citet{suyu12}). Also, as
-we have shown here, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the
-edge-on disc.
-Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}
+  anomaly gravitational lens B1555+375 that can also account for the
+  required perturbation in the mass model. Such high-order deviations
+  from a smooth mass distribution have already been suggested
+  previously \citep{evans03, congdon05}, but this is the first time
+  that an observed disc has been explicitly modelled to account for a
+  flux-ratio anomaly. However, it is important to realise that by
+  including observationally-motivated perturbations to a `smooth' mass
+  distribution, such as luminous dwarf companions or edge-on discs, in
+  the mass models, we are still limited in our interpretation since we
+  must assume that the anomalies are due exclusively to these
+  additional components.  For B1555+375, it may be possible to
+  independently constrain the mass of the disc through kinematic
+  measurements (most likely from mm-wavelength resolved emission line
+  observations), which would test whether the disc makes a sufficient
+  contribution to the mass model (e.g. as in the case of B1933+503;
+  \citet{suyu12}). Also, as we have shown here, B1555+375 shows
+  evidence for an extended $\sim$ 100 mas gravitational arc at radio
+  wavelengths that crosses the edge-on disc. Further high resolution
+  imaging with very long baseline interferometry will provide the
+  observational constraints required to fully test whether the disc is
+  sufficient to cause the anomaly.}
 
 \textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies.
-Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
+Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
  (e.g., \citet{Xu15}).
@@
 Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+Finally, we note that massive edge-on discs are \textit{not} observed in some [most??] flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
 
@@
 \section*{Acknowledgments}
+We thank the referee for comments that improved the paper.
 We are grateful to Dandan Xu for useful discussions.

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex

@@
 Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Finally, we note that massive edge-on discs are \textit{not} observed in some [most??] flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
 

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
make change according to Loen's comments

@@
 {\bf In the NIR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the mass in the ExpDisc component as the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+We therefore interpret the mass in the ExpDisc component as a good description of the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
@@
   flux-ratio anomaly. However, it is important to realise that by
-  including observationally-motivated perturbations to a `smooth' mass
+  including observationally-motivated additional components/modification[?] to a `smooth' mass
   distribution, such as luminous dwarf companions or edge-on discs, in
@@
   contribution to the mass model (e.g. as in the case of B1933+503;
-  \citet{suyu12}). Also, as we have shown here, B1555+375 shows
+  \citet{suyu12}). Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows
   evidence for an extended $\sim$ 100 mas gravitational arc at radio

### 2015-11-19 papers/B1555_EdgeOn/B1555_letter.tex
tex file change for Matt & Simona's comments

@@
 Also, any variation in the properties of the radio images that are due to propagation effects (e.g.
-interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for (e.g.
-\citealt{biggs03,M07,winn04}).
+interstellar scattering or free-free absorption) have a well understood frequency dependence that can be identified and accounted for \citep[e.g.][]{biggs03,M07,winn04}.
 This makes the flux-ratio anomalies of radio-loud lensed images a promising tool to detect and measure dark matter substructures in a large sample of distant galaxies \citep{Dalal2002}.
@@
 The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}.
-This method has given a measurement of the substructure mass fraction for a sample of 10 lensing galaxies that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
+This method has given a measurement of the substructure mass fraction for a sample of {\bf 11 lenses} that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
 The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is currently not clear.
@@
 There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from what appears to be an edge-on lensing galaxy, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q$ as $q=1-e$.
+These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from {\bf the lensing galaxy what appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q$ as $q=1-e$.
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
@@
 The source position adds two additional model parameters.
-We have not included a third component such as an external shear or an NFW halo because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
-Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
+{\bf We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
+An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.} Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
 
@@
 The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
-{\bf In the NIR imaging there is no sign of a bulge; a formal bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the mass in the ExpDisc component as a good description of the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+{\bf In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+We therefore interpret the convergence of the ExpDisc component as a good description of the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
@@
 {\bf The extinction in the AO imaging is so severe that components B and D are not visible, and the arc that connects A and B appears to be truncated.
-The low signal-to-noise ratio and the strong extinction prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.
+The low signal-to-noise ratio and the strong extinction in lens galaxy prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.
 Future high resolution radio imaging is needed in order to place stronger constraints on the mass model.}
@@
 
-{\bf Here, we find evidence for an edge-on disc in the flux-ratio
+\textbf{
+Here, we find evidence for an edge-on disc in the flux-ratio
   anomaly gravitational lens B1555+375 that can also account for the
@@
   must assume that the anomalies are due exclusively to these
-  additional components.  For B1555+375, it may be possible to
-  independently constrain the mass of the disc through kinematic
-  measurements (most likely from mm-wavelength resolved emission line
-  observations), which would test whether the disc makes a sufficient
-  contribution to the mass model (e.g. as in the case of B1933+503;
-  \citet{suyu12}). Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows
-  evidence for an extended $\sim$ 100 mas gravitational arc at radio
-  wavelengths that crosses the edge-on disc. Further high resolution
-  imaging with very long baseline interferometry will provide the
-  observational constraints required to fully test whether the disc is
-  sufficient to cause the anomaly.}
+  additional components.
+For B1555+375, it may be possible to independently constrain the mass of the disc 		through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which 	would test whether the disc makes a sufficient contribution to the mass model \citep[e.g.
+as in the case of 	B1933+503;][]{suyu12}.
+Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the edge-on disc.
+Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}
 
@@
 Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
- (e.g., \citet{Xu15}).
+\citep[e.g.][]{Xu15}.
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
-  be measured using narrow lines (e.g., \citet{N14}).
-Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyway; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
+  be measured using narrow lines \citep[e.g.][]{N14}.
+Finally, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.}
+  %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.
 

### 2015-12-03 papers/B1555_EdgeOn/B1555_letter.tex
Shifted order of a couple of paragraphs in the last section

@@
   anomaly gravitational lens B1555+375 that can also account for the
-  required perturbation in the mass model. Such high-order deviations
+  required perturbation in the mass model.
+Moreover, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
+Such high-order deviations
   from a smooth mass distribution have already been suggested
@@
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
-  be measured using narrow lines \citep[e.g.][]{N14}.
-Finally, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.}
+  be measured using narrow lines \citep[e.g.][]{N14}.}
   %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.

### 2015-12-06 papers/B1555_EdgeOn/B1555_letter.tex
Updates to the paper text
Still need to modify the figure

@@
 There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from {\bf the lensing galaxy what appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an ellipticity $e \sim 0.8$, where $e$ is defined in terms of the axis ratio $q$ as $q=1-e$.
+These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from {\bf the lensing galaxy that appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an {\bf axis ratio $q \sim 0.2$}.
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
@@
 
-We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in size.
+We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in {\bf length}.
 Image C is still compact on mas-scales, whereas image D is only marginally detected ($\sim6~\sigma$).
@@
 
-The flux-ratio anomaly and relative sizes of the images at radio-wavelengths implies that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line of sight to the lensed images \citep{Dalal2002,Xu12,Xu15}.
+The flux-ratio anomaly and relative sizes of the images at radio-wavelengths imply that there must be some form of perturbation to the gravitational lens mass model, which has thus far been attributed to dark matter substructure within the lensing galaxy or along the line of sight to the lensed images \citep{Dalal2002,Xu12,Xu15}.
 However, our high-resolution near infrared imaging suggests the intriguing possibility that the mass perturbation could be due to an edge-on disc component within the lens.
@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$), and scale length ($R_s$).
+The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
 The source position adds two additional model parameters.
-{\bf We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
-An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.} Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
+{\bf We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.}
+%An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.} 
+Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
 
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the ExpDisc component makes up about 10 per cent of the total mass within the Einstein radius (1.7~kpc for a lens redshift of $z_l = 1$), which is not unreasonable.
-{\bf In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the convergence of the ExpDisc component as a good description of the baryonic mass of lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+The model requires that the ExpDisc component makes up about 10 per cent of the total {\bf projected} mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+{\bf In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
+In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+We therefore interpret the convergence of the ExpDisc component as a good description of the baryonic mass of the lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
@@
 
-\textbf{
-Here, we find evidence for an edge-on disc in the flux-ratio
+\textbf{ Here, we find evidence for an edge-on disc in the flux-ratio
   anomaly gravitational lens B1555+375 that can also account for the
-  required perturbation in the mass model.
-Moreover, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.
-Such high-order deviations
-  from a smooth mass distribution have already been suggested
-  previously \citep{evans03, congdon05}, but this is the first time
-  that an observed disc has been explicitly modelled to account for a
-  flux-ratio anomaly. However, it is important to realise that by
-  including observationally-motivated additional components/modification[?] to a `smooth' mass
-  distribution, such as luminous dwarf companions or edge-on discs, in
-  the mass models, we are still limited in our interpretation since we
-  must assume that the anomalies are due exclusively to these
-  additional components.
-For B1555+375, it may be possible to independently constrain the mass of the disc through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which 	would test whether the disc makes a sufficient contribution to the mass model \citep[e.g.
-as in the case of 	B1933+503;][]{suyu12}.
-Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the edge-on disc.
-Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}
+  required perturbation in the mass model.  Moreover, near-infrared AO
+  imaging of other lenses in the SHARP sample shows that B1555+375 is
+  not the only system having a significant disc component detection in
+  the lensing galaxy; these gravitational lenses will be investigated
+  in future work, but the images alone suggest that other systems may
+  have similar links between flux-ratio anomalies and disc
+  components. Such high-order deviations from a smooth mass
+  distribution have already been suggested previously \citep{evans03,
+    congdon05}, but this is the first time that an observed disc has
+  been explicitly modelled to account for a flux-ratio
+  anomaly. However, it is important to realise that by including
+  observationally-motivated modifications to a
+  `smooth' mass distribution, such as luminous dwarf companions or
+  edge-on discs, in the mass models, we are still limited in our
+  interpretation if we can not determine how much of the anomalies are
+  due to these components. For our current analysis of B1555+375, we have
+  shown that the entire anomaly could be caused by the edge-on disc.  However,
+  it may be
+  possible to independently constrain the mass of the disc through
+  kinematic measurements (most likely from mm-wavelength resolved
+  emission line observations), which would test whether the disc actually makes
+  a sufficient contribution to the mass model \citep[e.g. as in the
+    case of B1933+503;][]{suyu12}. Also, in the blue contours of
+  Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended
+  $\sim$ 100 mas gravitational arc at radio wavelengths that crosses
+  the edge-on disc. Further high resolution imaging with very long
+  baseline interferometry will provide the observational constraints
+  required to fully test whether the disc is sufficient to cause the
+  anomaly.}
 
-\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies.
+\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
 Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
 \citep[e.g.][]{Xu15}.
+The SWELLS survey, for example, presents a sample of 16 edge-on disks from SDSS \citep{swells1}.
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can

### 2015-12-06 python/plot_fns_b1555.py

@@ -15,6 +15,24 @@ from matplotlib import pyplot as plt
 import plot_lensmod as pltlm
 
 #---------------------------------------------------------------------------
+def model_plot(sx, sy, cx, cy):
+    plt.plot(sx,sy,'o',ms=10,mec='k',mfc='r',label='source')
+    plt.plot(cx,cy,'^',ms=10,label='lenses',mfc='k')
+
+#---------------------------------------------------------------------------
+
+def img_pos(obsfile, xmod, ymod, showylab=True):
+
+    x0,y0 = n.loadtxt(obsfile,unpack=True,usecols=(0,1))
+
+    plt.plot(x0,y0,'b+',ms=10,label='observed')
+    plt.plot(xmod,ymod,'o',ms=10,mec='r',mfc='none',label='predicted')
+    
+    plt.xlabel(r'$\Delta  \alpha $ (arcsec)')
+    if showylab:
+        plt.ylabel('$\Delta \delta$ (arcsec)')
+
+#---------------------------------------------------------------------------
 
 def radio_overlay_b1555():
     """
@@ -83,9 +101,6 @@ def gravlens_b1555():
     critfile = '../models/B1555/gravlens_code/B1555_expdisk_try5_1.crit'
     obsfile  = '../models/B1555/B1555_obsdat.txt'
 
-    """ Get observed image postions """
-    x0,y0 = n.loadtxt(obsfile,unpack=True,usecols=(0,1))
-
     """ Set model-predicted positions """
     xmod = [-0.4117 , -0.1629 ,-0.00,-0.0727]
     ymod = [-0.0281,-0.3653,-0.00 ,0.0477]
@@ -94,13 +109,24 @@ def gravlens_b1555():
     cx = [ -1.818271e-01, -1.471605e-01] # x position
     cy = [ -1.987580e-01, -2.056755e-01] # y position
 
+    """ Set the source positions """
+    sx,sy= -1.952576e-01, -1.493771e-01
+
     """ Do the plotting """
     pltlm.plot_critcaust(critfile,'crit')
     pltlm.plot_critcaust(critfile,'caust',sls=':')
-    model_plot()
-    img_pos()
+    model_plot(sx,sy,cx,cy)
+    img_pos(obsfile,xmod,ymod)
 
     plt.xlim(0.4,-0.8)
     plt.ylim(-0.8,0.4)
     plt.legend(loc=1)
+    plt.axes().set_aspect('equal')
 
+#---------------------------------------------------------------------------
+
[…]

### 2015-12-06 papers/B1555_EdgeOn/B1555_letter.tex
Updates to the paper text and plotting code

@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e$), position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 %An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.} 
-Significantly deeper observations at a higher bandwidth with current very long baseline interferometric arrays can test more complex models in the future by imaging the extended gravitational arc and more significantly detecting image D.
+{\bf 
+More sophisticated mass models require additional
+constraints, such as those from the lensed extended emission in either
+the NIR or radio imaging.  While we have successfully used the former
+approach in the past \citep[e.g.][]{V12}, for B1555+375 the extinction
+in the AO imaging is so severe that components B and D are not
+visible, and the arc that connects A and B appears to be truncated.
+The low signal-to-noise ratio in the ring away from the lensed AGN and
+the strong extinction in lens galaxy prevent us from using this
+approach.  What are, thus, needed are significantly deeper
+observations at a higher bandwidth with very long baseline
+interferometric arrays, which can test more complex models in the
+future by imaging the extended gravitational arc and more
+significantly detecting image D. }
 
@@
 In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the convergence of the ExpDisc component as a good description of the baryonic mass of the lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
-Again, more complex mass models need the full extent of the gravitational arc for constraints.
-{\bf The extinction in the AO imaging is so severe that components B and D are not visible, and the arc that connects A and B appears to be truncated.
-The low signal-to-noise ratio and the strong extinction in lens galaxy prevent us from using modeling techniques that incorporate the extended NIR emission \citep[e.g.][]{V12}.
-Future high resolution radio imaging is needed in order to place stronger constraints on the mass model.}
+Again, more complex mass models require {\bf the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.}
 
@@
 
-\textbf{ Here, we find evidence for an edge-on disc in the flux-ratio
-  anomaly gravitational lens B1555+375 that can also account for the
-  required perturbation in the mass model.  Moreover, near-infrared AO
-  imaging of other lenses in the SHARP sample shows that B1555+375 is
-  not the only system having a significant disc component detection in
-  the lensing galaxy; these gravitational lenses will be investigated
-  in future work, but the images alone suggest that other systems may
-  have similar links between flux-ratio anomalies and disc
-  components. Such high-order deviations from a smooth mass
-  distribution have already been suggested previously \citep{evans03,
-    congdon05}, but this is the first time that an observed disc has
-  been explicitly modelled to account for a flux-ratio
-  anomaly. However, it is important to realise that by including
-  observationally-motivated modifications to a
+\textbf{ 
+Here, we find evidence for an edge-on disc in the flux-ratio anomaly
+gravitational lens B1555+375 that can also account for the required
+perturbation in the mass model.  Moreover, near-infrared AO imaging of
+other lenses in the SHARP sample shows that B1555+375 is not the only
+system having a significant disc component detection in the lensing
+galaxy; these gravitational lenses will be investigated in future
+work, but the images alone suggest that other systems may have similar
+links between flux-ratio anomalies and disc components. Such
+high-order deviations from a smooth mass distribution have already
+been suggested previously \citep{evans03, congdon05}, but this is the
+first time that an observed disc has been explicitly modelled to
+account for a flux-ratio anomaly. However, it is important to realise
+that by including observationally-motivated modifications to a
 `smooth' mass distribution, such as luminous dwarf companions or
@@
 interpretation if we can not determine how much of the anomalies are
-  due to these components. For our current analysis of B1555+375, we have
-  shown that the entire anomaly could be caused by the edge-on disc.  However,
-  it may be
-  possible to independently constrain the mass of the disc through
-  kinematic measurements (most likely from mm-wavelength resolved
-  emission line observations), which would test whether the disc actually makes
-  a sufficient contribution to the mass model \citep[e.g. as in the
-    case of B1933+503;][]{suyu12}. Also, in the blue contours of
-  Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended
-  $\sim$ 100 mas gravitational arc at radio wavelengths that crosses
-  the edge-on disc. Further high resolution imaging with very long
-  baseline interferometry will provide the observational constraints
-  required to fully test whether the disc is sufficient to cause the
-  anomaly.}
+due to these components. For our current analysis of B1555+375, we
+have shown that the entire anomaly could be caused by the edge-on
+disc.  However, it may be possible to independently constrain the mass
+of the disc through kinematic measurements (most likely from
+mm-wavelength resolved emission line observations), which would test
+whether the disc actually makes a sufficient contribution to the mass
+model \citep[e.g. as in the case of B1933+503;][]{suyu12}. Also, in
+the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence
+for an extended $\sim$ 100 mas gravitational arc at radio wavelengths
+that crosses the edge-on disc. Further high resolution imaging with
+very long baseline interferometry will provide the observational
+constraints required to fully test whether the disc is sufficient to
+cause the anomaly.}
 
@@
 Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
-\citep[e.g.][]{Xu15}.
-The SWELLS survey, for example, presents a sample of 16 edge-on disks from SDSS \citep{swells1}.
+\citep[e.g.][]{Xu15}. A number of systems with significant disc components are
+already known.
+These include, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}.
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can

### 2015-12-06 python/plot_fns_b1555.py

@@ -15,23 +15,20 @@ from matplotlib import pyplot as plt
 import plot_lensmod as pltlm
 
 #---------------------------------------------------------------------------
+
 def model_plot(sx, sy, cx, cy):
     plt.plot(sx,sy,'o',ms=10,mec='k',mfc='r',label='source')
     plt.plot(cx,cy,'^',ms=10,label='lenses',mfc='k')
 
 #---------------------------------------------------------------------------
 
-def img_pos(obsfile, xmod, ymod, showylab=True):
+def img_pos(obsfile, xmod, ymod):
 
     x0,y0 = n.loadtxt(obsfile,unpack=True,usecols=(0,1))
 
     plt.plot(x0,y0,'b+',ms=10,label='observed')
     plt.plot(xmod,ymod,'o',ms=10,mec='r',mfc='none',label='predicted')
     
-    plt.xlabel(r'$\Delta  \alpha $ (arcsec)')
-    if showylab:
-        plt.ylabel('$\Delta \delta$ (arcsec)')
-
 #---------------------------------------------------------------------------
 
 def radio_overlay_b1555():
@@ -40,9 +37,9 @@ def radio_overlay_b1555():
     """
 
     """ Set the input file names """
-    aoim      = 'B1555_nirc2_n_Kp_6x6.fits'
-    merlin_im = '1555_merlin_5ghz.fits'
-    vlbi_im   = 'B1555_vlbi_fix_astrom.fits'
+    aoim      = '../data/B1555_nirc2_n_Kp_6x6.fits'
+    merlin_im = '../data/1555_merlin_5ghz.fits'
+    vlbi_im   = '../data/B1555_vlbi_fix_astrom.fits'
 
     """ Hardwire rms levels if needed """
     rms_vlbi = 0.0001
@@ -50,7 +47,7 @@ def radio_overlay_b1555():
     """ Set the image center, origin location, and size """
     racent  = 239.29968
     deccent = 37.359921
-    zeropos = (0.2236,0.2174)
+    zeropos = (0.2276,0.2194)
     imsize  = 1.2       # Value in arcsec
 
     """ Make the overlay plot """
@@ -88,13 +85,17 @@ def radio_overlay_b1555():
 
 #---------------------------------------------------------------------------
 
-def gravlens_b1555():
+def gravlens_b1555(ax=None, showylab=True):
     """
     Plots the gravlens model.  This includes the following information:
        observed image positions
[…]

### 2015-12-07 papers/B1555_EdgeOn/B1555_letter.tex
Updated paper, with temporary version of new figure

@@
 
-A common feature of dark-matter only simulations of structure formation is the presence of thousands of sub-haloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
+A common feature of dark-matter only simulations of structure formation is the presence of thousands of subhaloes that are associated with larger mass haloes \citep[e.g.][]{Springel08}.
 However, observations of the Local Group show many fewer satellite galaxies than are predicted by the simulations, even when taking into account the latest discoveries of new dwarf galaxies \citep{DES15,Kop15} and completeness corrections arising from the limited sky coverage imposed by the Galactic Plane.
@@
 In order to understand this discrepancy, it is imperative to build up a large sample of satellites/subhaloes in galaxies outside the Local Group.
-However, this process is challenging due to the optical/infrared faintness of the satellite galaxies.
-Furthermore, lower-mass satellites may not be able to retain the gas needed for ongoing star formation \citep[e.g.][]{P11}, rendering them effectively dark.
+However, this process is challenging due to the
+%optical/infrared 
+faintness of the satellite galaxies.  In fact, lower-mass satellites may not be able to retain the gas needed for ongoing star formation \citep[e.g.][]{P11}, rendering them effectively dark.
 
@@
 Keck-II Telescope on 2012 May 16 (PI: Fassnacht).
-The AO system was used, with the corrections derived from the laser guide star and a $R=14.4$-mag tip-tilt star that was located $\sim45$~arcsec from the lens.
+The AO system was used, with the corrections derived from the laser guide star and a $R=14.4$-mag tip-tilt star located $\sim45$~arcsec from the lens.
 The narrow camera mode was used, giving a field of view of $\sim10$~arcsec on a side and a pixel scale of 10~mas.
-Six dithered 300~s exposures were obtained in the $K^{\prime}$-band filter.
+Six dithered 300~s exposures were obtained in the $K^{\prime}$ filter.
 The data were reduced with the standard SHARP pipeline, which is a python-based package that is a refinement of the process described by \citet{Auger_EELS1}.
-A cutout of the final reduced image is shown in Fig.~\ref{fig:multiband} and also in Fig.~\ref{fig:merlin}, where the contours from 5-GHz Multi-Element Radio Link Interferometer Network (MERLIN) imaging by \citet{Marlow99} and 1.66-GHz VLBA imaging (see below) are overlaid.
+A cutout of the final reduced image is shown in Fig.~\ref{fig:multiband} and also in Fig.~\ref{fig:3panel}a, where the contours from 5-GHz Multi-Element Radio Link Interferometer Network (MERLIN) imaging by \citet{Marlow99} and 1.66-GHz VLBA imaging (see below) are overlaid.
 
@@
 
-There are several notable features in the high-resolution AO and {\it HST} data.
-These include the nearly complete lack of emission associated with lensed images B and D, as can be seen by comparing the radio contours to the $K^\prime$-band emission  (Fig.~\ref{fig:merlin}), and the faint, but clearly visible emission from {\bf the lensing galaxy that appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an {\bf axis ratio $q \sim 0.2$}.
+There are several notable features in the high-resolution AO and {\it HST} data. These include the nearly complete lack of emission associated with lensed images B and D, 
+%as can be seen by comparing the radio contours to the $K^\prime$-band emission 
+(Fig.~\ref{fig:3panel}b), and the faint, but clearly visible emission from {\bf the lensing galaxy that appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an {\bf axis ratio $q \sim 0.2$}.
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
-Therefore, the lack of emission that is seen from these images is likely due to dust extinction and additional demagnification due to lensing.
+Therefore, the lack of emission from these images is likely due to dust extinction and additional demagnification due to lensing.
 
@@
 Imaging was done with the {\sc clean} algorithm in AIPS using natural weighting of the visibilities, and restored using an elliptical beam of size $9.7 \times 6.9$~mas at a position angle of $-7.6^\circ$ east of north.
-The final map (also shown in Fig.~\ref{fig:merlin}) has an rms of 78~$\mu$Jy~beam$^{-1}$.
+The final map (also shown in Fig.~\ref{fig:3panel}a) has an rms of 78~$\mu$Jy~beam$^{-1}$.
 
@@
 Image C is still compact on mas-scales, whereas image D is only marginally detected ($\sim6~\sigma$).
-We immediately see from the high resolution VLBA imaging that image B has a smaller angular size than image A, which is consistent with a perturbation in the mass model being responsible for the flux-ratio anomaly (recall that gravitational lensing conserves surface brightness), as opposed to free-free absorption or interstellar scattering.
+%We immediately see from the high resolution VLBA imaging 
+The VLBA imaging shows that image B has a smaller angular size than image A, which is consistent with a perturbation in the mass model being responsible for the flux-ratio anomaly (recall that gravitational lensing conserves surface brightness), as opposed to free-free absorption or interstellar scattering.
 
@@
 
-The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:model}.
+The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
@@
 
-\begin{figure}
-%\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
-\includegraphics[width=72mm]{fig2_twocontour_b.eps}
-\caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.}
-\label{fig:merlin}
-\end{figure}
+\begin{figure*}
+\includegraphics[width=0.9\textwidth]{b1555_3panel.eps}
+\caption{
+{\bf (a)} High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.
+%
+{\bf (b)} Test, for now
+%
+{\bf (c)} Observed radio (blue pluses) and model-predicted (red open
+circles) image positions of B1555+375. The lens-plane critical curves
+are shown with the blue solid line and the source-plane caustics are
+shown with the red dotted line. The position of the source is at
+($-0.1953$, $-0.1494$), which is marked by the red filled circle. The
+centroid positions of the two mass components of the lens (a SIE and
+an exponential disc) are marked by the black filled triangles.
+}
+\label{fig:3panel}
+\end{figure*}
 
-\begin{figure}
-%\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
-\includegraphics[width=72mm]{gravlens_exp_try5_plot-2.eps}
-%\includegraphics[width=72mm]{fig2_twocontour_b.eps}
-\caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.
+% \begin{figure}
+% %\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
+% \includegraphics[width=72mm]{fig2_twocontour_b.eps}
+% \caption{High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.}
+% \label{fig:merlin}
+% \end{figure}
+% 
+% \begin{figure}
+% %\includegraphics[width=72mm]{gravlens_exp_try5_plot.eps}
+% \includegraphics[width=72mm]{gravlens_exp_try5_plot-2.eps}
+% %\includegraphics[width=72mm]{fig2_twocontour_b.eps}
+% \caption{Observed radio (blue pluses) and model-predicted (red open circles) image positions of B1555+375.
 The lens-plane critical curves are shown with the blue solid line and the source-plane caustics are shown with the red dashed line.
@@
 The centroid positions of the two mass components of the lens (an SIE and an exponential disc) are marked by the black filled triangles.}
-\label{fig:model}
-\end{figure}
+% \label{fig:model}
+% \end{figure}
 
@@
 Here, we find evidence for an edge-on disc in the flux-ratio anomaly
-gravitational lens B1555+375 that can also account for the required
+gravitational lens B1555+375 that can account for the required
 perturbation in the mass model.  Moreover, near-infrared AO imaging of
 other lenses in the SHARP sample shows that B1555+375 is not the only
-system having a significant disc component detection in the lensing
+system that has a significant disc component detection in the lensing
 galaxy; these gravitational lenses will be investigated in future
@@
 model \citep[e.g. as in the case of B1933+503;][]{suyu12}. Also, in
-the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence
+the blue contours of Fig.~\ref{fig:3panel}a, B1555+375 shows evidence
 for an extended $\sim$ 100 mas gravitational arc at radio wavelengths
@@
 \textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account
-\citep[e.g.][]{Xu15}. A number of systems with significant disc components are
-already known.
-These include, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}.
+Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) be taken into account
+\citep[e.g.][]{Xu15}. A number of lens systems with significant disc components are
+already known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}.
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
@@
 LVEK is supported in part through an NWO-VICI career grant (project number 639.043.308).
-The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+The NRAO is a facility of the NSF operated under cooperative agreement by Associated Universities, Inc.
 Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute.

### 2015-12-07 B1555/plot_B1555_3panel.py

@@ -1,0 +1,1 @@
+../python/plot_B1555_3panel.py

### 2015-12-07 python/plot_B1555_3panel.py

@@ -1,0 +1,30 @@
+"""
+A bit of code to create a 3-panel plot that combines the old Figure 2
+(radio contours overlaid on AO greyscale) and Figure 3 (lensing caustics
+and critical curves) from the submitted version of the B1555 paper into
+one figure.
+"""
+
+import sys
+from matplotlib import pyplot as plt
+import plot_fns_b1555 as plt1555
+
+""" Check the command line for an optional output file name """
+print ''
+if len(sys.argv)>1:
+	outfile = sys.argv[1]
+	print 'Will save output to %s' % outfile
+	print ''
+else:
+	outfile = None
+	print 'No output file requested.'
+	print ''
+
+""" Create the 3-panel figure """
+plt1555.plot_3panel_b1555()
+
+""" Save the output, if requested """
+if outfile:
+	plt.savefig(outfile,bbox_inches='tight')
+else:
+	plt.show()

### 2015-12-07 python/plot_fns_b1555.py

@@ -33,7 +33,8 @@ def img_pos(obsfile, xmod, ymod):
 
 def radio_overlay_b1555():
     """
-    Set up basic parameters of the B1555 system.
+    Plots the NIR AO image in greyscale, and then overlays contours
+    from two radio data sets: MERLIN and VLBA
     """
 
     """ Set the input file names """
@@ -82,6 +83,29 @@ def radio_overlay_b1555():
     labt = ['A', 'B', 'C', 'D']
     for i in range(len(labx)):
         plt.text(labx[i],laby[i],labt[i],fontdict=font)
+
+#---------------------------------------------------------------------------
+
+def mark_radio_b1555():
+    """
+    Plots the NIR AO image in greyscale, and then marks with circles
+    the location of the lensed AGN images
+    """
+
+    """ Set the input file names """
+    aofile = '../data/B1555_nirc2_n_Kp_6x6.fits'
+
+    """ Set the image center, origin location, and size """
+    racent  = 239.29968
+    deccent = 37.359921
+    zeropos = (0.2276,0.2194)
+    imsize  = 1.2       # Value in arcsec
+
+    """ Plot the AO image """
+    aoim = imf.Image(aofile)
+    aoim.display(cmap='gray_inv',subimdef='radec',subimcent=(racent,deccent),
+                 subimsize=(imsize,imsize),dispunits='radec',sighigh=6.,
+                 zeropos=zeropos)
 
 #---------------------------------------------------------------------------
 
@@ -165,4 +189,51 @@ def plot_2panel_b1555():
     """ Handle the axis labels"""
     yticklabels = ax2.get_yticklabels()
     #yticklabels = ax1.get_yticklabels() + ax2.get_yticklabels()
+    plt.setp(yticklabels, visible=False)
+
+#---------------------------------------------------------------------------
+
+def plot_3panel_b1555():
+    """
+    Creates a 2-panel figure, with one panel showing the radio/NIR overlay,
+    one showing the NIR image with just circles indicating the lensed image
+    locations, and the third showing the results of the lens modeling.
+    """
+
+    """ Set x and y limits for the plots """
+    x1 =  0.3724
+    x2 = -0.8276
+    y1 = -0.8194
+    y2 =  0.3806
+
[…]

### 2015-12-07 papers/B1555_EdgeOn/Resubmission/referee_response.txt
updates to referee response

@@
 responded to the comments below, and modified the text accordingly.
-Overall, we have toned down our somewhat sweeping claims.
 
@@
 the edge-on disk and the dark-matter halo of the lensing galaxy.
+[SHOULD WE MENTION SWELLS RESULTS HERE??]
 
@@
 elliptical galaxy.  We would therefore expect a lower incidence of
-disky systems in SLACS than in the SHARP sample.  We agree completely
+disky systems in SLACS than in the SHARP sample.  The SWELLS sample
+shows a number of massive disc systems, that contribute significantly
+to the mass within 2.2 scale radii [WE DON'T MENTION THIS IN THE TEXT.
+SHOULD WE, AS LEON SUGGESTED?]
+We agree completely
 with the referee that doing a quantification of the statistics of

### 2015-12-09 papers/B1555_EdgeOn/Resubmission/referee_response.txt
Updates to code, figure, and paper text

@@
 contains at least one other system, B1600+434 (albeit a double), where
-the lensing galaxy appears to be an edge-on disk with a very low
+the lensing galaxy is an edge-on disk with a very low
 bulge/disk ratio.  In contrast, SLACS lenses were selected to be

### 2015-12-09 python/plot_fns_b1555.py

@@ -12,6 +12,7 @@ Functions
 import numpy as n
 import imfuncs as imf
 from matplotlib import pyplot as plt
+from matplotlib import patches
 import plot_lensmod as pltlm
 
 #---------------------------------------------------------------------------
@@ -86,7 +87,7 @@ def radio_overlay_b1555():
 
 #---------------------------------------------------------------------------
 
-def mark_radio_b1555():
+def mark_radio_b1555(color='r', radius=0.05, lw=2):
     """
     Plots the NIR AO image in greyscale, and then marks with circles
     the location of the lensed AGN images
@@ -106,6 +107,16 @@ def mark_radio_b1555():
     aoim.display(cmap='gray_inv',subimdef='radec',subimcent=(racent,deccent),
                  subimsize=(imsize,imsize),dispunits='radec',sighigh=6.,
                  zeropos=zeropos)
+
+    """ Add circles for radio positions """
+    obsfile  = '../models/B1555/B1555_obsdat.txt'
+    x0,y0 = n.loadtxt(obsfile,unpack=True,usecols=(0,1))
+    ax = plt.gca()
+    for i in range(x0.size):
+        circ = patches.Circle((x0[i],y0[i]),radius,edgecolor=color,
+                              facecolor='none',lw=lw)
+        ax.add_patch(circ)
+    plt.ylabel('')
 
 #---------------------------------------------------------------------------
 

### 2015-12-09 papers/B1555_EdgeOn/Resubmission_1208/referee_response.txt
the complete resubmit version

--- 2015-11-17 papers/B1555_EdgeOn/Resubmission/referee_response.txt
@@
 RESPONSE: The referee is correct to point out that we did not quantify
-the bulge/disk ratio in the lensing galaxy.  We have performed a
-bulge+disk fit to the lens-galaxy surface brightness distribution.
-Our fit returns a bulge component that is consistent with zero
-emission.  We have added text to the paper describing this result.  We
-note that the two components in our lens model can be thought of as
-the edge-on disk and the dark-matter halo of the lensing galaxy.
+the stellar mass in the lensing galaxy.  However, without the
+redshifts of the lensing galaxy, we cannot convert the photometry into
+a mass estimate.  That being said, the scale radius of the disk is
+larger than the Einstein ring radius.  In this regime, studies of
+edge-on disk lens galaxies (e.g., Dutton et al. 2011 and 2013) show
+that the baryonic component can be significant, often contributing around
+40 percent of the circular velocity at 2.2 scale radii.  We have also
+performed a bulge+disk fit to the lens-galaxy surface brightness
+distribution.  Our fit returns a bulge component that is consistent
+with zero emission.  We have added text to the paper describing this
+result.  We note that the two components in our lens model can be
+thought of as (1) the edge-on disk and (2) the (minimal) bulge +
+dark-matter halo of the lensing galaxy.
 
@@
 contains at least one other system, B1600+434 (albeit a double), where
-the lensing galaxy appears to be an edge-on disk with a very low
-bulge/disk ratio.  In contrast, SLACS lenses were selected to be
-systems where the lensing galaxy was known a priori to be a massive
-elliptical galaxy.  We would therefore expect a lower incidence of
-disky systems in SLACS than in the SHARP sample.  We agree completely
-with the referee that doing a quantification of the statistics of
-massive disks and their effects on flux-ratio anomalies is an
-extremely important task and, in fact, this is one of the future
-projects that we are planning.  However, we feel that such an
-extensive analysis is beyond the scope of this letter.  As such, we
-have modified the text to focus more on this individual lens system
-and put more caveats on the possible generalization of the results.
+the lensing galaxy is an edge-on disk with a very low bulge/disk
+ratio, and at least 2 more disky lenses.  In contrast, SLACS lenses
+were selected to be systems where the lensing galaxy was known to be a
+luminous red galaxy, and thus likely to be an elliptical.  We would
+therefore expect a lower incidence of disc systems in SLACS than in
+the SHARP sample.  The SWELLS sample, on the other hand, was selected
+to have edge-on disc galaxies as lenses.  Due to the selection effects
+in each case, neither of these samples will be much help in
+determining the statistics of disc lenses.  The CLASS sample, with 3-4
+disk lenses out of 22 systems, might be more informative if it were
+not so small.  Overall, we agree completely with the referee that
+doing a quantification of the statistics of massive disks and their
+effects on flux-ratio anomalies is an extremely important task and, in
+fact, this is one of the future projects that we are planning.
+However, we feel that such an extensive analysis is beyond the scope
+of this letter.  As such, we have modified the text to focus more on
+this individual lens system and put more caveats on the possible
+generalization of the results.

### 2015-12-09 papers/B1555_EdgeOn/Resubmission_1208/B1555_EdgeOn.tex
the complete resubmit version

--- 2015-12-07 papers/B1555_EdgeOn/B1555_letter.tex
@@
 \caption{
-{\bf (a)} High-resolution $K^\prime$-band imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.
+{\bf (a)} $K^\prime$-band AO imaging of B1555+375 with contours from the MERLIN observations (red) of \citet{Marlow99} and the VLBA observations presented here (blue) overlaid.
 %
-{\bf (b)} Test, for now
+{\bf (b)} $K^\prime$-band AO image with the locations of the four radio components
+marked with circles.  
 %

### 2016-01-06 papers/B1555_EdgeOn/arXiv_0106/B1555_EdgeOn.tex
update new dir for arXiv submit

--- 2015-12-09 papers/B1555_EdgeOn/Resubmission_1208/B1555_EdgeOn.tex
@@
 Here we present the case of CLASS~B1555+375, which has a strong radio-wavelength flux-ratio anomaly.
-{\bf Our high-resolution near-infrared Keck~II adaptive optics imaging and archival {\it Hubble Space Telescope} data reveal the lensing galaxy in this system} to have  a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
+Our high-resolution near-infrared Keck~II adaptive optics imaging and archival {\it Hubble Space Telescope} data reveal the lensing galaxy in this system to have  a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
 We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
-Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model {\bf may} overestimate the substructure mass fraction in massive lensing galaxies.
+Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model may overestimate the substructure mass fraction in massive lensing galaxies.
 \end{abstract}
@@
 The \emph{gravitational imaging technique}, which alternatively utilizes the surface brightness distribution of extended arcs and Einstein rings to detect low-mass substructures within lensing haloes, was introduced by \citet{K05} and \citet{V09}.
-This method has given a measurement of the substructure mass fraction for a sample of {\bf 11 lenses} that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
+This method has given a measurement of the substructure mass fraction for a sample of 11 lenses that is currently in agreement with the theoretical expectations from cold matter matter simulations \citep{V14a,V12}.
 The reason for the conflicting results between the flux-ratio anomaly and gravitational imaging techniques is currently not clear.
@@
 %as can be seen by comparing the radio contours to the $K^\prime$-band emission 
-(Fig.~\ref{fig:3panel}b), and the faint, but clearly visible emission from {\bf the lensing galaxy that appears to be an edge-on disc}, with a position angle of $\sim 10$~deg and an {\bf axis ratio $q \sim 0.2$}.
+(Fig.~\ref{fig:3panel}b), and the faint, but clearly visible emission from the lensing galaxy that appears to be an edge-on disc, with a position angle of $\sim 10$~deg and an axis ratio $q \sim 0.2$.
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
@@
 
-We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in {\bf length}.
+We find that lensed images A and B have been resolved into a gravitational arc that is $\sim100$~mas in length.
 Image C is still compact on mas-scales, whereas image D is only marginally detected ($\sim6~\sigma$).
@@
 The source position adds two additional model parameters.
-{\bf We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.}
+We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
 %An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}
-{\bf 
+
 More sophisticated mass models require additional
@@
 future by imaging the extended gravitational arc and more
-significantly detecting image D. }
+significantly detecting image D.
 
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the ExpDisc component makes up about 10 per cent of the total {\bf projected} mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
-{\bf In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
+The model requires that the ExpDisc component makes up about 10 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
 In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.
+We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
-Again, more complex mass models require {\bf the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.}
+Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.
 
@@
 
-\textbf{ 
 Here, we find evidence for an edge-on disc in the flux-ratio anomaly
@@
 constraints required to fully test whether the disc is sufficient to
-cause the anomaly.}
+cause the anomaly.
 
-\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
+Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
 Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) be taken into account
@@
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
-  be measured using narrow lines \citep[e.g.][]{N14}.}
+  be measured using narrow lines \citep[e.g.][]{N14}.
   %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.

### 2016-01-06 papers/B1555_EdgeOn/arXiv_0106/B1555_EdgeOn.tex
change arXiv tex file

@@
 $^{4}$Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands\\
-$^{5}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{6}$University of Lyon, 92 Rue Pasteur, 69007 Lyon, France}
+$^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{6}$Universit\'e Lyon, CRAL, Observatoire de Lyon, 92 Rue Pasteur, 69007 Lyon, France}
 \begin{document}

### 2016-01-19 papers/B1555_EdgeOn/arXiv_0106/B1555_EdgeOn.tex
B1555 new model (9 paras)

--- 2016-01-06 papers/B1555_EdgeOn/arXiv_0106/B1555_EdgeOn.tex
@@
 $^{4}$Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands\\
-$^{5}$Institute of Astronomy, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{6}$University of Lyon, 92 Rue Pasteur, 69007 Lyon, France}
+$^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{6}$University of Lyon, CRAL, Observatoire de Lyon, 92 Rue Pasteur, 69007 Lyon, France}
 \begin{document}

### 2016-01-19 papers/B1555_EdgeOn/B1555_letter.tex
Edit B1555 modelling part in text

@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), and the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+The free parameters of the the are SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
 The source position adds two additional model parameters.
-{\bf We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.}
+We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
 %An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}
-{\bf 
+
 More sophisticated mass models require additional
@@
 future by imaging the extended gravitational arc and more
-significantly detecting image D. }
+significantly detecting image D.
 
-To obtain the best-fit lens model, we explore the parameter space with the following steps.
-First, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE and exponential disc profiles.
-We add information from the Keck AO image for the disc, starting with an ellipticity of $e=0.8$ and a position angle of $\theta=10^\circ$.
-All of the model parameters are then allowed to vary, but we fix the centroid positions of the SIE and exponential disc to the infrared positions with a Gaussian prior ($\sigma = 0.05 $~arcsec).
-The total number of free parameters is 13.
-After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to explore the parameter space for the uncertainties.
+\textbf{To obtain the best-fit lens model, we explore the parameter space as the following:  First, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile.
+By looking at the NICMOS F160W imaging, which has the highest signal-to-noise ratio of disc among the data, we fix the centroid position as $(-0.162, -0.206)$ , ellipticity as $e=0.83$, and position angle of $\theta=8^\circ$.
+The total number of free parameters is 9.
+After obtaining the best-fit lens model from {\sc gravlens}, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}
 
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the ExpDisc component makes up about 10 per cent of the total {\bf projected} mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
-{\bf In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
+The model requires that the ExpDisc component makes up about 10 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
 In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
-We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.}  We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
+We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.
+\textbf{[Is 0.015" still a large offset?]}
+%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
 from an external shear) that is being partly compensated for by the disc component.
-Again, more complex mass models require {\bf the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.}
+Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.
 
@@
 \hline
-$\Delta$RA	& $-0.182 \pm 0.005$		& $-0.147 \pm 0.005$\\
-$\Delta$Dec	& $-0.199 \pm 0.005$		& $-0.206 \pm 0.006$ \\
-$b$ 			& $0.21 \pm 0.01$  		& ...  \\
-$\kappa_0$ & ... &$0.11 \pm 0.01$\\
-$e$	  		& $0.31 \pm 0.01$			& $0.87 \pm 0.01$ \\
-$\theta$ 		& $3.0 \pm 0.6$			& $7.0 \pm 0.7$	 \\
-$R_s$			& ...  						& $0.28 \pm 0.01$	 \\
+$\Delta$RA	& $-0.176 \pm 0.005$		& $-0.162$ \textit{(fixed)}\\
+$\Delta$Dec	& $-0.212 \pm 0.005$		& $-0.206$ \textit{(fixed)} \\
+$b$ 			& $0.19 \pm 0.01$  		& ...  \\
+$\kappa_0$ & ... &$0.19 \pm 0.01$\\
+$e$	  		& $0.40 \pm 0.01$			& $0.83$ \textit{(fixed)} \\
+$\theta$ 		& $4.4 \pm 0.6$			& $8.0$ \textit{(fixed)}	 \\
+$R_s$			& ...  						& $0.21 \pm 0.01$	 \\
 \hline

### 2016-01-30 papers/B1555_EdgeOn/B1555_letter.tex
B1555 advance model + paper text edit

@@
 
-\textbf{To obtain the best-fit lens model, we explore the parameter space as the following:  First, we use the best-fit model of \citet{Marlow99} as the starting point for the SIE profile.
+\textbf{We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model.
+The best-fit parameters from \citet{Marlow99} are set as the starting point of the SIE profile.
 By looking at the NICMOS F160W imaging, which has the highest signal-to-noise ratio of disc among the data, we fix the centroid position as $(-0.162, -0.206)$ , ellipticity as $e=0.83$, and position angle of $\theta=8^\circ$.
 The total number of free parameters is 9.
-After obtaining the best-fit lens model from {\sc gravlens}, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}
+After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}
 
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the ExpDisc component makes up about 10 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
-In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2}.
-In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2, swells5}.}  In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
 We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.
-\textbf{[Is 0.015" still a large offset?]}
 %We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g.
@@
 A  &$0$    		&$0$			&  $1$ 				&$+0.000$  &$+0.000$	& $1$ 		& $1$\\  
-B  &$-0.073$	&$+0.048$	& $0.620 \pm 0.039$ 	&$-0.073$ &$+0.048$		& $0.620$ 	& $0.971$ \\  
-C  &$-0.412$ 	&$-0.028$	& $0.507\pm 0.030$	&$-0.412$ &$-0.028$		& $0.461$ 	& $0.312$\\  
-D  &$-0.162$	&$-0.368$	& $0.086 \pm 0.024$ 	&$-0.163$ &$-0.365$		& $0.115$ 	& $0.106$\\  
+B  &$-0.0726$	&$+0.0480$	& $0.620 \pm 0.039$ 	&$-0.0715$ &$+0.0487$		& $0.606$ 	& $0.971$ \\  
+C  &$-0.4117$ 	&$-0.0280$	& $0.507\pm 0.030$	&$-0.4115$ &$-0.0278$		& $0.445$ 	& $0.312$\\  
+D  &$-0.1619$	&$-0.3680$	& $0.086 \pm 0.024$ 	&$-0.1693$ &$-0.3704$		& $0.123$ 	& $0.106$\\  
 \hline
@@
 \hline
-$\Delta$RA	& $-0.176 \pm 0.005$		& $-0.162$ \textit{(fixed)}\\
-$\Delta$Dec	& $-0.212 \pm 0.005$		& $-0.206$ \textit{(fixed)} \\
-$b$ 			& $0.19 \pm 0.01$  		& ...  \\
-$\kappa_0$ & ... &$0.19 \pm 0.01$\\
-$e$	  		& $0.40 \pm 0.01$			& $0.83$ \textit{(fixed)} \\
-$\theta$ 		& $4.4 \pm 0.6$			& $8.0$ \textit{(fixed)}	 \\
-$R_s$			& ...  						& $0.21 \pm 0.01$	 \\
+$\Delta$RA	& $-0.177 \pm 0.005$		& $-0.162$ \textit{(fixed)}\\
+$\Delta$Dec	& $-0.205 \pm 0.005$		& $-0.206$ \textit{(fixed)} \\
+$b$ 			& $0.18 \pm 0.01$  		& ...  \\
+$\kappa_0$ & ... &$0.27 \pm 0.01$\\
+$e$	  		& $0.25 \pm 0.01$			& $0.83$ \textit{(fixed)} \\
+$\theta$ 		& $4.9 \pm 0.6$			& $8.0$ \textit{(fixed)}	 \\
+$R_s$			& ...  						& $0.24 \pm 0.01$	 \\
 \hline
@@
 gravitational lens B1555+375 that can account for the required
-perturbation in the mass model.  Moreover, near-infrared AO imaging of
-other lenses in the SHARP sample shows that B1555+375 is not the only
-system that has a significant disc component detection in the lensing
-galaxy; these gravitational lenses will be investigated in future
-work, but the images alone suggest that other systems may have similar
-links between flux-ratio anomalies and disc components. Such
+perturbation in the mass model.
+\textbf{Although the constraint on disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux anomalies in B1555+375, at least, have strong link to the present of its edge-on disc.
+} Such
 high-order deviations from a smooth mass distribution have already
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) be taken into account
-\citep[e.g.][]{Xu15}. A number of lens systems with significant disc components are
-already known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}.
+\textbf{\citet{Maller97,Kee98, Moller03} have shown that a disc with high inclination angle can significantly affects the lensing cross-section.
+While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc is sufficient to bring a bias into the substructure analysis.
+Moreover, near-infrared AO imaging of
+other lenses in the SHARP sample shows that B1555+375 is not the only
+system that has a significant disc component detection close to merging images among the current sample of flux ratio anomalous systems; these gravitational lenses will be investigated in future
+work, but the images alone suggest that other systems may have similar
+links between flux-ratio anomalies and disc components.
+This bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future.
+Therefore, it is critical to obtain high-resolution imaging like SHARP of target lenses to detect `sharp' mass features such as edge-on disks or even massive luminous satellites.}
+% A number of lens systems with significant disc components arealready known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}. 
  This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
@@
 \bibliographystyle{mnras}
-\bibliography{reference.bib}
+\bibliography{reference}
 

### 2016-01-30 models/B1555/gravlens_code/emcee_gravlens_2.py

@@ -1,0 +1,288 @@
+import os
+import numpy as np
+import emcee
+import scipy.stats
+import itertools as it
+import commands
+
+img_obs=np.array([0.0,0.0,17.0,-0.0726,0.0480,10.54,-0.4117,-0.0280,8.619,-0.1619,-0.3680,1.462])
+err_obs=np.array([1.0e-6,1.0e-6,1.70,0.01,0.01,0.97,0.01,0.01,0.83,0.06,0.06,0.13])
+
+
+def call_findimage(paras):
+    
+    ## create input file
+        head=open('input_exp.head','r')
+        #tail=open('input_exp.tail','r')
+        inp=open('B1555_emcee.input','w')
+        
+        # read head of input template
+        for line in head.readlines():
+            #print line
+            inp.write(line)
+    
+        head.close()
+        inp.write('\n')
+        
+        # prepare for lens model parameters
+        lens_para=['','','']
+        
+        for i in range(5):
+            lens_para[0]=lens_para[0]+'%f '%paras[i]    #bulge
+            #lens_para[1]=lens_para[1]+'%f '%paras[5+i]  #disk
+
+
+        lens_para[1]=lens_para[1]+'%f '%paras[5]+'-1.615516e-1 -2.056755e-1 8.28e-1 -8.0e+0 0.0 0.0 '+'%f '%paras[6] #r_s for expdisk
+        
+        # write lens models into input file
+        inp.write('alpha '+lens_para[0]+'0.0 0.0 0.0 0.0 1.0 \n') #SIE
+        inp.write('expdisk '+lens_para[1]+'0.0 0.0 \n')       #expdisk
+
+        inp.write('\n 0 0 0 0 0 0 0 0 0 0 \n 0 0 0 0 0 0 0 0 0 0 \n')
+
+        # findimg [souce pos]
+
+        lens_para[2]=lens_para[2]+'%f '%paras[7]+'%f '%paras[8]
+
+        inp.write('\n findimg '+lens_para[2]+'\n')
+        
+
+        inp.close()
+    
+        print_out=commands.getstatusoutput('./lensmodel B1555_emcee.input')
+        print_out=print_out[1]
+        print_out=print_out.split('\n')
+                        
+        ot=len(print_out)
+
+        # extract findimg result
+
+        # get img number info
+
+        check=print_out[-6]
+        #print check
+        check=check.split()
+        #print check[0]
+
[…]

### 2016-01-30 python/emcee_corner.py

@@ -3,7 +3,7 @@ import triangle
 import matplotlib.pyplot as plt
 #import matplotlib.patches as mpat
 
-file_name=['B1555_parachain.dat']
+file_name=['../data/exp_chain.dat']
 
 k=0
 for i in file_name:
@@ -27,7 +27,7 @@ for i in file_name:
 
 #data=t[:,:11] #ignore source posotions first
 #data=t[:,:9]
-data=t[:,13:]
+data=t[:,:7]
 #print len(chi2)
 
 
@@ -36,14 +36,14 @@ data=t[:,13:]
 #ndim, nsamples = 10, len(chi2)
 
 figure = triangle.corner(data, labels=[
-                                       #r"$b$", r"$x1$", r"$y1$",
-                                       #r"$e1$",r"$PA1$",
-                                       #r"$kappa_0$",
+                                       r"$b$", r"$x1$", r"$y1$",
+                                       r"$e1$",r"$PA1$",
+                                       r"$kappa_0$",
                                        #r"$x2$", r"$y2$",
                                        #r"$e2$",r"$PA2$"
-                                       #,r"$rs$"
-                                       #,r"x_s",r"y_s",
-                                       r"b_sub",r"x_sub",r"y_sub"],
+                                       r"$rs$"],
+                                       #,r"x_s",r"y_s"]
+                                       #r"b_sub",r"x_sub",r"y_sub"],
 #                         extents=[(120.,170.),(0.1,0.25),(-0.35,-0.2),(0.,0.5),(60.,110.),
 #                                  (110.,160.),(0.1,0.25),(-0.3,-0.1),(0.75,0.95),(0.,20.)],
                          #range=[0.999,0.999,0.999,0.999,0.999,

### 2016-01-30 python/lens_plot.py

@@ -155,8 +155,12 @@ model_plot()
 #print x,y
 img_pos(lens_name)
 
-plt.xlim(0.4,-0.8)
-plt.ylim(-0.8,0.4)
+#plt.xlim(0.4,-0.8)
+#plt.ylim(-0.8,0.4)
+
+plt.xlim(1.6,-0.4)
+plt.ylim(-0.8,1.2)
+
 plt.legend(loc=1)
 
 if outfile:

### 2016-02-01 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
Added second B1555 referee response to the repo

>The revised version of the paper still contains the unsubstantiated speculation pointed out in my previous report, with no additional supporting evidence.  I am puzzled by the authors' statement in their response that an analysis of the effects of disks on lens statistics would be beyond the scope of the paper, since this is literally the topic of the paper.  The main problem now is that the paper's title is misleading, since nothing in this work provides any reason to believe that there is a bias in observational measurements of dark matter substructure with gravitational lens flux ratios.

RESPONSE: The referee is correct to point out that our title may be misleading in implying that we intend to discuss the effects of disks on lens statistics.  Thus, we add more description on how can we be informed by a new model of a single system in the discussion. That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, which has been shown in Maller et al. 1997, Möller et al. 2003, and Keeton & Kochanek 1998.  Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies is fairly small size.  Therefore, if even a few systems within the sample have edge-on discs, these are sufficient to bias the substructure analysis. As the current work of flux anomalous lenses are analyzed with a standard SIE mass profile, it is fair to say that the disc effect is a bias that been ignored for a long time. Moreover, from the high-resolution IR imaging among these flux anomalous lenses, we know that B1555 is not the only system having an edge-on disc across lensed images. Since this is the first time an edge-on disc been confirmed that can be accounted for, at least, part of flux anomalies, we think it is reasonable to keep our title with the wording ‘bias’ rather scope down the implication from our results.

[SOMETHING TO ADD SOMEWHERE ABOVE]:  We seem to have a fundamental disagreement with the referee about the topic of the paper.  The referee feels that it should be an analysis of the statistical effect of disks in lenses.  Most/all previous substructure analyses have interpreted _all_ radio-wavelength flux ratio anomalies as being due to substructure.  We feel that the point of this Letter is to show that the previous assumptions may be wrong, since we have a clear case in which a disc _may_ produce the observed flux-ratio anomaly.  Having made that point in this short letter, we intend to write (and are actively working on) a longer paper that does a full statistical analysis.    
-- We also need to discuss the higher incidence of spirals in small-separation lens systems

>As noted in my previous report, the observational result is quite interesting and merits publication. Since the authors were unable to support their speculations about biases in lens modeling, and have revised the text to focus more on this one specific lens system, I recommend that they amend the title and abstract to more accurately reflect the actual contents of the paper. Something along the lines of "An edge-on disk in the anomalous lens B1555+375" would be more accurate and less misleading than the current title, which is unacceptable for publication given what is actually in the paper.  Similarly, the last 2 sentences of the abstract is misleading.  Although the authors' observations lack sufficient signal/noise to constrain the amplitude of the disk mass in this system, in other lens systems with arcs, the fraction of mass in disky components is constrained to be <~ 1% of the mass in the Einstein radius.  Unless the authors present evidence or arguments for why these previous findings are incorrect, the last sentence of the abstract should be removed.

RESPONSE: We understand that if a constraint from photometry can be applied on B1555+375, it will help us to claim that the best-fit model we found is a ’true’ model. However, the goal of this paper is to demonstrate and bring the attention to the community about the disc-effect. Indeed, as the referee mentioned, the disc mass fraction in the Einstein radius can be down to  <~1%. This is true for massive elliptical lenses but does not hold for spiral lenses especially for lenses having high-inclined discs. The SWELLS samples, 19 spiral lenses, have stellar mass at least >~40% in the Einstein radius. Despise most of SWELLS lenses have a significant bulge therefore they are not perfect analogous systems to B1555+375, it is still unphysical to say that the bulge accounts for more than 97% of stellar mass in the Einstein radius with a clear late-type disc detected.

>Similarly, the penultimate sentence of the abstract is also potentially misleading.  The modeling presented in this paper does not show that simple models containing disks can reproduce the observations, since those models are woefully underconstrained by the data that the authors fit.  Indeed, for the casual reader it would be useful for the text to explicitly state in words that the number of model parameters (13) exceeds the number of observational constraints (11), and that therefore the model should fit the data exactly with 2 exact parameter degeneracies.  Presumably, the weak prior on the centroid locations of the two lens components acts to break the exact degeneracy, though it is puzzling that the uncertainties on the model parameters listed in Table 3 are so much smaller than the 0.05 arcsecond prior on the centroids.  It would be useful for the text to provide an explanation for why the uncertainties on the parameters are so small, since in the absence of the centroid prior there should be 2 exact degeneracies.

RESPONSE: We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions. We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry and fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search. This reduces the number of free parameters from 13 to 9. The predicted image positions and flux ratios in this new model is still agree with the observations, which supports our original statements and conclusions. We also take off the 0.05 arcseoncd prior on the centroids in the best-fit model search. The alignment between two components without using a prior implies that this centroid prior is not necessary.

### 2016-02-04 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
update B1555 paper text

@@
 
-[SOMETHING TO ADD SOMEWHERE ABOVE]:  We seem to have a fundamental disagreement with the referee about the topic of the paper.
+[SOMETHING TO ADD SOMEWHERE ABOVE]:  
+As the reason describing above, we seem to have a fundamental disagreement with the referee about the topic of the paper.
 The referee feels that it should be an analysis of the statistical effect of disks in lenses.
@@
 This is true for massive elliptical lenses but does not hold for spiral lenses especially for lenses having high-inclined discs.
-The SWELLS samples, 19 spiral lenses, have stellar mass at least >~40% in the Einstein radius.
-Despise most of SWELLS lenses have a significant bulge therefore they are not perfect analogous systems to B1555+375, it is still unphysical to say that the bulge accounts for more than 97% of stellar mass in the Einstein radius with a clear late-type disc detected.
+The SWELLS samples, 19 spiral lenses, have stellar mass at least >~40% in the Einstein radius (see Brewer et al.
+2012, Table 1).
+Also, in Treu et al.
+2011, Figure 4 presents the average stellar surface mass density profile, which showing that SWELLS lenses have approximately the same average surface mass density of bulge and disc component within the 2 kpc circular aperture.
+By saying that the total projected mass is about the same for bulge and disc on the scale larger than kpc, and the stellar mass within the Einstein radius of spiral lenses can contribute more than 40%, we think the studies on SWELLS spiral lenses well support our finding on the disk mass fraction in B1555+375.
+Even most of SWELLS lenses have a significant bulge so that they may not be perfect analogous systems to B1555+375, it is still unphysical to say that the 99% of the mass in the Einstein radius are dark matter when a clear late-type disc is detected.
 

### 2016-02-04 papers/B1555_EdgeOn/B1555_letter.tex
update B1555 paper text

@@
 The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
-In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total enclosed mass \citep[e.g.][]{swells2, swells5}.}  In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
+In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
+The sample of 16 edge-on disks from SDSS found in the SWELLS survey shows that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3}.}
+%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
 We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy.
@@
 \hline
-$\Delta$RA	& $-0.177 \pm 0.005$		& $-0.162$ \textit{(fixed)}\\
-$\Delta$Dec	& $-0.205 \pm 0.005$		& $-0.206$ \textit{(fixed)} \\
-$b$ 			& $0.18 \pm 0.01$  		& ...  \\
-$\kappa_0$ & ... &$0.27 \pm 0.01$\\
-$e$	  		& $0.25 \pm 0.01$			& $0.83$ \textit{(fixed)} \\
-$\theta$ 		& $4.9 \pm 0.6$			& $8.0$ \textit{(fixed)}	 \\
-$R_s$			& ...  						& $0.24 \pm 0.01$	 \\
+$\Delta$RA	& $-0.177 \pm 0.003$		& $-0.162$ \textit{(fixed)}\\
+$\Delta$Dec	& $-0.205 \pm 0.004$		& $-0.206$ \textit{(fixed)} \\
+$b$ 			& $0.178 \pm 0.004$  		& ...  \\
+$\kappa_0$ & ... &$0.273 \pm 0.003$\\
+$e$	  		& $0.25 \pm 0.05$			& $0.83$ \textit{(fixed)} \\
+$\theta$ 		& $4.9 \pm 1.3$			& $8.0$ \textit{(fixed)}	 \\
+$R_s$			& ...  						& $0.236 \pm 0.003$	 \\
 \hline

### 2016-02-04 python/lens_plot.py

@@ -38,8 +38,8 @@ plot_type=int(plot_type)
 """Also put that under /data/lens_info dir"""
 
 if plot_type==0:
-    file_name=raw_input('file name of .crit file:')
-    name='../data/lens_info/'+file_name+'.crit'
+    file_name=raw_input('file name of _crit.dat file:')
+    name='../data/lens_info/'+file_name+'_crit.dat'
 
 
 
@@ -155,11 +155,11 @@ model_plot()
 #print x,y
 img_pos(lens_name)
 
-#plt.xlim(0.4,-0.8)
-#plt.ylim(-0.8,0.4)
+plt.xlim(0.4,-0.8)
+plt.ylim(-0.8,0.4)
 
-plt.xlim(1.6,-0.4)
-plt.ylim(-0.8,1.2)
+#plt.xlim(1.6,-0.4)
+#plt.ylim(-0.8,1.2)
 
 plt.legend(loc=1)
 

### 2016-02-04 python/sigma.py

@@ -26,6 +26,6 @@ sigR=np.floor(0.84*nch)
 for i in range(npara):
     array=t[:,i]
     array=np.sort(array)
-    print array[sigL],array[mid],array[sigR]
-#    print array[mid]-array[sigL],array[sigR]-array[mid]
+    #    print array[sigL],array[mid],array[sigR]
+    print array[mid]-array[sigL],array[sigR]-array[mid]
 

### 2016-02-09 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
update referee response

--- 2016-02-01 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
@@
 Since this is the first time an edge-on disc been confirmed that can be accounted for, at least, part of flux anomalies, we think it is reasonable to keep our title with the wording ‘bias’ rather scope down the implication from our results.
+[But to be more conservative about our finding on disc-effect, we decide to rephrase 'bias' into 'potential bias' in the title.
+]
 
-[SOMETHING TO ADD SOMEWHERE ABOVE]:  We seem to have a fundamental disagreement with the referee about the topic of the paper.
+As the reason describing above, we seem to have a fundamental disagreement with the referee about the topic of the paper.
 The referee feels that it should be an analysis of the statistical effect of disks in lenses.
@@
 Having made that point in this short letter, we intend to write (and are actively working on) a longer paper that does a full statistical analysis.
--- We also need to discuss the higher incidence of spirals in small-separation lens systems
 
@@
 This is true for massive elliptical lenses but does not hold for spiral lenses especially for lenses having high-inclined discs.
-The SWELLS samples, 19 spiral lenses, have stellar mass at least >~40% in the Einstein radius.
-Despise most of SWELLS lenses have a significant bulge therefore they are not perfect analogous systems to B1555+375, it is still unphysical to say that the bulge accounts for more than 97% of stellar mass in the Einstein radius with a clear late-type disc detected.
+SWELLS lenses, a group of spiral lenses selected from SDSS spectra, provide clear evidence of high fraction of stellar mass within the Einstein radius.
+Figure 5 in Brewer et al.
+2012 shows that stellar mass dominates the lens mass.
+This is quite common in the small-seperation lens systems since that the very inner region of galaxies are mostly stellar mass.
+And these systems are more likely to be spirals.
+By fitting to photometry, we conclude that B1555+375 is a late-type spiral with no appreance of bulge.
+We think it is clear that saying the disc of B1555+375 accounts for less than 1% of lens mass is unphysical base on the stuides of spiral lenses.
+
+Moreover, by combining the information given in Treu et al.
+2011 and Brewer et al.
+2012, the disc mass fraction of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
+Especially when we look at J0820+4847, being a good anologous system to B1555+375, we notice that it has an arc right across its edge-on disc and has 15% of disc mass fraction within the Einstein radius.
+Again, the studies on spiral galaxies support our model having ~15% of disc mass fraction.
+The cases hold for disc mass fraction <~1% is most likely massive elliptical lenses, but not edge-on spiral lenses.
 

### 2016-02-09 papers/B1555_EdgeOn/B1555_letter.tex
little change to B1555 text

@@
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-The sample of 16 edge-on disks from SDSS found in the SWELLS survey shows that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3}.}
+Studies on edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3}.}
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.

### 2016-02-10 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
minor change of referee response for ref & typo

@@
 And these systems are more likely to be spirals.
-By fitting to photometry, we conclude that B1555+375 is a late-type spiral with no appreance of bulge.
-We think it is clear that saying the disc of B1555+375 accounts for less than 1% of lens mass is unphysical base on the stuides of spiral lenses.
+By fitting to photometry, we conclude that B1555+375 is a late-type spiral with no appearance of bulge.
+We think it is clear that saying the disc of B1555+375 accounts for less than 1% of lens mass is unphysical base on the studies of spiral lenses.
 
@@
 2011 and Brewer et al.
-2012, the disc mass fraction of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
-Especially when we look at J0820+4847, being a good anologous system to B1555+375, we notice that it has an arc right across its edge-on disc and has 15% of disc mass fraction within the Einstein radius.
+2014, the disc mass fraction of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
+Especially when we look at J0820+4847, being a good analogous system to B1555+375, we notice that it has an arc right across its edge-on disc and has 15% of disc mass fraction within the Einstein radius.
 Again, the studies on spiral galaxies support our model having ~15% of disc mass fraction.
@@
 The predicted image positions and flux ratios in this new model is still agree with the observations, which supports our original statements and conclusions.
-We also take off the 0.05 arcseoncd prior on the centroids in the best-fit model search.
+We also take off the 0.05 arcsecond prior on the centroids in the best-fit model search.
 The alignment between two components without using a prior implies that this centroid prior is not necessary.

### 2016-02-10 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
minor changes to ref in response
rearrange and rewrite the SWELLS part in response

@@
 
-RESPONSE: We understand that if a constraint from photometry can be applied on B1555+375, it will help us to claim that the best-fit model we found is a ’true’ model.
-However, the goal of this paper is to demonstrate and bring the attention to the community about the disc-effect.
-Indeed, as the referee mentioned, the disc mass fraction in the Einstein radius can be down to  <~1%.
-This is true for massive elliptical lenses but does not hold for spiral lenses especially for lenses having high-inclined discs.
-SWELLS lenses, a group of spiral lenses selected from SDSS spectra, provide clear evidence of high fraction of stellar mass within the Einstein radius.
-Figure 5 in Brewer et al.
-2012 shows that stellar mass dominates the lens mass.
+RESPONSE: As we mentioned in the previous response, SWELLS lenses, a group of spiral lenses selected from SDSS spectra, provide clear evidence of high fraction of stellar mass within the Einstein radius.
+Some of SWELLS samples also have arcs right across their edge-on discs, which is similar to B1555+375.
+Figure 6 in Brewer et al.
+2014 shows that stellar mass dominates the lens mass.
 This is quite common in the small-seperation lens systems since that the very inner region of galaxies are mostly stellar mass.
@@
 2014, the disc mass fraction of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
-Especially when we look at J0820+4847, being a good analogous system to B1555+375, we notice that it has an arc right across its edge-on disc and has 15% of disc mass fraction within the Einstein radius.
-Again, the studies on spiral galaxies support our model having ~15% of disc mass fraction.
-The cases hold for disc mass fraction <~1% is most likely massive elliptical lenses, but not edge-on spiral lenses.
+Especially when we look at J0820+4847, a good analogous system to B1555+375, we notice that it  has 15% of disc mass fraction within the Einstein radius.
+This supports our model having ~15% of disc mass fraction in a lens system with clear arcs.
+The statement from referee about "disc mass fraction <~1% within the Einstein radius" most likely holds for massive elliptical lenses but not for edge-on spiral lenses.
+As we can see there is a huge difference in nature between elliptical lenses and spiral lenses, the studies in SWELLS lenses support our best-fit model to be one of the probable model of B1555+375.
+
+We understand that if a constraint from photometry can be applied on B1555+375, it will help us to claim our best-fit model to be a ’true’ model.
+However, the goal of this paper is to demonstrate and bring the attention to the community about the disc-effect.
+It is possible that the disc in B1555+375 only contributes part of flux ratio anomalies, but still, making a statement that its disc component only makes up 1% of lens mass so that all the anomalies are from substructures and applying this assumption to all other edge-on spiral lenses with anomalies is over simplifying this problem.
 

### 2016-02-10 papers/B1555_EdgeOn/B1555_letter.tex
add J0820 case into paper text & update bibfile

@@
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Studies on edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3}.}
+Studies on edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3,swells6}.}
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 have shown that the entire anomaly could be caused by the edge-on
-disc.  However, it may be possible to independently constrain the mass
+disc.
+\textbf{Some of concerns may arise that an overestimated disc component leads to a model can explain the entire anomaly.
+One is saying can a spiral lens with massive disc not distort the arc close to the disc.
+J0820+4847, one of the SWELLS samples, is an edge-on lens has an arc right across its disc.
+The SWELLS studies indicate it has 15 per cent of disc mass within the Einstein radius.
+Other SWELLS lenses have disc mass fraction range from 5 per cent to 30 per cent \citep{swells1,swells3,swells6}.
+These numbers tell that the disc in our best-fit model of B1555+375 still fits into the nature of general spiral lenses.}  However, it may be possible to independently constrain the mass
 of the disc through kinematic measurements (most likely from

### 2016-02-10 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
Updated B1555 paper referee response

--- 2016-02-10 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
@@
->The revised version of the paper still contains the unsubstantiated speculation pointed out in my previous report, with no additional supporting evidence.
+REFEREE: The revised version of the paper still contains the unsubstantiated speculation pointed out in my previous report, with no additional supporting evidence.
 I am puzzled by the authors' statement in their response that an analysis of the effects of disks on lens statistics would be beyond the scope of the paper, since this is literally the topic of the paper.
@@
 Thus, we add more description on how can we be informed by a new model of a single system in the discussion.
-That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, which has been shown in Maller et al.
+That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, as has been shown in Maller et al.
 1997, Möller et al.
 2003, and Keeton & Kochanek 1998.
-Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies is fairly small size.
+Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies is fairly small size (around 10 in all).
 Therefore, if even a few systems within the sample have edge-on discs, these are sufficient to bias the substructure analysis.
-As the current work of flux anomalous lenses are analyzed with a standard SIE mass profile, it is fair to say that the disc effect is a bias that been ignored for a long time.
-Moreover, from the high-resolution IR imaging among these flux anomalous lenses, we know that B1555 is not the only system having an edge-on disc across lensed images.
-Since this is the first time an edge-on disc been confirmed that can be accounted for, at least, part of flux anomalies, we think it is reasonable to keep our title with the wording ‘bias’ rather scope down the implication from our results.
-[But to be more conservative about our finding on disc-effect, we decide to rephrase 'bias' into 'potential bias' in the title.
-]
+As previous work on flux ratios in lensed quasar systems did its analysis with standard SIE mass profiles, it is fair to say that the disc effect is a bias that been ignored for a long time.
+Moreover, from our high-resolution IR imaging of anomalous flux-ratio lenses, we know that B1555 is not the only system that has an edge-on disc across lensed images.
+Since this is the first time that an edge-on disc has been detected that can account for at least some part of observed flux ratio anomalies, we think it is reasonable to keep our title with the wording ‘bias’ rather scope down the implication from our results.
+However, to be more conservative about our finding on discs, we decided to change 'bias' into 'potential bias' in the title.
 
-As the reason describing above, we seem to have a fundamental disagreement with the referee about the topic of the paper.
-The referee feels that it should be an analysis of the statistical effect of disks in lenses.
+As described above, we seem to have a disagreement with the referee about the topic of the paper.
+The referee feels that it should be a broad analysis of the statistical effect of disks in lenses.
 Most/all previous substructure analyses have interpreted _all_ radio-wavelength flux ratio anomalies as being due to substructure.
@@
 
->As noted in my previous report, the observational result is quite interesting and merits publication.
+---------
+
+REFEREE: As noted in my previous report, the observational result is quite interesting and merits publication.
 Since the authors were unable to support their speculations about biases in lens modeling, and have revised the text to focus more on this one specific lens system, I recommend that they amend the title and abstract to more accurately reflect the actual contents of the paper.
@@
 
-RESPONSE: We understand that if a constraint from photometry can be applied on B1555+375, it will help us to claim that the best-fit model we found is a ’true’ model.
-However, the goal of this paper is to demonstrate and bring the attention to the community about the disc-effect.
-Indeed, as the referee mentioned, the disc mass fraction in the Einstein radius can be down to  <~1%.
-This is true for massive elliptical lenses but does not hold for spiral lenses especially for lenses having high-inclined discs.
-SWELLS lenses, a group of spiral lenses selected from SDSS spectra, provide clear evidence of high fraction of stellar mass within the Einstein radius.
-Figure 5 in Brewer et al.
-2012 shows that stellar mass dominates the lens mass.
-This is quite common in the small-seperation lens systems since that the very inner region of galaxies are mostly stellar mass.
-And these systems are more likely to be spirals.
-By fitting to photometry, we conclude that B1555+375 is a late-type spiral with no appearance of bulge.
-We think it is clear that saying the disc of B1555+375 accounts for less than 1% of lens mass is unphysical base on the studies of spiral lenses.
+RESPONSE: As we mentioned in the previous revision, the fraction of mass within the Einstein ring radius that is due to the disk for the B1555 system is perfectlyy consistent with the results found in SWELLS sample of lenses.
+That reference in the text was a bit subtle, so we have made this point more explicit in the current version of the paper (and in this response to the referee).
+The SWELLS sample is a group of edge-on spiral lenses selected from SDSS spectra.
+These systems provide clear evidence of high fractions of stellar mass within the Einstein radius and, furthermore, some of the SWELLS systems also have arcs right across their edge-on discs, similar to what we see in B1555+375.
+Below we discuss some specific results from several SWELLS papers that directly address the referee's point.
 
-Moreover, by combining the information given in Treu et al.
+First, though, we provide a general argument for why finding that the edge-on disc component in B1555 contributes around 15 per cent of the Einstein ring mass is reasonable.
+We note that the B1555 is a small-separation lens system, with an Einstein ring radius of less than 0.25 arcsec.
+It has been known from the early days of lensing (e.g., Turner, Ostriker, and Gott) that spiral lenses should be more common among smaller separation systems, since they tend to have lower mass.
+Furthermore, many studies of both local galaxies and more distant lensing galaxies have shown that in the inner portions of galaxies the baryonic component is more important, with the dark matter component becoming increasingly dominant at greater galactocentric distance.
+Among these studies, Figure 6 in Brewer et al.
+2014 (Paper VI in the SWELLS series) shows that stellar mass dominates the lens mass inside the critical curves and, furthermore, this trend becomes slightly stronger for the smaller-separation systems.
+Finally, as mentioned in our first response to the referee, we have fit to the photometry of B1555+375 and found no evidence for a luminous bulge.
+Thus, the referee's expectation that <1% of the total mass within the critical curve for this system is in a disc would imply that 99% of the Einstein ring mass is in a dark-matter halo, which is not at all consistent with what is seen in other small-separation lens systems.
+
+All that being said, however, the SWELLS data do provide specific and strong evidence for many edge-on spiral systems in which the disc component makes up more than 1% of the mass within the Einstein ring radius.
+By combining the information given in Treu et al.
 2011 and Brewer et al.
-2014, the disc mass fraction of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
-Especially when we look at J0820+4847, being a good analogous system to B1555+375, we notice that it has an arc right across its edge-on disc and has 15% of disc mass fraction within the Einstein radius.
-Again, the studies on spiral galaxies support our model having ~15% of disc mass fraction.
-The cases hold for disc mass fraction <~1% is most likely massive elliptical lenses, but not edge-on spiral lenses.
+2014, the disc mass fraction measured within the critical curves of SWELLS lenses ranges from 5% to 30% under a conservative 'minimal' Chabrier ISM assumption.
+Especially when we look at SWELLS J0820+4847, a good analogy to B1555+375 with an edge-on disc and a clear arc across the disc, we find that it has a 15% disc mass fraction within the Einstein radius.
+This is very similar to our B1555 model that also has a ~15% disc mass fraction.
+Overall, we suspect that the statement from referee about "disc mass fraction <~1% within the Einstein radius" most likely holds for massive elliptical lenses but not for edge-on spiral lenses.
 
->Similarly, the penultimate sentence of the abstract is also potentially misleading.
+We understand that if a constraint from photometry can be applied on B1555+375, it will help us to put better constraints on our model.
+However, the goal of this paper is to demonstrate and bring the to the attention of the community the effects of edge-on discs.
+Please note that we are _not_ claiming that the model presented in this paper is the only correct model.
+Far from it.
+It is entirely possible that the disc in B1555+375 only contributes part of the flux ratio anomaly.
+However, even that statement is important for analyses of the current flux-ratio samples, in which substructure has previously been assumed to be the sole cause of any anomalies.
+Our view is that the attribution of at least some portion of the flux-ratio anomaly to a clearly visible disc component is at least as physically motivated as assigning the cause of the anomaly to unseen substructures.
+
+------
+
+REFEREE: Similarly, the penultimate sentence of the abstract is also potentially misleading.
 The modeling presented in this paper does not show that simple models containing disks can reproduce the observations, since those models are woefully underconstrained by the data that the authors fit.
@@
 RESPONSE: We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions.
-We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry and fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search.
+We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry to fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search.
 This reduces the number of free parameters from 13 to 9.
-The predicted image positions and flux ratios in this new model is still agree with the observations, which supports our original statements and conclusions.
+The predicted image positions and flux ratios in this new model still agree with the observations, which supports our original statements and conclusions.
 We also take off the 0.05 arcsecond prior on the centroids in the best-fit model search.

### 2016-02-11 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
update referee response due to title change

@@
 
-RESPONSE: The referee is correct to point out that our title may be misleading in implying that we intend to discuss the effects of disks on lens statistics.
-Thus, we add more description on how can we be informed by a new model of a single system in the discussion.
+RESPONSE: The referee is correct to point out that our title may be misleading in implying that we intend to analyze the effects of disks on lens statistics.
+Thus, we change our title in order to focus on the disc effect itself.
+Describing the important role in the flux ratio anomaly of B1555+375 rather than misleading readers to consider the entire flux anomalous lens samples.
+Also, we add more text in paper to how can we be informed by a new model of a single system.
 That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, as has been shown in Maller et al.
@@
 Moreover, from our high-resolution IR imaging of anomalous flux-ratio lenses, we know that B1555 is not the only system that has an edge-on disc across lensed images.
-Since this is the first time that an edge-on disc has been detected that can account for at least some part of observed flux ratio anomalies, we think it is reasonable to keep our title with the wording ‘bias’ rather scope down the implication from our results.
-However, to be more conservative about our finding on discs, we decided to change 'bias' into 'potential bias' in the title.
+Since this is the first time that an edge-on disc has been detected that can account for at least some part of observed flux ratio anomalies, we think it is reasonable to talk about this ‘potential bias’ in the discussion.
 
@@
 
-RESPONSE: We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions.
+We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions.
 We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry to fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search.
 This reduces the number of free parameters from 13 to 9.
+This is the typical number of free parameters for a standard SIE plus external shear lens model, with the replacement of exponential disc component.
 The predicted image positions and flux ratios in this new model still agree with the observations, which supports our original statements and conclusions.

### 2016-02-11 papers/B1555_EdgeOn/B1555_letter.tex
update referee response due to title change

@@
 % Keep the title short and informative.
-\title[Beware the effect of edge-on discs]{SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios}
+\title[Beware the effect of edge-on discs]{SHARP - II. Mass structure in strong lenses is not necessarily substructure: A flux ratio anomaly from an edge-on disc }
 \author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. P. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$

### 2016-02-12 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
update referee response, letter to editor

@@
 The alignment between two components without using a prior implies that this centroid prior is not necessary.
+
+Besides from the responses above, we think our work include the following new discovers hence should be published:
+1) new infrared imaging with Keck and HST that show there is a disc that directly crosses the problem images.
+2) new radio VLBA imaging that show the radio images are not point-sources as have been previously assumed by Dalal & Kochanek (2002) and others, and so will be less sensitive to substructure, that is, the demagnification will be felt less over the whole arc.
+3) new radio VLBA imaging that show image A has a smaller angular size, relative to image B, which demonstrates that there must be a perturbation of the mass model, that is, not due to extinction (seen at optical) or absorption.
+4) new estimates of the flux-ratios using the monitoring data by Koopmans et al. (2003), which was the largest source of uncertainty in the Dalal & Kochanek analysis.
+5) a new mass model that includes the disc and can reproduce the observed image positions and flux-ratios without the need for substructure.
+6) a potential bias in substructure analysis from flux ratio anomalous quasars due to the small size of the current sample.

### 2016-02-12 papers/B1555_EdgeOn/B1555_letter.tex
update referee response, letter to editor

@@
 \textbf{\citet{Maller97,Kee98, Moller03} have shown that a disc with high inclination angle can significantly affects the lensing cross-section.
-While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc is sufficient to bring a bias into the substructure analysis.
+While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc may be sufficient to bring a bias into the substructure analysis.
 Moreover, near-infrared AO imaging of
@@
 links between flux-ratio anomalies and disc components.
-This bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future.
+This potential bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future.
 Therefore, it is critical to obtain high-resolution imaging like SHARP of target lenses to detect `sharp' mass features such as edge-on disks or even massive luminous satellites.}

### 2016-02-23 papers/B1555_EdgeOn/B1555_letter.tex
Small changes to manuscript text

@@
 \textbf{We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model.
-The best-fit parameters from \citet{Marlow99} are set as the starting point of the SIE profile.
-By looking at the NICMOS F160W imaging, which has the highest signal-to-noise ratio of disc among the data, we fix the centroid position as $(-0.162, -0.206)$ , ellipticity as $e=0.83$, and position angle of $\theta=8^\circ$.
+The best-fit parameters from \citet{Marlow99} are chosen as the starting point of the SIE profile.
+We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the centroid position to $(-0.162, -0.206)$, the ellipticity to $e=0.83$, and the position angle to $\theta=8^\circ$.
 The total number of free parameters is 9.
@@
 The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+The model requires that the \textbf{ExpDisc component make up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Studies on edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent mass in the Einstein radius \citep{swells1,swells3,swells6}.}
+Investigations of edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent of the mass within the Einstein radius \citep{swells1,swells3,swells6}.}
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 perturbation in the mass model.
-\textbf{Although the constraint on disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux anomalies in B1555+375, at least, have strong link to the present of its edge-on disc.
+\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomalies in B1555+375, at least, have a strong link to the presence of its edge-on disc.
 } Such

### 2016-02-23 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
minor changes in 1st part of response

@@
 Thus, we change our title in order to focus on the disc effect itself.
-Describing the important role in the flux ratio anomaly of B1555+375 rather than misleading readers to consider the entire flux anomalous lens samples.
-Also, we add more text in paper to how can we be informed by a new model of a single system.
+Also, we add more text in paper to show how we can be informed by a new model of a single system.
 That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, as has been shown in Maller et al.

### 2016-02-23 papers/B1555_EdgeOn/B1555_letter.tex
Further update of the manuscript text

@@
 perturbation in the mass model.
-\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomalies in B1555+375, at least, have a strong link to the presence of its edge-on disc.
+\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomalies in B1555+375, at least, have a strong link to the presence of its edge-on disc.
 } Such
@@
 disc. 
-\textbf{Some of concerns may arise that an overestimated disc component leads to a model can explain the entire anomaly.
-One is saying can a spiral lens with massive disc not distort the arc close to the disc.
-J0820+4847, one of the SWELLS samples, is an edge-on lens has an arc right across its disc.
-The SWELLS studies indicate it has 15 per cent of disc mass within the Einstein radius.
-Other SWELLS lenses have disc mass fraction range from 5 per cent to 30 per cent \citep{swells1,swells3,swells6}.
-These numbers tell that the disc in our best-fit model of B1555+375 still fits into the nature of general spiral lenses.}  However, it may be possible to independently constrain the mass
+\textbf{That is not to imply this is a unique model, but rather that the
+disc component is a possible explanation of the anomaly.  We note that
+one of the SWELLS systems, J0820+4847, has an edge-on disc that directly
+crosses but does not significantly distort the arc of lensed emission in the system \citep{swells1}. The disc in this system
+has been shown to comprise 15 per cent of the mass within the Einstein
+radius, comparable to our results on B1555+375 and also fully consistent with
+the 5 to 30 per cent contributions of discs in the other lenses in the 
+SWELLS sample \citep{swells1,swells3,swells6}.}
+
+In future it may be possible to independently constrain the mass
 of the disc through kinematic measurements (most likely from
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-\textbf{\citet{Maller97,Kee98, Moller03} have shown that a disc with high inclination angle can significantly affects the lensing cross-section.
-While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc may be sufficient to bring a bias into the substructure analysis.
-Moreover, near-infrared AO imaging of
+\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral [CITE Turner, Ostriker, Gott].
+This is because \citet{Maller97}, \citet{Kee98}, and \citet{Moller03} have shown that a disc with high inclination angle can significantly affect the lensing cross-section for such systems.
+The current sample of lensed quasars with radio-wavelength flux ratio measurements is small.
+Therefore, having even a few systems with edge-on discs may be sufficient to introduce a bias into the substructure analysis.
+In fact, our near-infrared AO imaging of
 other lenses in the SHARP sample shows that B1555+375 is not the only
-system that has a significant disc component detection close to merging images among the current sample of flux ratio anomalous systems; these gravitational lenses will be investigated in future
+system that has a significant disc component that crosses the merging lensed images.  These gravitational lenses will be investigated in future
 work, but the images alone suggest that other systems may have similar

### 2016-02-23 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
changes from John [not yet finished]

--- 2016-02-11 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
@@
 Thus, we change our title in order to focus on the disc effect itself.
-Describing the important role in the flux ratio anomaly of B1555+375 rather than misleading readers to consider the entire flux anomalous lens samples.
-Also, we add more text in paper to how can we be informed by a new model of a single system.
-That being said, discs with high inclination in lens system can significantly affect the lensing cross-section, as has been shown in Maller et al.
+Also, we add more text in paper to show how we can be informed by a new model of a single system.
+That being said, discs with high inclination in lens systems can significantly affect the lensing cross-section, as has been shown in Maller et al.
 1997, Möller et al.
 2003, and Keeton & Kochanek 1998.
-Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies is fairly small size (around 10 in all).
+Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies has a fairly small size (around 10 in all).
 Therefore, if even a few systems within the sample have edge-on discs, these are sufficient to bias the substructure analysis.
-As previous work on flux ratios in lensed quasar systems did its analysis with standard SIE mass profiles, it is fair to say that the disc effect is a bias that been ignored for a long time.
-Moreover, from our high-resolution IR imaging of anomalous flux-ratio lenses, we know that B1555 is not the only system that has an edge-on disc across lensed images.
-Since this is the first time that an edge-on disc has been detected that can account for at least some part of observed flux ratio anomalies, we think it is reasonable to talk about this ‘potential bias’ in the discussion.
+As previous work on the flux ratios in lensed quasar systems used standard SIE mass profiles, it is fair to say that the disc effect is a bias that has been ignored for a long time.
+Moreover, from our high-resolution IR imaging of anomalous flux-ratio lenses, we know that B1555 is not the only system that has an edge-on disc across the problematic lensed images.
+Since this is the first time that an edge-on disc has been detected that can account for at least some part of an observed flux ratio anomaly, we think it is reasonable to talk about this ‘potential bias’ in the discussion.
 
 As described above, we seem to have a disagreement with the referee about the topic of the paper.
-The referee feels that it should be a broad analysis of the statistical effect of disks in lenses.
+The referee feels that it should be a broad analysis of the statistical effect of discs in lenses.
 Most/all previous substructure analyses have interpreted _all_ radio-wavelength flux ratio anomalies as being due to substructure.
@@
 
-RESPONSE: As we mentioned in the previous revision, the fraction of mass within the Einstein ring radius that is due to the disk for the B1555 system is perfectlyy consistent with the results found in SWELLS sample of lenses.
-That reference in the text was a bit subtle, so we have made this point more explicit in the current version of the paper (and in this response to the referee).
+RESPONSE: As we mentioned in the previous revision, the fraction of mass within the Einstein ring radius that is due to the disc for the B1555 system is perfectly consistent with the results found in the SWELLS sample of lenses.
+That reference in the text was a bit subtle, so we have made this point more explicit in the current version of the paper.
 The SWELLS sample is a group of edge-on spiral lenses selected from SDSS spectra.
@@
 First, though, we provide a general argument for why finding that the edge-on disc component in B1555 contributes around 15 per cent of the Einstein ring mass is reasonable.
-We note that the B1555 is a small-separation lens system, with an Einstein ring radius of less than 0.25 arcsec.
-It has been known from the early days of lensing (e.g., Turner, Ostriker, and Gott) that spiral lenses should be more common among smaller separation systems, since they tend to have lower mass.
+We note that B1555 is a small-separation lens system, with an Einstein ring radius of less than 0.25 arcsec.
+It has been known from the early days of lensing (e.g., Turner, Ostriker, and Gott) that spiral lenses should be more common among smaller separation systems, since they tend to have lower mass (and has been seen in observations, e.g.
+the smallest separation lens B0218+357).
 Furthermore, many studies of both local galaxies and more distant lensing galaxies have shown that in the inner portions of galaxies the baryonic component is more important, with the dark matter component becoming increasingly dominant at greater galactocentric distance.
@@
 This is very similar to our B1555 model that also has a ~15% disc mass fraction.
-Overall, we suspect that the statement from referee about "disc mass fraction <~1% within the Einstein radius" most likely holds for massive elliptical lenses but not for edge-on spiral lenses.
+Overall, we suspect that the suggested "disc mass fraction <~1% within the Einstein radius" most likely holds for massive elliptical lenses but not for edge-on spiral lenses.
 
 We understand that if a constraint from photometry can be applied on B1555+375, it will help us to put better constraints on our model.
-However, the goal of this paper is to demonstrate and bring the to the attention of the community the effects of edge-on discs.
+However, the goal of this paper is to demonstrate and bring to the attention of the community the effects of edge-on discs.
 Please note that we are _not_ claiming that the model presented in this paper is the only correct model.
@@
 Our view is that the attribution of at least some portion of the flux-ratio anomaly to a clearly visible disc component is at least as physically motivated as assigning the cause of the anomaly to unseen substructures.
+
+In addition, the suggested title by the referee doesn’t fully encompass the work that is contained in the paper, which is significantly more than the detection of a disc. For example, we present
+1) new infrared imaging with Keck and HST that show there is a disc that directly crosses the problem images;
+2) new radio VLBA imaging that show image A has a smaller angular size, relative to image B, which demonstrates that there must be a perturbation of the mass model, that is, not due to extinction (seen at optical) or absorption;
+3) new radio VLBA imaging that show the radio images are not point-sources as have been previously assumed by Dalal & Kochanek (2002) and others, and so will be less sensitive to substructure, that is, the demagnification will be felt less over the whole arc;
+4) new estimates of the flux-ratios using the monitoring data by Koopmans et al. (2003), which was the largest source of uncertainty in the Dalal & Kochanek analysis;
+5) a new mass model that includes the disc and can reproduce the observed image positions and flux-ratios without the need for substructure;
+6) a potential bias in substructure analysis from flux ratio anomalous quasars due to the small size of the current sample.
+
+Our new title reflects these findings.
 
@@
 We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions.
-We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry to fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search.
+We therefore follow the approach in the studies of B1600 and B1933, two other edge-on disc lenses, looking at the photometry to fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search.
 This reduces the number of free parameters from 13 to 9.
-This is the typical number of free parameters for a standard SIE plus external shear lens model, with the replacement of exponential disc component.
+This is the typical number of free parameters for a standard SIE plus external shear lens model, with the replacement of an exponential disc component.
 The predicted image positions and flux ratios in this new model still agree with the observations, which supports our original statements and conclusions.

### 2016-02-23 papers/B1555_EdgeOn/B1555_letter.tex
changes from John [not yet finished]

@@
 % Keep the title short and informative.
-\title[Beware the effect of edge-on discs]{SHARP - II. Mass structure in strong lenses is not necessarily substructure: A flux ratio anomaly from an edge-on disc }
+\title[Beware the effect of edge-on discs]{SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc }
 \author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. P. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
@@
 In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of clumpy substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered.
-To this end, we use new infrared imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][]{mckean07,lagattuta10,SHARP12, V12}.
-The main goal of SHARP is to investigate galaxy structure and other astrophysical topics through the re-observation of known gravitational lens systems at high angular resolution, making use of observations with (1) adaptive optics (AO) on the W.
+To this end, we use new infrared \textbf{and radio interferometric} imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][Chen et al.
+2016 submitted]{mckean07,lagattuta10,SHARP12, V12}.
+The main goal of SHARP is to investigate galaxy structure and other astrophysical topics through the re-observation of known gravitational lens systems at high angular resolution, making use of observations with adaptive optics (AO) on the W.
 M.
-Keck telescope, (2) the {\it Hubble Space Telescope (HST)}, and (3) large radio and mm interferometric arrays.
+Keck telescope, the {\it Hubble Space Telescope (HST)}, and  large radio and mm interferometric arrays.
 
@@
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
-Therefore, the lack of emission from these images is likely due to dust extinction and additional demagnification due to lensing.
+Therefore, the lack of emission from these \textbf{rest-frame optical} images is likely due to dust extinction and additional demagnification due to lensing.
 
@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of the the are SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+The free parameters of are SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 The low signal-to-noise ratio in the ring away from the lensed AGN and
-the strong extinction in lens galaxy prevent us from using this
-approach.  What are, thus, needed are significantly deeper
-observations at a higher bandwidth with very long baseline
+the strong extinction in the lens galaxy prevent us from using this
+approach.  Significantly deeper
+observations are needed at a higher bandwidth with very long baseline
 interferometric arrays, which can test more complex models in the
@@
 The best-fit parameters from \citet{Marlow99} are chosen as the starting point of the SIE profile.
-We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the centroid position to $(-0.162, -0.206)$, the ellipticity to $e=0.83$, and the position angle to $\theta=8^\circ$.
+We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the centroid position relative to image A to $(-0.162, -0.206)$, the ellipticity to $e=0.83$, and the position angle to $\theta=8^\circ$.
 The total number of free parameters is 9.
-After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain uncertainties.}
+After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain the uncertainties.}
 
-The best-fit model parameters and 68\% CL errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
+The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
 Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
@@
 The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B.
-The remaining differences in fluxes may due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component make up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model.
+The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Investigations of edge-on spiral lenses, for example the SWELLS survey, show that the disc can contribute more than 20 per cent of the mass within the Einstein radius \citep{swells1,swells3,swells6}.}
+Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc can contribute more than 20 per cent of the mass within the Einstein radius \citep{swells1,swells3,swells6}.}
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 \caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here).
-The positions are measured in arcsec, relative to the radio position of image A.
+The positions are measured in arcsec, relative to the MERLIN radio position of image A.
 The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north.
@@
 perturbation in the mass model.
-\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomalies in B1555+375, at least, have a strong link to the presence of its edge-on disc.
+\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomaly in B1555+375 has a strong link to the presence of an edge-on disc.
 } Such
@@
 edge-on discs, in the mass models, we are still limited in our
-interpretation if we can not determine how much of the anomalies are
+interpretation if we can not determine how much of the anomaly are
 due to these components. For our current analysis of B1555+375, we
@@
 disc component is a possible explanation of the anomaly.  We note that
-one of the SWELLS systems, J0820+4847, has an edge-on disc that directly
-crosses but does not significantly distort the arc of lensed emission in the system \citep{swells1}. The disc in this system
+the SWELLS system J0820+4847 has an edge-on disc that directly
+crosses but does not significantly distort the lensed arc emission in the system \citep{swells1}. The disc in this system
 has been shown to comprise 15 per cent of the mass within the Einstein
-radius, comparable to our results on B1555+375 and also fully consistent with
-the 5 to 30 per cent contributions of discs in the other lenses in the 
+radius, comparable to our results on B1555+375 and is also fully consistent with
+the 5 to 30 per cent contribution of discs in the other lenses in the 
 SWELLS sample \citep{swells1,swells3,swells6}.}
@@
 \textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral [CITE Turner, Ostriker, Gott].
-This is because \citet{Maller97}, \citet{Kee98}, and \citet{Moller03} have shown that a disc with high inclination angle can significantly affect the lensing cross-section for such systems.
+This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97}, \citet{Kee98}, and \citet{Moller03}.
 The current sample of lensed quasars with radio-wavelength flux ratio measurements is small.
@@
 other lenses in the SHARP sample shows that B1555+375 is not the only
-system that has a significant disc component that crosses the merging lensed images.  These gravitational lenses will be investigated in future
-work, but the images alone suggest that other systems may have similar
-links between flux-ratio anomalies and disc components.
-This potential bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future.
-Therefore, it is critical to obtain high-resolution imaging like SHARP of target lenses to detect `sharp' mass features such as edge-on disks or even massive luminous satellites.}
+system that has a significant disc component that crosses the merging lensed images (Fassnacht et al., in prep.).  
+These gravitational lenses will be investigated in future
+work, but the images alone suggest that other systems may have a similar
+link between flux-ratio anomalies and disc components.
+This potential bias brought by edge-on discs may be avoided by post-selection as  sample sizes grow in the future.
+Therefore, it is critical to obtain high-resolution imaging lenses to detect additional mass features such as edge-on discs or even massive luminous satellites.}
 % A number of lens systems with significant disc components arealready known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}. 
- This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
+ This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, \textit{Euclid}, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
   be measured using narrow lines \citep[e.g.][]{N14}.

### 2016-02-25 papers/B1555_EdgeOn/B1555_letter.tex
update ref & take out J0820 in text

@@
 \textbf{That is not to imply this is a unique model, but rather that the
-disc component is a possible explanation of the anomaly.  We note that
-the SWELLS system J0820+4847 has an edge-on disc that directly
-crosses but does not significantly distort the lensed arc emission in the system \citep{swells1}. The disc in this system
-has been shown to comprise 15 per cent of the mass within the Einstein
-radius, comparable to our results on B1555+375 and is also fully consistent with
-the 5 to 30 per cent contribution of discs in the other lenses in the 
-SWELLS sample \citep{swells1,swells3,swells6}.}
+disc component is a possible explanation of the anomaly. }
+ %We note that the SWELLS system J0820+4847 has an edge-on disc that directly crosses but does not significantly distort the lensed arc emission in the system \citep{swells1}.
+The disc in this system has been shown to comprise 15 per cent of the mass within the Einstein radius, comparable to our results on B1555+375 and is also fully consistent with the 5 to 30 per cent contribution of discs in the other lenses in the  SWELLS sample \citep{swells1,swells3,swells6}.}
 
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral [CITE Turner, Ostriker, Gott].
+\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep{Turner84}.
 This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97}, \citet{Kee98}, and \citet{Moller03}.

### 2016-02-26 papers/B1555_EdgeOn/B1555_letter.tex
Tiny changes to manuscript (not done editing yet)

@@
 \caption{A summary of the observational constraints and the predicted lens-model parameters.
-The lensed image positions in the radio \citep{Marlow99} (in arcsec) and average flux ratios \citep{K03} are respect to image A.
+The lensed image positions in the radio \citep{Marlow99} (in arcsec) and average flux ratios \citep{K03} are with respect to image A.
 Uncertainties in the position measurements for images A, B and C are $0.001$~arcsec and for image D are $0.006$~arcsec.}
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep{Turner84}.
-This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97}, \citet{Kee98}, and \citet{Moller03}.
+\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep[e.g.,][]{Turner84}.
+This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97,Kee98,Moller03}.
 The current sample of lensed quasars with radio-wavelength flux ratio measurements is small.

### 2016-02-29 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt
Small editing changes to B1555 manuscript

@@
 2003, and Keeton & Kochanek 1998.
-Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies has a fairly small size (around 10 in all).
+Although the fraction of high-inclination spiral lenses may not be high in the general population, the current sample of lensed quasars that have flux-ratio anomalies has a fairly small size (with fewer than 10 systems in all).
 Therefore, if even a few systems within the sample have edge-on discs, these are sufficient to bias the substructure analysis.
@@
 Moreover, from our high-resolution IR imaging of anomalous flux-ratio lenses, we know that B1555 is not the only system that has an edge-on disc across the problematic lensed images.
-Since this is the first time that an edge-on disc has been detected that can account for at least some part of an observed flux ratio anomaly, we think it is reasonable to talk about this ‘potential bias’ in the discussion.
+Since this is the first time that an edge-on disc has been detected that can account for at least some part of an observed flux ratio anomaly, we think it is reasonable to talk about this 'potential bias' in the discussion.
 
@@
 the smallest separation lens B0218+357).
-Furthermore, many studies of both local galaxies and more distant lensing galaxies have shown that in the inner portions of galaxies the baryonic component is more important, with the dark matter component becoming increasingly dominant at greater galactocentric distance.
+Furthermore, many studies of both local galaxies and more distant lensing galaxies have shown that in the innermost portions of galaxies the baryonic component is more important, with the dark matter component becoming increasingly dominant at greater galactocentric distance.
 Among these studies, Figure 6 in Brewer et al.
@@
 It is entirely possible that the disc in B1555+375 only contributes part of the flux ratio anomaly.
-However, even that statement is important for analyses of the current flux-ratio samples, in which substructure has previously been assumed to be the sole cause of any anomalies.
+However, even that statement is important for analyses of the current flux-ratio samples, in which substructure has previously been assumed to be the _sole_ cause of any anomalies.
 Our view is that the attribution of at least some portion of the flux-ratio anomaly to a clearly visible disc component is at least as physically motivated as assigning the cause of the anomaly to unseen substructures.
 
-In addition, the suggested title by the referee doesn’t fully encompass the work that is contained in the paper, which is significantly more than the detection of a disc. For example, we present
+In addition, the suggested title by the referee doesn't fully encompass the work that is contained in the paper, which is significantly more than the detection of a disc. For example, we present
 1) new infrared imaging with Keck and HST that show there is a disc that directly crosses the problem images;

### 2016-02-29 papers/B1555_EdgeOn/B1555_letter.tex
Small editing changes to B1555 manuscript

@@
 Our high-resolution near-infrared Keck~II adaptive optics imaging and archival {\it Hubble Space Telescope} data reveal the lensing galaxy in this system to have  a clear edge-on disc component that crosses directly over the pair of images that exhibit the flux-ratio anomaly.
-We find simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
+We find that simple models that include the disc can reproduce the cm-wavelength flux-ratio anomaly without requiring additional dark matter substructure.
 Although further studies are required, our results suggest the assumption that all flux-ratio anomalies are due to a population of dark matter sub-haloes may be incorrect, and analyses that do not account for the full complexity of the lens macro-model may overestimate the substructure mass fraction in massive lensing galaxies.
@@
 2016 submitted]{mckean07,lagattuta10,SHARP12, V12}.
-The main goal of SHARP is to investigate galaxy structure and other astrophysical topics through the re-observation of known gravitational lens systems at high angular resolution, making use of observations with adaptive optics (AO) on the W.
+The main goal of SHARP is to investigate galaxy structure and other astrophysical topics through the re-observation of known gravitational lens systems at high angular resolution, making use of observations with (1) adaptive optics (AO) on the W.
 M.
-Keck telescope, the {\it Hubble Space Telescope (HST)}, and  large radio and mm interferometric arrays.
+Keck telescope, (2) the {\it Hubble Space Telescope (HST)}, and (3) large radio and mm interferometric arrays.
 
@@
 In total, there are 11 constraints to the mass model provided by the observational data.
-As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear (SIE; 7 free parameters) model of \citet{Marlow99} to check the performance of a simple lensing potential.
+As a first trial of modelling, we re-create the singular isothermal ellipsoid without external shear model (SIE; 7 free parameters) of \citet{Marlow99} to check the performance of a simple lensing potential.
 Consistent with previous studies \citep{Marlow99,Xu15}, a single elliptical potential model cannot reproduce the observed flux ratios in B1555+375 (see Table~\ref{tab:results}).
@@
 We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of are SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 the strong extinction in the lens galaxy prevent us from using this
-approach.  Significantly deeper
+gravitational imaging approach.  Significantly deeper
 observations are needed at a higher bandwidth with very long baseline
@@
 The best-fit parameters from \citet{Marlow99} are chosen as the starting point of the SIE profile.
-We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the centroid position relative to image A to $(-0.162, -0.206)$, the ellipticity to $e=0.83$, and the position angle to $\theta=8^\circ$.
+We have used the NICMOS F160W imaging, in which the disc component has the highest signal-to-noise ratio amongst our data, to fix the disc centroid position relative to image A to $(-0.162, -0.206)$, its ellipticity to $e=0.83$, and its position angle to $\theta=8^\circ$.
 The total number of free parameters is 9.
@@
 perturbation in the mass model.
-\textbf{Although a constraint on the disc mass from photometry is currently not avaliable due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomaly in B1555+375 has a strong link to the presence of an edge-on disc.
+\textbf{Although a constraint on the disc mass from photometry is currently not available due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomaly in B1555+375 has a strong link to the presence of an edge-on disc.
 } Such
@@
 link between flux-ratio anomalies and disc components.
-This potential bias brought by edge-on discs may be avoided by post-selection as  sample sizes grow in the future.
+This potential bias introduced by edge-on discs may be avoided by post-selection as  sample sizes grow in the future.
 Therefore, it is critical to obtain high-resolution imaging lenses to detect additional mass features such as edge-on discs or even massive luminous satellites.}

### 2016-02-29 papers/B1555_EdgeOn/B1555_letter.tex
update paper text [Leon's comments]

@@
 The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$).
+The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since the model parameters are scale free).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc can contribute more than 20 per cent of the mass within the Einstein radius \citep{swells1,swells3,swells6}.}
+Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.}
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 \textbf{That is not to imply this is a unique model, but rather that the
-disc component is a possible explanation of the anomaly. }
+disc component is a plausible explanation of the anomaly. }
  %We note that the SWELLS system J0820+4847 has an edge-on disc that directly crosses but does not significantly distort the lensed arc emission in the system \citep{swells1}.
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep[e.g.,][]{Turner84}.
+\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep[e.g.,][]{Turner84, F92}.
 This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97,Kee98,Moller03}.

### 2016-02-29 python/Substructure/NFWprofile.py

@@ -1,0 +1,50 @@
+
+import numpy as np
+import DistanceTool as distance
+
+"""This function compute scaling radius of a NFW halo from velocity dispersion"""
+""" Output is in arcsec """
+
+def scaleR(lenspara):
+
+## parameters
+	q,b = lenspara.q, lenspara.b
+
+	zl,zs =lenspara.zl, lenspara.zs 
+
+	c = 3e8 # m/s
+	G = 6.67e-11 # m^3/kg/s^2
+
+## cosmology parameter (cosmopara class)
+	class cosmopara:
+		OM = 0.27
+		h = 0.68
+
+## velocity dispersion
+
+	Ds = distance.angular_distance(cosmopara, zs)
+	Dl = distance.angular_distance(cosmopara, zl)
+	Dls = Ds - Dl
+
+	b = np.radians(b/3600)
+
+	sig = b * np.sqrt(q)/(4*np.pi)*(Ds/Dls)*c**2
+	sig = np.sqrt(sig)
+
+## M200, c200 & scale length
+
+	Hz = 100*cosmopara.h*distance.Ez(cosmopara,zl) # km/s/Mpc
+	Hz = Hz*1e3/3.08e22 # s-1
+
+	M_200 = sig**3*(G/Hz**2)**(0.5)*(2/G)**(3./2.) # kg
+	M_200_sun = M_200/2e30 # M_sun
+
+	c_200 = 5.71*(M_200_sun/2e12*cosmopara.h)**(-0.084)*(1+zl)**(-0.47) # no unit
+
+	rho_c = 3*Hz**2/(8*np.pi*G) # kg/m^3
+
+	rs = (3*M_200/8/np.pi/rho_c/c_200**3)**(1.0/3.0) # m * h^-1
+	rs = rs/3.08e22/cosmopara.h/100 # convert to Mpc
+	rs = np.degrees(rs/Dl)*3600 # arcsec 
+
+	return rs

### 2016-02-29 python/Substructure/ScalingR.py

@@ -1,57 +1,0 @@
-"""This code compute scaling radius of a NFW halo from velocity dispersion"""
-
-import numpy as np
-import AngularDistance as distance
-
-## parameters
-q=0.3
-b=0.5 # arcsec
-
-zl=0.4
-zs=1.3
-
-c = 3e8 # m/s
-G = 6.67e-11 # m^3/kg/s^2
-
-
-## cosmology parameter (cosmopara class)
-class cosmopara:
-	OM = 0.27
-	h = 0.68
-
-## velocity dispersion
-
-Ds = distance.angular_distance(cosmopara, zs)
-Dl = distance.angular_distance(cosmopara, zl)
-Dls = Ds - Dl
-
-b = np.radians(b/3600)
-
-sig = b * np.sqrt(q)/(4*np.pi)*(Ds/Dls)*c**2
-sig = np.sqrt(sig)
-
-## M200, c200 & scale length
-
-Hz = 100*cosmopara.h*distance.Ez(cosmopara,zl) # km/s/Mpc
-Hz = Hz*1e3/3.08e22 # s-1
-#print Hz
-#Hz = distance.Ez(cosmopara,zl) # h
-
-#M_200 = sig**3*(G/100/Hz**2)**(0.5)*(2/G)**(3/2) # kg
-M_200 = sig**3*(G/Hz**2)**(0.5)*(2/G)**(3./2.) # kg
-M_200_sun = M_200/2e30 # M_sun
-
-print M_200_sun
-
-c_200 = 5.71*(M_200_sun/2e12*cosmopara.h)**(-0.084)*(1+zl)**(-0.47) # no unit
-
-print c_200
-
-rho_c = 3*Hz**2/(8*np.pi*G) # kg/m^3
-
-rs = (3*M_200/8/np.pi/rho_c/c_200**3)**(1.0/3.0) # m * h^-1
-rs = rs/3.08e22/cosmopara.h/100 # convert to Mpc
-print rs
-rs = np.degrees(rs/Dl)*3600 # arcsec 
-
-print rs

### 2016-02-29 python/Substructure/spatial_dist.py

@@ -1,0 +1,64 @@
+""" This code test different profiles in 2D projected position """
+
+import numpy as np
+import NFWprofile as NFW
+import scipy.stats
+
+import matplotlib.pyplot as plt
+
+## lenspara
+
+class lenspara:
+	q=0.3
+	b=0.5 # arcsec
+
+	zl=0.4
+	zs=1.3
+
+##------------
+
+rs = NFW.scaleR(lenspara)
+print rs
+'''
+""" NFW distirbution class """
+class NFW_norm(scipy.stats.rv_continuous):
+	def _pdf(self,r):
+		x = r/rs
+		return 1.0/x/(1+x)**2
+		#return x
+
+NFW_prob = NFW_norm(a=0,b=np.Inf,name = 'NFW_norm')
+
+print NFW_prob.a, NFW_prob.b
+check = NFW_prob.rvs(size=4)*10*rs
+
+print check
+
+#plt.hist(check)
+#plt.show()
+'''
+
+# core radius
+rc = 0.0 # arcsec
+
+def NFW_profile(r):
+	x = r/rs
+	xc = rc/rs
+	return 1.0/(x+xc)/(1+x)**2
+
+
+x = np.random.rand(500000)*10*rs
+check = NFW_profile(x)
+plt.hist(check,bins = np.linspace(0,19,2000))
+plt.xlim(0.1,1.0)
+plt.ylim(0,2000)
+plt.show()
+
+'''
+
+x = np.linspace(0,10*rs,10000)
+y = NFW_profile(x)
+
+plt.loglog(x,y)
+plt.show()
+'''

### 2016-02-29 papers/B1555_EdgeOn/Resubmission_v2/B1555_EdgeOn.tex
update for manuscript change

--- 2016-02-29 papers/B1555_EdgeOn/B1555_letter.tex
@@
 The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since the model parameters are scale free).
+The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.

### 2016-03-13 papers/B1555_EdgeOn/B1555_letter.tex
enclose_mass [unit check] half way

@@
 \hline
-Image	&\multicolumn{3}{c}{Observed MERLIN} 	 	& \multicolumn{4}{c}{Model-Predicted}\\
-		&\multicolumn{3}{c}{5 GHz}		& & & {SIE+ExpDisc} & SIE-only\\
+Image	&\multicolumn{3}{c}{Observed} 	 	& \multicolumn{4}{c}{Model-Predicted}\\
+		&\multicolumn{3}{c}{MERLIN 5 GHz}		& & & {SIE+ExpDisc} & SIE-only\\
 		&East &North & Flux ratio &East 	&North & Flux ratio &Flux ratio\\ 
@@
 The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north.
-The Einstein radius $b$ and disc scale radius are measured in arcsec.}
+The Einstein radius $b$ and disc scale radius ($R_s$) are measured in arcsec.}
 \begin{tabular}{ccc}

### 2016-03-13 papers/B1555_EdgeOn/arXiv_v2/B1555_letter.tex
enclose_mass [unit check] half way

--- 2016-03-13 papers/B1555_EdgeOn/B1555_letter.tex
@@
 In this letter, we explore the idea that not all flux-ratio anomalies are due to the presence of clumpy substructure, but that some originate from more complex lens galaxy mass distributions than have initially been considered.
-To this end, we use new infrared \textbf{and radio interferometric} imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][Chen et al.
+To this end, we use new infrared and radio interferometric imaging data from the Strong lensing at High Angular Resolution Programme \citep[SHARP;][Chen et al.
 2016 submitted]{mckean07,lagattuta10,SHARP12, V12}.
@@
 We note that the position angle of the lensing galaxy is such that the disc emission lies close to the lensed images B and D.
-Therefore, the lack of emission from these \textbf{rest-frame optical} images is likely due to dust extinction and additional demagnification due to lensing.
+Therefore, the lack of emission from these rest-frame optical images is likely due to dust extinction and additional demagnification due to lensing.
 
@@
 
-\textbf{We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model.
+We use {\sc gravlens} to obtain the best-fit SIE+ExpDisc lens model.
 The best-fit parameters from \citet{Marlow99} are chosen as the starting point of the SIE profile.
@@
 The total number of free parameters is 9.
-After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain the uncertainties.}
+After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain the uncertainties.
 
@@
 The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).
+The model requires that the ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.}
+Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 perturbation in the mass model.
-\textbf{Although a constraint on the disc mass from photometry is currently not available due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomaly in B1555+375 has a strong link to the presence of an edge-on disc.
-} Such
+Although a constraint on the disc mass from photometry is currently not available due to the low signal-to-noise ratio in the AO imaging and the lack of redshift information, our model indicates that the flux-ratio anomaly in B1555+375 has a strong link to the presence of an edge-on disc.
+Such
 high-order deviations from a smooth mass distribution have already
@@
 disc. 
-\textbf{That is not to imply this is a unique model, but rather that the
-disc component is a plausible explanation of the anomaly. }
+That is not to imply this is a unique model, but rather that the
+disc component is a plausible explanation of the anomaly. 
  %We note that the SWELLS system J0820+4847 has an edge-on disc that directly crosses but does not significantly distort the lensed arc emission in the system \citep{swells1}.
@@
 Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems.
-\textbf{Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep[e.g.,][]{Turner84, F92}.
+Special care may be needed for small-separation lens systems, in which the lensing galaxy is likely to be a spiral \citep[e.g.,][]{Turner84, F92}.
 This is because a disc with a high inclination angle can significantly affect the lensing cross-section for such systems \citep{Maller97,Kee98,Moller03}.
@@
 This potential bias introduced by edge-on discs may be avoided by post-selection as  sample sizes grow in the future.
-Therefore, it is critical to obtain high-resolution imaging lenses to detect additional mass features such as edge-on discs or even massive luminous satellites.}
+Therefore, it is critical to obtain high-resolution imaging lenses to detect additional mass features such as edge-on discs or even massive luminous satellites.
 % A number of lens systems with significant disc components arealready known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}. 

### 2016-03-13 python/Substructure/DistanceTool.py

@@ -50,7 +50,12 @@ def critical_density(cospara, lenspara):
 	Dls = Ds - Dl
 
 	Sigma_c = c**2/(4.0*np.pi*G)*Ds/(Dl*Dls) # kg/Mpc^2
-	Sigma_c = Sigma_c/2e30#/h # h M_sun/Mpc^2
+	Sigma_c = Sigma_c/2e30 # h M_sun/Mpc^2
 
 	return Sigma_c
 
+def arcs2meter(arcs,z):
+
+	meter = np.radians(arcs/3600.)*angular_distance(z)*3.08e22
+
+	return meter

### 2016-03-13 python/Substructure/NFWprofile.py

@@ -30,10 +30,12 @@ def scaleR(cosmopara,lenspara,M_200,c_200):
 	rho_c = 3*Hz**2/(8*np.pi*G) # kg/m^3
 
 	rs = (3*M_200/8/np.pi/rho_c/c_200**3)**(1.0/3.0) # m * h^-1
+	rs_m = rs/cosmopara.h # m
+
 	rs = rs/3.08e22/cosmopara.h/100 # convert to Mpc
 	rs = np.degrees(rs/Dl)*3600 # arcsec 
 
-	return rs
+	return np.array([rs,rs_m])
 
 """ velocity dispersion of lens [m/s] """
 
@@ -72,12 +74,11 @@ def M200(cosmopara,lenspara,sig):
 
 	return M_200
 
-def c200(cosmopara,lenspara,M_200):
+def c200(h,zl,M_200):
 
-	M_200_sun = M_200/2e30 # M_sun
-	zl = lenspara.zl
+	#M_200_sun = M_200/2e30 # M_sun
 
-	c_200 = 5.71*(M_200_sun/2e12*cosmopara.h)**(-0.084)*(1+zl)**(-0.47) # no unit
+	c_200 = 5.71*(M_200/2e12*h)**(-0.084)*(1+zl)**(-0.47) # no unit
 
 	return c_200
 
@@ -123,16 +124,24 @@ def inverse_cdf(r,rs,r_end):
 def set_halopara(cosmopara,lenspara):
 
 	zl,zs = lenspara.zl, lenspara.zs
-	print zl,zs
 	
+	''' expand a parameter to array contains 2 forms of units '''
 	class halopara:
-		sig = velocity_dispersion(cosmopara,lenspara)
-		M_200 = M200(cosmopara,lenspara,sig)
-		c_200 = c200(cosmopara,lenspara,M_200)
-		rs = scaleR(cosmopara,lenspara,M_200,c_200)
-		r_200 = rs*c_200
+		sig = velocity_dispersion(cosmopara,lenspara) # m/s
+		
+		M_200 = np.array([M200(cosmopara,lenspara,sig),0.]) 
+		M_200 = np.array([M_200[0],M_200[0]/2e30])# [kg, M_sun]
+		
+		c_200 = c200(cosmopara.h,lenspara.zl,M_200[1]) # no unit
+
+		rs = scaleR(cosmopara,lenspara,M_200[0],c_200) # [arc sec, m]
+
[…]

### 2016-03-13 python/Substructure/spatial_dist.py

@@ -35,6 +35,8 @@ x_lim, y_lim = lenspara.xc+np.array([-2.0*lenspara.b,2.0*lenspara.b]), lenspara.
 
 #rs = NFW.scaleR(cosmopara,lenspara)
 '''use set_halopara to replace'''
+halopara = NFW.set_halopara(cosmopara,lenspara)
+rs = halopara.rs
 r_end = 100*lenspara.b
 
 ## -----substructure setting---------##
@@ -47,10 +49,9 @@ f_sub = 0.01 # substructure mass fraction
 def NFW_2d(n_draw):
 #n_draw = 100000
 
-	uni_r = np.random.uniform(n_draw)
+	uni_r = np.random.rand(n_draw)
 
 	r_d = NFW.inverse_cdf(uni_r,rs,r_end)
-
 
 ## 3D->2D projection
 
@@ -70,7 +71,7 @@ def NFW_2d(n_draw):
 	x_d = lenspara.xc+rp_d*np.cos(phi_d)
 	y_d = lenspara.yc+rp_d*np.sin(phi_d)
 
-	return x_d,y_d,rp_d
+	return x_d,y_d,rp_d,r_d
 
 
 def uniform_2d(n_draw):
@@ -81,7 +82,9 @@ def uniform_2d(n_draw):
 
 	return x,y,r
 
-def subhalo_lens(n_draw):
+def subhalo_lens(r_d):
+
+	n_draw = len(r_d)
 
 	Sig_c = distance.critical_density(cosmopara,lenspara) # h M_sun/Mpc^2
 	print Sig_c
@@ -96,18 +99,15 @@ def subhalo_lens(n_draw):
 
 	## b_sub (arc sec) & truncation radius
 
-	b_com4 = (m_d/(np.pi*Sig_c))**2 # b_sub^3*b [Mpc^4]
-	b_com4 = b_com4/Dl**4 # rad^4
-	b_sub3 = b_com4/lenspara.b # b_sub^3 [rad^3]
+	r_t = r_d*(m_d/NFW.enclose_mass(r_d,lenspara.zl,halopara.rho_s))**(1.0/3.0) # arc sec
 
-	b_sub = (b_sub3)**(1.0/3.0) # rad
-	b_sub = np.degrees(b_sub)*3600 # arc sec
-
-	r_t = np.sqrt(b_sub*lenspara.b) # arc sec
-
[…]

### 2016-06-21 python/Substructure/dan_crosscheck.py
change legend setting in plot_fns_b1555.py

@@ -4,16 +4,17 @@ import matplotlib.pyplot as plt
 basePath = '../../data/illustris_1'
 ssNumber = '99'
 
-catalog = basePath+'/Galaxy_Lens'+ssNumber+'_str.dat'
+catalog = basePath+'/Galaxy_Lens'+ssNumber+'_sig.dat'
 #GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 Mass = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
 str_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
-morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[12])
+sigma = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
+morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[13])
 
-Re = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[6,7,8])
-DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[9,10,11])
+Re = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[7,8,9])
+DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[10,11,12])
 
-theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3,4,5])
+theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4,5,6])
 
 # reduce to 1d [x...y...z...]
 Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta) 
@@ -22,6 +23,7 @@ Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta)
 
 Mass = np.array([Mass,Mass,Mass]).flatten()
 str_ms = np.array([str_ms,str_ms,str_ms]).flatten()
+sigma = np.array([sigma,sigma,sigma]).flatten()
 #print Mass
 
 ## Dandan's pick
@@ -38,6 +40,7 @@ DMfrac_dan = DMfrac[cri]
 theta_dan = theta[cri]
 Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
+sig_dan = sigma[cri]
 
 # Edge-on/Face-on
[…]

### 2016-06-21 python/Substructure/galaxy_cat.py

@@ -37,6 +37,12 @@ GroupCM = GroupCM[GroupFirstSub,:]
 
 star_ms = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloMassType'])[:,4]*1e10/cosmopara.h
 star_ms = star_ms[GroupFirstSub]
+
+sigma = groupcat.loadSubhalos(basePath,ssNumber,fields = ['SubhaloVelDisp'])
+sigma = sigma[GroupFirstSub]
+
+sigma_h = 370.
+sigma_l = 130.
 '''
 #photometry
 V_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,2]
@@ -53,25 +59,28 @@ K_mag = K_mag+5.*(np.log10(DL)-1)
 ## rewrite this part!!! [str mass]
 ## use group mass as galaxy cretria 
 ## here!!
-GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str = [],[],[],[]
+GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig = [],[],[],[],[]
 
-for i in range(star_ms.size):
-	if star_ms[i]<mhigh and star_ms[i]>mlow:
+for i in range(sigma.size):
+	if sigma[i]<sigma_h and sigma[i]>sigma_l:
+		#print sigma[i]
 		GalaxyID.append(GroupFirstSub[i])
 		GalaxyPos.append(GroupCM[i,:])
 		Galaxy_ms.append(GalaxyMass[i])
 		Galaxy_str.append(star_ms[i])
+		Galaxy_sig.append(sigma[i])
 
 
-catalog = open(basePath+'/Galaxy_'+str(ssNumber)+'_str.dat','w')
+catalog = open(basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat','w')
 
 catalog.write('# [0]: Galaxy SubID w/ group mass between 10^'+str(np.log10(mlow))+'~10^'+str(np.log10(mhigh))+'\n')
 catalog.write('# [1]-[3]: Group pos in ckpc/h \n')
 catalog.write('# [4]: Subhalo Mass in M_sun \n')
 catalog.write('# [5]: Stellar mass in M_sun \n')
+catalog.write('# [6]: 1d Velocity dispersion from all particles in km/s \n')
[…]

### 2016-06-21 python/Substructure/gravlens_tool.py

@@ -2,8 +2,8 @@ import os
 import numpy as np
 import commands
 
-def create_opt(macro_mod,micro_mod,path):
-	opt_file = open(path+'opt_realization.input','w')
+def create_opt(macro_mod,micro_mod,path,output):
+	opt_file = open(path+output,'w')
 	opt_header = open(path+'opt.head','r')
 
 	## write head file
@@ -51,8 +51,14 @@ def create_opt(macro_mod,micro_mod,path):
 
 	return
 
-def create_findimg(micro_mod,path):
-	findimg_file = open(path+'findimg_realization.input','w')
+def run_opt(path,optfile):
+
+	os.system('./lensmodel '+path+optfile)
+
+	return
+
+def create_findimg(micro_mod,path,output):
+	findimg_file = open(path+output,'w')
 	opt_result = open(path+'best.dat','r')
 
 	## need to modify
@@ -82,11 +88,13 @@ def create_findimg(micro_mod,path):
 
 	## write findimg command
 
+	opt_result.readline() # get rid of 'SOURCE PARMS:'
+	raw_line = opt_result.readline().split()
 
+	findimg_file.write('findimg '+raw_line[1]+raw_line[2]+'\n')
 
-	findimg_file.write('findimg \n')
-
-	opt_file.close()
+	opt_result.close()
+	findimg_file.close()
 
 	return
 
@@ -106,6 +114,6 @@ def gravlens_pjaffe(b,x,y,rt):
 
 	return Aline
 
-def opt_result(opt_file):
-	opt_output = commands.getstatusoutput('./lensmodel '+opt_file)
+def find_result(findimg_file):
+	opt_output = commands.getstatusoutput('./lensmodel '+findimg_file)
 

### 2016-06-21 python/Substructure/illustris_angularM.py

@@ -13,7 +13,8 @@ class cosmopara:
 
 ## read in Galaxy catalog
 
-catalog = '../../data/illustris_1/Galaxy_'+str(snapNum)+'_str.dat'
+catalog = '../../data/illustris_1/Galaxy_'+str(snapNum)+'_sig.dat'
+in_cat = open('../../data/illustris_1/Inclination_'+str(snapNum)+'_sig.dat','w')
 GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 CM_x = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
 CM_y = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
@@ -52,7 +53,7 @@ def boundary(ci):
 Axis = np.zeros((GalaxyID.size,3))*np.nan  # principle ratational axis of each galaxy
 theta_i = np.zeros((GalaxyID.size,3))*np.nan # inclination angle of three main axis
 
-in_cat = open('../../data/illustris_1/Inclination_'+str(snapNum)+'_str.dat','w')
+
 in_cat.write('# Galaxy ID 	theta_x		theta_y		theta_z \n')
 
 for i in range(GalaxyID.size):

### 2016-06-21 python/Substructure/realization.py

@@ -168,8 +168,17 @@ def set_realization(): # need to add realization number
 
 
 re_mod = set_realization()
-
 print len(re_mod.xi)
 ##--- realization valid check
 
-gTool.create_opt(Lens,re_mod,gravlensPath)
+opt_name = 'opt_realization.input'
+finding_name = 'findimg_realization.input'
+
+gTool.create_opt(Lens,re_mod,gravlensPath,opt_name)
+## run opt file
+gTool.run_opt(gravlensPath,opt_name)
+
+## write findimg file
+gTool.create_findimg(re_mod,gravlensPath,finding_name)
+
+

### 2016-06-21 python/Substructure/standard_cata.py

@@ -24,10 +24,11 @@ GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 bulge_frac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
 disk_frac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
 '''
-catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_str.dat'
+catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
 GalaxyID = np.loadtxt(catalog2,dtype = 'int',unpack=True, usecols=[0])
 Galaxy_ms = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[4])
 Galaxy_str = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[5])
+Galaxy_sig = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[6])
 
 
 
@@ -76,7 +77,7 @@ for i in range(LensID.size):
 
 ## Inclination angle
 
-catalog4 = basePath+'/Inclination_'+str(ssNumber)+'_str.dat'
+catalog4 = basePath+'/Inclination_'+str(ssNumber)+'_sig.dat'
 #thetaID = np.loadtxt(catalog4,dtype = 'int',unpack=True, usecols=[0])
 theta_x = np.loadtxt(catalog4,dtype='float',unpack=True,usecols=[1])
 theta_y = np.loadtxt(catalog4,dtype='float',unpack=True,usecols=[2])
@@ -86,17 +87,18 @@ theta_z = np.loadtxt(catalog4,dtype='float',unpack=True,usecols=[3])
 
 ## The standard catalog use LensID
 
-s_cata = open(basePath+'/Galaxy_Lens'+str(ssNumber)+'_str.dat','w')
+s_cata = open(basePath+'/Galaxy_Lens'+str(ssNumber)+'_sig.dat','w')
 s_cata.write('#[0]: SubfindID \n')
 s_cata.write('#[1]: Total Mass [M_sun] \n')
 s_cata.write('#[2]: Stellar Mass [M_sun] \n')
+s_cata.write('#[3]: Velocity Dispertion [km/s] \n')
 # add tot-mass here
 #s_cata.write('#[2]: Disk str fraction > 0.4, flag = 1 \n')
[…]

### 2016-06-21 python/plot_fns_b1555.py

@@ -18,8 +18,10 @@ import plot_lensmod as pltlm
 #---------------------------------------------------------------------------
 
 def model_plot(sx, sy, cx, cy):
-    plt.plot(sx,sy,'o',ms=10,mec='k',mfc='r',label='source')
-    plt.plot(cx,cy,'^',ms=10,label='lenses',mfc='k')
+    plt.scatter(sx,sy,'o',ms=10,mec='k',mfc='r',label='source')
+    #plt.scatter(cx,cy,'^',ms=10,label='lenses',mfc='k')
+    plt.scatter(cx[0],cy[0],'^',ms=10,mec='k',mfc='none',label = 'SIE center')
+    plt.scatter(cx[1],cy[1],'^',ms=10,mec='r',mfc='none',label = 'Disc center')
 
 #---------------------------------------------------------------------------
 
@@ -27,8 +29,14 @@ def img_pos(obsfile, xmod, ymod):
 
     x0,y0 = n.loadtxt(obsfile,unpack=True,usecols=(0,1))
 
-    plt.plot(x0,y0,'b+',ms=10,label='observed')
-    plt.plot(xmod,ymod,'o',ms=10,mec='r',mfc='none',label='predicted')
+    plt.scatter(x0,y0,'b+',ms=10,label='observed')
+    plt.scatter(xmod,ymod,'o',ms=10,mec='r',mfc='none',label='predicted')
+
+#---------------------------------------------------------------------------
+
+def disc_plane(x_sec,y_sec):
+
+    plt.plot(xsec,y_sec,'k--')
     
 #---------------------------------------------------------------------------
 
@@ -149,11 +157,17 @@ def gravlens_b1555(ax=None, showylab=True):
     """ Set the source positions """
     sx,sy= -1.971670e-01, -1.512136e-01
 
+    """ Set the observed disc mid plane """
+
+    x_sec = [-0.098,-0.3126]
+    y_sec = [0.3806,-0.8194]
+
     """ Do the plotting """
     pltlm.plot_critcaust(critfile,'crit',ax=ax)
     pltlm.plot_critcaust(critfile,'caust',sls=':',ax=ax)
     model_plot(sx,sy,cx,cy)
     img_pos(obsfile,xmod,ymod)
+    disc_plane(x_sec,y_sec)
 
     plt.xlabel(r'$\Delta  \alpha $ (arcsec)')
     if showylab:
[…]

### 2016-06-22 papers/B1555_EdgeOn/B1555_letter.tex
change legend setting in plot_fns_b1555.py
minor text change (shrink) in B1555 paper

@@
 % Keep the title short and informative.
-\title[Beware the effect of edge-on discs]{SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc }
+\title[Beware the effect of edge-on discs]{SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc in B1555+375}
 \author[Hsueh et al.]{J.-W. Hsueh,$^{1}$\thanks{E-mail: jwhsueh@ucdavis.edu} C. D. Fassnacht,$^{1}$ S. Vegetti,$^{2}$  J. P. McKean,$^{3,4}$ C. Spingola,$^{4}$ M. W. Auger,$^{5}$
@@
 The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B.
-An exponential disc profile best describes the disc component in spiral galaxies because it matches the light distribution \citep{Kee98}.
-We thus choose a SIE plus an exponential disc model (SIE+ExpDisc) in our study of B1555+375.
-The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+\textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
 The source position adds two additional model parameters.
-We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
+%We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
 %An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}
 
-More sophisticated mass models require additional
+More sophisticated mass models \textbf{(i.e. external shear or additional halo term)} require additional
 constraints, such as those from the lensed extended emission in either
@@
 The total number of free parameters is 9.
-After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain the uncertainties.}
+After obtaining the best-fit lens model, we run a Markov-Chain Monte-Carlo (MCMC) analysis to obtain the uncertainties.
 
-The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model} and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
-Table \ref{tab:results} also shows the comparison between the observed radio data and the model-predicted image positions and flux ratios.
-We find that by adding an elongated exponential disc to a smooth SIE model there is significant improvement in the predicted flux ratios when compared to the results for the SIE-only model.
+\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.}The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
+We find that adding an elongated exponential disc to a smooth SIE model \textbf{successfully reproduces the flux ratio anomaly in this system}.
 % with a reduced $\chi^2 = 2.7$
@@
 The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model.
-The model requires that the \textbf{ExpDisc component makes up about 15 per cent of the total projected mass within the Einstein radius (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).
+The model requires that the disc component makes up about 15 per cent of the total projected mass within the Einstein radius.
+% (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.}
+\textbf{While} investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.
@@
 The positions are measured in arcsec, relative to the MERLIN radio position of image A.
-The ellipticity is defined as $e=1-q$ and the position angles are measured in degrees east of north.
+The position angles are measured in degrees east of north.
 The Einstein radius $b$ and disc scale radius ($R_s$) are measured in arcsec.}

### 2016-06-22 papers/B1555_EdgeOn/B1555_letter.tex
update paper minor typo

@@
 The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B.
-\textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
-A detailed definition of these mass profiles is described by \citet{Kee01}.
-The source position adds two additional model parameters.
+\textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).\textbf{ A detailed definition of these mass profiles is described by \citet{Kee01} eq.
+(73) \& (74) .} The source position adds two additional model parameters.
 %We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
@@
 \begin{figure*}
-\includegraphics[width=0.9\textwidth]{b1555_3panel.eps}
+\includegraphics[width=0.9\textwidth]{b1555_3panel_new.eps}
 \caption{
@@
 %
-{\bf (c)} Observed radio (blue pluses) and model-predicted (red open
-circles) image positions of B1555+375. The lens-plane critical curves
+{\bf (c)} Observed radio position: blue pluses. Model-predicted position: red open
+circles. The lens-plane critical curves
 are shown with the blue solid line and the source-plane caustics are
@@
 ($-0.1953$, $-0.1494$), which is marked by the red filled circle. The
-centroid positions of the two mass components of the lens (a SIE and
-an exponential disc) are marked by the black filled triangles.
+centroid positions of the SIE and ExpDisc components of the lens are marked by the black and red filled triangles respectively.
+The disc middle plane measured with NICMOS image is shown with the black dashed line.
 }

### 2016-06-22 python/Substructure/dan_crosscheck.py
minor text change in B1555 paper

@@ -9,12 +9,12 @@ catalog = basePath+'/Galaxy_Lens'+ssNumber+'_sig.dat'
 Mass = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
 str_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
 sigma = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
-morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[13])
+morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[15])
 
-Re = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[7,8,9])
-DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[10,11,12])
+Re = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[9,10,11])
+DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[12,13,14])
 
-theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4,5,6])
+theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[6,7,8])
 
 # reduce to 1d [x...y...z...]
 Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta) 
@@ -41,7 +41,7 @@ theta_dan = theta[cri]
 Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
 sig_dan = sigma[cri]
-
+'''
 # Edge-on/Face-on
 edge = theta_dan == 1
 face = theta_dan == 0
@@ -66,8 +66,8 @@ print Mass_dan_ed.size,Mass_dan_fa.size
 '''
 ## Kinematics pick
 
-df = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2]) # disk str frac
-bf = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
+df = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4]) # disk str frac
+bf = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[5])
 
 df = np.array([df,df,df]).flatten()
[…]

### 2016-06-22 python/Substructure/illustris_circ.py

@@ -10,7 +10,7 @@ class cosmopara:
 	OM = 0.27
 
 basePath = '../../data/illustris_1'
-ssNumber = 108
+ssNumber = 99
 
 Snapshot_num = 'Snapshot_'+str(ssNumber)
 
@@ -24,9 +24,9 @@ Js = circFile[Snapshot_num]['SpecificAngMom']
 
 ## read in Galaxy catalog
 
-catalog = basePath+'/Galaxy_'+str(ssNumber)+'.dat'
+catalog = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
 GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
-star_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4]) # stellar mass
+#star_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4]) # stellar mass
 
 GalaxyID_end = max(GalaxyID)
 
@@ -40,7 +40,7 @@ CircAbove07Frac = CircAbove07Frac[mask]
 beta = beta[mask]
 Js = Js[mask]
 SubfindID_circ = SubfindID_circ[mask]
-
+'''
 ## indicator of specific angular momentum
 
 Ms = []
@@ -53,15 +53,15 @@ for i in range(GalaxyID.size):
 Ms = np.array(Ms)
 
 AngMomIndex = np.log10(Js/Ms**(2./3.))
-
-catalog = open(basePath+'/kinematics_'+str(ssNumber)+'.dat','w')
+'''
+catalog = open(basePath+'/kinematics_'+str(ssNumber)+'_sig.dat','w')
 #catalog.write('# Galaxy SubID   Angular Momemtum   Disk star frac    Bulge star frac'+'\n')
 
 catalog.write('# [0]: Galaxy SubID'+'\n')
 catalog.write('# [1]-[2]: Disk star fraction & Bulge star fraction'+'\n')
-catalog.write('# [3]: log10 SpecificAngMom/M_star^(2/3)'+'\n')
+#catalog.write('# [3]: log10 SpecificAngMom/M_star^(2/3)'+'\n')
 
 
 for i in range(SubfindID_circ.size):
-	catalog.write(str(SubfindID_circ[i])+'    '+str(CircAbove07Frac[i])+'    '+str(beta[i])+'	'+str(AngMomIndex[i])+'\n')
[…]

### 2016-06-22 python/Substructure/standard_cata.py

@@ -15,15 +15,15 @@ DanID = np.union1d(DanID,DanID_z)
 #DanID.sort()
 
 # If they are in DanID, morphology pick flag = 1
-'''
+
 ## Kinematics
 
-catalog = basePath+'/kinematics_'+str(ssNumber)+'.dat'
+catalog = basePath+'/kinematics_'+str(ssNumber)+'_sig.dat'
 GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 
 bulge_frac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
 disk_frac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
-'''
+
 catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
 GalaxyID = np.loadtxt(catalog2,dtype = 'int',unpack=True, usecols=[0])
 Galaxy_ms = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[4])
@@ -93,12 +93,12 @@ s_cata.write('#[1]: Total Mass [M_sun] \n')
 s_cata.write('#[2]: Stellar Mass [M_sun] \n')
 s_cata.write('#[3]: Velocity Dispertion [km/s] \n')
 # add tot-mass here
-#s_cata.write('#[2]: Disk str fraction > 0.4, flag = 1 \n')
-#s_cata.write('#[3]: Bulge str fraction < 0.6, flag = 1 \n')
-s_cata.write('#[4-6]: high inclination angle (60-120 degree), flag = 1; x,y,z \n')
-s_cata.write('#[7-9]: Re x,y,z \n')
-s_cata.write('#[10-12]: DM frac w/i Re x,y,z \n')
-s_cata.write('#[13]: Dandan morphology pick, flag =1 \n')
+s_cata.write('#[4]: Disk str fraction > 0.4, flag = 1 \n')
+s_cata.write('#[5]: Bulge str fraction < 0.6, flag = 1 \n')
+s_cata.write('#[6-8]: high inclination angle (60-120 degree), flag = 1; x,y,z \n')
+s_cata.write('#[9-11]: Re x,y,z \n')
+s_cata.write('#[12-14]: DM frac w/i Re x,y,z \n')
+s_cata.write('#[15]: Dandan morphology pick, flag =1 \n')
 
 
[…]

### 2016-06-23 python/Substructure/galaxy_cat.py
update catalog codes

@@ -4,8 +4,8 @@ import DistanceTool as distance
 
 basePath = '../../data/illustris_1'
 
-ssNumber = 99 # snapshotnumber
-z = 0.6
+ssNumber = 85 # snapshotnumber
+z = 1.0
 
 ## total mass
 #mlow = 1e12
@@ -73,7 +73,7 @@ for i in range(sigma.size):
 
 catalog = open(basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat','w')
 
-catalog.write('# [0]: Galaxy SubID w/ group mass between 10^'+str(np.log10(mlow))+'~10^'+str(np.log10(mhigh))+'\n')
+catalog.write('# [0]: Galaxy SubID w/ velocity dispertion between '+str(sigma_l)+'~'+str(sigma_h)+' km/s\n')
 catalog.write('# [1]-[3]: Group pos in ckpc/h \n')
 catalog.write('# [4]: Subhalo Mass in M_sun \n')
 catalog.write('# [5]: Stellar mass in M_sun \n')

### 2016-06-23 python/Substructure/illustris_circ.py

@@ -10,7 +10,7 @@ class cosmopara:
 	OM = 0.27
 
 basePath = '../../data/illustris_1'
-ssNumber = 99
+ssNumber = 85
 
 Snapshot_num = 'Snapshot_'+str(ssNumber)
 

### 2016-06-23 python/Substructure/readout_DanCat.py

@@ -10,28 +10,28 @@ Proj = ['NatProj_1/','NatProj_2/','NatProj_3/']
 
 ## catalog file names
 
-galaxy_cata = basePath+'Galaxy_'+str(ssNumber)+'.dat'
-GalaxyID = np.loadtxt(galaxy_cata,dtype = 'int',unpack=True, usecols=[0])
+#galaxy_cata = basePath+'Galaxy_'+str(ssNumber)+'_sig.dat'
+#GalaxyID = np.loadtxt(galaxy_cata,dtype = 'int',unpack=True, usecols=[0])
 
 #GroupFirstSub = groupcat.loadHalos(basePath,ssNumber,fields = ['GroupFirstSub'])
 
 TotList = ['TotCata_Lens.list','TotCata_Phot.list']
-list_idx = 0
+list_idx = 1
 
 p_index = 2 # Proj index
 
-cataName = basePath+'Dandan_Lens'+str(ssNumber)+'_z.dat'
+cataName = basePath+'Dandan_Phot'+str(ssNumber)+'_z.dat'
 
 CataList = open(catPath+Proj[p_index]+TotList[list_idx],'r')
 CataList = CataList.read().splitlines()
 
 ## Lens
-field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
-f_idx = np.array([0,5,6,7,11])
+#field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
+#f_idx = np.array([0,5,6,7,11])
 
 ## Phot
-#field = ['SubfindID','mass [M_sun/h]','stellar mass','Sersic index', '1:Early(deV);0:Late type(Exp)']
-#f_idx = np.array([0,3,4,18,24])
+field = ['SubfindID','mass [M_sun/h]','stellar mass','Sersic index','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
+f_idx = np.array([0,3,4,18,22,24])
 
 
 new_cata = open(cataName,'w')
@@ -46,25 +46,27 @@ for file_name in CataList:
 
 	#cata_file = open(catPath+Proj[p_index]+file_name,'r')
 	groupID = np.loadtxt(cata_file,dtype = 'int',skiprows = 1,unpack=True, usecols=[0])
-	print groupID
[…]

### 2016-06-23 python/Substructure/standard_cata.py

@@ -1,10 +1,21 @@
 import numpy as np
+import h5py
+import DistanceTool as distance
+import snapshot
 
 ### This code combine Lens properties of three projection
 
 basePath = '../../data/illustris_1'
 ssNumber = 99
 Snapshot_num = 'Snapshot_'+str(ssNumber)
+
+## get header file
+headerPath = '/Volumes/narsil_1/jwhsueh/illustris_1'
+
+f = h5py.File(snapshot.snapPath(headerPath,ssNumber),'r')
+header = dict( f['Header'].attrs.items() )
+
+redshift = header['Redshift']
 
 ### Dandan's morphology pick
 DanID_x = np.loadtxt('JenWei_table_disk_in_x.dat',dtype = 'int',unpack=True, usecols=[0])
@@ -54,25 +65,52 @@ DMfrac_z = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
 LensID = np.union1d(LensID_x,LensID_y)
 LensID = np.union1d(LensID,LensID_z)
 
+## Photometry properties (Dandan's full catalog)
+catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_x.dat'
+bright_x = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+
+catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_y.dat'
+bright_y = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+
+catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_z.dat'
+bright_z = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+
+
+## absolute mag to apparent mag
+
+''' cosmopara '''
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+DL = distance.luminosity_distance(cosmopara,redshift)*1e6 # pc
+bright_x = bright_x+5.*(np.log10(DL)-1)
+bright_y = bright_y+5.*(np.log10(DL)-1)
+bright_z = bright_z+5.*(np.log10(DL)-1)
+
 ## get Re & DMfrac table
 Re = np.zeros((LensID.size,3))*np.nan
 DMfrac = np.zeros((LensID.size,3))*np.nan
[…]

### 2016-06-23 python/plot_fns_b1555.py

@@ -21,7 +21,7 @@ def model_plot(sx, sy, cx, cy):
     plt.scatter(sx,sy,marker='o',s= 50,edgecolor='k',facecolors='r',label='Source')
     #plt.scatter(cx,cy,'^',ms=10,label='lenses',mfc='k')
     plt.scatter(cx[0],cy[0],marker='^',edgecolor='k',s= 100,facecolors='k',label = 'SIE center')
-    plt.scatter(cx[1],cy[1],marker='^',edgecolor='k',s= 100,facecolors='r',label = 'Disc center')
+    plt.scatter(cx[1],cy[1],marker='v',edgecolor='k',s= 100,facecolors='r',label = 'Disc center')
 
 #---------------------------------------------------------------------------
 

### 2016-06-25 papers/B1555_EdgeOn/B1555_letter.tex
minor text change in B1555 text

@@
 The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B.
-\textbf{Our model contains a SIE plus an exponential disc component (SIE+ExpDisc) due to that  exponential disc profile matches the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+\textbf{An exponential disc component is added to the smooth lens model.
+Former study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 
-\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.}The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
+\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.} The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
 We find that adding an elongated exponential disc to a smooth SIE model \textbf{successfully reproduces the flux ratio anomaly in this system}.
@@
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-\textbf{While} investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent\citep{swells1,swells3,swells6}.
+\textbf{While} investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent \citep{swells1,swells3,swells6}.
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.

### 2016-06-25 python/Substructure/gravlens_tool.py

@@ -115,5 +115,11 @@ def gravlens_pjaffe(b,x,y,rt):
 	return Aline
 
 def find_result(findimg_file):
-	opt_output = commands.getstatusoutput('./lensmodel '+findimg_file)
+	findimg_out = commands.getstatusoutput('./lensmodel '+findimg_file)
+
+	findimg_out=findimg_out[1].split('\n')
+
+	## checking img #
+
+	check_line = findimg_out
 

### 2016-06-27 python/Substructure/dan_crosscheck.py
update for photometry cut code

@@ -1,15 +1,18 @@
 import numpy as np
 import matplotlib.pyplot as plt
+import DistanceTool as distance
 
 basePath = '../../data/illustris_1'
 ssNumber = '99'
+z = 0.6
 
+## change
 catalog = basePath+'/Galaxy_Lens'+ssNumber+'_sig.dat'
 #GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 Mass = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
 str_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
 sigma = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
-morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[15])
+morph = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[18])
 
 Re = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[9,10,11])
 DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[12,13,14])
@@ -41,6 +44,38 @@ theta_dan = theta[cri]
 Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
 sig_dan = sigma[cri]
+
+## ------ surface brigtness selection
+
+
+''' cosmopara '''
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+DL = distance.luminosity_distance(cosmopara,z)*1e6 # pc
+
+brightness = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[15,16,17])
+
+# reduce to 1d [x...y...z...]]
+brightness = np.ravel(brightness)
+
+## cut for all
+
+cri_cut = brightness<23.5
+print Re.size, cri_cut.size
+Re_all = Re[cri_cut]
+
+## morphology pick
+brightness_dan = brightness[cri] # cri = morph
+#print brightness_dan[:100]
+
+## surface brightness cut
+cri2 = brightness_dan<23.5
+#print cri2
+
+Re_dan = Re_dan[cri2]
+#print len(Re_dan)
 '''
 # Edge-on/Face-on
 edge = theta_dan == 1
[…]

### 2016-06-27 python/Substructure/redshift_evo.py

@@ -1,0 +1,65 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+basePath = '../../data/illustris_1'
+
+ssNumber = ['85','99','120']
+
+All = []
+disk_frac = []
+bulge_frac = []
+dot_z = []
+for i in range(len(ssNumber)):
+	catalog = basePath+'/Galaxy_Lens'+ssNumber[i]+'_sig.dat'
+
+	Re_proj = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[12,13,14])
+	df = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4])
+	bf = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[5])
+
+	# reduce to 1d [x...y...z...]
+
+	Re = np.ravel(Re_proj)
+
+	df = np.array([df,df,df]).flatten()
+	bf = np.array([bf,bf,bf]).flatten()
+	#disk_frac.append(df)
+	#bulge_frac.append(bf)
+
+	## plotting
+
+	# criteria flag
+
+	cri_k1 = df==1
+	cri_k2 = bf==1
+
+	Re_df,Re_bf = Re[cri_k1],Re[cri_k2]
+
+	# histogram
+	se = np.linspace(0.2,1.2,20)
+	dot = []
+	for i in range(se.size-1):
+		dot.append((se[i]+se[i+1])/2.)
+
+	dot_z.append(dot)
+
+	All.append(np.histogram(Re,bins = se)[0].astype(float))
+	disk_frac.append(np.histogram(Re_df,bins = se)[0].astype(float))
+	bulge_frac.append(np.histogram(Re_bf,bins = se)[0].astype(float))
+
+
+## plot
+
+plt.plot(dot_z[0],disk_frac[0]/All[0],color='k',label = 'z = 1.0')
+plt.plot(dot_z[1],disk_frac[1]/All[1],color='b',label = 'z = 0.6')
+plt.plot(dot_z[2],disk_frac[2]/All[2],color='r',label = 'z = 0.2')
+
+plt.legend()
+
+plt.xlabel('Einstein Radius')
+plt.ylabel('Galaxy Fraction')
+plt.title('Redshift comparison: Disk star frac > 40%')
+
+plt.show()
+
+
+

### 2016-06-29 papers/B1555_EdgeOn/B1555_letter.tex
update Dave's affiliation

@@
 $^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{6}$University of Lyon, CRAL, Observatoire de Lyon, 92 Rue Pasteur, 69007 Lyon, France}
+$^{6}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}
 \begin{document}

### 2016-06-29 python/Substructure/galaxy_cat.py

@@ -4,8 +4,10 @@ import DistanceTool as distance
 
 basePath = '../../data/illustris_1'
 
-ssNumber = 85 # snapshotnumber
-z = 1.0
+ssNumber = 99 # snapshotnumber
+z = 0.6
+
+a = 1./(1.+z)
 
 ## total mass
 #mlow = 1e12
@@ -38,6 +40,8 @@ GroupCM = GroupCM[GroupFirstSub,:]
 star_ms = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloMassType'])[:,4]*1e10/cosmopara.h
 star_ms = star_ms[GroupFirstSub]
 
+#Rhal_st = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloHalfmassRadType'])[:,4]*a # kpc/h, half mass radius of star particles
+
 sigma = groupcat.loadSubhalos(basePath,ssNumber,fields = ['SubhaloVelDisp'])
 sigma = sigma[GroupFirstSub]
 
@@ -59,7 +63,7 @@ K_mag = K_mag+5.*(np.log10(DL)-1)
 ## rewrite this part!!! [str mass]
 ## use group mass as galaxy cretria 
 ## here!!
-GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig = [],[],[],[],[]
+GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh = [],[],[],[],[],[]
 
 for i in range(sigma.size):
 	if sigma[i]<sigma_h and sigma[i]>sigma_l:
@@ -69,6 +73,7 @@ for i in range(sigma.size):
 		Galaxy_ms.append(GalaxyMass[i])
 		Galaxy_str.append(star_ms[i])
 		Galaxy_sig.append(sigma[i])
+		#Galaxy_Rh.append(Rhal_st[i])
 
 
 catalog = open(basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat','w')
@@ -78,9 +83,10 @@ catalog.write('# [1]-[3]: Group pos in ckpc/h \n')
 catalog.write('# [4]: Subhalo Mass in M_sun \n')
 catalog.write('# [5]: Stellar mass in M_sun \n')
 catalog.write('# [6]: 1d Velocity dispersion from all particles in km/s \n')
[…]

### 2016-06-29 python/Substructure/illustris_angularM.py

@@ -73,7 +73,10 @@ for i in range(GalaxyID.size):
 	if (max(st_y)-min(st_y)> 0.5*boxsize): 
 		st_y = boundary(st_y)
 	if (max(st_z)-min(st_z)> 0.5*boxsize): 
-		st_z = boundary(st_z)	
+		st_z = boundary(st_z)
+
+	## change ref point to subhalo CM
+	st_x,st_y,st_z = st_x-CM_x[i],st_y-CM_y[i],st_z-CM_z[i]	
 
 	vel = subhalo_st['Velocities']
 	# relative velocity to center

### 2016-06-29 python/Substructure/illustris_scatter.py

@@ -1,0 +1,149 @@
+import numpy as np
+import snapshot
+import h5py
+import DistanceTool as distance
+import matplotlib.pyplot as plt
+import scipy.ndimage
+
+basePath = '/Volumes/narsil_1/jwhsueh/illustris_1'
+snapNum = 99
+
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+## read in Galaxy catalog
+catalog = '../../data/illustris_1/Galaxy_'+str(snapNum)+'_sig.dat'
+
+GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
+CM_x = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
+CM_y = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
+CM_z = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
+
+p_type = ['gas','dm','stars']
+
+field = ['Masses']
+
+## read in snapshot header
+
+f = h5py.File(snapshot.snapPath(basePath,snapNum),'r')
+header = dict( f['Header'].attrs.items() )
+
+boxsize = header['BoxSize']  # ckpc/h
+redshift = header['Redshift']
+
+a = 1.0/(1.0+redshift) # scale factor
+
+# region
+r_cut = 30. # 30 kpc/h
+
+## this function deal w/ galaxy on the boundary
+def boundary(ci):
+	
+	#ci[ci< 0.5*boxsize] = ci[ci< 0.5*boxsize]+boxsize
+
+	for i in ci:
+		if i<0.5*boxsize:
+			i = i+boxsize
+
+	return ci
+
+## projection function
+
+def projection(c0,c1,c2,axis):
+
+	if axis == 0: # y-z plane
+		p0,p1 = c1,c2
+	elif axis == 1: # x-z plane
+		p0,p1 = c0,c2
+	else: # x-y plane
+		p0,p1 = c0,c1
+
+	return p0,p1
+
+
+## -------start to plot particles
+
+ID = 93295
+
+idx = list(GalaxyID).index(ID)
+print idx
+GalaxyID = ID
+
+# Use star particles only
+
[…]

### 2016-06-29 python/Substructure/standard_cata.py

@@ -130,7 +130,7 @@ s_cata.write('#[0]: SubfindID \n')
 s_cata.write('#[1]: Total Mass [M_sun] \n')
 s_cata.write('#[2]: Stellar Mass [M_sun] \n')
 s_cata.write('#[3]: Velocity Dispertion [km/s] \n')
-# add tot-mass here
+# add CM here
 s_cata.write('#[4]: Disk str fraction > 0.4, flag = 1 \n')
 s_cata.write('#[5]: Bulge str fraction < 0.6, flag = 1 \n')
 s_cata.write('#[6-8]: high inclination angle (60-120 degree), flag = 1; x,y,z \n')

### 2016-07-07 python/Substructure/dan_crosscheck.py
update referee response_v3

@@ -19,6 +19,8 @@ DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[12,13,14])
 
 theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[6,7,8])
 
+relax = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[19])
+K_mag = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[20])
 # reduce to 1d [x...y...z...]
 Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta) 
 
@@ -27,7 +29,13 @@ Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta)
 Mass = np.array([Mass,Mass,Mass]).flatten()
 str_ms = np.array([str_ms,str_ms,str_ms]).flatten()
 sigma = np.array([sigma,sigma,sigma]).flatten()
+relax = np.array([relax,relax,relax]).flatten()
+K_mag = np.array([K_mag,K_mag,K_mag]).flatten()
 #print Mass
+
+## magnitude cut for all
+cri0 = K_mag<23.5
+Re_mag = Re[cri0]
 
 ## Dandan's pick
 
@@ -38,12 +46,24 @@ morph = morph.flatten()
 morph = np.array([morph,morph,morph]).flatten()
 cri = morph==1
 
+Dan_relax = relax[cri]
 Re_dan = Re[cri]
 DMfrac_dan = DMfrac[cri]
 theta_dan = theta[cri]
 Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
 sig_dan = sigma[cri]
+Kmag_dan = K_mag[cri]
+
+## relax
+cri_relax = Dan_relax ==0
+Re_dan = Re_dan[cri_relax]
+Kmag_dan = Kmag_dan[cri_relax]
+
+# mag cut
+cri_K = Kmag_dan<23.5
+Re_dan = Re_dan[cri_K]
+
 
 ## ------ surface brigtness selection
 
@@ -77,7 +97,7 @@ cri2 = brightness_dan<23.5
 Re_dan = Re_dan[cri2]
 #print len(Re_dan)
 '''
-
+'''
 # Edge-on/Face-on
 edge = theta_dan == 1
 face = theta_dan == 0
[…]

### 2016-07-07 python/Substructure/galaxy_cat.py

@@ -48,7 +48,7 @@ sigma = sigma[GroupFirstSub]
 
 sigma_h = 370.
 sigma_l = 130.
-'''
+
 #photometry
 V_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,2]
 K_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,3]
@@ -57,14 +57,14 @@ K_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotom
 DL = distance.luminosity_distance(cosmopara,z)*1e6 # pc
 V_mag = V_mag+5.*(np.log10(DL)-1)
 K_mag = K_mag+5.*(np.log10(DL)-1)
-'''
+
 
 #print star_ms
 
 ## rewrite this part!!! [str mass]
 ## use group mass as galaxy cretria 
 ## here!!
-GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh = [],[],[],[],[],[]
+GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh,Galaxy_K = [],[],[],[],[],[],[]
 
 for i in range(sigma.size):
 	if sigma[i]<sigma_h and sigma[i]>sigma_l:
@@ -75,6 +75,7 @@ for i in range(sigma.size):
 		Galaxy_str.append(star_ms[i])
 		Galaxy_sig.append(sigma[i])
 		Galaxy_Rh.append(Rhal_st[i])
+		Galaxy_K.append(K_mag[i])
 
 ## check if the halo is relax
 
@@ -82,18 +83,14 @@ catalog_r =basePath+'/m200_halos_hydr_rel_'+str(ssNumber)+'.txt'
 cat_ID = np.loadtxt(catalog_r,dtype = 'int',unpack=True, usecols=[4])
 relax = np.loadtxt(catalog_r,dtype = 'int',unpack=True, usecols=[1]) # 0:relax, 1:not relax
 
+relax_flag = np.zeros(len(GalaxyID))
+
 for i in range(cat_ID.size):
 
-	if cat_ID[i] in GalaxyID and relax[i] == 1:
-		print cat_ID[i]
+	if cat_ID[i] in GalaxyID:
[…]

### 2016-07-07 python/Substructure/gravlens_tool.py

@@ -57,24 +57,51 @@ def run_opt(path,optfile):
 
 	return
 
+def create_bestSub(path):
+
+	best_out = open(path+'best.dat','r')
+
+	lines = best_out.readlines()
+
+	lines = lines[1:-17]
+
+	best_sub = open(path+'bestSub.dat','w')
+
+	for Aline in lines:
+		best_sub.write(Aline)
+
+	best_out.close()
+	best_sub.close()
+
+	return
+
 def create_findimg(micro_mod,path,output):
 	findimg_file = open(path+output,'w')
-	opt_result = open(path+'best.dat','r')
+
+	create_bestSub(path)
+	opt_result = open(path+'bestSub.dat','r')
 
 	## need to modify
 	## write number of lens and srcs [startup]
 
-	n_lens = 1+len(micro_mod.xi)
+	# get another function to create pure best substructure result
+
+	lines = opt_result.readlines()[:-1]
+	n_lens = len(lines)
 	findimg_file.write('startup '+str(n_lens)+' 1\n')
 
-	opt_result.readline() # get rid of first line
+	#opt_result.readline() # get rid of first line
 	#opt_lines = opt_result.readlines()
 
+	# write in substructures
 
-	for i in range(n_lens):
-		Aline = opt_result.readline()
+	for Aline in lines:
+		#Aline = opt_result.readline()
 		findimg_file.write(Aline)
+		#print Aline
+		#print '##'+str(i)
 
+	opt_result.close()
 
 	## --end of gravlens startup--
 
@@ -87,11 +114,14 @@ def create_findimg(micro_mod,path,output):
 	findimg_file.write('\n')
 
 	## write findimg command
+	# get srcs position
+	opt_result = open(path+'best.dat','r')
+	raw_line = opt_result.readlines() # get all the rest lines
+	#print raw_line
+	raw_line = raw_line[-11].split()
+	#print raw_line
 
-	opt_result.readline() # get rid of 'SOURCE PARMS:'
-	raw_line = opt_result.readline().split()
-
-	findimg_file.write('findimg '+raw_line[1]+raw_line[2]+'\n')
+	findimg_file.write('findimg '+raw_line[1]+' '+raw_line[2]+'\n')
 
 	opt_result.close()
 	findimg_file.close()
@@ -114,10 +144,12 @@ def gravlens_pjaffe(b,x,y,rt):
 
 	return Aline
 
[…]

### 2016-07-07 python/Substructure/realization.py

@@ -206,16 +206,21 @@ gTool.create_findimg(re_mod,gravlensPath,findimg_name)
 
 print '----create findimg file done----'
 
-result = gTool.run_findimg(findimg_name)
+result = gTool.run_findimg(gravlensPath,findimg_name)
 
 if result == np.nan:
 	# run above again
+	print 'realization fail'
+	print result
 
 elif pos_check(Lens.img_x,Lens.img_y,Lens.img_err,result): # check if within 2-sigma position, True = valid
-
+	## ok we need to assign image letter again
 	# calculate R_cusp, R_fold
+	print 'calculate R_cusp'
 
 else:
 	# run above again
+	print 'realization fail'
+	print result
 
 

### 2016-07-07 python/Substructure/standard_cata.py

@@ -40,8 +40,8 @@ GalaxyID = np.loadtxt(catalog2,dtype = 'int',unpack=True, usecols=[0])
 Galaxy_ms = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[4])
 Galaxy_str = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[5])
 Galaxy_sig = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[6])
-
-
+Galaxy_relax = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[8])
+Galaxy_K = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[9])
 
 ## Lens properties from Dandan's full catalog [all mass range]
 
@@ -138,6 +138,8 @@ s_cata.write('#[9-11]: Re x,y,z \n')
 s_cata.write('#[12-14]: DM frac w/i Re x,y,z \n')
 s_cata.write('#[15-17]: surface brightness at Reff_exp in x,y,z [mag/arcsec^2] \n')
 s_cata.write('#[18]: Dandan morphology pick, flag =1 \n')
+s_cata.write('#[19]: relax = 0, not relax =1 \n')
+s_cata.write('#[20]: Galaxy magnitude K-band\n')
 
 
 for i in range(LensID.size):
@@ -185,6 +187,12 @@ for i in range(LensID.size):
 		## Dandan's morphology pick flag
 
 		if LensID[i] in DanID:
-			s_cata.write('1 \n')
+			s_cata.write('1  ')
 		else:
-			s_cata.write('0 \n')
+			s_cata.write('0  ')
+
+		# relax flag
+		s_cata.write(str(int(Galaxy_relax[idx]))+' ')
+
+		# Photometry
+		s_cata.write(str(Galaxy_K[idx])+'\n')

### 2016-07-07 python/Substructure/dan_crosscheck.py
update text in B1555 paper and response

@@ -20,7 +20,7 @@ DMfrac = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[12,13,14])
 theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[6,7,8])
 
 relax = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[19])
-K_mag = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[20])
+V_mag = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[20])
 # reduce to 1d [x...y...z...]
 Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta) 
 
@@ -30,13 +30,13 @@ Mass = np.array([Mass,Mass,Mass]).flatten()
 str_ms = np.array([str_ms,str_ms,str_ms]).flatten()
 sigma = np.array([sigma,sigma,sigma]).flatten()
 relax = np.array([relax,relax,relax]).flatten()
-K_mag = np.array([K_mag,K_mag,K_mag]).flatten()
+V_mag = np.array([V_mag,V_mag,V_mag]).flatten()
 #print Mass
-
+'''
 ## magnitude cut for all
-cri0 = K_mag<23.5
+cri0 = V_mag<24
 Re_mag = Re[cri0]
-
+'''
 ## Dandan's pick
 
 # three projections
@@ -53,17 +53,17 @@ theta_dan = theta[cri]
 Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
 sig_dan = sigma[cri]
-Kmag_dan = K_mag[cri]
+Vmag_dan = V_mag[cri]
 
 ## relax
 cri_relax = Dan_relax ==0
 Re_dan = Re_dan[cri_relax]
-Kmag_dan = Kmag_dan[cri_relax]
-
+Vmag_dan = Vmag_dan[cri_relax]
+'''
 # mag cut
-cri_K = Kmag_dan<23.5
-Re_dan = Re_dan[cri_K]
-
+cri_V = Vmag_dan<24
+Re_dan = Re_dan[cri_V]
+'''
 
 ## ------ surface brigtness selection
 
@@ -139,19 +139,19 @@ Mass_bf = Mass[cri_k2]
 theta_bf = theta[cri_k2]
 
 relax_df,relax_bf = relax[cri_k1],relax[cri_k2]
[…]

### 2016-07-07 python/Substructure/galaxy_cat.py

@@ -64,7 +64,7 @@ K_mag = K_mag+5.*(np.log10(DL)-1)
 ## rewrite this part!!! [str mass]
 ## use group mass as galaxy cretria 
 ## here!!
-GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh,Galaxy_K = [],[],[],[],[],[],[]
+GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh,Galaxy_V = [],[],[],[],[],[],[]
 
 for i in range(sigma.size):
 	if sigma[i]<sigma_h and sigma[i]>sigma_l:
@@ -75,7 +75,7 @@ for i in range(sigma.size):
 		Galaxy_str.append(star_ms[i])
 		Galaxy_sig.append(sigma[i])
 		Galaxy_Rh.append(Rhal_st[i])
-		Galaxy_K.append(K_mag[i])
+		Galaxy_V.append(V_mag[i])
 
 ## check if the halo is relax
 
@@ -101,10 +101,10 @@ catalog.write('# [5]: Stellar mass in M_sun \n')
 catalog.write('# [6]: 1d Velocity dispersion from all particles in km/s \n')
 catalog.write('# [7]: half mass radius of star particle in kpc/h \n')
 catalog.write('# [8]: main halo is relax: 0, not relax:1 \n')
-catalog.write('# [9]: photometry K-band \n')
+catalog.write('# [9]: photometry V-band \n')
 #catalog.write('# [6]-[7]: photometry V-band & K-band \n')
 
 for i in range(len(GalaxyID)):
-	catalog.write(str(GalaxyID[i])+'    '+str(GalaxyPos[i])[1:-1]+'    '+str(Galaxy_ms[i])+'    '+str(Galaxy_str[i])+'	'+str(Galaxy_sig[i])+' '+str(Galaxy_Rh[i]) +' '+str(relax_flag[i])+' '+str(Galaxy_K[i])+'\n')
+	catalog.write(str(GalaxyID[i])+'    '+str(GalaxyPos[i])[1:-1]+'    '+str(Galaxy_ms[i])+'    '+str(Galaxy_str[i])+'	'+str(Galaxy_sig[i])+' '+str(Galaxy_Rh[i]) +' '+str(relax_flag[i])+' '+str(Galaxy_V[i])+'\n')
 	#catalog.write(str(table[i,:])[1:-1]+'\n')
 

### 2016-07-07 python/Substructure/standard_cata.py

@@ -41,7 +41,7 @@ Galaxy_ms = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[4])
 Galaxy_str = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[5])
 Galaxy_sig = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[6])
 Galaxy_relax = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[8])
-Galaxy_K = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[9])
+Galaxy_V = np.loadtxt(catalog2,dtype = 'float',unpack=True, usecols=[9])
 
 ## Lens properties from Dandan's full catalog [all mass range]
 
@@ -139,7 +139,7 @@ s_cata.write('#[12-14]: DM frac w/i Re x,y,z \n')
 s_cata.write('#[15-17]: surface brightness at Reff_exp in x,y,z [mag/arcsec^2] \n')
 s_cata.write('#[18]: Dandan morphology pick, flag =1 \n')
 s_cata.write('#[19]: relax = 0, not relax =1 \n')
-s_cata.write('#[20]: Galaxy magnitude K-band\n')
+s_cata.write('#[20]: Galaxy magnitude V-band\n')
 
 
 for i in range(LensID.size):
@@ -195,4 +195,4 @@ for i in range(LensID.size):
 		s_cata.write(str(int(Galaxy_relax[idx]))+' ')
 
 		# Photometry
-		s_cata.write(str(Galaxy_K[idx])+'\n')
+		s_cata.write(str(Galaxy_V[idx])+'\n')

### 2016-07-11 papers/B1555_EdgeOn/Resubmission_v3/B1555_EdgeOn.tex
prepare to do realization valid test

--- 2016-06-29 papers/B1555_EdgeOn/B1555_letter.tex
@@
 \textbf{An exponential disc component is added to the smooth lens model.
-Former study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+Previous study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass.
-\textbf{While} investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent \citep{swells1,swells3,swells6}.
+Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent \citep{swells1,swells3,swells6}.
 %In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.

### 2016-07-11 python/Substructure/dan_crosscheck.py

@@ -21,8 +21,12 @@ theta = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[6,7,8])
 
 relax = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[19])
 V_mag = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[20])
+
+SB = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[15,16,17])
+
 # reduce to 1d [x...y...z...]
-Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta) 
+Re,DMfrac,theta = np.ravel(Re),np.ravel(DMfrac),np.ravel(theta)
+SB = np.ravel(SB) 
 
 # expend array
 
@@ -32,11 +36,15 @@ sigma = np.array([sigma,sigma,sigma]).flatten()
 relax = np.array([relax,relax,relax]).flatten()
 V_mag = np.array([V_mag,V_mag,V_mag]).flatten()
 #print Mass
-'''
+mag_cut = 24.
+SB_cut = 24
+
+
 ## magnitude cut for all
-cri0 = V_mag<24
+#cri0 = V_mag<mag_cut
+cri0 = SB<SB_cut
 Re_mag = Re[cri0]
-'''
+
 ## Dandan's pick
 
 # three projections
@@ -54,44 +62,23 @@ Mass_dan = Mass[cri]
 str_dan = str_ms[cri]
 sig_dan = sigma[cri]
 Vmag_dan = V_mag[cri]
+SB_dan = SB[cri]
 
 ## relax
 cri_relax = Dan_relax ==0
 Re_dan = Re_dan[cri_relax]
 Vmag_dan = Vmag_dan[cri_relax]
-'''
+SB_dan = SB_dan[cri_relax]
+
 # mag cut
-cri_V = Vmag_dan<24
+#cri_V = Vmag_dan<mag_cut
+cri_V = SB_dan <SB_cut
 Re_dan = Re_dan[cri_V]
+
+
 '''
-
-## ------ surface brigtness selection
-
-
-''' cosmopara '''
-class cosmopara:
-	h = 0.704
-	OM = 0.27
-
-DL = distance.luminosity_distance(cosmopara,z)*1e6 # pc
-
-brightness = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[15,16,17])
-
-# reduce to 1d [x...y...z...]]
[…]

### 2016-07-11 python/Substructure/galaxy_cat.py

@@ -52,11 +52,13 @@ sigma_l = 130.
 #photometry
 V_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,2]
 K_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,3]
+r_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,5]
 
 # apparent mag
 DL = distance.luminosity_distance(cosmopara,z)*1e6 # pc
 V_mag = V_mag+5.*(np.log10(DL)-1)
 K_mag = K_mag+5.*(np.log10(DL)-1)
+r_mag = r_mag+5.*(np.log10(DL)-1)
 
 
 #print star_ms
@@ -101,7 +103,7 @@ catalog.write('# [5]: Stellar mass in M_sun \n')
 catalog.write('# [6]: 1d Velocity dispersion from all particles in km/s \n')
 catalog.write('# [7]: half mass radius of star particle in kpc/h \n')
 catalog.write('# [8]: main halo is relax: 0, not relax:1 \n')
-catalog.write('# [9]: photometry V-band \n')
+catalog.write('# [9]: photometry r-band \n')
 #catalog.write('# [6]-[7]: photometry V-band & K-band \n')
 
 for i in range(len(GalaxyID)):

### 2016-07-11 python/Substructure/gravlens_tool.py

@@ -59,11 +59,12 @@ def run_opt(path,optfile):
 
 def create_bestSub(path):
 
-	best_out = open(path+'best.dat','r')
+	best_out = open('best.dat','r')
 
 	lines = best_out.readlines()
 
-	lines = lines[1:-17]
+	lines = lines[1:-16]
+	#print lines
 
 	best_sub = open(path+'bestSub.dat','w')
 
@@ -115,7 +116,7 @@ def create_findimg(micro_mod,path,output):
 
 	## write findimg command
 	# get srcs position
-	opt_result = open(path+'best.dat','r')
+	opt_result = open('best.dat','r')
 	raw_line = opt_result.readlines() # get all the rest lines
 	#print raw_line
 	raw_line = raw_line[-11].split()
@@ -149,7 +150,9 @@ def run_findimg(path,findimg_file):
 
 	findimg_out=findimg_out[1].split('\n')
 
-	print findimg_out
+	#print findimg_out
+
+	result = open(path+'findimg.out','w')
 
 	## checking img #
 
@@ -157,20 +160,66 @@ def run_findimg(path,findimg_file):
 	# if it's four images
 	if check_line[0] == '#':
 		# save x y mag
-		x,y,mag = [],[],[]
+		#x,y,mag = [],[],[]
 		for i in [-2,-3,-4,-5]:
 			Aline = findimg_out[i].split()
-			x.append(float(Aline[0]))
-			y.append(float(Aline[1]))
-			mag.append(float(Aline[2]))
+			#x.append(float(Aline[0]))
+			#y.append(float(Aline[1]))
+			#mag.append(float(Aline[2]))
+			result.write(Aline[0]+' '+Aline[1]+' '+Aline[2]+'\n')
 
-		result = [x,y,mag]
+			flag = True
+
+		#result = [x,y,mag] # write into a file
 
 
 	else:
 		print '* Not a quad-system'
+		flag = False
+		result.write('# Not a quad-system')
 
-		result = np.nan
+	result.close()
+
+	return flag
+
+def assign_img(path,x_obs):
+	img_file = path+'findimg.out'
+	
+	table = np.loadtxt(img_file)
+
+	result = open(path+'findimg.out','w')
+
+	for i in range(len(x_obs)):
+		d = table[:,0] - x_obs[i] # difference in pos_x
+		d = np.abs(d)
+		d_min = np.min(d)
[…]

### 2016-07-11 python/Substructure/realization.py

@@ -30,7 +30,7 @@ y_lim = np.array([Lens.yc-2.*Lens.b,Lens.yc+2.*Lens.b])
 
 
 ## substructure mass fraction
-f_sub = 0.01
+f_sub = 0.005
 
 sigma_c = Lens.critical_density()*cospara.h # M_sun/Mpc^2
 sigma_c = sigma_c/(distance.mpc2arcs(cospara,1.,Lens.zl))**2
@@ -166,25 +166,6 @@ def set_realization(): # need to add realization number
 		
 	return real_one
 
-## ---- check if result is w/i 2-sigma----
-def pos_check(obs_x,obs_y,obs_err,opt):
-
-	mod_x,mod_y = opt[0],opt[1]
-	dif_x = np.fabs(obs_x - mod_x)
-	dif_y = np.fabs(obs_y - mod_y)
-	obs_err = np.average(obs_err)
-
-	result = True 
-
-	for element in dif_x:
-		if element > 2.*obs_err:
-			result = False
-
-	for element in dif_y:
-		if element > 2.*obs_err:
-			result = False
-
-	return result
 
 ## ------
 
@@ -206,21 +187,27 @@ gTool.create_findimg(re_mod,gravlensPath,findimg_name)
 
 print '----create findimg file done----'
 
-result = gTool.run_findimg(gravlensPath,findimg_name)
+flag = gTool.run_findimg(gravlensPath,findimg_name)
 
-if result == np.nan:
+print '----write findimg result----'
+
+sucess = 0
+
+if flag == False:
 	# run above again
 	print 'realization fail'
 	print result
-
-elif pos_check(Lens.img_x,Lens.img_y,Lens.img_err,result): # check if within 2-sigma position, True = valid
-	## ok we need to assign image letter again
-	# calculate R_cusp, R_fold
-	print 'calculate R_cusp'
 
 else:
-	# run above again
-	print 'realization fail'
-	print result
+	gTool.assign_img(gravlensPath,Lens.img_x)
+	check = gTool.pos_check(gravlensPath,Lens.img_x,Lens.img_y,Lens.img_err)
+
+	if check == False:
+		print '# realization fail'
+
+	else:
+		print '# realization created'
+		sucess = sucess+1
+
 
 

### 2016-07-11 python/Substructure/sigma2mag.py

@@ -1,0 +1,55 @@
+import numpy as np
+import DistanceTool as distance
+
+basePath = '../../data/illustris_1/'
+
+ssNumber = 99
+redshift = 0.6
+
+cataName = basePath+'Dandan_Phot'+str(ssNumber)+'_x.dat'
+sigma_x = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[5])
+R_x = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[4])
+
+cataName = basePath+'Dandan_Phot'+str(ssNumber)+'_y.dat'
+sigma_y = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[5])
+R_y = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[4])
+
+cataName = basePath+'Dandan_Phot'+str(ssNumber)+'_z.dat'
+sigma_z = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[5])
+R_z = np.loadtxt(cataName,dtype = 'float',unpack=True, usecols=[4])
+
+
+
+''' cosmopara '''
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+
+DL = distance.luminosity_distance(cosmopara,redshift)*1e6 # pc
+
+sigma_x = sigma_x+5.*(np.log10(DL)-1)
+sigma_y = sigma_y+5.*(np.log10(DL)-1)
+sigma_z = sigma_z+5.*(np.log10(DL)-1)
+
+Sigma_x = 10**(-1.*sigma_x/2.5)
+fx = Sigma_x/(np.pi*R_x**2)
+mx = -2.5*np.log10(fx)
+
+Sigma_y= 10**(-1.*sigma_y/2.5)
+fy = Sigma_y/(np.pi*R_y**2)
+my = -2.5*np.log10(fy)
+
+Sigma_z = 10**(-1.*sigma_z/2.5)
+fz = Sigma_x/(np.pi*R_z**2)
+mz = -2.5*np.log10(fz)
+
+disk = open(basePath+'DiskMag_'+str(ssNumber)+'.dat','w')
+
+#Sigma0_x = Sigma_x*np.exp(1.)/2./(np.exp(1.)-2.)
+
+#sigma0_x = -2.5*np.log10(Sigma0_x)
+#print sigma0_x
+
+#mu_x = sigma0_x+1.086*2
+#print mu_x[mu_x>25.5].size

### 2016-07-11 python/Substructure/standard_cata.py

@@ -67,13 +67,16 @@ LensID = np.union1d(LensID,LensID_z)
 
 ## Photometry properties (Dandan's full catalog)
 catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_x.dat'
-bright_x = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+Reff_x = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+bright_x = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[5])
 
 catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_y.dat'
-bright_y = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+Reff_y = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+bright_y = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[5])
 
 catalog3 = basePath+'/Dandan_Phot'+str(ssNumber)+'_z.dat'
-bright_z = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+Reff_z = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[4])
+bright_z = np.loadtxt(catalog3,dtype='float',unpack=True,usecols=[5])
 
 
 ## absolute mag to apparent mag
@@ -84,9 +87,23 @@ class cosmopara:
 	OM = 0.27
 
 DL = distance.luminosity_distance(cosmopara,redshift)*1e6 # pc
-bright_x = bright_x+5.*(np.log10(DL)-1)
-bright_y = bright_y+5.*(np.log10(DL)-1)
-bright_z = bright_z+5.*(np.log10(DL)-1)
+
+bright_x = bright_x+5.*(np.log10(DL)-1) 
+bright_y = bright_y+5.*(np.log10(DL)-1) 
+bright_z = bright_z+5.*(np.log10(DL)-1) 
+
+
+Sigma_x = 10**(-1.*bright_x/2.5)
+fx = Sigma_x/(np.pi*Reff_x**2)
+mx = -2.5*np.log10(fx)
+
+Sigma_y= 10**(-1.*bright_y/2.5)
+fy = Sigma_y/(np.pi*Reff_y**2)
+my = -2.5*np.log10(fy)
+
+Sigma_z = 10**(-1.*bright_z/2.5)
[…]

### 2016-07-18 papers/B1555_EdgeOn/B1555_letter.tex
update realization code for chi2

@@
 The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B.
-\textbf{An exponential disc component is added to the smooth lens model.
-Former study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
+An exponential disc component is added to the smooth lens model.
+Previous study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.
+The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$).
 A detailed definition of these mass profiles is described by \citet{Kee01}.
@@
 
-More sophisticated mass models \textbf{(i.e. external shear or additional halo term)} require additional
+More sophisticated mass models (i.e. external shear or additional halo term) require additional
 constraints, such as those from the lensed extended emission in either
@@
 
-\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.} The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
-We find that adding an elongated exponential disc to a smooth SIE model \textbf{successfully reproduces the flux ratio anomaly in this system}.
+Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.
+The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.
+We find that adding an elongated exponential disc to a smooth SIE model successfully reproduces the flux ratio anomaly in this system.
 % with a reduced $\chi^2 = 2.7$
@@
 %
-{\bf (c)} Observed radio position: blue pluses. Model-predicted position: red open
-circles. The lens-plane critical curves
-are shown with the blue solid line and the source-plane caustics are
-shown with the red dotted line. The position of the source is at
+{\bf (c)} Observed radio positions: blue pluses; Model-predicted positions: red open
+circles; Lens-plane critical curves: blue solid curves; Source-plane caustics: red dotted curves. The source position is at
 ($-0.1953$, $-0.1494$), which is marked by the red filled circle. The
@@
 \centering
-\caption{Best-fit model parameters and uncertainties for our two-component SIE + exponential disc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here).
+\caption{Best-fit model parameters and uncertainties for our two-component SIE + ExpDisc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here).
 The positions are measured in arcsec, relative to the MERLIN radio position of image A.

### 2016-07-18 python/Substructure/Basic_class.py

@@ -38,7 +38,8 @@ class Lens:
 		self.img_y = data[:,1]
 		self.img_f = data[:,2]
 		self.img_err = data[:,3]
-		self.img_ferr = data[:,4]
+		self.img_fr = data[:,4]
+		self.img_frerr = data[:,5]
 
 	def  lens_setFile(self,setup):
 

### 2016-07-18 python/Substructure/create_pfile.py

@@ -1,0 +1,162 @@
+import numpy as np
+import snapshot
+import h5py
+import DistanceTool as distance
+import matplotlib.pyplot as plt
+
+basePath = '/Volumes/narsil_1/jwhsueh/illustris_1'
+snapNum = 99
+
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+## read in Galaxy catalog
+catalog = '../../data/illustris_1/Galaxy_'+str(snapNum)+'_sig.dat'
+
+GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
+CM_x = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
+CM_y = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
+CM_z = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
+
+p_type = ['gas','dm','stars']
+
+field = ['Masses']
+
+## read in snapshot header
+
+f = h5py.File(snapshot.snapPath(basePath,snapNum),'r')
+header = dict( f['Header'].attrs.items() )
+
+#dm_ms =  header['MassTable'][1]*1e10/cosmopara.h # mass of dm particle [M_sun]
+dm_ms =  header['MassTable'][1]*1e10
+
+boxsize = header['BoxSize']  # ckpc/h
+redshift = header['Redshift']
+
+a = 1.0/(1.0+redshift) # scale factor
+
+## this function deal w/ galaxy on the boundary
+def boundary(ci):
+	
+	#ci[ci< 0.5*boxsize] = ci[ci< 0.5*boxsize]+boxsize
+
+	for i in ci:
+		if i<0.5*boxsize:
+			i = i+boxsize
+
+	return ci
+
+## projection function
+
+def projection(c0,c1,c2,axis):
+
+	if axis == 0: # y-z plane
+		p0,p1 = c1,c2
+	elif axis == 1: # x-z plane
+		p0,p1 = c0,c2
+	elif axis==2: # x-y plane
+		p0,p1 = c0,c1
+
+	return p0,p1
+
+## -------start to plot particles
+
+ID = 113727
+
+idx = list(GalaxyID).index(ID)
[…]

### 2016-07-18 python/Substructure/gravlens_tool.py

@@ -255,3 +255,42 @@ def write_Rfold(Rfile,path):
 	Rfile.write(str(R_fold)+'\n')
 
 	return
+
+def write_chi2(chi_file,lens,path):
+	mod_file = path+'findimg.out'
+	x_mod = np.loadtxt(mod_file,dtype='float',unpack=True,usecols=[0])
+	y_mod = np.loadtxt(mod_file,dtype='float',unpack=True,usecols=[1])
+	f_mod = np.loadtxt(mod_file,dtype='float',unpack=True,usecols=[2])
+
+	# flux ratio
+	fr_mod = f_mod/f_mod[0]
+
+	x_obs,y_obs,fr_obs = lens.img_x,lens.img_y,lens.img_fr
+	pos_err,fr_err = lens.img_err,lens.img_frerr
+
+	print x_obs,y_obs,fr_obs,pos_err,fr_err
+	print x_mod,y_mod,fr_mod
+
+	chi2 = 0.
+	for i in range(x_obs.size):
+		chi2 = chi2+(x_obs[i]-x_mod[i])**2/pos_err[i]**2+(y_obs[i]-y_mod[i])**2/pos_err[i]**2
+
+		if i >0:
+			chi2 = chi2 + (fr_obs[i]-fr_mod[i])**2/fr_err[i]**2
+
+
+	chi_file.write(str(chi2)+'\n')
+
+def write_realization(Rnum,path,Rpath):
+
+	info = open(path+'bestSub.dat','r')
+	real_file = open(Rpath+'realization_'+str(Rnum)+'.dat','w')
+
+	lines = info.readlines()
+
+	for Aline in lines:
+		real_file.write(Aline)
+
+	info.close()
+	real_file.close()
+

### 2016-07-18 python/Substructure/realization.py

@@ -13,6 +13,7 @@ lens_name = 'B1422'
 lens_type = 'cusp'
 lensPath = '../../models/lens_info/'
 gravlensPath = '../../data/sub_gravlens/'
+realPath = gravlensPath+lens_name+'_realization/'
 
 # Lens setup file
 lens_setup = np.loadtxt(lensPath+lens_name+'_setup.dat')
@@ -178,6 +179,9 @@ cusp_file.write('# f_sub='+str(f_sub)+', realization='+str(valid_num)+'\n')
 fold_file = open(gravlensPath+str(lens_name)+'_Rfold.dat','a')
 fold_file.write('# f_sub='+str(f_sub)+', realization='+str(valid_num)+'\n')
 
+chi_file = open(gravlensPath+str(lens_name)+'_chi2.dat','a')
+fold_file.write('# f_sub='+str(f_sub)+', realization='+str(valid_num)+'\n')
+
 
 while True:
 	re_mod = set_realization()
@@ -214,12 +218,21 @@ while True:
 		if check == False:
 			print '# realization fail'
 
-		else:
+		else: ##------created
 			print '# realization created'
 			sucess = sucess+1
 
 			gTool.write_Rcusp(cusp_file,gravlensPath)
 			gTool.write_Rfold(fold_file,gravlensPath)
+			gTool.write_chi2(chi_file,Lens,gravlensPath)
+
+			## save realization info
+			gTool.write_realization(sucess,gravlensPath,realPath)
+
+
+
+
+
 
 
 	if sucess>=valid_num:

### 2016-07-23 papers/B1555_EdgeOn/Resubmission_vclear/B1555_EdgeOn.tex
update clean version

--- 2016-07-18 papers/B1555_EdgeOn/B1555_letter.tex
@@
 \centering
-\caption{Best-fit model parameters and uncertainties for our two-component SIE + ExpDisc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here).
-The positions are measured in arcsec, relative to the MERLIN radio position of image A.
+\caption{Best-fit model parameters and uncertainties for our two-component SIE + ExpDisc lens model (our single SIE model is effectively equivalent to the model in \citet{Marlow99} and so is not shown here.) The positions are measured in arcsec, relative to the MERLIN radio position of image A.
 The position angles are measured in degrees east of north.

### 2016-07-23 python/Substructure/illustris_diskplot.py

@@ -1,0 +1,61 @@
+import pandas as pd
+import seaborn as sns
+import numpy as np
+
+import matplotlib.pyplot as plt
+import DistanceTool as distance
+
+basePath = '../../data/illustris_1/'
+ssNumber = 99
+redshift = 0.6
+
+catalog_x = basePath+'full_'+str(ssNumber)+'_x.dat'
+catalog_y = basePath+'full_'+str(ssNumber)+'_y.dat'
+catalog_z = basePath+'full_'+str(ssNumber)+'_z.dat'
+table_x,table_y,table_z = pd.read_csv(catalog_x,sep = '\t'),pd.read_csv(catalog_y,sep = '\t'),pd.read_csv(catalog_z,sep = '\t')
+
+## to a long table
+table = table_x.append(table_y,ignore_index = True)
+table = table.append(table_z,ignore_index = True)
+
+## relaxation
+table = table.loc[(table.relaxation == 0),:]
+
+## velocity dispersion pick
+table = table.loc[(table.velDisp > 130) & (table.velDisp < 370),:]
+
+## add log mass
+table['log_stellar_mass'] = pd.Series(np.log10(table.stellar_mass))
+
+## add apparent surface brightness
+''' cosmopara '''
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+DL = distance.luminosity_distance(cosmopara,redshift)*1e6 # pc
+
+table['SB_exp_m'] = pd.Series(table.SB_Exp+5.*(np.log10(DL)-1))
+
+## add disk total flux
+disk_M = table.SB_Exp -2.5*np.log10(np.pi*table.SteR_halfmass**2)
+
+
+table['disk_mag_r'] = pd.Series(disk_M+5.*(np.log10(DL)-1))
+
+
+## ---- morphology pick ----- ##
+
+morphology = table.loc[(table.Sersic <2) & (table.morphology == 1),:]
+
+## ---- kinematics pick ---- ##
+
+disk_star = table.loc[(table.disk_star_f > 0.4),:]
+bulge_star = table.loc[(table.bulge_star_f < 0.6),:]
+
+## ----- ploting w/ seaborn ----- ##
+
+fig = sns.jointplot(x = 'log_stellar_mass', y = 'r_mag', data=morphology,color = 'r')
+fig.set_axis_labels('log(stellar_mass)','total r_band mag')
+plt.ylim(32,20)
+plt.show()

### 2016-07-23 python/Substructure/real_annulus.py

@@ -1,0 +1,69 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import DistanceTool as distance
+import Basic_class as bClass
+
+import pandas as pd
+
+## read-in realization files & calculate f_sub w/i annulus Re(+0.05",-0.05")
+
+## M_sub = pi*r_t*b_sub*Sigma_c
+
+lensPath = '../../models/lens_info/'
+lens_name = 'B1422'
+gravlensPath = '../../data/sub_gravlens/'
+realPath = gravlensPath+lens_name+'_realization_2/'
+
+num = 1
+
+filePath = realPath+'realization_'+str(num)+'.dat'
+
+b_sub = np.loadtxt(filePath,dtype='float',unpack=True,usecols=[1])
+x = np.loadtxt(filePath,dtype='float',unpack=True,usecols=[2])
+y = np.loadtxt(filePath,dtype='float',unpack=True,usecols=[3])
+rt = np.loadtxt(filePath,dtype='float',unpack=True,usecols=[9])
+
+# get rid of macro model
+b_sub,x,y,rt = b_sub[1:],x[1:],y[1:],rt[1:]
+
+
+## Lens & Cosmology class
+delta = 0.05 # arcsec
+
+# Lens setup file
+lens_setup = np.loadtxt(lensPath+lens_name+'_setup.dat')
+
+Lens = bClass.Lens(lens_setup)
+
+## cosmology parameter
+cospara = bClass.Cosmology()
+
+# critical surface density
+sigma_c = Lens.critical_density()*cospara.h # M_sun/Mpc^2
+sigma_c = sigma_c/(distance.mpc2arcs(cospara,1.,Lens.zl))**2 # M_sub/arcsec^2
+
+## ------annulus mock ------ ##
+
+r_out = Lens.b+delta
+r_in = Lens.b-delta
+
+r = np.sqrt(x**2+y**2)
+
+# ----
+cri_out = r < r_out
+
+b_sub,x,y,rt = b_sub[cri_out],x[cri_out],y[cri_out],rt[cri_out]
+r = r[cri_out]
+
+# ---
+cri_in = r > r_in
+
+b_sub,x,y,rt = b_sub[cri_in],x[cri_in],y[cri_out],rt[cri_out]
+
+
+## -----------
+
+# calculate mass w/i rt
+
+

### 2016-07-23 python/Substructure/standard_cata2.py

@@ -1,0 +1,118 @@
+import numpy as np
+import h5py
+import DistanceTool as distance
+import snapshot
+
+import pandas as pd
+
+basePath = '../../data/illustris_1'
+ssNumber = 99
+Snapshot_num = 'Snapshot_'+str(ssNumber)
+
+## get header file
+headerPath = '/Volumes/narsil_1/jwhsueh/illustris_1'
+
+f = h5py.File(snapshot.snapPath(headerPath,ssNumber),'r')
+header = dict( f['Header'].attrs.items() )
+
+redshift = header['Redshift']
+
+
+## maybe we don't need this part
+'''
+## ----------- Dandan's morphology pick --------------- ##
+# read-in galaxy IDs
+DanM_fx,DanM_fy,DanM_fz = ['subfindID','R_Ex'],['subfindID','R_Ey'],['subfindID','R_Ez']
+DanM_x = pd.read_csv('JenWei_table_disk_in_x.dat',sep = '\t',names = DanM_fx,comment = '#')
+DanM_y = pd.read_csv('JenWei_table_disk_in_y.dat',sep = '\t',names = DanM_fy,comment = '#')
+DanM_z = pd.read_csv('JenWei_table_disk_in_z.dat',sep = '\t',names = DanM_fz,comment = '#')
+
+DanM = pd.merge(DanM_x,DanM_y,how = 'outer',on = 'subfindID')
+DanM = pd.merge(DanM,DanM_z,how = 'outer',on = 'subfindID')
+
+DanM = DanM.sort(['subfindID'])
+DanM['subfindID'] = DanM['subfindID'].astype(int)
+
+DanM = DanM['subfindID']
+'''
+## --------- kinematics ------------ ##
+
+catalog = basePath+'/kinematics_'+str(ssNumber)+'_sig.dat'
+kine_field = ['subfindID','disk_star_f','bulge_star_f']
+kinematics = pd.read_csv(catalog,sep = '\s+',names = kine_field,comment = '#')
+
+## -------- group catalog properties ----- ##
+
+catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
+group_field = ['subfindID','pos_x','pos_y','pos_z','mass','stellar_mass','velDisp','R_halfmass','relaxation','r_mag']
[…]

### 2016-08-04 papers/illustris_disk/ms.tex
update illustris disk paper draft

\documentclass[useAMS,usenatbib]{mn2e}
%\documentclass[usenatbib]{mn2e}
\usepackage{graphicx}
%\usepackage[nottoc]{tocbibind}
\setlength{\topmargin}{-1.2cm}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%

% Journal definitions
\newcommand{\apj}[1]{ApJ}
\newcommand{\mnras}[1]{MNRAS}
\newcommand{\apjl}[1]{ApJL}
\newcommand{\pasj}[1]{PASJ}
\newcommand{\aj}[1]{AJ}
\newcommand{\nat}[1]{Nature}
\newcommand{\aap}{A\&A}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Flux ratio anomalies from disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
SHARP IV: Flux ratio anomalies from disks in the Illustris simulation
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

%\date{Accepted 1988 December 15. Received 1988 December 14; in original form 1988 October 11}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

\maketitle

\label{firstpage}

\begin{abstract}

\end{abstract}

\begin{keywords}
gravitational lensing
\end{keywords}

\section{Introduction}
\section{The Illustris simulation}
\section{Disks selection}
\begin{itemize}
\item discuss how realistic disks in illustris are
\end{itemize}
\subsection{Morphological selection}
\subsection{Kinematical selection I}
\subsection{Kinematical selection II}
\section{Disk properties}
\begin{itemize}
\item how many galaxies have disks
\item mass in disk
\item redshift evolution
\item comparison with B1555 and SWELLS
\item observability of the disks
\end{itemize}
\section{Flux ratio anomalies from disks}

\section{Discussion}
\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{reference.bib}

\label{lastpage}

\end{document}

### 2016-08-04 python/Substructure/create_DanCat.py

@@ -1,0 +1,37 @@
+import pandas as pd
+import numpy as np
+
+## read-in Dandan's catalog list and create two 'TotList'
+
+ssNumber = '120'
+
+catPath = '/Volumes/narsil_1/jwhsueh/illustris_1/snapshot_catalog/LensingCataSnap'+ssNumber+'/'
+
+catfile = 'InAll3Proj.list'
+
+table = pd.read_csv(catPath+catfile,sep= '_',names = 'abcdef')
+
+# get the list of fxx
+# get rid of duplicates
+table = table.drop_duplicates('c')
+
+#print table
+
+name_list = np.array(table.c)
+
+## output Lens & Phot file list
+
+TotList = ['TotCata_Lens.list','TotCata_Phot.list','TotCata_Gas.list']
+
+LensList = open(catPath+TotList[0],'w')
+PhotList = open(catPath+TotList[1],'w')
+GasList = open(catPath+TotList[2],'w')
+
+for f_name in name_list:
+	LensList.write('IllustrisLens_'+f_name+'_LensingGalParam.dat\n')
+	PhotList.write('IllustrisLens_'+f_name+'_LightMeasInStrDymBID.dat\n')
+	GasList.write('IllustrisLens_'+f_name+'_ShapeFracSlpMeasInMorphBID.dat\n')
+
+LensList.close()
+PhotList.close()
+GasList.close()

### 2016-08-04 python/Substructure/galaxy_cat.py

@@ -4,8 +4,8 @@ import DistanceTool as distance
 
 basePath = '../../data/illustris_1'
 
-ssNumber = 99 # snapshotnumber
-z = 0.6
+ssNumber = 85 # snapshotnumber
+z = 1.0
 
 a = 1./(1.+z)
 
@@ -46,16 +46,20 @@ Rhal_st = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloHalfmassRad
 sigma = groupcat.loadSubhalos(basePath,ssNumber,fields = ['SubhaloVelDisp'])
 sigma = sigma[GroupFirstSub]
 
-sigma_h = 370.
-sigma_l = 130.
+#sigma_h = 370.
+#sigma_l = 130.
+sigma_h = 500.
+sigma_l = 0.
 
 #photometry
+B_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,1]
 V_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,2]
 K_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,3]
 r_mag = groupcat.loadSubhalos(basePath,ssNumber, fields = ['SubhaloStellarPhotometrics'])[:,5]
 
 # apparent mag
 DL = distance.luminosity_distance(cosmopara,z)*1e6 # pc
+B_mag = B_mag+5.*(np.log10(DL)-1)
 V_mag = V_mag+5.*(np.log10(DL)-1)
 K_mag = K_mag+5.*(np.log10(DL)-1)
 r_mag = r_mag+5.*(np.log10(DL)-1)
@@ -66,7 +70,7 @@ r_mag = r_mag+5.*(np.log10(DL)-1)
 ## rewrite this part!!! [str mass]
 ## use group mass as galaxy cretria 
 ## here!!
-GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh,Galaxy_V = [],[],[],[],[],[],[]
+GalaxyID,GalaxyPos,Galaxy_ms,Galaxy_str,Galaxy_sig,Galaxy_Rh,Galaxy_r,Galaxy_B,Galaxy_V = [],[],[],[],[],[],[],[],[]
 
 for i in range(sigma.size):
 	if sigma[i]<sigma_h and sigma[i]>sigma_l:
[…]

### 2016-08-04 python/Substructure/illustris_diskplot.py

@@ -6,26 +6,42 @@ import matplotlib.pyplot as plt
 import DistanceTool as distance
 
 basePath = '../../data/illustris_1/'
-ssNumber = 99
-redshift = 0.6
+ssNumber = '120'
+redshift = 0.2
 
-catalog_x = basePath+'full_'+str(ssNumber)+'_x.dat'
-catalog_y = basePath+'full_'+str(ssNumber)+'_y.dat'
-catalog_z = basePath+'full_'+str(ssNumber)+'_z.dat'
+catalog_x = basePath+'test_'+str(ssNumber)+'_x.dat'
+catalog_y = basePath+'test_'+str(ssNumber)+'_y.dat'
+catalog_z = basePath+'test_'+str(ssNumber)+'_z.dat'
 table_x,table_y,table_z = pd.read_csv(catalog_x,sep = '\t'),pd.read_csv(catalog_y,sep = '\t'),pd.read_csv(catalog_z,sep = '\t')
 
 ## to a long table
 table = table_x.append(table_y,ignore_index = True)
-table = table.append(table_z,ignore_index = True)
+all_table = table.append(table_z,ignore_index = True)
+
+all_table = all_table.loc[(all_table.r_mag <100)&(all_table.B_mag <100)&(all_table.V_mag <100),:]
+
+#print all_table
+
+## stellar mass lower limit
+all_table = all_table.loc[(all_table.stellar_mass>1e10),:]
+
+## total flux cut
+
+#all_table = all_table.loc[(all_table.r_mag<25.),:]
+
 
 ## relaxation
-table = table.loc[(table.relaxation == 0),:]
+table = all_table.loc[(all_table.relaxation == 0),:] # table is for disk systems
 
-## velocity dispersion pick
-table = table.loc[(table.velDisp > 130) & (table.velDisp < 370),:]
+## edge-on pick
+#table = table.loc[(table.theta > 80.) & (table.theta < 100.),:]
 
-## add log mass
-table['log_stellar_mass'] = pd.Series(np.log10(table.stellar_mass))
+## add columns
+
+table['log_stellar_mass']= np.log10(table.stellar_mass)
+table['color'] = table.B_mag - table.V_mag
+
+#print table.log_stellar_mass
 
 ## add apparent surface brightness
[…]

### 2016-08-04 python/Substructure/illustris_gplot.py

@@ -1,0 +1,47 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+basePath = '../../data/illustris_1/'
+
+ssNumber = ['085','099','120'] # snapshotnumber
+z = [1.0,0.6,0.2]
+
+## -------- group catalog properties [general] ----- ##
+
+catalog = basePath+'/Galaxy_'+ssNumber[0]+'_test.dat'
+group_field = ['subfindID','pos_x','pos_y','pos_z','mass','stellar_mass','velDisp','R_halfmass','relaxation','r_mag','B_mag','V_mag']
+group0 = pd.read_csv(catalog,sep = '\s+',names = group_field,comment = '#')
+
+catalog = basePath+'/Galaxy_'+ssNumber[1]+'_test.dat'
+group1 = pd.read_csv(catalog,sep = '\s+',names = group_field,comment = '#')
+
+catalog = basePath+'/Galaxy_'+ssNumber[2]+'_test.dat'
+group2 = pd.read_csv(catalog,sep = '\s+',names = group_field,comment = '#')
+
+## stellar_mass cut
+
+#group0 = group0.loc[(group0.stellar_mass>1e10),:]
+#group1 = group1.loc[(group1.stellar_mass>1e10),:]
+#group2 = group2.loc[(group2.stellar_mass>1e10),:]
+
+se = np.linspace(0,370,40)
+dot = []
+for i in range(se.size-1):
+	dot.append((se[i]+se[i+1])/2.)
+
+group0_vel = np.histogram(group0.velDisp,bins = se)[0].astype(float)
+group1_vel = np.histogram(group1.velDisp,bins = se)[0].astype(float)
+group2_vel = np.histogram(group2.velDisp,bins = se)[0].astype(float)
+
+## plot
+
+plt.plot(dot,group0_vel,color='k',drawstyle='steps',label = 'z='+str(z[0]))
+plt.plot(dot,group1_vel,color='b',drawstyle='steps',label = 'z='+str(z[1]))
+plt.plot(dot,group2_vel,color='r',drawstyle='steps',label = 'z='+str(z[2]))
+plt.legend()
+plt.xlabel('velocity dispersion [km/s]')
+plt.ylabel('counts')
+plt.title('All galaxies')
+#plt.show()
+plt.savefig(basePath+'redshift_evo/velDisp.png')

### 2016-08-04 python/Substructure/illustris_theta.py

@@ -1,0 +1,136 @@
+import numpy as np
+import snapshot
+import h5py
+import groupcat
+import DistanceTool as distance
+
+#### --------------change path setting here -------------#####
+## snapshotPath: where the snapshot directory is
+## catalog: Galaxy catalog (read in)
+## in_cata: Inclination catalog (write out)
+
+snapshotPath = '/Volumes/narsil_1/jwhsueh/illustris_1'
+snapNum = '099'
+ssNum = 99
+
+catalog = '../../data/illustris_1/Galaxy_'+str(snapNum)+'_sig.dat'
+in_cata = open('../../data/illustris_1/Inclination_'+str(snapNum)+'_test.dat','w')
+
+#### -------------------------------- #####
+
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+## read in Galaxy catalog
+
+GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
+CM_x = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[1])
+CM_y = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[2])
+CM_z = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[3])
+R_half = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[7]) # kpc/h
+
+p_type = ['gas','dm','stars']
+
+field = ['Masses','Velocities']
+
+## read in snapshot header
+
+f = h5py.File(snapshot.snapPath(snapshotPath,ssNum),'r')
+header = dict( f['Header'].attrs.items() )
+
+boxsize = header['BoxSize']  # ckpc/h
+redshift = header['Redshift']
+
+a = 1.0/(1.0+redshift) # scale factor
+
+# get peculiar velocity of group
+SubVel = groupcat.loadSubhalos(snapshotPath,snapNum, fields = ['SubhaloVel'])
+
+## this function deal w/ galaxy on the boundary
+def boundary(ci):
+	
[…]

### 2016-08-04 python/Substructure/illustris_zplot.py

@@ -1,0 +1,65 @@
+import pandas as pd
+import seaborn as sns
+import numpy as np
+
+import matplotlib.pyplot as plt
+import DistanceTool as distance
+
+basePath = '../../data/illustris_1/redshift_evo/'
+ssNumber = ['085','099','120']
+redshift = [1.0,0.6,0.2]
+
+file0 = basePath+'snapshot'+ssNumber[0]+'_three.dat'
+file1 = basePath+'snapshot'+ssNumber[1]+'_three.dat'
+file2 = basePath+'snapshot'+ssNumber[2]+'_three.dat'
+
+## scatter plot
+z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
+#print z0
+
+plt.scatter(z0.V_mag,z0.color,c = 'b',label = 'z='+str(redshift[0]),marker = '.')
+plt.scatter(z1.V_mag,z1.color,c='g',label = 'z='+str(redshift[1]),marker = 'x')
+plt.scatter(z2.V_mag,z2.color,c = 'r',label = 'z='+str(redshift[2]))
+
+plt.title('Galaxies satisfy all criteria')
+plt.legend(loc = 1)
+plt.xlabel('V_mag')
+plt.ylabel('B-V')
+plt.xlim(15,35)
+plt.ylim(-0.2,1.)
+#plt.show()
+plt.savefig('./illustris_cross/zEvo_color_three.png',bbox_inches='tight')
+
+'''
+## hist
+
+z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
+
+z0['mor_hist'] = z0.morphology/z0.All
+z1['mor_hist'] = z1.morphology/z0.All
+z2['mor_hist'] = z2.morphology/z0.All
+
+z0['disk_hist'] = z0.disk_star/z0.All
+z1['disk_hist'] = z1.disk_star/z0.All
+z2['disk_hist'] = z2.disk_star/z0.All
+
+z0['bulge_hist'] = z0.bulge_star/z0.All
+z1['bulge_hist'] = z1.bulge_star/z0.All
+z2['bulge_hist'] = z2.bulge_star/z0.All
+
+#print z0
+
[…]

### 2016-08-04 python/Substructure/readout_DanCat.py

@@ -1,10 +1,10 @@
 import numpy as np
 import groupcat
 
-catPath = '../../data/Snap099Data4JW/Snap099Cata/'
-basePath = '../../data/illustris_1/'
+ssNumber = '085'
 
-ssNumber = 99
+catPath = '/Volumes/narsil_1/jwhsueh/illustris_1/snapshot_catalog/LensingCataSnap'+str(ssNumber)+'/'
+basePath = '../../data/illustris_1/'
 
 Proj = ['NatProj_1/','NatProj_2/','NatProj_3/']
 
@@ -15,23 +15,26 @@ Proj = ['NatProj_1/','NatProj_2/','NatProj_3/']
 
 #GroupFirstSub = groupcat.loadHalos(basePath,ssNumber,fields = ['GroupFirstSub'])
 
-TotList = ['TotCata_Lens.list','TotCata_Phot.list']
-list_idx = 1
-
+TotList = ['TotCata_Lens.list','TotCata_Phot.list','TotCata_Gas.list']
+list_idx = 0
 p_index = 0 # Proj index
 
-cataName = basePath+'Dandan_Phot'+str(ssNumber)+'_x.dat'
+cataName = basePath+'Dandan_Lens'+ssNumber+'_x.dat'
 
 CataList = open(catPath+Proj[p_index]+TotList[list_idx],'r')
 CataList = CataList.read().splitlines()
 
 ## Lens
-#field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
-#f_idx = np.array([0,5,6,7,11])
+field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
+f_idx = np.array([0,5,6,7,11])
 
 ## Phot
-field = ['SubfindID','mass [M_sun/h]','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
-f_idx = np.array([0,3,4,10,18,22,24])
+#field = ['SubfindID','mass [M_sun/h]','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
[…]

### 2016-08-04 python/Substructure/rerun_findimg.py

@@ -62,52 +62,76 @@ find_input = 'rescale_find.input'
 
 findimg_file = open(path+output,'w')
 
-	create_bestSub(path)
-	opt_result = open(path+'bestSub.dat','r')
+gTool.create_bestSub(path)
+opt_result = open(path+'bestSub.dat','r')
 
-	## need to modify
-	## write number of lens and srcs [startup]
-
-	# get another function to create pure best substructure result
-
-	lines = opt_result.readlines()[:-1]
-	n_lens = len(lines)
-	findimg_file.write('startup '+str(n_lens)+' 1\n')
-
-	#opt_result.readline() # get rid of first line
-	#opt_lines = opt_result.readlines()
+lines = opt_result.readlines()[:-1]
+n_lens = len(lines)
+findimg_file.write('startup '+str(n_lens)+' 1\n')
 
 	# write in substructures
 
-	for Aline in lines:
-		#Aline = opt_result.readline()
-		findimg_file.write(Aline)
-		#print Aline
-		#print '##'+str(i)
+for Aline in lines:
 
-	opt_result.close()
+	findimg_file.write(Aline)
 
-	## --end of gravlens startup--
+opt_result.close()
 
-	## --write a bunch of zeros--
+## --end of gravlens startup--
 
-	zeros = '0 0 0 0 0 0 0 0 0 0\n'
-	for i in range(n_lens):
-		findimg_file.write(zeros)
+## --write a bunch of zeros--
 
-	findimg_file.write('\n')
+zeros = '0 0 0 0 0 0 0 0 0 0\n'
+for i in range(n_lens):
+	findimg_file.write(zeros)
 
-	## write findimg command
-	# get srcs position
-	opt_result = open('best.dat','r')
-	raw_line = opt_result.readlines() # get all the rest lines
-	#print raw_line
-	raw_line = raw_line[-11].split()
-	#print raw_line
+findimg_file.write('\n')
+## write findimg command
+# get srcs position
+opt_result = open('best.dat','r')
+raw_line = opt_result.readlines() # get all the rest lines
+#print raw_line
+raw_line = raw_line[-11].split()
+#print raw_line
 
-	findimg_file.write('findimg '+raw_line[1]+' '+raw_line[2]+'\n')
+findimg_file.write('findimg '+raw_line[1]+' '+raw_line[2]+'\n')
 
-	opt_result.close()
-	findimg_file.close()
+opt_result.close()
[…]

### 2016-08-04 python/Substructure/standard_cata3.py

@@ -6,9 +6,9 @@ import snapshot
 import pandas as pd
 
 basePath = '../../data/illustris_1'
-redshift = 0.2
+redshift = 1.0
 
-ssNumber = '120'
+ssNumber = '085'
 
 
 ## maybe we don't need this part
@@ -36,12 +36,13 @@ kinematics = pd.read_csv(catalog,sep = '\s+',names = kine_field,comment = '#')
 
 ## -------- group catalog properties [general] ----- ##
 
-catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
+catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_test.dat'
 group_field = ['subfindID','pos_x','pos_y','pos_z','mass','stellar_mass','velDisp','R_halfmass','relaxation','r_mag','B_mag','V_mag']
 group = pd.read_csv(catalog2,sep = '\s+',names = group_field,comment = '#')
 
 # standard DataFrame
-standard = pd.merge(group,kinematics,how = 'inner',on = 'subfindID')
+standard = pd.merge(group,kinematics,how = 'outer',on = 'subfindID')
+print np.array(group.subfindID)[-1],np.array(standard.subfindID)[-1]
 
 ## -------- inclination angle --------- ##
 
@@ -120,27 +121,27 @@ Gas_z = pd.read_csv(catalog3z,sep = '\s+',names = Gas_fz,comment = '#')
 
 ## -------- put together to larger cataloga (x,y,z) ------- ##
 
-standard_x = pd.merge(standard,Lens_x,how = 'inner',on = 'subfindID')
-standard_x = pd.merge(standard_x,inc_x,how = 'inner',on = 'subfindID')
-standard_x = pd.merge(standard_x,Phot_x,how = 'inner',on = 'subfindID')
-standard_x = pd.merge(standard_x,Gas_x,how = 'inner',on = 'subfindID')
+standard_x = pd.merge(standard,Lens_x,how = 'outer',on = 'subfindID')
+standard_x = pd.merge(standard_x,inc_x,how = 'outer',on = 'subfindID')
+standard_x = pd.merge(standard_x,Phot_x,how = 'outer',on = 'subfindID')
+standard_x = pd.merge(standard_x,Gas_x,how = 'outer',on = 'subfindID')
 
-standard_y = pd.merge(standard,Lens_y,how = 'inner',on = 'subfindID')
[…]

### 2016-08-09 papers/illustris_disk/ms.tex
update disk paper draft

@@
 \end{itemize}
+Resolution: stellar mass cut between 7E9Msun~1E10Msun. Due to the resolution limitation, our disk galaxy samples are from the high-mass range of disk galaxy population, with mass range [].
+
 \subsection{Morphological selection}
+Photometric properties are commonly used in surveys to identify the morphology type of galaxies.
+Star particles in simulation can also be visualized (SUNRISE) and provide photometric observants for individual galaxy.
+We apply the following two criteria to identity a disk galaxy in Illustris simulation: 1) The galaxy has a
+better fit (i.e.
+a smaller $\chi^2$) in exponential disk light profile than in de Vaucouleur light profile, and 2) the galaxy has a Sersic index smaller than two.
+The sample selected by these photometric properties are called morphological selection in this work.
+
 \subsection{Kinematical selection I}
+In kinematical view, stellar disk is a group of stars co-rotate in the same direction with the common symmetric axis.
+One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle.
+These kinematical properties provide an approach to decompose different components in disk galaxy: thin disk, thick disk, and spheroid.
+z-component angular momentum (symmetric axis)
+Jz vs binding energy: $J_{circ}$ curve
+circularity parameter $\epsilon_z = Jz/J_{circ}$
+
+decomposition: thin disk+thick disk+spheroid
+
+thin disk star fraction larger than 40\%
+
 \subsection{Kinematical selection II}
+stars in spheroid: bulge stars
+bulge star fraction less than 60\%
 \section{Disk properties}

### 2016-08-09 python/Substructure/illustris_circ.py

@@ -10,7 +10,7 @@ class cosmopara:
 	OM = 0.27
 
 basePath = '../../data/illustris_1'
-ssNumber = 85
+ssNumber = 120
 
 Snapshot_num = 'Snapshot_'+str(ssNumber)
 
@@ -24,7 +24,7 @@ Js = circFile[Snapshot_num]['SpecificAngMom']
 
 ## read in Galaxy catalog
 
-catalog = basePath+'/Galaxy_'+str(ssNumber)+'_sig.dat'
+catalog = basePath+'/Galaxy_'+str(ssNumber)+'_test.dat'
 GalaxyID = np.loadtxt(catalog,dtype = 'int',unpack=True, usecols=[0])
 #star_ms = np.loadtxt(catalog,dtype = 'float',unpack=True, usecols=[4]) # stellar mass
 
@@ -54,7 +54,7 @@ Ms = np.array(Ms)
 
 AngMomIndex = np.log10(Js/Ms**(2./3.))
 '''
-catalog = open(basePath+'/kinematics_'+str(ssNumber)+'_sig.dat','w')
+catalog = open(basePath+'/kinematics_'+str(ssNumber)+'_test.dat','w')
 #catalog.write('# Galaxy SubID   Angular Momemtum   Disk star frac    Bulge star frac'+'\n')
 
 catalog.write('# [0]: Galaxy SubID'+'\n')

### 2016-08-09 python/Substructure/illustris_diskplot.py

@@ -8,6 +8,7 @@ import DistanceTool as distance
 basePath = '../../data/illustris_1/'
 ssNumber = '120'
 redshift = 0.2
+print ssNumber
 
 catalog_x = basePath+'test_'+str(ssNumber)+'_x.dat'
 catalog_y = basePath+'test_'+str(ssNumber)+'_y.dat'
@@ -23,7 +24,14 @@ all_table = all_table.loc[(all_table.r_mag <100)&(all_table.B_mag <100)&(all_tab
 #print all_table
 
 ## stellar mass lower limit
-all_table = all_table.loc[(all_table.stellar_mass>1e10),:]
+all_table = all_table.loc[(all_table.stellar_mass>1e9),:]
+
+## add columns
+
+all_table.stellar_mass = all_table.stellar_mass/0.71
+all_table['log_stellar_mass']= np.log10(all_table.stellar_mass)
+all_table['color'] = all_table.B_mag - all_table.V_mag
+all_table['mor_mix'] = 0
 
 ## total flux cut
 
@@ -32,14 +40,12 @@ all_table = all_table.loc[(all_table.stellar_mass>1e10),:]
 
 ## relaxation
 table = all_table.loc[(all_table.relaxation == 0),:] # table is for disk systems
+#table = all_table # disk_table
 
 ## edge-on pick
 #table = table.loc[(table.theta > 80.) & (table.theta < 100.),:]
 
-## add columns
 
-table['log_stellar_mass']= np.log10(table.stellar_mass)
-table['color'] = table.B_mag - table.V_mag
 
 #print table.log_stellar_mass
 
@@ -58,7 +64,11 @@ table['SB_exp_m'] = -5./2.*(table.SB_Exp+8.9)
 
 ## ---- morphology pick ----- ##
 
-morphology = table.loc[(table.Sersic <2) & (table.morphology == 0),:]
+morphology_single = table.loc[(table.Sersic <2) & (table.morphology == 0),:]
+
+table.mor_mix.loc[table.subfindID.isin(morphology_single.subfindID)] = 1 # morphology coverage pick
+
+morphology = table.loc[(table.mor_mix == 1),:]
 
 ## ---- kinematics pick ---- ##
 
@@ -67,7 +77,7 @@ bulge_star = table.loc[(table.bulge_star_f < 0.6),:]
 '''
 ## ---- hybird catagories ---- ##
 
[…]

### 2016-08-09 python/Substructure/illustris_gplot.py

@@ -21,10 +21,24 @@ group2 = pd.read_csv(catalog,sep = '\s+',names = group_field,comment = '#')
 
 ## stellar_mass cut
 
-#group0 = group0.loc[(group0.stellar_mass>1e10),:]
-#group1 = group1.loc[(group1.stellar_mass>1e10),:]
-#group2 = group2.loc[(group2.stellar_mass>1e10),:]
+z0 = group0.loc[(group0.stellar_mass>1e9),:]
+z1 = group1.loc[(group1.stellar_mass>1e9),:]
+z2 = group2.loc[(group2.stellar_mass>1e9),:]
 
+z0['log_stellar_mass'] = np.log10(z0.stellar_mass)
+z1['log_stellar_mass'] = np.log10(z1.stellar_mass)
+z2['log_stellar_mass'] = np.log10(z2.stellar_mass)
+
+
+## scatter plot
+
+plt.scatter(z0.velDisp,z0.log_stellar_mass,c = 'b',label = 'z='+str(z[0]),marker = 'x')
+plt.scatter(z1.velDisp,z1.log_stellar_mass,c='g',label = 'z='+str(z[1]),marker = 'x')
+plt.scatter(z2.velDisp,z2.log_stellar_mass,c = 'r',label = 'z='+str(z[2]),marker = 'x')
+plt.title('All galaxies')
+plt.show()
+
+'''
 se = np.linspace(0,370,40)
 dot = []
 for i in range(se.size-1):
@@ -45,3 +59,4 @@ plt.ylabel('counts')
 plt.title('All galaxies')
 #plt.show()
 plt.savefig(basePath+'redshift_evo/velDisp.png')
+'''

### 2016-08-09 python/Substructure/illustris_zplot.py

@@ -9,10 +9,10 @@ basePath = '../../data/illustris_1/redshift_evo/'
 ssNumber = ['085','099','120']
 redshift = [1.0,0.6,0.2]
 
-file0 = basePath+'snapshot'+ssNumber[0]+'_three.dat'
-file1 = basePath+'snapshot'+ssNumber[1]+'_three.dat'
-file2 = basePath+'snapshot'+ssNumber[2]+'_three.dat'
-
+file0 = basePath+'snapshot'+ssNumber[0]+'st_hist_30.dat'
+file1 = basePath+'snapshot'+ssNumber[1]+'st_hist_30.dat'
+file2 = basePath+'snapshot'+ssNumber[2]+'st_hist_30.dat'
+'''
 ## scatter plot
 z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
 #print z0
@@ -36,30 +36,29 @@ plt.savefig('./illustris_cross/zEvo_color_three.png',bbox_inches='tight')
 z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
 
 z0['mor_hist'] = z0.morphology/z0.All
-z1['mor_hist'] = z1.morphology/z0.All
-z2['mor_hist'] = z2.morphology/z0.All
+z1['mor_hist'] = z1.morphology/z1.All
+z2['mor_hist'] = z2.morphology/z2.All
 
 z0['disk_hist'] = z0.disk_star/z0.All
-z1['disk_hist'] = z1.disk_star/z0.All
-z2['disk_hist'] = z2.disk_star/z0.All
+z1['disk_hist'] = z1.disk_star/z1.All
+z2['disk_hist'] = z2.disk_star/z2.All
 
 z0['bulge_hist'] = z0.bulge_star/z0.All
-z1['bulge_hist'] = z1.bulge_star/z0.All
-z2['bulge_hist'] = z2.bulge_star/z0.All
+z1['bulge_hist'] = z1.bulge_star/z1.All
+z2['bulge_hist'] = z2.bulge_star/z2.All
 
 #print z0
 
-plt.plot(z0.R_E,z0.mor_hist,color='k',label = 'z='+str(redshift[0]),drawstyle='steps',linestyle = 'dashdot')
[…]

### 2016-08-09 python/Substructure/readout_DanCat.py

@@ -1,7 +1,7 @@
 import numpy as np
 import groupcat
 
-ssNumber = '085'
+ssNumber = '120'
 
 catPath = '/Volumes/narsil_1/jwhsueh/illustris_1/snapshot_catalog/LensingCataSnap'+str(ssNumber)+'/'
 basePath = '../../data/illustris_1/'
@@ -16,7 +16,7 @@ Proj = ['NatProj_1/','NatProj_2/','NatProj_3/']
 #GroupFirstSub = groupcat.loadHalos(basePath,ssNumber,fields = ['GroupFirstSub'])
 
 TotList = ['TotCata_Lens.list','TotCata_Phot.list','TotCata_Gas.list']
-list_idx = 0
+list_idx = 2
 p_index = 0 # Proj index
 
 cataName = basePath+'Dandan_Lens'+ssNumber+'_x.dat'
@@ -25,12 +25,12 @@ CataList = open(catPath+Proj[p_index]+TotList[list_idx],'r')
 CataList = CataList.read().splitlines()
 
 ## Lens
-field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
-f_idx = np.array([0,5,6,7,11])
+#field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
+#f_idx = np.array([0,5,6,7,11])
 
 ## Phot
-#field = ['SubfindID','mass [M_sun/h]','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
-#f_idx = np.array([0,3,4,10,18,22,24])
+field = ['SubfindID','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
+f_idx = np.array([0,8,10,18,22,24])
 
 ## Gas
 #field = ['subfindID','fgas','fcgs']
@@ -57,7 +57,7 @@ for file_name in CataList:
 	#cata_file = open(catPath+Proj[p_index]+file_name,'r')
 	#sub_table = np.loadtxt(cata_file,skiprows=1,unpack=True, usecols=[3,4,18,22,24])
[…]

### 2016-08-09 python/Substructure/standard_cata3.py

@@ -6,9 +6,10 @@ import snapshot
 import pandas as pd
 
 basePath = '../../data/illustris_1'
-redshift = 1.0
+redshift = 0.2
 
-ssNumber = '085'
+ssNumber = '120'
+print ssNumber
 
 
 ## maybe we don't need this part
@@ -20,8 +21,8 @@ DanM_x = pd.read_csv('JenWei_table_disk_in_x.dat',sep = '\t',names = DanM_fx,com
 DanM_y = pd.read_csv('JenWei_table_disk_in_y.dat',sep = '\t',names = DanM_fy,comment = '#')
 DanM_z = pd.read_csv('JenWei_table_disk_in_z.dat',sep = '\t',names = DanM_fz,comment = '#')
 
-DanM = pd.merge(DanM_x,DanM_y,how = 'outer',on = 'subfindID')
-DanM = pd.merge(DanM,DanM_z,how = 'outer',on = 'subfindID')
+DanM = pd.merge(DanM_x,DanM_y,how = 'inner',on = 'subfindID')
+DanM = pd.merge(DanM,DanM_z,how = 'inner',on = 'subfindID')
 
 DanM = DanM.sort(['subfindID'])
 DanM['subfindID'] = DanM['subfindID'].astype(int)
@@ -30,20 +31,21 @@ DanM = DanM['subfindID']
 '''
 ## --------- kinematics ------------ ##
 
-catalog = basePath+'/kinematics_'+str(ssNumber)+'_sig.dat'
+catalog = basePath+'/kinematics_'+str(ssNumber)+'_test.dat'
 kine_field = ['subfindID','disk_star_f','bulge_star_f']
 kinematics = pd.read_csv(catalog,sep = '\s+',names = kine_field,comment = '#')
 
 ## -------- group catalog properties [general] ----- ##
 
 catalog2 = basePath+'/Galaxy_'+str(ssNumber)+'_test.dat'
-group_field = ['subfindID','pos_x','pos_y','pos_z','mass','stellar_mass','velDisp','R_halfmass','relaxation','r_mag','B_mag','V_mag']
+group_field = ['subfindID','pos_x','pos_y','pos_z','mass','stellar_mass_all','velDisp','R_halfmass','relaxation','r_mag','B_mag','V_mag']
 group = pd.read_csv(catalog2,sep = '\s+',names = group_field,comment = '#')
 
 # standard DataFrame
[…]

### 2016-08-09 python/lens_plot.py

@@ -158,8 +158,8 @@ img_pos(lens_name)
 #plt.xlim(0.4,-0.8)
 #plt.ylim(-0.8,0.4)
 
-plt.xlim(1.6,-0.4)
-plt.ylim(-0.8,1.2)
+plt.xlim(2.0,-0.5)
+plt.ylim(-1.0,1.5)
 
 plt.legend(loc=1)
 

### 2016-08-11 papers/illustris_disk/ms.tex
update illustris paper draft

@@
 \subsection{Kinematical selection I}
-In kinematical view, stellar disk is a group of stars co-rotate in the same direction with the common symmetric axis.
-One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle.
+In kinematical view, stellar disk is a group of stars co-rotate in the same direction around the  symmetric axis (we will call this symmetric axis ``z-axis,'' for short.) One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle.
 These kinematical properties provide an approach to decompose different components in disk galaxy: thin disk, thick disk, and spheroid.
-z-component angular momentum (symmetric axis)
-Jz vs binding energy: $J_{circ}$ curve
-circularity parameter $\epsilon_z = Jz/J_{circ}$
-
-decomposition: thin disk+thick disk+spheroid
-
-thin disk star fraction larger than 40\%
+The dynamical decomposition can be done in the parameter space of the z-component of specific angular momemtum, $J_z$, and the specific binding energy, $E$, of each star (Abadi, et al.
+2003).
+On the $J_z - E$ plane, stellar and gaseous components co-rorating in the same direction define a solid curve $J_{circ}(E)$ (see Fig.2 in Abadi, et al.
+2003), which represents the coratating circular orbits in the disk as a function of specific binding energy.
+The circularity parameter $\epsilon_z$ of each star is defined as the ratio between its  $J_z$ and corresponding $J_{circ}(E)$, showing how closely a stellar or gaseous component follows the circular motion of the disk.
+In general, the gaseous disk and the thin disk stellar components have a sharp distribution of $\epsilon_z$ peaked about unity.
+Base on the $\epsilon_z$ distribution, all stars within the ``luminous'' radius can be decomposed into three different dynamical components: a spheriod (including bulge and halo stars), thin disk (stars with $\epsilon_z > 0.7$), and thick disk.
+Galaxies with more than 40 per cent of stars in thin disk are considered as late-type spirals.
 
 \subsection{Kinematical selection II}
-stars in spheroid: bulge stars
-bulge star fraction less than 60\%
+Having more than 40 per cent of stars in thin disk is a strict criteria which selects the galaxies with a large disk and a small bulge.
+However, spirals with a smaller thin disk but large enough thick disk may also provide sufficient gravitational perturbation to influence lens image flux ratios.
+Thus we select galaxies having more than 40 per cent stars in their thin disk and thick disk, in another word, galaxies having less than 60 per cent of stars in bulge and halo as the second kinematical selection of disk galaxies.
+
 \section{Disk properties}

### 2016-08-11 python/Substructure/illustris_circ.py

@@ -10,7 +10,8 @@ class cosmopara:
 	OM = 0.27
 
 basePath = '../../data/illustris_1'
-ssNumber = 120
+ssNumber = 85
+print ssNumber
 
 Snapshot_num = 'Snapshot_'+str(ssNumber)
 
@@ -21,7 +22,7 @@ SubfindID_circ = circFile[Snapshot_num]['SubfindID']
 CircAbove07Frac = circFile[Snapshot_num]['CircAbove07Frac']
 beta = circFile[Snapshot_num]['CircTwiceBelow0Frac']
 Js = circFile[Snapshot_num]['SpecificAngMom']
-
+'''
 ## read in Galaxy catalog
 
 catalog = basePath+'/Galaxy_'+str(ssNumber)+'_test.dat'
@@ -36,10 +37,13 @@ mask = np.array(mask)
 
 ## star fraction& specific angular momentum
 
+# only get central galaxy
 CircAbove07Frac = CircAbove07Frac[mask]
 beta = beta[mask]
 Js = Js[mask]
 SubfindID_circ = SubfindID_circ[mask]
+'''
+
 '''
 ## indicator of specific angular momentum
 
@@ -54,7 +58,7 @@ Ms = np.array(Ms)
 
 AngMomIndex = np.log10(Js/Ms**(2./3.))
 '''
-catalog = open(basePath+'/kinematics_'+str(ssNumber)+'_test.dat','w')
+catalog = open(basePath+'/kinematics_0'+str(ssNumber)+'_all.dat','w')
 #catalog.write('# Galaxy SubID   Angular Momemtum   Disk star frac    Bulge star frac'+'\n')
 
 catalog.write('# [0]: Galaxy SubID'+'\n')

### 2016-08-11 python/Substructure/illustris_diskplot2.py

@@ -1,0 +1,182 @@
+import pandas as pd
+import seaborn as sns
+import numpy as np
+
+import matplotlib.pyplot as plt
+import DistanceTool as distance
+
+basePath = '../../data/illustris_1/'
+ssNumber = '085'
+redshift = 1.0
+print ssNumber
+
+catalog_x = basePath+'AllGalaxy_'+str(ssNumber)+'_x.dat'
+catalog_y = basePath+'AllGalaxy_'+str(ssNumber)+'_y.dat'
+catalog_z = basePath+'AllGalaxy_'+str(ssNumber)+'_z.dat'
+table_x,table_y,table_z = pd.read_csv(catalog_x,sep = '\t'),pd.read_csv(catalog_y,sep = '\t'),pd.read_csv(catalog_z,sep = '\t')
+
+## to a long table
+table = table_x.append(table_y,ignore_index = True)
+all_table = table.append(table_z,ignore_index = True)
+
+#all_table = all_table.loc[(all_table.r_mag <100)&(all_table.B_mag <100)&(all_table.V_mag <100),:]
+
+#print all_table
+
+## stellar mass lower limit
+all_table = all_table.loc[(all_table.stellar_mass>1e9),:]
+
+## add columns
+
+all_table.stellar_mass = all_table.stellar_mass/0.71
+all_table['log_stellar_mass']= np.log10(all_table.stellar_mass)
+#all_table['color'] = all_table.B_mag - all_table.V_mag
+all_table['mor_mix'] = 0
+
+## total flux cut
+
+#all_table = all_table.loc[(all_table.r_mag<25.),:]
+
+
+## relaxation
+table = all_table.loc[(all_table.relaxation == 0),:] # table is for disk systems
+#table = all_table # disk_table
+
+## edge-on pick
+#table = table.loc[(table.theta > 80.) & (table.theta < 100.),:]
+
+
+
+#print table.log_stellar_mass
+
+## add apparent surface brightness
+''' cosmopara '''
+class cosmopara:
+	h = 0.704
+	OM = 0.27
+
+#DL = distance.luminosity_distance(cosmopara,redshift)*1e6 # pc
+
+table['SB_exp_m'] = -5./2.*(table.SB_Exp+8.9)
+
+## SB cut
+#table = table.loc[(table.SB_exp_m < 25),:]
+
[…]

### 2016-08-11 python/Substructure/illustris_zplot.py

@@ -12,6 +12,10 @@ redshift = [1.0,0.6,0.2]
 file0 = basePath+'snapshot'+ssNumber[0]+'st_hist_30.dat'
 file1 = basePath+'snapshot'+ssNumber[1]+'st_hist_30.dat'
 file2 = basePath+'snapshot'+ssNumber[2]+'st_hist_30.dat'
+
+file0_all = basePath+'snapshot'+ssNumber[0]+'st_hist_all.dat'
+file1_all = basePath+'snapshot'+ssNumber[1]+'st_hist_all.dat'
+file2_all = basePath+'snapshot'+ssNumber[2]+'st_hist_all.dat'
 '''
 ## scatter plot
 z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
@@ -34,6 +38,7 @@ plt.savefig('./illustris_cross/zEvo_color_three.png',bbox_inches='tight')
 ## hist
 
 z0,z1,z2 = pd.read_csv(file0,sep = '\t'),pd.read_csv(file1,sep = '\t'),pd.read_csv(file2,sep = '\t')
+z0_all,z1_all,z2_all = pd.read_csv(file0_all,sep = '\t'),pd.read_csv(file1_all,sep = '\t'),pd.read_csv(file2_all,sep = '\t')
 
 z0['mor_hist'] = z0.morphology/z0.All
 z1['mor_hist'] = z1.morphology/z1.All
@@ -49,16 +54,18 @@ z2['bulge_hist'] = z2.bulge_star/z2.All
 
 #print z0
 
-plt.plot(z0.log_stellar_mass,z0.mor_hist,color='k',label = 'z='+str(redshift[0]),drawstyle='steps',linestyle = 'dashdot')
-plt.plot(z0.log_stellar_mass,z1.mor_hist,'b',label = 'z='+str(redshift[1]),drawstyle='steps',linestyle = 'dashed')
-plt.plot(z0.log_stellar_mass,z2.mor_hist,'r',label = 'z='+str(redshift[2]),drawstyle='steps')
+plt.plot(z0.log_stellar_mass,z0.disk_hist,color='k',label = 'z='+str(redshift[0]),drawstyle='steps',linestyle = 'dashdot')
[…]

### 2016-08-11 python/Substructure/readout_DanCat.py

@@ -1,7 +1,8 @@
 import numpy as np
 import groupcat
 
-ssNumber = '120'
+ssNumber = '085'
+print ssNumber
 
 catPath = '/Volumes/narsil_1/jwhsueh/illustris_1/snapshot_catalog/LensingCataSnap'+str(ssNumber)+'/'
 basePath = '../../data/illustris_1/'
@@ -16,25 +17,26 @@ Proj = ['NatProj_1/','NatProj_2/','NatProj_3/']
 #GroupFirstSub = groupcat.loadHalos(basePath,ssNumber,fields = ['GroupFirstSub'])
 
 TotList = ['TotCata_Lens.list','TotCata_Phot.list','TotCata_Gas.list']
-list_idx = 2
-p_index = 0 # Proj index
+list_idx = 1
+p_index = 2 # Proj index
+print p_index
 
-cataName = basePath+'Dandan_Lens'+ssNumber+'_x.dat'
+cataName = basePath+'Tot_Phots'+ssNumber+'_z.dat'
 
 CataList = open(catPath+Proj[p_index]+TotList[list_idx],'r')
 CataList = CataList.read().splitlines()
 
 ## Lens
 #field = ['SubfindID','mass [M_sun/h]','mass w/i R_ein','R_ein', 'DMfrac w/i R_ein']
-#f_idx = np.array([0,5,6,7,11])
+#f_idx = np.array([0,1,5,6,7,11])
 
 ## Phot
-field = ['SubfindID','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
-f_idx = np.array([0,8,10,18,22,24])
+field = ['SubfindID','central galaxy = 0','stellar mass','Sersic index','half-stellar mass radius (arcsec)','surface brightness ar Reff_Exp (mag/arcsec^2)','1:Early(deV);0:Late type(Exp)']
+f_idx = np.array([0,1,8,10,18,22,24])
 
 ## Gas
 #field = ['subfindID','fgas','fcgs']
-#f_idx = np.array([0,25,28])
+#f_idx = np.array([0,1,25,28])
 
 
 new_cata = open(cataName,'w')
@@ -48,32 +50,27 @@ for file_name in CataList:
[…]

### 2016-08-11 python/Substructure/standard_cata4.py

@@ -1,0 +1,175 @@
+import numpy as np
+import h5py
+import DistanceTool as distance
+import snapshot
+
+import pandas as pd
+
+basePath = '../../data/illustris_1'
+redshift = 1.0
+
+ssNumber = '085'
+print ssNumber
+
+
+## maybe we don't need this part
+'''
+## ----------- Dandan's morphology pick --------------- ##
+# read-in galaxy IDs
+DanM_fx,DanM_fy,DanM_fz = ['subfindID','R_Ex'],['subfindID','R_Ey'],['subfindID','R_Ez']
+DanM_x = pd.read_csv('JenWei_table_disk_in_x.dat',sep = '\t',names = DanM_fx,comment = '#')
+DanM_y = pd.read_csv('JenWei_table_disk_in_y.dat',sep = '\t',names = DanM_fy,comment = '#')
+DanM_z = pd.read_csv('JenWei_table_disk_in_z.dat',sep = '\t',names = DanM_fz,comment = '#')
+
+DanM = pd.merge(DanM_x,DanM_y,how = 'inner',on = 'subfindID')
+DanM = pd.merge(DanM,DanM_z,how = 'inner',on = 'subfindID')
+
+DanM = DanM.sort(['subfindID'])
+DanM['subfindID'] = DanM['subfindID'].astype(int)
+
+DanM = DanM['subfindID']
+'''
+## --------- kinematics ------------ ##
+
+catalog = basePath+'/kinematics_'+str(ssNumber)+'_all.dat'
+kine_field = ['subfindID','disk_star_f','bulge_star_f']
+kinematics = pd.read_csv(catalog,sep = '\s+',names = kine_field,comment = '#')
+
+## -------- relaxation ------------ ##
+
+catalog_r =basePath+'/m200_halos_hydr_rel_'+str(ssNumber)+'.txt'
+cat_ID = np.loadtxt(catalog_r,dtype = 'int',unpack=True, usecols=[4])
+relax_flag = np.loadtxt(catalog_r,dtype = 'int',unpack=True, usecols=[1]) # 0:relax, 1:not relax
+r_field = ['groupID','relaxation']
+relax = pd.DataFrame({'groupID':cat_ID,'relaxation':relax_flag})
+not_relax = relax.loc[(relax.relaxation == 1),:]
+
+
+'''
[…]
